### 2021-10-13 Article.tex
First commit

\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{amssymb}

% To have Times only in text not maths
\renewcommand{\rmdefault}{ptm}

\makeatletter

\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}

% specify here the journal
\journal{NAME OF THE JOURNAL}

% use this if you need line numbers
\usepackage{lineno}

\makeatother

\usepackage{babel}
\providecommand{\theoremname}{Theorem}

\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\newcommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
\newcommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
\newcommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
\newcommand{\dotp}{\boldsymbol{\cdot}}
\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\newcommand*{\ie}{\emph{i.e.}\@\xspace}
\newcommand*{\versus}{\emph{vs.}\@\xspace}
\newcommand*{\eal}{et \emph{al.}\@\xspace}
\newcommand*{\eg}{e.g.,\@\xspace}
\newcommand{\ERMS}{\text{E}_\text{RMS}}
\newcommand{\AARE}{\text{E}_\text{AAR}}
\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\sigmoid}{sig}

% Redefine the esvector shape to remove overlapping
\usepackage{esvect}
\def\traitfill@#1#2#3#4{%
  $\m@th\mkern2mu\relax#4#1\mkern-1.5mu %on met \relbaredd au d\'ebut
   \cleaders\hbox{$#4\mkern-0.3mu#2\mkern-0.3mu$}\hfill %remplit avec relbareda
   \mkern-1.5mu#3$%
}
\renewcommand{\overrightarrow}{\vv}

\begin{document}

\begin{frontmatter}{}

\title{TITLE}

\author[LGP]{Olivier Pantalé \corref{cor1}}

\ead{Olivier.Pantale@enit.fr}
\ead[url]{http://www.enit.fr}

\author[LGP]{AUTHOR 2}

\author[LGP]{AUTHOR 3}

\cortext[cor1]{Corresponding author}

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}

\begin{abstract}
ABSTRACT
\end{abstract}
\begin{keyword}
KEY1 \sep KEY2 \sep KEY3 \sep KEY4 \sep KEY5
\end{keyword}

\end{frontmatter}{}

\section{SECTION 1\label{sec:SECTION1}}

BLA BLA \cite{mime}

\section{SECTION 2\label{sec:SECTION2}}

BLA BLA

\section{SECTION 3\label{sec:SECTION3}}
BLA BLA

\bibliographystyle{elsarticle-num}
\addcontentsline{toc}{section}{\refname}
\bibliography{bibtex}

\end{document}

### 2022-10-06 Article_PTM.tex
Article added to the repository

% !TeX encoding = UTF-8
\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage[colorlinks = true]{hyperref}

% To have Times only in text not maths
\renewcommand{\rmdefault}{ptm}

\makeatletter

\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}

% specify here the journal
\journal{International Journal of Mechanical Sciences}

% use this if you need line numbers
\usepackage{lineno}

\makeatother

\usepackage{babel}
\providecommand{\theoremname}{Theorem}

%\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
%\newcommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
%\newcommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
%\newcommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
\newcommand{\dotp}{\boldsymbol{\cdot}}
%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\newcommand*{\ie}{\emph{i.e.}\@\xspace}
\newcommand*{\versus}{\emph{vs.}\@\xspace}
\newcommand*{\eal}{et \emph{al.}\@\xspace}
\newcommand*{\eg}{e.g.,\@\xspace}
%\newcommand{\ERMS}{\text{E}_\text{RMS}}
\newcommand{\AARE}{\text{E}_\text{AAR}}
\newcommand{\R}{\text{R}}
%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
%\DeclareMathOperator{\sech}{sech}
%\DeclareMathOperator{\sigmoid}{sig}

\usepackage{esvect}
% Redefine the esvector shape to remove overlapping
\def\traitfill@#1#2#3#4{%
  $\m@th\mkern2mu\relax#4#1\mkern-1.5mu %on met \relbaredd au d\'ebut
   \cleaders\hbox{$#4\mkern-0.3mu#2\mkern-0.3mu$}\hfill %remplit avec relbareda
   \mkern-1.5mu#3$%
}
\renewcommand{\overrightarrow}{\vv}

\begin{document}
\begin{frontmatter}

\title{Phenomelogical and artificial neural network models' comparison study for hot deformation of AISI P20: Interpolation and extrapolation predictions}

\author[LGP]{Pierre Tize Mha}
\author[LGP]{Amèvi Tongne}
\author[LGP]{Olivier Pantalé \corref{cor1}}
\ead{Olivier.Pantale@enit.fr}
\ead[url]{http://www.enit.fr}

\cortext[cor1]{Corresponding author}

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}

\begin{abstract}
Non-linear numerical modeling is increasingly used for the simulation of complex processes such as forming or machining. The constitutive laws necessary for these simulations are therefore becoming more and more complex regarding the increasingly precise consideration of physical phenomena (plasticity, thermal dependence, damage ...) and their implementation in numerical codes requires the identification of many parameters. The use of these constitutive laws for dynamic or quasi-static applications requires the identification of these parameters under conditions close to those encountered during the real process, mainly in terms of deformation, strain rates, and temperatures. The availability of a constitutive law in the finite element codes does not guarantee the success of a study to be carried out if it does not comply with the model development criteria. This is because the models integrated in the numerical codes are not developed based on forms that are adjustable to any type of study. In this study, a new form of non-linear constitutive flow law based on the Modified Zerilli--Armstrong model, which can answer the above problem, has been developed to apply it to the numerical simulation of two different tests (a quasi-static compression test, the necking of a circular bar). This flow law is based on the modified Zerilli--Armstrong model, which, together with the new modified Johnson--Cook model, has been compared to appreciate the relevance of the proposal. For that, an implementation of this new law via the VUHARD subroutine into the Abaqus/Explicit finite element code was made to model the two tests. The comparison of the results obtained (from identification) by our proposed law with those obtained using the NMJC shows that this new law better approaches the experiments than the other one. This is also showed through the numerical results using the Abaqus software. It can be said that this way of formulating a flow law allows to highlight the great performance of the proposed approach. Although this law has been used only used for quasi-static tests, we can say that it can also be used in dynamic tests.
\end{abstract}

\begin{keyword}
Zerilli--Armstrong flow law \sep Constitutive Behavior \sep Finite Element Method \sep Numerical Implementation \sep Johnson--Cook flow law
\end{keyword}

\end{frontmatter}
\linenumbers

%--------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%--------------------------------------------------------------------------
\textcolor{red}{Due to technological advances, industries are constantly looking for innovations to maintain their competitiveness. For the metallurgical industry, these innovations involve the development of new materials. In conjunction with the implementation of these new materials, it becomes necessary to characterize their thermomechanical behavior, in particular in order to feed the data bases used by the numerical simulation models more and more widespread nowadays \cite{Trimble-2020-Finite, Yuan-2021-Particle}}.

\textcolor{red}{Among the different approaches used, the finite element method (FEM) is one of the numerical methods that has become the most popular nowadays. Like any numerical method, the accuracy of the solution depends very strongly on the constitutive equation describing the behavior of the material and implemented in the computational code \cite{Li-2021-Finite, Liu-2021-Finite}. This constitutive equation is linked to the mathematical model that describes it. This choice is not entirely free, insofar as the choice of the behavior law (speaking of an analytically formulated model) used to describe the behavior of a material is guided by its availability in the finite element codes \cite{Miller-2021-Thermomechanical}. This forces an adaptation between the studied material (which is real) and the behavior law (representative mathematical model) available in the FEM code which is not necessarily the one able to describe the behavior of the studied material. The problem of the non flexibility of the models available in the finite element codes appears immediately and limits the adequacy of the model to the reality of the behavior since the behavior laws established and available in the FEM codes are for the most part specific to a particular material or class of materials. In other words, as soon as they are applied to materials different from the one for which they were originally developed, they find their limits because they do not manage to represent the reality described by the experiment as one would wish. It is therefore interesting to think about developing a method that can be applied to any material of any class and implemented in a finite element code. This approach involves a number of parameters depending on the material studied, but with a more global mathematical form adaptable to a wider range of materials. In this study, we propose an approach allowing a better adaptability of the behavior law to various materials. To justify the relevance of this proposal, let us first examine the models developed so far and try to see if some of them meet this need}.

\textcolor{red}{According to the literature, analytical models describing the behavior of materials can be grouped into three categories: empirical models, semi-empirical models, and physical models. Empirical models describe the behavior of the material by considering macroscopic quantities without considering its microstructure, whereas physical models consider the microstructure. As for the semi-empirical models, they try to be at the border between the empirical and physical models. Among a large number of models, the Johnson--Cook (JC) \cite{Johnson-1983-Constitutive, Johnson-1985-Fracture} and the Zerilli--Armstrong (ZA) \cite{Zerilli-1987-Dislocation} models are the best known and available in finite element codes. The JC model is widely used because it is simple to use and has fewer constants to be determined \cite{Khan-2004-Quasi-static, NematNasser-2003-Thermomechanical}. However, this model, in its original state, contains some problems related to the phenomena describing the behavior of the material. We refer here to strain hardening, strain rate hardening, and thermal effects that are described separately in the JC model as analyzed by Jia \eal \cite{Jia-2021-Modified-JC}. To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998-Revised-JC, Vural-2003-Large, Lin-2010-Modified-JC, Lin-2012-Phenomenological, Li-2013-Modified-JC, Zhou-2019-Research, Zhang-2015-Modified-JC}}.

\textcolor{red}{Due to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988-Evaluation, Voyiadjis-2005-Microstructural, Dey-2007-Influence}. However, the drawbacks of this model are related to the temperature limit value of the test. Indeed, this model applies only to low strain rates and for temperatures limited to $0.6~T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005-Strain, Lee-2005-Strain, Chen-2007-Comparative, Lee-2006-Effects}. Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009-Thermo-viscoplastic}. In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{Nemat-2004-Plasticity, Lennon-2004-Influence, Muralli-2017-Performance, Cheng-2021-Modified-ZA, Muralli-2021-Finite}}.

\textcolor{red}{These two approaches are among the most popular and the choice depends on the effectiveness of the method for a given problem. So we have on the one hand, the JC formulation and its variants and on the other hand the ZA approach with its variants too. Another approach proposed by Lin \eal \cite{Lin-2010-Modified-JC} is to combine the JC model with the MZA model (in its modified form proposed by Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic}). This approach allows combining on the one hand the factor taking into account the strain hardening effects described by the JC model and on the other hand the factor describing the strain rate effects and the thermal softening described by the MZA model in a unified formulation. The major difficulty of all the variants mentioned above is the restriction of the parameters on which the model depends, thus limiting the applicability domain of the developed model. Therefore, it seems necessary to look for a method that does not limit the number of parameters, unlike the approaches mentioned above, and that can describe more accurately the reality observed by the experiment}.

\textcolor{red}{Artificial neural networks (ANNs) offer an alternative way to solve these problems. ANNs are currently used to solve problems that are difficult to conceptualize using traditional computational methods. Thus, unlike a classical approach based on a regression method, an artificial neural network does not need to know the mathematical form of the model it seeks to reproduce and can therefore learn directly from experimental data without any prior assumption on the nature of the input parameters and their interactions. Thus, artificial neural networks can enable new approaches for modeling material behavior and have been successfully applied for the prediction of constitutive relationships of some metals and alloys \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Huang-2021-CMM}. Although this approach is very effective, it does not allow the interpretation of the obtained results, because it does not take into account the physics of the phenomena for the considered material}.

\textcolor{red}{From the above, we can retain that there are two main families of models to describe the behavior of a material. On the one hand, analytical models presenting a problem of flexibility and on the other hand, implicit models, based on neural networks, more adaptable but presenting a problem of physical interpretation. It is therefore interesting to develop a physical model that is able to adapt to any material and can be efficiently implemented in a finite element code. In this perspective, we propose here a new formulation based on the MZA model, whose interest is to answer the two problems mentioned above. To appreciate the relevance of our approach, we used the Abaqus/Explicit software which offers the possibility to implement a new behavior law using a FORTRAN VUMAT or VUHARD subroutine following the example of the works proposed by \cite{Gao-2007-FRT, JansenVanRensburg-2012-TSV, Duc-Toan-2012-MJC, Ming-2018-ERV}}.

\textcolor{red}{The main paragraphs of this work are as follows: Section \ref{sec:ConstLaws} presents two  known constitutive laws which will serve as the basis of the the proposed one presented in Section \ref{sec:ProposedModel}. Since this model is new and will be used to perform a numerical model using Abaqus, the three derivatives of flow stress $\sigma$ with respect to the strain $\varepsilon^p$, the strain rate $\mdot{\varepsilon}^p$ and temperature are required. So, determination of these derivatives is done in this Section. Section \ref{sec:Application} is devoted to the comparison of the proposed model to the others one where identification is done on a 100Cr6 steel. Section \ref{sec:NumSimulations} details the numerical results of the models identified in Section \ref{sec:Application} using the cylindrical compression test and the necking of circular benchmark tests. Conclusion and future works are detailed in Section \ref{sec:Conclusion}}.

%----------------------------------------------
\section{Experimental procedure}
%----------------------------------------------
The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table. Cylindrical specimens were machined with an initial diameter of $10$ mm and a height of $15$ mm. Hot compression tests were conducted on a Gleeble-3800 thermo-simulator (Figure \ref{fig:Gleeble3800}), at temperatures of $1050^\circ$C,  $1050^\circ$C,  $1100^\circ$C,  $1150^\circ$C,  $1200^\circ$C and  $1250^\circ$C with strain rates of $0.001\ \text{s}^{-1}$, $0.01\ \text{s}^{-1}$, $0.1\ \text{s}^{-1}$, $1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$. Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during hot deformation. The samples were heated to $1260^\circ$C temperature and were held for $5$ min to eliminate thermal gradients at the test temperatures. Then cooled to test temperature where the specimen is held $1$ minute before deformation. After compression the specimen is quencted rapidly for microstructure studies. The procedure of this test is illustrated in Figure \ref{fig:Heating}.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/Gleeble-3}
\caption{Gleeble 3800 simulator system}
\label{fig:Gleeble3800}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/GleebleDesign}
\caption{Schematic diagram of the experimental process.}
\label{fig:Heating}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Chemical Composition of the AISI P20 Steel (Weight Percent)}
\scalebox{0.9}{
\begin{tabular}{lcccccccc}
\hline
C  &Mn & Mo   & Si   & Ni       &Cr& Cu & Other& Balance\\
\hline
 0.30        &       0.89      &0.52		   &	0.34     &	 0.68          &1.86& 0.17& Microalloying& Iron\\
\hline
\label{tab: Composition}
\end{tabular}}
\end{table}
%------------------------------------------------------------------------
\section{Results and discussion\label{sec:ConstLaws}}
%------------------------------------------------------------------------

%------------------------------------------------------------------------
\subsection{Flow stress behaviour}
%------------------------------------------------------------------------
The flow stress curves obtained from the compression tests performed on Gleeble-3800 simulator for each test condition are shown in Figure \ref{fig:rawData}. From these curves it can be seen that the flow stress increases with increasing strain rate but decreases with increasing temperature. It should be noted that the strain influences the flow stress. Indeed, for all strain values below $0.2$, the stress increases with strain before reaching a peak value at low strain rates and then decreases to maintain a stable value until the end of the test. The peak stress value increases with strain rate but decreases with temperature. For higher strain rates ($1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$) the flow stress increases throughout the test. The slight increase in stress at low strain rates when the strain is large is due to friction between the specimen and the grip during the test. For low strain rates, lubrication is lost over time and therefore friction occurs. This results in a progressive increase in stress.

To explain the overall behaviour of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX). At the beginning of the deformation, the amount of dislocations increases and they start to move, leading to a rapid increase in stress known as work-hardening. As the strain continues to increase, the dislocations are set in motion, leading to a stress relaxation phenomenon usually known as DRC. During this DRC mechanism, some of the dislocations are removed, due to their combination with another dislocation, or due to their integration into a grain boundary, and some of them are rearranged and formed as sub-grains within the initial grains. The combination of these dislocations moderates the increase of dislocations linked to strain hardening and thus controls the amount of energy stored in the material and manages the increase in flow stress. DRX consists of the germination of new grains, at the borders or inside the initial grains. These two phenomena therefore explain the different shapes of the flow stress curves observed for this alloy. As an example, the Figure \ref{fig:BarNecking} , and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression. As observed on the flow curves, it can be seen that recrystallisation is almost complete for this temperature and strain rate. Indeed, most of the grain boundaries start to form new grains. The identification of the behavioural laws of these curves will be done in the next section in order to predict its behaviour in any test condition. This will be done on the one hand to test the ability of the models to describe an interpolation and on the other hand to do extrapolation.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:rawData}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/BeforeCompM}
\caption{Optical micrograph of the AISI P20 steel before hot compression held during $5$ minutes at $1260^\circ$C}
\label{fig:BeforeCompM}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/AfterCompM}
\caption{Optical micrograph of AISI P20 alloy after howt compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
\label{fig:AfterCompM}
\end{figure}
%-------------------------------------------------------------------------
\subsection{Analytical constitutive flow laws}
%-------------------------------------------------------------------------
The complete characterization of the thermomechanical behavior of a material is very important before its use in numerical simulations. This characterization usually involves experimental tests that serve as a basis for the development of constitutive laws. As mentioned in the introduction, many constitutive laws exist today, and selecting one of them based on explicit criteria hinders the development of computational models for new materials. Since the purpose of this work is to compare analytical models with the ANN model in terms of interpolation and extrapolation, it is important to justify the choice of the analytical models presented here among the many that exist in the literature. Among the most widely used analytical models nowadays, the Johnson-Cook (JC) model is the most used due to its simplicity of use linked to the number of its reduced and easy to obtain parameters. It should be noted that it is not the best model but the most integrated in finite element software. Hence the existence of several modified forms of this model. The Zerilli-Armstrong model, and particularly its modified form (MZA), is also widely known since it tries to provide solutions to the shortcomings of the JC model, particularly with regard to the coupling of physical parameters. Hence its use also in this study. In this perspective, the Hansel Spittel model (HS)is also one of the most widely used models in numerical simulation of casting and forging operations as it is integrated in the FORGE software. Also, the method of identifying its parameters is very simple to do as it is done in one step. Of course, it has its limitations as will be shown in the following sections. Furthermore, the Arrhenius model will be used in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter Q (the deformation activation energy coefficient) which is of great importance in the study related to the microstructural analysis of materials. Hence its use in the development of analytical models dedicated to the microstructural analysis of materials. The shortcomings of these models were the main motivation for the formulation of the model proposed in this work, the details of which can be found in our previous work.
%-------------------------------------------------------------------------
\subsubsection{Johnson--Cook model\label{sec:JC}}
%-------------------------------------------------------------------------
The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature. However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature. Indeed, it is formulated by describing the effect of each physical parameter (strain, strain rate and temperature) separately as a factor in the mathematical expression of the model. Hence its inability to describe the phenomenon of temperature-induced softening. The equation that describes this model is given as follows:
\begin{equation}
\label{eq: JCmodel}
\sigma^y = \left(A + B\varepsilon^{p^n}\right)\left(1+C\ln\mdot{\varepsilon}^*\right)\left(1-T^{*^m}\right)
\end{equation}
Where $\sigma^y$ is the equivalent stress flow stress, $\varepsilon^p$ is the plastic strain, ($A=\sigma_0$) is the elastic limit of the material, $B$ is the strain hardening's coefficient, $n$ is the strain hardening's exponent. $C$ and $m$ are the material constants that describe the strain rate hardening and thermal softening exponent respectively. $\mdot{\varepsilon}^*$ is the dimensionless strain rate which is given by $\mdot{\varepsilon}^* = \mdot{\varepsilon^p}/\mdot{\varepsilon_0}$. $\mdot{\varepsilon^p}$ and $\mdot{\varepsilon_0}$ are strain rate and reference strain rate respectively. $T^{*^m} = (T-T_0)/(T_m - T_0)$ is homologous temperature where $T, T_m$ and $T_0$ are the déformation temperature, meltinng temperature (1460$^\circ$C in our case) and reference temperature respectively. For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050^\circ$C respectively and the value of $A$ is $43.0988$ MPa. Here after datailed the steps for determination the JC model parameters.
At the reference strain rate, Equation \ref{eq: JCmodel} becomes:
\begin{equation}
\label{eq: JCbn}
\sigma^y = A + B\varepsilon^{p^n}
\end{equation}
Taking the natural logarithm on both sides of Equation \ref{eq: JCbn} we have:
\begin{equation}
\label{eq:JClog1}
\ln\left(\sigma^y-A\right)= \ln(B) + n\ln\varepsilon^p
\end{equation}
By plotting $\ln(\sigma^y-A)$ \versus $\ln\varepsilon^p$ (Figure \ref{fig:JCSigmaAB}) from Equation \ref{eq:JClog1}, $n$ and $B$ can be obtained as slope and intercept respectively. Thus, for a strain value equal to $0.1$ the values of these two parameters are $n=0.313969$ and $B=114.518$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/JCSigmaAB}
\caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050^\circ$C and $0.1$}
\label{fig:JCSigmaAB}
\end{figure}
\FloatBarrier
Once the parameters $A$, $B$ and $n$ are known and at the reference temperature, the Equation \ref{eq: JCmodel} becomes:
\begin{equation}
\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 + C\ln\mdot{\varepsilon}^*
\end{equation}
From this equation one can easily obtain the parameter $C$ using the linear fitting method for each strain value and averaging all these values as shown in Figure \ref{fig:JCSigmaAB1} the value is $0.0976681$. 
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/JCSigmaAB1}
\caption{Relationship between $\sigma^y/(A+ B\varepsilon^{p^n})$ and $\ln(\dot{\varepsilon}^*)$}
\label{fig:JCSigmaAB1}
\end{figure}
The $m$ parameter is determined at the reference strain rate. Under this condition, the Equation \ref{eq: JCmodel} can be written as following:
\begin{equation}
\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 - T^{*^m}
\end{equation}
Taking the natural logarithm of both sides of that equation, we have:
\begin{equation}
\ln\left(1 - \frac{\sigma^y}{A + B\varepsilon^{p^n}}\right)  = m\ln T^*
\end{equation}
Plotting $\ln\left(1 - \frac{\sigma^y}{A + B\varepsilon^{p^n}}\right)$ as a function of $\ln T^*$ allows us to get the parameter $m$ as a slope for all values of the deformation by averaging them and the value is $0.898932$. Figure \ref{fig:JCSigmaT} illustrates this determination for some deformations.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.85\columnwidth]
{newFigures/JCSigmaT}
\caption{Relationship between $\ln\left(1 - \sigma^y/\left(A + B\varepsilon^{p^n}\right)\right)$ and $\ln T^*$}
\label{fig:JCSigmaT}
\end{figure}
Having determined all the parameters of the Johnson--Cook model, its mathematical formulation can be written as follows:
\begin{equation}
\label{eq: JCmodelf}
\sigma^y = \left(43.0988 + 114.518\varepsilon^{p^{0.313969}}\right)\left(1+0.0976681\ln\mdot{\varepsilon}^*\right)\left(1-T^{*^{0.898932}}\right)
\end{equation}
The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC} and Figure  \ref{fig:eCorrelationJC}. The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates. The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/iCorrelationJC}
\caption{Comparison between the experimental and predicted flow stresses by JC model for interpolation estimation}
\label{fig:iCorrelationJC}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/eCorrelationJC}
\caption{Comparison between the experimental and predicted flow stresses by JC model for extrapolation estimation}
\label{fig:eCorrelationJC}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Johnson-Cook Model}
\scalebox{1.2}{
\begin{tabular}{lccccc}
\hline
&         &             &		   &		  &\\
&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
&         &             &		   &	     &	    \\
\hline
Interpolation&$43.0988$&$114.518$& $0.313969$&$0.0993506$&$0.898932$\\
%\hdashline
Extrapolation&$43.0988$&$114.518$& $0.313969$&$0.0992144$&$0.910297$\\
\hline
\label{tab: JCparameters}
\end{tabular}}
\end{table}
%-------------------------------------------------------------------------
\subsubsection{The Modified Zerilli--Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------

As mentioned earlier, Johnson--Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately. Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model. In fact, the Zerilli--Armstrong model is based on a physical consideration of heat-activated dislocation motion and the interaction of individual dislocations with each other as shown by Hull \eal \cite{Hull-2011-ITD}. The ZA model is therefore a constitutive law based on a study of the material microstructure. For a FCC material, the original equation describing the Zerilli--Armstrong model \cite{Zerilli-1987-DMB} is given by:
\begin{equation}
\label{eq:ZA-model}
\sigma^y = A_{0} + A_{1}\varepsilon^{p^n} \exp\left[-A_{2}T + A_{3}T\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where $\sigma^y$ is the von Mises flow stress, $\varepsilon^p$ is the equivalent plastic strain, $\mdot{\varepsilon}^p$ is the equivalent plastic strain rate, $\mdot{\varepsilon}_0$ is the reference strain rate and $T$ is the absolute temperature within the material. The coefficients $A_0$, $A_1$, $A_2$, $A_3$ and $n$ are the parameters of the model to be identified for a given material and $\mdot{\varepsilon}_0$ is the reference strain rate as proposed by many models in the literature.
It is important to note that this model is globally split in two terms. The first term is a constant stress threshold representing the yield strength of the material and the second term is a thermo-viscous component considering the variation of the work hardening threshold of the material with temperature and strain rate.
With face-centered cubic (FCC) materials, the strain hardening shows a greater dependence on both temperature and strain rate. The thermal component of strain hardening in FCC materials is physically interpreted as the resistance to dislocation motion by the mutual interaction of dislocations \cite{Voyia-2005-MBM}. The flow stress threshold of an FCC material is independent of temperature and strain rate, so that the flow stress threshold is constant and equal to the initial stress \cite{Nemat-2004-Plasticity, Voyia-2005-MBM}. The limitation of the ZA model is that it cannot be used for flow stress prediction at high strain rates and temperatures above $0.6~T_m$. To circumvent this problem, Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic} proposed a modified form of the Zerilli--Armstrong law (MZA) given by the following relationship:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. This formulation was initially developed from a compression test of 15Cr--15Ni--2.2Mo Ti-modified austenitic stainless steel (the D9 alloy). This test was performed over a range of plastic strains ($\varepsilon^p=0.1-0.5$), strain rates ($\mdot{\varepsilon}^p=10^{-3}-1~\text{s}^{-1}$) and temperatures ($T=800-1200^\circ\text{C}$). In attempting to apply the original Johnson--Cook model, the authors of this work found that it was unable to describe the behavior of this type of material over the ranges of strain, strain rate, and temperature mentioned above. The same conclusion was made regarding the ZA model who was also unable to correctly describe the behavior of this material. Based on the ZA model, Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic} have therefore proposed a modified form of the ZA model to better describe the behavior of this material. This modified model takes into account the effect of isotropic strain hardening, strain rate hardening, thermal softening and the coupled effects of strain, strain rate and temperature on the flow stress. It predicts the evolution of the high-temperature flow threshold of the D9 alloy over the above ranges of strain, strain rate and temperature with good correlation to the experimental data and good generalization. The correlation coefficient obtained is $0.995$ while the average error for the whole data set is only $5.3~\%$. For more details about the formulation of this model the author can read \cite{Samantaray-2009-Thermo-viscoplastic}.

The Equation (\ref{eq:ZA-model}) of the original Zerilli--Armstrong model defines the flow stress in two terms: a thermal stress and an athermal stress that depends on the grain size of the material and is independent of temperature. However, several studies have shown that this independence decreases when the temperature increases beyond a certain value. Based on these observations, Samantaray questioned the athermal consideration for the D9 material. This approach then allows for the consideration of temperature effects on the yield strength of D9 steel and even other materials. Here after how to get all parameters of the MZA model:

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters (both the interpolation and extrapolation indentification) of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA} and Figure \ref{fig:eCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{tize2022generalized}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified--Zerrilli-Armstrong Model}
\scalebox{0.83}{
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Interpolation&$43.0988$&$112.975$& $330.976$&$4.27581$&$14036.3$&$17.1520$&$0.305028$\\
%\hdashline
Extrapolation&$43.0988$&$112.975$& $330.976$&$4.27581$&$14496.9
$&$18.9194$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/iCorrelationMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model for interpolation estimation}
\label{fig:iCorrelationMZA}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/eCorrelationMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model for extrapolation estimation}
\label{fig:eCorrelationMZA}
\end{figure}
\FloatBarrier

%-------------------------------------------------------------------------
\subsubsection{Hansel and Spittel\label{sec:HSmodel}}
%-------------------------------------------------------------------------
The Hansel-Spittel model is one of the least known models in terms of its  integration in softwae for finite element simulation although the determination of its parameters is easier than the JC model. A single programming command is sufficient for its identification. However, this model has some difficulties as it loses its accuracy when all parameters are taken into account. For this reason, several authors limit its use to $5$ or $6$ parameters \cite{chadha2018approach, rudnytskyj2020constitutive, el2015comparison}. In this paper the good predictions are with $5$ parameters summarized in Table \ref{tab: HSparameters}. The equation of the model is given by the following relation: 
\begin{equation}
\sigma^y = Ae^{m_1T}\varepsilon^{p^{m_2}}\mdot{\varepsilon}^{p^{m_3}}e^{\frac{m_4}{\varepsilon^p}}(1+\varepsilon^p)^{m_5T}e^{m_6\varepsilon^p}\mdot{\varepsilon}^{p^{m_7T}}T^{m_8}
\end{equation}
Where $\sigma^y$ is the flow stess, $\varepsilon^p$ strain, $\mdot{\varepsilon}^p$ strain rate and $T$ temperature. The other coefficients $A$ and $m_j$ are model constants up to $m_5$ for our case. Comparison of predicted values of the HS model and experimental values is shown in Figure \ref{fig:iCorrelationHS} and Figure \ref{fig:eCorrelationHS}. It appears that this model as well as the previous ones do not predict the experimental well and the gap is relatively large. This shows that this model is not appropriate for the characterisation of this alloy.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Hansel and Spittel Model}
\scalebox{0.9}{
\begin{tabular}{llccccc}
\hline
&         &             &		   &		 &			   &\\
&$A_0(\text{GPa})$    &$m_1$        & $m_2$     & $m_3$   & $m_4$       &$m_5$\\
&         &             &		   &	     &	           &\\
\hline
Interpolation&$10.1777$&$-0.00384785$& $0.195671$&$0.183171$&$-0.0035643$&$-0.00059302$\\
%\hdashline
Extrapolation&$11.3176$&$-0.00388286$& $0.204999$&$0.19018$&$-0.00316225$&$-0.000658053$\\
\hline
\label{tab: HSparameters}
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/iCorrelationHS}
\caption{Comparison between the experimental and predicted flow stresses by HS model for interpolation estimation}
\label{fig:iCorrelationHS}
\end{figure}
\FloatBarrier
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/eCorrelationHS}
\caption{Comparison between the experimental and predicted flow stresses by HS model for extrapolation estimation}
\label{fig:eCorrelationHS}
\end{figure}
\FloatBarrier
%----------------------------------------------------------------------------------
\subsubsection{Arrhenius model (AR model), \label{sec:ARmodel}}
%----------------------------------------------------------------------------------
The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material. Indeed, this model takes into account the physical phenomena that describe the behaviour of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot{\varepsilon}^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation. This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature. The following equations describe the Arrhenius model.
\begin{equation}
\label{eq:ARmodel1}
\mdot{\varepsilon}^p = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)
\end{equation}
\begin{equation}
\label{eq:ARmodel2}
\mdot{\varepsilon}^p = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)
\end{equation}
\begin{equation}
\label{eq:ARmodel}
\mdot{\varepsilon}^p = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)
\end{equation}
Where $\mdot{\varepsilon}^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants. To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener--Hollomon parameter is introduced whose expression is given as follows:
\begin{equation}
\label{eq:Zparam}
Z = \mdot{\varepsilon}^p\exp\left(\frac{Q}{RT}\right)
\end{equation}
By replacing the relation (\ref{eq:ARmodel}) in the (\ref{eq:Zparam}) one it comes:
\begin{equation}
\label{eq:Zparam1}
Z = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2} \qquad \Rightarrow \qquad \sinh(\alpha\sigma^y) = \left(\frac{Z}{A_3}\right)^{1/n_2}
\end{equation}
Furthermore, it is known that:
\begin{equation}
arc\sinh(x) = \ln\left(x + \sqrt{1+x^2}\right)
\end{equation}
Therefore the Equation (\ref{eq:Zparam1}) becomes and which is actually the Arrhenius model: 
\begin{equation}
\sigma^y = \frac{1}{\alpha}\ln\left\{\left(\frac{Z}{A_3}\right)^{1/n_2} + \left[1 + \left(\frac{Z}{A_3}\right)^{2/n_2}\right]^{1/2}\right\}
\end{equation}
To obtain the constitutive equation, all parameters $\alpha$, $Q$, $n_2$, and $A_3$ needed to be determined. The following part shows the calculation procedures of these material constants at $0.1$ strain as example.\\
Taking the natural logarithm of Equations (\ref{eq:ARmodel1}) and (\ref{eq:ARmodel2}), the following relationships can be obtained: 
\begin{equation}
\ln \sigma^y = \frac{1}{n_1}\ln \mdot{\varepsilon}^p -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}
\end{equation}
\begin{equation}
\sigma^y = \frac{1}{\beta}\ln \mdot{\varepsilon}^p - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT} 
\end{equation}
From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot{\varepsilon}^p)$  and $\sigma^y = f(\ln\mdot{\varepsilon}^p)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $0.1$ value of strain. It should be noted that later in this document all values of strain will be taken into account.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]{newFigures/LnAlp}
\caption{Relationship between $\ln \sigma^y$ and $\ln \dot{\varepsilon}^p$}
\label{fig:LnAlp}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhE0}
\caption{Relationship between $\sigma^y$ and $\ln \dot{\varepsilon}^p$}
\label{fig:LnSinhE0}
\end{figure}
The values of those parameters are therefore equal to $n_1=4.93599$ and $\beta=0.150438$ ($\alpha=\beta/n_1 = 0.0220306$). 
Taking the natural logarithm of Equation (\ref{eq:ARmodel}), the following relationship can be obtained:
\begin{equation}
\label{eq:lnSinh}
\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot{\varepsilon}^p  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
\end{equation}
By applying the chain derivative rule, we get the following relationship to calculate the energy activation coefficient $Q$.
\begin{equation}
\label{eq:parQ}
Q = R\left[\frac{\partial \ln \mdot{\varepsilon}^p}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot{\varepsilon}^p}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
\end{equation}
From Equation (\ref{eq:lnSinh}) and Equation (\ref{eq:parQ}) we can deduce the parameters $n_2 $ and $Q $ from the slopes of the functions $\ln \sinh(\alpha\sigma^y) = f(\ln \dot{\varepsilon}^p)$ and $\ln \sinh(\alpha\sigma^y) = g(1/T)$ as shown in Figure \ref{fig:LnSinhE} and Figure \ref{fig:LnSinhT}. Thus those values are $3.21374$ and $432.722\ KJ.mol^{-1}$ respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhE}
\caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $\ln \dot{\varepsilon}^p$}
\label{fig:LnSinhE}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhT}
\caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $1/T$}
\label{fig:LnSinhT}
\end{figure}
As these coefficients are calculated for a single strain value as example, it is possible to take into account their dependence on all strain values. Hence the need to find a function for each coefficient for all temperatures and strains. Figure  \ref{fig:ARparameters} shows the relationships between $\alpha$, $Q$, $n$, $\ln A$ and true strain $\varepsilon^p$ for P20 alloy using leasquare method to fit the measured data. For each parameter (whose strain dependant expressions are given by Equations \ref{eq:alpha}, \ref{eq:Q}, \ref{eq:n} and \ref{eq:lnA}), the values of constants are summarized in Table \ref{tab: ARparameters}. Figure \ref{fig:iCorrelationAR} and Figure\ref{fig:eCorrelationAR} are the comparison of predicted values of AR model and experimental values where the correlaton is good. The gap between experimental and prediction is small. But for the strain rate $\mdot{\varepsilon}^p = 0.01$ and for the two low temperatures values, the AR model is not able to predict the softening.
\begin{equation}
\label{eq:alpha}
\alpha(\varepsilon^p) = \alpha_0 + \alpha_1\varepsilon^{{p^1}} + \alpha_2\varepsilon^{p^2} + \alpha_3\varepsilon^{p^3} + \alpha_4\varepsilon^{p^4} + \alpha_5\varepsilon^{p^5} + \alpha_6\varepsilon^{p^6}
\end{equation}
\begin{equation}
\label{eq:Q}
Q(\varepsilon^p) = Q_0 + Q_1\varepsilon^{{p^1}} + Q_2\varepsilon^{p^2} + Q_3\varepsilon^{p^3} + Q_4\varepsilon^{p^4} + Q_5\varepsilon^{p^5} + Q_6\varepsilon^{p^6}
\end{equation}
\begin{equation}
\label{eq:n}
n(\varepsilon^p) = n_0 + n_1\varepsilon^{{p^1}} + n_2\varepsilon^{p^2} + n_3\varepsilon^{p^3} + n_4\varepsilon^{p^4} + n_5\varepsilon^{p^5} + n_6\varepsilon^{p^6}
\end{equation}
\begin{equation}
\label{eq:lnA}
\ln A(\varepsilon^p) = \ln A_0 + \ln A_1\varepsilon^{{p^1}} + \ln A_2\varepsilon^{p^2} + \ln A_3\varepsilon^{p^3} + \ln A_4\varepsilon^{p^4} + \ln A_5\varepsilon^{p^5} + \ln A_6\varepsilon^{p^6}
\end{equation}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]{newFigures/ARparameters}
\caption{Relationships between $\alpha$ (a)  , $Q$ (b) , $n$ (c)  and $lnA$ (d)  with the true strain $\varepsilon^p$ by polynomial functions}
\label{fig:ARparameters}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Arrhenius Model}
\scalebox{0.95}{
\begin{tabular}{lllll}
\hline
&						&				   &				  &\\
&$\alpha$          & $Q (\times10^{6})$ & $n$      & $\ln A$\\
&						&				   &				  &\\
\hline
&$\alpha_0 = 0.0368199$ & $Q_0 = 0.451215$  & $n_0 = 4.52844$ & $\ln A_0 = 34.4714$\\
&$\alpha_1 = -0.300454$ & $Q_1 = -0.526197$ & $n_1 = 15.6433$ & $\ln A_1 = -42.818$\\
&$\alpha_2 = 2.19468$   & $Q_2 =5.99635 $ & $n_2 = -176.65$ & $\ln A_2 = 493.325$\\
Interpolation&$\alpha_3 =-8.29695$ & $Q_3 =-37.4915 $  & $n_3 = 682.187$ & $\ln A_3 =-3095.19 $\\
&$\alpha_4 = 16.8067$   & $Q_4 = 102.928$  & $n_4 = -1289.52$& $\ln A_4 = 8516.02$\\
&$\alpha_5 = -17.2641$  & $Q_5 =-127.865$  & $n_5 = 1205.95$ & $\ln A_5 = -10594.8$\\
&$\alpha_6 = 7.04353$   & $Q_6 = 59.2928$  & $n_6 =-446.166$ & $\ln A_6 = 4918.17$\\
%\hdashline
&$\alpha_0 = 0.0392338$ & $Q_0 = 0.437281$  & $n_0 = 4.3178$ & $\ln A_0 = 32.872$\\
&$\alpha_1 =-0.323238$ & $Q_1 =-0.401528$ & $n_1 = 17.3196$ & $\ln A_1 = -32.2877$\\
&$\alpha_2 = 2.38426$   & $Q_2 = 4.86745$ & $n_2 = -192.485$ & $\ln A_2 = 397.553$\\
Extrapolation&$\alpha_3 = -9.04342$& $Q_3 = -33.2061$& $n_3 = 752.451$ & $\ln A_3 =-2725.91 $\\
&$\alpha_4 = 18.34$   & $Q_4 = 95.0889$  & $n_4 = -1450.86$& $\ln A_4 = 7825.29$\\
&$\alpha_5 = -18.8254$  & $Q_5 =-120.398$  & $n_5 = 1391.74$ & $\ln A_5 =-9924.46$\\
&$\alpha_6 = 7.66332$   & $Q_6 = 56.2666$  & $n_6 =-530.417$ & $\ln A_6 = 4644.18$\\
\hline
\label{tab: ARparameters}
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/iCorrelationAR}
\caption{Comparison between the experimental and predicted flow stresses by AR model for interpolation estimation}
\label{fig:iCorrelationAR}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/eCorrelationAR}
\caption{Comparison between the experimental and predicted flow stresses by AR model for extrapolation estimation}
\label{fig:eCorrelationAR}
\end{figure}
\FloatBarrier
%-------------------------------------------------------------------------
\subsubsection{Proposed model (PTM model)\label{sec:ProposedModel}}
%--------------------------------------------------------------------------
The PTM model is a generalized formulation of the MZA model. Indeed, the shortcomings of the MZA model are taken into account in this formulation, which makes the model flexible for any type of studied material as it does not require a limited number of parameters. The intrinsic functions of the model, which are the polynomial type functions, will determine the parameters of the model according to the degree of the polynomial, which provides a good fit for each function. The direct objective of this work being to demonstrate the ability of the neural network based model to override analytical models in the term of interpolation and extrapolation, it is important to point out that the PTM model can give better results than those presented in this work. For more details of this model we invite the reader to consult our previous work \cite{tize2022generalized}. The equation describing the PTM model is therefore given by:
\begin{equation}
\label{eq:PTM-model}
\sigma^y(\varepsilon^p,\mdot{\varepsilon}^p,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where $A_i, B_j, C_k^l$ are the parameters of the model to be identified using the procedure proposed in  \cite{tize2022generalized}. Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material. The larger these quantities are, the more parameters need to be identified for the PTM model.

The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016-LNL} and according to the following three steps:
\begin{itemize}
\item \textbf{Step 1} : Determination of the two functions $I_1(\varepsilon^p)$ and $S_1(\varepsilon^p)$\\
At the reference strain rate, \ie when $\mdot{\varepsilon}^p=\mdot{\varepsilon}_0$, Equation (\ref{eq:PTM-model}) is written as:
\begin{equation}
\sigma^y(\varepsilon^p,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right)
\exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) \right]
\end{equation}
Taking the logarithm of each member of this equation we obtain:
\begin{equation}
\label{eq:I1S0}
\ln \sigma^y(\varepsilon^p,T) = I_1(\varepsilon^p) + S_1(\varepsilon^p)\left(T-T_0\right)
\end{equation}
where:
\begin{equation}
\label{eq:I1S1}
I_1(\varepsilon^p) = \ln\left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right)\qquad \text{and}\qquad S_1(\varepsilon^p) = \sum_{j=0}^{r}{B_j\varepsilon^{p^j}}
\end{equation}
Plotting the function $\ln \sigma^y(T)$ for a given value of $\varepsilon^p$ allows us to deduce $I_1(\varepsilon^p)$ and $S_1(\varepsilon^p)$ from the y-intercept and the slope, respectively. These functions are calculated for all plastic strain values $\varepsilon^p$ available in the experimental database. Analysis of those results allows us to propose some adequate values for the $q$ and $r$ quantities. Once those values have been selected, an identification procedure allow us to compute the $q$ parameters $A_i$ and $r$ parameters $B_j$ of the PTM model.
\item \textbf{Step 2} : Determination of the function $S_2(\varepsilon^p,T)$ as polynomials depending on the temperature $T$\\
Once the Step $1$ is done, it is possible to take the logarithm of the whole Equation (\ref{eq:PTM-model}) to obtain:
\begin{equation}
\ln \sigma^y(\varepsilon^p,\mdot{\varepsilon}^p,T) - I_1(\varepsilon^p) - S_1(\varepsilon^p)\left(T-T_0\right) = S_2(\varepsilon^p,T)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
\label{eq:SlopeS2}
\end{equation}
where :
\begin{equation}
S_2 (\varepsilon^p,T)= \sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k
\label{eq:S2_coefs}
\end{equation}
From this latter the plot of $\ln \sigma^y - I_1(\varepsilon^p) - S_1(\varepsilon^p)\left(T-T_0\right)$ versus $\ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows us to deduce $S_2(\varepsilon^p,T)$ as its slope for a given plastic strain value $\varepsilon^p$. The evolution of $S_2$ versus $\left(T-T_0\right)$ allows to find the same function for all plastic strains which is described in the polynomial forms of degree $k$ in Equation (\ref{eq:PTM-model}). The plastic strain $\varepsilon^p$ dependance of $S_2(\varepsilon^p,T)$ need to be evaluated. In the previous works \cite{Gao-2020-FBC, Yu-2020-FSM, Gurusamy-2017-PMZA, Samantaray-2009-CSJC, He-2014-MZA, Zhan-2014-CMF, Gupta-2013-CMP, Samantaray-2011-AMM} authors never took into account that step.
\item \textbf{Step 3} : Determination of the coefficients of the function $S_2(\varepsilon^p,T)$ as polynomials depending on the plastic strain $\varepsilon^p$\\
This step is a direct consequence of the previous one, which consists in determining each coefficient of the function $S_2(\varepsilon^p,T)$ as polynomial functions. Once we know the order of the polynomial that describes the function $S_2(\varepsilon^p,T)$, for each strain value the corresponding coefficients of  $S_2(\varepsilon^p,T)~\text{s}$hould be recorded in the empty lists initialized before. Thus, with the empty lists initialized, for a given strain value, it is necessary to go through all the temperatures and deduce the values of each coefficient of the function $S_2(\varepsilon^p,T)$ for this strain which will be recorded in the empty lists initialized at the beginning. Thus, an algorithm must be written which goes through all the values of the strains and adds to each list of coefficients of the polynomial $S_2(\varepsilon^p,T)$ the value deduced from the corresponding strain. It is therefore necessary to evaluate the dependence of each parameter (described by one list) on the strain in order to finally deduce its polynomial from which we also deduce its coefficients. This is how the operation is performed for all the lists. Finally, we calculate all the parameters of the proposed model. 
\end{itemize}
Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM} and Figure \ref{fig:eCorrelationPTM}. The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$ the prediction in not quite good. The deviation between the predicted values and the experimental values is relatively good.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/iCorrelationPTM}
\caption{Comparison between the experimental and predicted flow stresses by PTM model for interpolation estimation}
\label{fig:iCorrelationPTM}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/eCorrelationPTM}
\caption{Comparison between the experimental and predicted flow stresses by PTM model for extrapolation estimation}
\label{fig:eCorrelationPTM}
\end{figure}

\begin{table}[!h]
\centering{}
\caption{Parameters of the proposed model\label{tab:PTM-parameters}}
\scalebox{1.2}{
\begin{tabular}{ccc}
\hline
&  & \\
Parameters & Interpolation &Extrapolation\\
&  & \\
\hline
$A_0 (\text{MPa})$ & $62.314$ & $62.314$\\
$A_1 (\text{MPa})$ & $559.827$ & $559.827$\\
$A_2 (\text{MPa})$ & $-2160.03$ & $-2160.03$\\
$A_3 (\text{MPa})$ & $4641.94,$ & $4641.94$\\
$A_4 (\text{MPa})$ & $-5193.06$ & $-5193.06$\\
$A_5 (\text{MPa})$ & $2379.1$ & $2379.1$\\
$B_0 $ & $-0.0035805$ & $-0.0035805$\\
$B_1 $ & $0.00282334$ & $0.00282334$\\
$B_2 $ & $-0.00775301$ & $-0.00775301$\\
$B_3 $ & $0.0085135$ & $0.0085135$\\
$B_4 $ & $-0.00412815$ & $-0.00412815$\\
$C_0^0 $ & $0.148539$ & $0.148766$\\
$C_0^1 $ & $-0.302363$ & $-0.304798$\\
$C_0^2 $ & $2.25845$ & $2.2891$\\
$C_0^3 $ & $-5.2651$ & $-5.36673$\\
$C_0^4 $ & $5.38382$ & $5.51053$\\
$C_0^5 $ & $-2.05958$ & $-2.1115$\\
$C_1^0 $ & $-4.3271\ \times10^{-7}$& $-9.92159\ \times10^{-7}$\\
$C_1^1 $ & $0.00165983$& $0.00166581$\\
$C_1^2 $ & $-0.00269801$ & $-0.00272071$\\
$C_1^3 $ & $-0.000132085$& $-8.59293\ \times10^{-5}$\\
$C_1^4 $ & $0.00182935$ & $0.00178989$\\
\hline
\end{tabular}}
\end{table}
%-------------------------------------------------------------------------
\subsection{Artificial neural network model\label{sec:ANNmodel}}
%--------------------------------------------------------------------------
The Artificial Neural Network model (ANN) is a mathematical formulation widely used in many fields today for better prediction. It is a model based on the principle of minimisation where it improves from the progressive decrease of the error during the learning process. Typically an ANN model contains an input layer, an output layer and hidden layers. Each hidden layer is connected to the one before it and the one after it via neurons. Indeed, all neurons in the $k$ layer are connected to each neuron in the ($k+1$ ) layer. To each layer is added another parameter called bias. As said the principle of the ANN model is therefore based on the minimisation of the difference between the value obtained from the output of the network and the expected value.  Indeed, once the error is calculated, it is propagated back to the input layer in order to update the model parameters via the minimisation algorithms. In our case, the ADAM algorithm is used. The architecture of the network used in this study is shown in Figure \ref{fig:ANN-scheme-2HL}. After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction as well as for interpolation and extrapolation where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot{\varepsilon}^p$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress. The good performance of the model is found to be stable between $800$ and $1000$ epochs. This number was therefore used to train the model for both interpolation prediction and extrapolation.

In this study $700$ of data were used; $80\%$ (560) are randomly selected for training and $20\%$ (140) for testing. Before learning, a normalisation of the data is required in order to have all data between $0$ and $1$. The Equation is widely used for normalization.
\begin{equation}
X_n = \frac{X - X_{min}}{X_{max} - X_{min}}
\end{equation}
Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot{\varepsilon}^p/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively. $X_n$ is the normalized data of the corresponding $X$. The trained model once tested can be used to predict the behaviour of the AISI P20 alloy. Figure and Figure show a comparison between the predicted ﬂow stresses from ANN model and measured data from hot compression test as well as for interpolation prediction and extrapolation prediction. As shown from these two figures, the correlation between the experimental and the ANN prediction based is very good over the full range of data and the predicted data can well track the hardening and softening regions of the hot deforming material. Therefore, the ANN model can be used to simulate the hot deformation of this type of alloy. This was not necessarily the case with the analytical models. The performance of this prediction will be much more appreciated when it comes to testing its ability to predict data that has not been used in either the training or the test data, but rather a full-fledged trial that we wish to validate the ANN prediction by experimental. This validation will be done both with a strain rate between those used in the training and in this case we will validate the interpolation and outside of the strain rates used in the training and in this case we will validate the extrapolation.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/ANN-scheme-2HL}
\caption{Multi-layer Artificial Neural Network architecture \cite{OPantale-2021-LGP}.}
\label{fig:ANN-scheme-2HL}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/iCorrelationANN}
\caption{Comparison between the experimental and predicted flow stresses by ANN model for interpolation estimation}
\label{fig:iCorrelationANN}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/eCorrelationANN}
\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
\label{fig:eCorrelationANN}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Comparison of analytical and ANN models\label{sec:Comparison}}
%--------------------------------------------------------------------------
%-------------------------------------------------------------------------
\subsubsection{Identification results' comparison \label{sec:Interpolation}}
%--------------------------------------------------------------------------
The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($AARE$ generally known as $\AARE$ ) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($RMSE$) (Equation (\ref{eq:RMSE-expression})).
\begin{equation}
\label{eq:R-expression}
\R(\%) = \frac{\displaystyle\sum_{i=1}^{N}{\left(E_i - \overline{E}\right)\left(P_i - \overline{P}\right)}}{\sqrt{\displaystyle\sum_{i=1}^{N}\left(E_i - \overline{E}\right)^2 .\displaystyle\sum_{i=1}^{N}\left(P_i - \overline{P}\right)^2}}\times 100
\end{equation}
\begin{equation}
\label{eq:AARE-expression}
\AARE(\%) = \frac{1}{N}\displaystyle\sum_{i=1}^{N} \displaystyle\left\lvert\frac{E_i- P_i}{E_i} \right\rvert\times 100
\end{equation}
\begin{equation}
\label{eq:RMSE-expression}
RMSE (\%) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2} \times 100
\end{equation}
Where $E_i$ is the experimental value and $P_i$ is the predicted value of the constitutive law (phenomenological and ANN models), $\overline{E}$ and $\overline{P}$ are the mean values of the experimental and predicted values, respectively.

The correlation coefficient $R$ is generally used to show the degree of linearity between the experimental and predicted values. The model sometimes tends to be biased towards low and high values. Therefore, a good (high) value of $R$ does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction \cite{phaniraj2003applicability}. On the other hand, other coefficients ($\AARE$ and $RMSE$) are used to estimate the predictive capacity of the model because they are considered unbiased as well as for low and high values. Indeed, they verify the predictability of a model term by term comparison of the relative error in relation to the real value of the variable \cite{srinivasulu2006comparative}. In the previous sections the correlations between the experimental flow stresses and those provided by the phenomenological and ANN models have been presented and the correlation coefficients $R$ for JC, MZA, HS, Arhenius, proposed and ANN models are $0.98405682$, $0.98786324$, $0.98413109$, $0.99829876$, $0.99524323$ and $0.99995003$, respectively in case of prediction for interpolation validation. These results show the Arrhenius-type, proposed and ANN models have better correlation between the experimental data and predicted results compared with the JC, MZA and HS models.

All coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work are summarized in the Table \ref{tab:Coefsparams}. From this Table, it can be seen that the ANN model has a good prediction than the analytical models. All this shows sufficiently that the ANN model is more effective in describing the behaviour of the AISI P20 alloy for high temperature deformation. This efficiency will therefore be validated on tests at two different selected strain rates. One between the minimum and the maximum strain rates used during identification or training for ANN model and another one outside higher than the maximum strain rate. This will validate the interpolation and extrapolation capability of the analytical and phenomenological models. The prediction results should lead to a better interpolation and extrapolation capability of the ANN model than phenomenological models as shown during identification step. The following sections will focus on this analysis.

Another thing to be analysed from this table is the link between the values of the correlation coefficient $R$ and the values of $\AARE$. Indeed, as mentioned above, the $R$ coefficient does not necessarily mean a good prediction of the model but a good relationship of linearity between the experiment and the prediction. To ensure a good prediction of the model, it is necessary to add to $R$, the values of $\AARE$. For example and in the case of identification for the validation of the interpolation (the same analysis can be done for the validation of the extrapolation), let us observe carefully taht, the values of the coefficients $R$ are $99.0145\%$, $98.4131\%$ and those of $\AARE$ are $12.7939\%$ and $8.7309\%$ respectively for the MZA model and the HS model. This seems contradictory when the $R$ of HS is smaller than that of MZA, whereas for the $\AARE$ values it is the opposite case. This simply means that the HS model has a good prediction compared to the MZA model whereas in the framework of the linear correlation between the experiment and the prediction the MZA model makes it better. All this can be seen from the figures where we can observe the HS curves are indeed closer to the experimental than those of MZA while the points are scattered for HS model on the correlation curve. This validates the analysis made by \cite{phaniraj2003applicability, srinivasulu2006comparative} their works. The same analysis can be applied to the other results of the other models, although the ANN model is still the best for a good prediction.
\begin{table}[h!]
\centering{}
\caption{Comparison of phenomenological an ANN models' accurary coefficients}
\scalebox{0.88}{
\begin{tabular}{lccccccc}
\hline
&		&		&         &             &		   &		  &						\\
Coefficients&JC  & MZA  &HS  & Arhenius      & Proposed  &ANN &Expected predictions \\
&				&				&         &             &		   &	     &	    \\
\hline
$R(\%)$&$98.4057$&$99.0145$&$98.4131$&$99.8299$& $99.5243$&$99.9950$&Interpolation  \\
$R(\%)$&$98.2519$&$98.7863$&$98.6493$&$99.7752$& $99.6527$&$99.9939$&Extrapolation  \\
%\hdashline
$\AARE(\%)$&$12.6421$&$12.7939$&$8.7309$&$3.7026$&$4.4781$&$0.6613$&Interpolation   \\
$\AARE(\%)$&$12.7567$&$11.7289$&$7.6883$&$3.7875$&$3.9697$&$0.6219$&Extrapolation   \\
\hline
\label{tab:Coefsparams}
\end{tabular}}
\end{table}
%-------------------------------------------------------------------------
\subsubsection{Interpolation and extrapolation validation\label{sec:Extrapolation}}
%--------------------------------------------------------------------------
This section is devoted to the validation of the models developed in this study. To do so, let us briefly recall the purpose of this work in order to make it much clearly. Indeed, we have developed analytical models and a model based on the neural network for certain values of strain, strain rates and temperatures. The idea is therefore to randomly fix two strain rates while keeping the same values of strains and temperatures used for the development of the phenomenological and ANN models. Of these two strain rates, one must be between the minimum and maximum strain rate values already known and another must be higher. This is to test the interpolation and extrapolation capability of these models in order to validate them by experimental data.

For the validation of the interpolation, the chosen strain rate is $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$. The Figure \ref{fig:inCombinaison1} and Figure \ref{fig:inCombinaison2} show the comparison between the predictions of the analytical and ANN models and the experiment. It appears from these Figures that all models have relatively good predictions but the ANN model remains the best because the value of its $\AARE$ is $1.4\%$ while it is between $2.33\%$ and $6.13\%$ for the analytical models. This further shows the performance of the ANN model compared to the analytical models. All these results are summarised in Table \ref{tab:CoefInEx}.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/inCombinaison1}
\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
\label{fig:inCombinaison1}
\end{figure}
For the validation of the extrapolation, the chosen strain rate is $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$. Figure \ref{fig:exCombinaison1} and Figure \ref{fig:exCombinaison2} show the comparison between the predictions  and the experimental. Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$. Again, the ANN model shows its ability to extrapolate data. This makes it possible to say that the ANN model remains the best tool to characterize the behaviour of a material subjected to certain deformation conditions. It can also be noted that the Arhenius and the proposed models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.78 \%$; which is not bad.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/inCombinaison2}
\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
\label{fig:inCombinaison2}
\end{figure}
\FloatBarrier
\begin{table}[h!]
\centering{}
\caption{Validatio of interpolation and extrapolation accurary coefficients}
\scalebox{0.92}{
\begin{tabular}{lccccccc}
\hline
&		&		&         &             &		   &		  &						\\
Coefficients&JC  & MZA  &HS  & Arhenius      & Proposed  &ANN &Validations 		    \\
&				&				&         &             &		   &	     &	    \\
\hline
$R(\%)$&$99.0590$&$99.0821$&$97.6008$&$99.8417$& $99.8760$&$99.9439$&Interpolation  \\
$R(\%)$&$99.2920$&$99.4879$&$93.9429$&$99.6870$& $99.7582$&$99.8047$&Extrapolation  \\
%\hdashline
$\AARE(\%)$&$4.2686$&$3.7440$&$6.1391$&$2.3321$&$2.7590$&$1.4018$&Interpolation   \\
$\AARE(\%)$&$4.8988$&$3.4506$&$12.9939$&$3.2008$&$3.8845$&$1.7433$&Extrapolation   \\
\hline
\label{tab:CoefInEx}
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.98\columnwidth]
{newFigures/exCombinaison1}
\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
\label{fig:exCombinaison1}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/exCombinaison2}
\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
\label{fig:exCombinaison2}
\end{figure}
\FloatBarrier

%---------------------------------------------------------------------
\section{Conclusion \label{sec:Conclusion}}
In order to describe the high temperature flow behaviour of the modified carbon alloy AISI P20, a comparative study between the phenomenologicalc(JC, MZA, HS, Arhenius and proposed) and ANN models was carried out. This study is done for temperatures ($1050$ -$1250^\circ$C ) and strain rates ($0.001 - 5.0\ \text{s}^{-1}$). Two fundamental works were compared in this study: on the one hand the flow stress prediction capacity of the studied models and on the other hand using these results to predict an interpolation test and another extrapolation test, all validated by experimental data. As a result of this study, the following conclusions were reached:
\begin{itemize}
\item The ﬂow stress increases with strain rate and decreases with the temperature, and strain has signiﬁcant inﬂuence on the ﬂow stress. Analytical models including JC, MZA, HS, Arhenius, proposed and ANN models were developed and a comparison of their predictions was made. Based on the prediction of those phenomenological models, JC and MZA models are not suitable for the AISI P20 alloy because their $\AARE$ are $12.64\%$ and $12.79\%$ respectively. But the Arhenius and proposed models can be used to describe the flow behabiour of this alloy because they have reduced $\AARE$ which are $3.78\%$ and $3.96\%$ respectively. For the ANN model, this coefficient is $0.62\%$. Regarding these results, the ANN model remains the best in terms of predicting the hot flow behaviour of the AISI P20 alloy to which can be added the Arhenius model and the proposed one.
\item All models developed have been validated on interpolation and extrapolation tests. Based on these results, all models have a good prediction of the interpolation although the prediction of the ANN model remains the best. On the other hand, the analytical models do not have a good prediction of extrapolation compared to the ANN model. All these results are summarised in Table \ref{tab:CoefInEx}. 
\end{itemize}

% \bibitem{}
\bibliographystyle{elsarticle-num}
\bibliography{Bibliography}
%\end{thebibliography}
\end{document}
\endinput

### 2022-10-12 Article_PTM.tex
updated version of .tex file

@@
 
-\title{Phenomelogical and artificial neural network models' comparison study for hot deformation of AISI P20: Interpolation and extrapolation predictions}
+\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation--extrapolation capacity validation}
 
 \author[LGP]{Pierre Tize Mha}
+\author[ETS]{Prashant Dhondapure}
 \author[LGP]{Amèvi Tongne}
+\author[ETS]{Mohammad Jahazi}
 \author[LGP]{Olivier Pantalé \corref{cor1}}
@@
 \address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}
+\address[ETS]{Écolde de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}
 
 \begin{abstract}
-Non-linear numerical modeling is increasingly used for the simulation of complex processes such as forming or machining.
-The constitutive laws necessary for these simulations are therefore becoming more and more complex regarding the increasingly precise consideration of physical phenomena (plasticity, thermal dependence, damage ...) and their implementation in numerical codes requires the identification of many parameters.
-The use of these constitutive laws for dynamic or quasi-static applications requires the identification of these parameters under conditions close to those encountered during the real process, mainly in terms of deformation, strain rates, and temperatures.
-The availability of a constitutive law in the finite element codes does not guarantee the success of a study to be carried out if it does not comply with the model development criteria.
-This is because the models integrated in the numerical codes are not developed based on forms that are adjustable to any type of study.
-In this study, a new form of non-linear constitutive flow law based on the Modified Zerilli--Armstrong model, which can answer the above problem, has been developed to apply it to the numerical simulation of two different tests (a quasi-static compression test, the necking of a circular bar).
-This flow law is based on the modified Zerilli--Armstrong model, which, together with the new modified Johnson--Cook model, has been compared to appreciate the relevance of the proposal.
-For that, an implementation of this new law via the VUHARD subroutine into the Abaqus/Explicit finite element code was made to model the two tests.
-The comparison of the results obtained (from identification) by our proposed law with those obtained using the NMJC shows that this new law better approaches the experiments than the other one.
-This is also showed through the numerical results using the Abaqus software.
-It can be said that this way of formulating a flow law allows to highlight the great performance of the proposed approach.
-Although this law has been used only used for quasi-static tests, we can say that it can also be used in dynamic tests.
+The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$ ) and temperatures ($1050^\circ\text{C} -1250^\circ$C ).
+Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
+Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model.
+These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $AARE$ and the Root Mean Square Error ($RMSE$).
+From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy.
+For the strain rate ($\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050^\circ$C and $1100^\circ$C  while in the case of the PTM model, the strain rate  ($\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$) is not well described.
+This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high.
+Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot{\varepsilon}^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
+The results of the ANN model show a very good agreement between the predictions and the experiment.
+This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction.
+To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.
 \end{abstract}
@@
 \begin{keyword}
-Zerilli--Armstrong flow law \sep Constitutive Behavior \sep Finite Element Method \sep Numerical Implementation \sep Johnson--Cook flow law
+Zerilli--Armstrong flow law \sep Constitutive behavior \sep Arhenius--flow law \sep Hansel--Spittel flow law \sep Johnson--Cook flow law \sep interpolation \sep extrapolation \sep Artificial neural network
 \end{keyword}
@@
 %--------------------------------------------------------------------------
-\textcolor{red}{Due to technological advances, industries are constantly looking for innovations to maintain their competitiveness.
-For the metallurgical industry, these innovations involve the development of new materials.
-In conjunction with the implementation of these new materials, it becomes necessary to characterize their thermomechanical behavior, in particular in order to feed the data bases used by the numerical simulation models more and more widespread nowadays \cite{Trimble-2020-Finite, Yuan-2021-Particle}}.
+Continuous casting and rolling mechanisms are an integral part of the technological methods of medium deformation through a continuous water-cooled crystalliser before entering a rolling mill.
+Some of the advantages of this method are increased metal yield, energy saving, improved quality of continuous casting and easier mechanisation and automation .
+Deformation being a very complex process involving both elastic and plastic deformation, is accompanied by high temperatures, high strain rates and complex and variable friction conditions \cite{he2013comparative}.
+However, a quantitative study and analysis of the deformation mechanism does not provide accurate analytical solutions .
+Moreover, conducting an experiment is not only time-consuming but also requires a high level of funding \cite{changizian2012high}.
+To mitigate these two factors (to name but a few), the Finite Element Method (FEM) is widely used in the analysis and optimisation of process parameters of various materials .
+FEM effectively compensates for the shortcomings of the analytical and experimental methods and plays an important role in the correct formulation of technological parameters, the improvement of product quality and the in-depth knowledge of the deformation mechanism.
+For example FEM has been widely used to simulate and analyse steel hot forming processes, such as forging, rolling, extrusion and casting but the accuracy of the numerical solution provided by FEM for this type of analysis strongly depends  on the accuracy of the constitutive equation of the concerned material \cite{qin2010modeling, mandal2009constitutive, ji2018constitutive}.
 
-\textcolor{red}{Among the different approaches used, the finite element method (FEM) is one of the numerical methods that has become the most popular nowadays.
-Like any numerical method, the accuracy of the solution depends very strongly on the constitutive equation describing the behavior of the material and implemented in the computational code \cite{Li-2021-Finite, Liu-2021-Finite}.
-This constitutive equation is linked to the mathematical model that describes it.
-This choice is not entirely free, insofar as the choice of the behavior law (speaking of an analytically formulated model) used to describe the behavior of a material is guided by its availability in the finite element codes \cite{Miller-2021-Thermomechanical}.
-This forces an adaptation between the studied material (which is real) and the behavior law (representative mathematical model) available in the FEM code which is not necessarily the one able to describe the behavior of the studied material.
-The problem of the non flexibility of the models available in the finite element codes appears immediately and limits the adequacy of the model to the reality of the behavior since the behavior laws established and available in the FEM codes are for the most part specific to a particular material or class of materials.
-In other words, as soon as they are applied to materials different from the one for which they were originally developed, they find their limits because they do not manage to represent the reality described by the experiment as one would wish.
-It is therefore interesting to think about developing a method that can be applied to any material of any class and implemented in a finite element code.
-This approach involves a number of parameters depending on the material studied, but with a more global mathematical form adaptable to a wider range of materials.
-In this study, we propose an approach allowing a better adaptability of the behavior law to various materials.
-To justify the relevance of this proposal, let us first examine the models developed so far and try to see if some of them meet this need}.
+Indeed, hot forming processes are an essential step in the manufacturing of mechanical components and directly affect the ﬁnal quality of the products such as microstructure and mechanical properties \cite{ashtiani2012constitutive}.
+Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallisation), which very often occur during hot working, influence the quality of the deformation of materials.
+The complexity of the deformation behavior, however, leads to the fact that the deformation can only be calculated accurately by using a computer code to model the response of the material under the specified loading conditions.
+To this end, a mathematical formulation is often used to represent the flow behavior of materials in a form that can be used in finite element software \cite{lin2008prediction,wu2012flow}.
 
-\textcolor{red}{According to the literature, analytical models describing the behavior of materials can be grouped into three categories: empirical models, semi-empirical models, and physical models.
-Empirical models describe the behavior of the material by considering macroscopic quantities without considering its microstructure, whereas physical models consider the microstructure.
+Based on a thorough search of the literature many researchers have tried to predict the mechanical behavior of materials under hot working conditions using constitutive models.
+Therefore, various constitutive equations have been proposed to describe the flow behavior including phenomenological, physical and artiﬁcial neural network (ANN) models \cite{lin2011critical,shin2010phenomenological,rusinek2010thermo}.
 As for the semi-empirical models, they try to be at the border between the empirical and physical models.
@@
 We refer here to strain hardening, strain rate hardening, and thermal effects that are described separately in the JC model as analyzed by Jia \eal \cite{Jia-2021-Modified-JC}.
-To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998-Revised-JC, Vural-2003-Large, Lin-2010-Modified-JC, Lin-2012-Phenomenological, Li-2013-Modified-JC, Zhou-2019-Research, Zhang-2015-Modified-JC}}.
-
-\textcolor{red}{Due to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988-Evaluation, Voyiadjis-2005-Microstructural, Dey-2007-Influence}.
+To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998-Revised-JC, Vural-2003-Large, Lin-2010-Modified-JC, Lin-2012-Phenomenological, Li-2013-Modified-JC, Zhou-2019-Research, Zhang-2015-Modified-JC}.
+According to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988-Evaluation, Voyiadjis-2005-Microstructural, Dey-2007-Influence}.
 However, the drawbacks of this model are related to the temperature limit value of the test.
@@
 Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009-Thermo-viscoplastic}.
-In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{Nemat-2004-Plasticity, Lennon-2004-Influence, Muralli-2017-Performance, Cheng-2021-Modified-ZA, Muralli-2021-Finite}}.
+In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{Nemat-2004-Plasticity, Lennon-2004-Influence, Muralli-2017-Performance, Cheng-2021-Modified-ZA, Muralli-2021-Finite}.
+The hyperbolic sine Arrhenius-type constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the microstructure of the studied material because   this model allows to estimate the deformation energy of the material \cite{jonas1969strength,zhang2012effect,mostafaei2012hot}.
+Its original formulation has been revised several times in order to properly describe the obtained experimental behavior.
+In order to increase the accuracy of the model, the effects of strain \cite{slooff2007constitutive, li2012flow, xu2013constitutive}, strain rate \cite{lin2008constitutive, mandal2009constitutive} have been considered by several researchers.
+For example, Sloof \eal \cite{slooff2007constitutive} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that their model could predict the high temperature flow behavior of a magnesium alloy.
+Lin \eal \cite{lin2008constitutive}, on the other hand, modified the model by introducing a strain rate compensation factor.
 
-\textcolor{red}{These two approaches are among the most popular and the choice depends on the effectiveness of the method for a given problem.
-So we have on the one hand, the JC formulation and its variants and on the other hand the ZA approach with its variants too.
-Another approach proposed by Lin \eal \cite{Lin-2010-Modified-JC} is to combine the JC model with the MZA model (in its modified form proposed by Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic}).
-This approach allows combining on the one hand the factor taking into account the strain hardening effects described by the JC model and on the other hand the factor describing the strain rate effects and the thermal softening described by the MZA model in a unified formulation.
-The major difficulty of all the variants mentioned above is the restriction of the parameters on which the model depends, thus limiting the applicability domain of the developed model.
-Therefore, it seems necessary to look for a method that does not limit the number of parameters, unlike the approaches mentioned above, and that can describe more accurately the reality observed by the experiment}.
+The method based on artiﬁcial neural networks is an approach to predict the deformation behavior of materials under different conditions.
+ANN is in fact a method originally developed to simulate the biological processes of the human brain.
+And therefore it is not necessary to formulate a mathematical expresson and identify these parameters for this kind of model.
+The response of the deformation behavior of materials is highly non-linear at high temperatures, and many factors affecting the deformation behavior of materials are also non-linear; this makes the accuracy of the flow stress predicted by regression methods and the appropriate range is limited.
+Faced with these limitations, ANN models are therefore of interest.
+Indeed, ANNs are particularly suited to deal with complex and non-linear relationships; consequently, ANNs have been successfully applied to predict the deformation behavior of materials under hot working conditions.
+ANNs can provide a fundamentally different approach to statistical or numerical techniques for materials modelling and materials processing control.
 
-\textcolor{red}{Artificial neural networks (ANNs) offer an alternative way to solve these problems.
-ANNs are currently used to solve problems that are difficult to conceptualize using traditional computational methods.
-Thus, unlike a classical approach based on a regression method, an artificial neural network does not need to know the mathematical form of the model it seeks to reproduce and can therefore learn directly from experimental data without any prior assumption on the nature of the input parameters and their interactions.
-Thus, artificial neural networks can enable new approaches for modeling material behavior and have been successfully applied for the prediction of constitutive relationships of some metals and alloys \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Huang-2021-CMM}.
-Although this approach is very effective, it does not allow the interpretation of the obtained results, because it does not take into account the physics of the phenomena for the considered material}.
+In this study, the high temperature deformation behavior of AISI P20 modified carbon steel subjected to compression tests will be highlighted.
+From the experimental data obtained, analytical models will be identified on the one hand in order to select the one that could better describe the behavior of this alloy and on the other hand, an ANN model is also developed and a comparative study between the analytical models and the ANN model will follow.
+A fundamental issue that will also be addressed in this work is the ability to interpolate and extrapolate of the developed models.
+Indeed, how do models behave when it comes to interpolating or extrapolating data that the model is never aware of ?
+the answer to this question will be well analyzed in this study.
 
-\textcolor{red}{From the above, we can retain that there are two main families of models to describe the behavior of a material.
-On the one hand, analytical models presenting a problem of flexibility and on the other hand, implicit models, based on neural networks, more adaptable but presenting a problem of physical interpretation.
-It is therefore interesting to develop a physical model that is able to adapt to any material and can be efficiently implemented in a finite element code.
-In this perspective, we propose here a new formulation based on the MZA model, whose interest is to answer the two problems mentioned above.
-To appreciate the relevance of our approach, we used the Abaqus/Explicit software which offers the possibility to implement a new behavior law using a FORTRAN VUMAT or VUHARD subroutine following the example of the works proposed by \cite{Gao-2007-FRT, JansenVanRensburg-2012-TSV, Duc-Toan-2012-MJC, Ming-2018-ERV}}.
-
-\textcolor{red}{The main paragraphs of this work are as follows: Section \ref{sec:ConstLaws} presents two  known constitutive laws which will serve as the basis of the the proposed one presented in Section \ref{sec:ProposedModel}.
-Since this model is new and will be used to perform a numerical model using Abaqus, the three derivatives of flow stress $\sigma$ with respect to the strain $\varepsilon^p$, the strain rate $\mdot{\varepsilon}^p$ and temperature are required.
-So, determination of these derivatives is done in this Section.
-Section \ref{sec:Application} is devoted to the comparison of the proposed model to the others one where identification is done on a 100Cr6 steel.
-Section \ref{sec:NumSimulations} details the numerical results of the models identified in Section \ref{sec:Application} using the cylindrical compression test and the necking of circular benchmark tests.
-Conclusion and future works are detailed in Section \ref{sec:Conclusion}}.
+The main parts of this work are as follows: Section \ref{sec:Materials} presents the material et experimental procedure inverstigated in this study.
+Section \ref{sec:ConstLaws} is devoted to the presentation of the models developed and their comparative.
+Section \ref{sec:inExtrapolation} details the validation of interpolation and extrapolation capacity of each model developped.
+Conclusion and future works are detailed in Section \ref{sec:Conclusion}.
 
 %----------------------------------------------
-\section{Experimental procedure}
+\section{ Materials and Experiments \label{sec:Materials}}
 %----------------------------------------------
-The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table.
+%----------------------------------------------
+\subsection{Experimental procedure}
+%----------------------------------------------
+The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table \ref{tab:Composition}.
 Cylindrical specimens were machined with an initial diameter of $10$ mm and a height of $15$ mm.
 Hot compression tests were conducted on a Gleeble-3800 thermo-simulator (Figure \ref{fig:Gleeble3800}), at temperatures of $1050^\circ$C,  $1050^\circ$C,  $1100^\circ$C,  $1150^\circ$C,  $1200^\circ$C and  $1250^\circ$C with strain rates of $0.001\ \text{s}^{-1}$, $0.01\ \text{s}^{-1}$, $0.1\ \text{s}^{-1}$, $1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$.
-Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during hot deformation.
-The samples were heated to $1260^\circ$C temperature and were held for $5$ min to eliminate thermal gradients at the test temperatures.
+Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during the tests.
+The samples were heated up to temperature $1260^\circ$C  and were held for $5$ min to eliminate thermal gradients.
 Then cooled to test temperature where the specimen is held $1$ minute before deformation.
 After compression the specimen is quencted rapidly for microstructure studies.
-The procedure of this test is illustrated in Figure \ref{fig:Heating}.
+The procedure of this test is illustrated in Figure \ref{fig:Heating} where $h_0$ and $R_0$ are the height and radius before compression; $h$, $R_M$, and $R_T$ are respectively the height, big radius and small radius of the specimen after compression.
 \begin{figure}[!ht]
@@
 \hline
-\label{tab: Composition}
+\label{tab:Composition}
 \end{tabular}}
@@
 %------------------------------------------------------------------------
-\section{Results and discussion\label{sec:ConstLaws}}
-%------------------------------------------------------------------------
-
-%------------------------------------------------------------------------
-\subsection{Flow stress behaviour}
+\subsection{Flow stress behavior}
 %------------------------------------------------------------------------
@@
 
-To explain the overall behaviour of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX).
+To explain the overall behavior of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX).
 At the beginning of the deformation, the amount of dislocations increases and they start to move, leading to a rapid increase in stress known as work-hardening.
@@
 These two phenomena therefore explain the different shapes of the flow stress curves observed for this alloy.
-As an example, the Figure \ref{fig:BarNecking} , and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression.
+As an example, the Figure \ref{fig:BeforeCompM} and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression.
 As observed on the flow curves, it can be seen that recrystallisation is almost complete for this temperature and strain rate.
 Indeed, most of the grain boundaries start to form new grains.
-The identification of the behavioural laws of these curves will be done in the next section in order to predict its behaviour in any test condition.
-This will be done on the one hand to test the ability of the models to describe an interpolation and on the other hand to do extrapolation.
+The identification of the behavioral laws of these curves will be done in the next section in order to predict its behavior in any test condition.
 \begin{figure}[!ht]
@@
 \end{figure}
+
 %-------------------------------------------------------------------------
-\subsection{Analytical constitutive flow laws}
+\section{Phenomenological constitutive flow laws\label{sec:ConstLaws}}
 %-------------------------------------------------------------------------
@@
 As mentioned in the introduction, many constitutive laws exist today, and selecting one of them based on explicit criteria hinders the development of computational models for new materials.
-Since the purpose of this work is to compare analytical models with the ANN model in terms of interpolation and extrapolation, it is important to justify the choice of the analytical models presented here among the many that exist in the literature.
+Since the purpose of this work is to compare ANN model to analytical models it is important to justify the choice of the analytical models presented here among the many that exist in the literature.
 Among the most widely used analytical models nowadays, the Johnson-Cook (JC) model is the most used due to its simplicity of use linked to the number of its reduced and easy to obtain parameters.
@@
 Furthermore, the Arrhenius model will be used in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter Q (the deformation activation energy coefficient) which is of great importance in the study related to the microstructural analysis of materials.
-Hence its use in the development of analytical models dedicated to the microstructural analysis of materials.
-The shortcomings of these models were the main motivation for the formulation of the model proposed in this work, the details of which can be found in our previous work.
+The PTM model is also used in this study as it is a model whose formulation does not impose a number of parameters a priori and has proven its ability in our previous work and therefore we want to test it on this type of material as it is formulated to fit any material.
 %-------------------------------------------------------------------------
-\subsubsection{Johnson--Cook model\label{sec:JC}}
+\subsection{Johnson--Cook model\label{sec:JC}}
 %-------------------------------------------------------------------------
-The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature.
+The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature .
 However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
@@
 Hence its inability to describe the phenomenon of temperature-induced softening.
-The equation that describes this model is given as follows:
+The equation that describes this model is given as follows \cite{johnson1985fracture}:
 \begin{equation}
@@
 \end{equation}
-Where $\sigma^y$ is the equivalent stress flow stress, $\varepsilon^p$ is the plastic strain, ($A=\sigma_0$) is the elastic limit of the material, $B$ is the strain hardening's coefficient, $n$ is the strain hardening's exponent.
+Where $\sigma^y$ is the equivalent stress flow stress, $\varepsilon^p$ is the plastic strain, ($A=\sigma^y_0$) is the elastic limit of the material, $B$ is the strain hardening's coefficient, $n$ is the strain hardening's exponent.
 $C$ and $m$ are the material constants that describe the strain rate hardening and thermal softening exponent respectively.
@@
 For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050^\circ$C respectively and the value of $A$ is $43.0988$ MPa.
-Here after datailed the steps for determination the JC model parameters.
+Here after datailed the steps for determination of the JC model parameters.
 At the reference strain rate, Equation \ref{eq: JCmodel} becomes:
@@
 \end{equation}
-From this equation one can easily obtain the parameter $C$ using the linear fitting method for each strain value and averaging all these values as shown in Figure \ref{fig:JCSigmaAB1} the value is $0.0976681$.
+From this equation one can easily obtain the parameter $C$ using the linear fitting method for each strain value and averaging all these values as shown in Figure \ref{fig:JCSigmaAB1} the value is $0.0995438$.
 \begin{figure}[!ht]
@@
 \end{figure}
-Having determined all the parameters of the Johnson--Cook model, its mathematical formulation can be written as follows:
-\begin{equation}
-\label{eq: JCmodelf}
-\sigma^y = \left(43.0988 + 114.518\varepsilon^{p^{0.313969}}\right)\left(1+0.0976681\ln\mdot{\varepsilon}^*\right)\left(1-T^{*^{0.898932}}\right)
-\end{equation}
-The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC} and Figure  \ref{fig:eCorrelationJC}.
+
+The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC}.
 The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates.
 The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates.
+All parameters of JC model are in Table \ref{tab: JCparameters}.
 \begin{figure}[!ht]
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/iCorrelationJC}
-\caption{Comparison between the experimental and predicted flow stresses by JC model for interpolation estimation}
+{newFigures/CompExpJC}
+\caption{Comparison between the experimental and predicted flow stresses by JC model} 
 \label{fig:iCorrelationJC}
-\end{figure}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{newFigures/eCorrelationJC}
-\caption{Comparison between the experimental and predicted flow stresses by JC model for extrapolation estimation}
-\label{fig:eCorrelationJC}
 \end{figure}
@@
 &         &             &		   &		  &\\
-&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
+Parameters&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
 &         &             &		   &	     &	    \\
 \hline
-Interpolation&$43.0988$&$114.518$& $0.313969$&$0.0993506$&$0.898932$\\
-%\hdashline
-Extrapolation&$43.0988$&$114.518$& $0.313969$&$0.0992144$&$0.910297$\\
+Values&$43.0988$&$114.518$& $0.313969$&$0.0995438$&$0.898932$\\
 \hline
@@
 %-------------------------------------------------------------------------
-\subsubsection{The Modified Zerilli--Armstrong model\label{sec:MZA}}
+\subsection{Modified Zerilli--Armstrong model\label{sec:MZA}}
 %-------------------------------------------------------------------------
@@
 As mentioned earlier, Johnson--Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
-Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model.
-In fact, the Zerilli--Armstrong model is based on a physical consideration of heat-activated dislocation motion and the interaction of individual dislocations with each other as shown by Hull \eal \cite{Hull-2011-ITD}.
-The ZA model is therefore a constitutive law based on a study of the material microstructure.
-For a FCC material, the original equation describing the Zerilli--Armstrong model \cite{Zerilli-1987-DMB} is given by:
-\begin{equation}
-\label{eq:ZA-model}
-\sigma^y = A_{0} + A_{1}\varepsilon^{p^n} \exp\left[-A_{2}T + A_{3}T\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
-\end{equation}
-where $\sigma^y$ is the von Mises flow stress, $\varepsilon^p$ is the equivalent plastic strain, $\mdot{\varepsilon}^p$ is the equivalent plastic strain rate, $\mdot{\varepsilon}_0$ is the reference strain rate and $T$ is the absolute temperature within the material.
-The coefficients $A_0$, $A_1$, $A_2$, $A_3$ and $n$ are the parameters of the model to be identified for a given material and $\mdot{\varepsilon}_0$ is the reference strain rate as proposed by many models in the literature.
-It is important to note that this model is globally split in two terms.
-The first term is a constant stress threshold representing the yield strength of the material and the second term is a thermo-viscous component considering the variation of the work hardening threshold of the material with temperature and strain rate.
-With face-centered cubic (FCC) materials, the strain hardening shows a greater dependence on both temperature and strain rate.
-The thermal component of strain hardening in FCC materials is physically interpreted as the resistance to dislocation motion by the mutual interaction of dislocations \cite{Voyia-2005-MBM}.
-The flow stress threshold of an FCC material is independent of temperature and strain rate, so that the flow stress threshold is constant and equal to the initial stress \cite{Nemat-2004-Plasticity, Voyia-2005-MBM}.
-The limitation of the ZA model is that it cannot be used for flow stress prediction at high strain rates and temperatures above $0.6~T_m$.
-To circumvent this problem, Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic} proposed a modified form of the Zerilli--Armstrong law (MZA) given by the following relationship:
+Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model \cite{Hull-2011-ITD}.
+But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic} proposed a modified form given by the following equation:
 \begin{equation}
@@
 where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
-This formulation was initially developed from a compression test of 15Cr--15Ni--2.2Mo Ti-modified austenitic stainless steel (the D9 alloy).
-This test was performed over a range of plastic strains ($\varepsilon^p=0.1-0.5$), strain rates ($\mdot{\varepsilon}^p=10^{-3}-1~\text{s}^{-1}$) and temperatures ($T=800-1200^\circ\text{C}$).
-In attempting to apply the original Johnson--Cook model, the authors of this work found that it was unable to describe the behavior of this type of material over the ranges of strain, strain rate, and temperature mentioned above.
-The same conclusion was made regarding the ZA model who was also unable to correctly describe the behavior of this material.
-Based on the ZA model, Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic} have therefore proposed a modified form of the ZA model to better describe the behavior of this material.
-This modified model takes into account the effect of isotropic strain hardening, strain rate hardening, thermal softening and the coupled effects of strain, strain rate and temperature on the flow stress.
-It predicts the evolution of the high-temperature flow threshold of the D9 alloy over the above ranges of strain, strain rate and temperature with good correlation to the experimental data and good generalization.
-The correlation coefficient obtained is $0.995$ while the average error for the whole data set is only $5.3~\%$.
-For more details about the formulation of this model the author can read \cite{Samantaray-2009-Thermo-viscoplastic}.
-
-The Equation (\ref{eq:ZA-model}) of the original Zerilli--Armstrong model defines the flow stress in two terms: a thermal stress and an athermal stress that depends on the grain size of the material and is independent of temperature.
-However, several studies have shown that this independence decreases when the temperature increases beyond a certain value.
-Based on these observations, Samantaray questioned the athermal consideration for the D9 material.
-This approach then allows for the consideration of temperature effects on the yield strength of D9 steel and even other materials.
-Here after how to get all parameters of the MZA model:
+The formulation of the model can be found in \cite{Samantaray-2009-Thermo-viscoplastic} and determination of its parameters is sumarized as following.
 
@@
 Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
-The parameters (both the interpolation and extrapolation indentification) of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA} and Figure \ref{fig:eCorrelationMZA}.
+The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}.
 It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
@@
 \centering{}
-\caption{Parameters' constants of Modified--Zerrilli-Armstrong Model}
+\caption{Parameters' constants of Modified--Zerilli-Armstrong Model}
 \scalebox{0.83}{
@@
 &         &             &		   &		 &			   &&\\
-&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
+Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
 &         &             &		   &	     &	           &&\\
 \hline
-Interpolation&$43.0988$&$112.975$& $330.976$&$4.27581$&$14036.3$&$17.1520$&$0.305028$\\
-%\hdashline
-Extrapolation&$43.0988$&$112.975$& $330.976$&$4.27581$&$14496.9
-$&$18.9194$&$0.305028$\\
+Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
 \hline
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/iCorrelationMZA}
-\caption{Comparison between the experimental and predicted flow stresses by MZA model for interpolation estimation}
+{newFigures/CompExpMZA}
+\caption{Comparison between the experimental and predicted flow stresses by MZA model}
 \label{fig:iCorrelationMZA}
-\end{figure}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{newFigures/eCorrelationMZA}
-\caption{Comparison between the experimental and predicted flow stresses by MZA model for extrapolation estimation}
-\label{fig:eCorrelationMZA}
 \end{figure}
@@
 %-------------------------------------------------------------------------
-\subsubsection{Hansel and Spittel\label{sec:HSmodel}}
+\subsection{Hansel and Spittel\label{sec:HSmodel}}
 %-------------------------------------------------------------------------
-The Hansel-Spittel model is one of the least known models in terms of its  integration in softwae for finite element simulation although the determination of its parameters is easier than the JC model.
+The Hansel-Spittel model is one of the least known models in terms of its  integration in software for finite element simulation although the determination of its parameters is easier than the JC model.
 A single programming command is sufficient for its identification.
@@
 The equation of the model is given by the following relation:
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/CompExpHS}
+\caption{Comparison between the experimental and predicted flow stresses by HS model}
+\label{fig:iCorrelationHS}
+\end{figure}
 \begin{equation}
@@
 The other coefficients $A$ and $m_j$ are model constants up to $m_5$ for our case.
-Comparison of predicted values of the HS model and experimental values is shown in Figure \ref{fig:iCorrelationHS} and Figure \ref{fig:eCorrelationHS}.
+Comparison of predicted values of the HS model and experimental values is shown in Figure \ref{fig:iCorrelationHS}.
 It appears that this model as well as the previous ones do not predict the experimental well and the gap is relatively large.
@@
 &         &             &		   &		 &			   &\\
-&$A_0(\text{GPa})$    &$m_1$        & $m_2$     & $m_3$   & $m_4$       &$m_5$\\
+Parameters&$A_0(\text{MPa})$    &$m_1$        & $m_2$     & $m_3$   & $m_4$       &$m_5$\\
 &         &             &		   &	     &	           &\\
 \hline
-Interpolation&$10.1777$&$-0.00384785$& $0.195671$&$0.183171$&$-0.0035643$&$-0.00059302$\\
-%\hdashline
-Extrapolation&$11.3176$&$-0.00388286$& $0.204999$&$0.19018$&$-0.00316225$&$-0.000658053$\\
+Values&$9254.77$&$-0.00375057$& $0.208975$&$0.184238$&$-0.00287837$&$-0.000583287$\\
 \hline
@@
 \end{table}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{newFigures/iCorrelationHS}
-\caption{Comparison between the experimental and predicted flow stresses by HS model for interpolation estimation}
-\label{fig:iCorrelationHS}
-\end{figure}
-\FloatBarrier
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{newFigures/eCorrelationHS}
-\caption{Comparison between the experimental and predicted flow stresses by HS model for extrapolation estimation}
-\label{fig:eCorrelationHS}
-\end{figure}
-\FloatBarrier
 %----------------------------------------------------------------------------------
-\subsubsection{Arrhenius model (AR model), \label{sec:ARmodel}}
+\subsection{Arrhenius model (AR model), \label{sec:ARmodel}}
 %----------------------------------------------------------------------------------
 The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material.
-Indeed, this model takes into account the physical phenomena that describe the behaviour of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot{\varepsilon}^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation.
+Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot{\varepsilon}^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation.
 This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature.
@@
 \end{equation}
-By replacing the relation (\ref{eq:ARmodel}) in the (\ref{eq:Zparam}) one it comes:
+By replacing the Equation (\ref{eq:ARmodel}) inton Equation (\ref{eq:Zparam}) it comes:
 \begin{equation}
@@
 \end{equation}
-Therefore the Equation (\ref{eq:Zparam1}) becomes and which is actually the Arrhenius model: 
+Therefore Equation (\ref{eq:Zparam1}) becomes and which is actually the Arhenius model: 
 \begin{equation}
@@
 To obtain the constitutive equation, all parameters $\alpha$, $Q$, $n_2$, and $A_3$ needed to be determined.
-The following part shows the calculation procedures of these material constants at $0.1$ strain as example.\\
+The following part shows the calculation procedures of these material constants at $\varepsilon^p = 0.1$ as example.
 Taking the natural logarithm of Equations (\ref{eq:ARmodel1}) and (\ref{eq:ARmodel2}), the following relationships can be obtained:
@@
 \end{equation}
-From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot{\varepsilon}^p)$  and $\sigma^y = f(\ln\mdot{\varepsilon}^p)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $0.1$ value of strain.
+From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot{\varepsilon}^p)$  and $\sigma^y = f(\ln\mdot{\varepsilon}^p)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$.
 It should be noted that later in this document all values of strain will be taken into account.
@@
 \end{figure}
-The values of those parameters are therefore equal to $n_1=4.93599$ and $\beta=0.150438$ ($\alpha=\beta/n_1 = 0.0220306$). 
-Taking the natural logarithm of Equation (\ref{eq:ARmodel}), the following relationship can be obtained:
+The values of those parameters are therefore equal to $n_1=6.78177$ and $\beta=0.150563$ ($\alpha=\beta/n_1 = 0.0222011$). 
+From Equation (\ref{eq:ARmodel}), the following relationship can be obtained:
 \begin{equation}
@@
 From Equation (\ref{eq:lnSinh}) and Equation (\ref{eq:parQ}) we can deduce the parameters $n_2 $ and $Q $ from the slopes of the functions $\ln \sinh(\alpha\sigma^y) = f(\ln \dot{\varepsilon}^p)$ and $\ln \sinh(\alpha\sigma^y) = g(1/T)$ as shown in Figure \ref{fig:LnSinhE} and Figure \ref{fig:LnSinhT}.
-Thus those values are $3.21374$ and $432.722\ KJ.mol^{-1}$ respectively.
+Thus those values are $4.94273$ and $437.385\ KJ.mol^{-1}$ respectively.
 \begin{figure}[!ht]
@@
 Hence the need to find a function for each coefficient for all temperatures and strains.
-Figure  \ref{fig:ARparameters} shows the relationships between $\alpha$, $Q$, $n$, $\ln A$ and true strain $\varepsilon^p$ for P20 alloy using leasquare method to fit the measured data.
+Figure  \ref{fig:ARparameters} shows the relationships between $\alpha$, $Q$, $n_2$, $\ln A$ and true strain $\varepsilon^p$ for AISI P20 alloy using leasquare method.
 For each parameter (whose strain dependant expressions are given by Equations \ref{eq:alpha}, \ref{eq:Q}, \ref{eq:n} and \ref{eq:lnA}), the values of constants are summarized in Table \ref{tab: ARparameters}.
-Figure \ref{fig:iCorrelationAR} and Figure\ref{fig:eCorrelationAR} are the comparison of predicted values of AR model and experimental values where the correlaton is good.
+Figure \ref{fig:iCorrelationAR} is the comparison of predicted values of AR model and experimental values where the correlaton is good.
 The gap between experimental and prediction is small.
-But for the strain rate $\mdot{\varepsilon}^p = 0.01$ and for the two low temperatures values, the AR model is not able to predict the softening.
+But for the strain rate $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ and for the two low temperatures values, the AR model is not able to predict the softening.
 \begin{equation}
@@
 \label{eq:n}
-n(\varepsilon^p) = n_0 + n_1\varepsilon^{{p^1}} + n_2\varepsilon^{p^2} + n_3\varepsilon^{p^3} + n_4\varepsilon^{p^4} + n_5\varepsilon^{p^5} + n_6\varepsilon^{p^6}
+n_2(\varepsilon^p) = n_{20} + n_{21}\varepsilon^{{p^1}} + n_{22}\varepsilon^{p^2} + n_{23}\varepsilon^{p^3} + n_{24}\varepsilon^{p^4} + n_{25}\varepsilon^{p^5} + n_{26}\varepsilon^{p^6}
 \end{equation}
@@
 \includegraphics[width=1.02\columnwidth]{newFigures/ARparameters}
-\caption{Relationships between $\alpha$ (a)  , $Q$ (b) , $n$ (c)  and $lnA$ (d)  with the true strain $\varepsilon^p$ by polynomial functions}
+\caption{Relationships between $\alpha$ (a)  , $Q$ (b) , $n_2$ (c)  and $lnA$ (d)  with the plastic strain $\varepsilon^p$ by polynomial functions}
 \label{fig:ARparameters}
@@
 &					  &				      &				        &\\
-&$\alpha$          & $Q (\times10^{6})$ & $n$      & $\ln A$\\
+Parameters&$\alpha$   &$Q (MJ.mol^{-1})$ &$n_2$                &$\ln A$\\
 &					  &				      &				        &\\
 \hline
-&$\alpha_0 = 0.0368199$ & $Q_0 = 0.451215$  & $n_0 = 4.52844$ & $\ln A_0 = 34.4714$\\
-&$\alpha_1 = -0.300454$ & $Q_1 = -0.526197$ & $n_1 = 15.6433$ & $\ln A_1 = -42.818$\\
-&$\alpha_2 = 2.19468$   & $Q_2 =5.99635 $ & $n_2 = -176.65$ & $\ln A_2 = 493.325$\\
-Interpolation&$\alpha_3 =-8.29695$ & $Q_3 =-37.4915 $  & $n_3 = 682.187$ & $\ln A_3 =-3095.19 $\\
-&$\alpha_4 = 16.8067$   & $Q_4 = 102.928$  & $n_4 = -1289.52$& $\ln A_4 = 8516.02$\\
-&$\alpha_5 = -17.2641$  & $Q_5 =-127.865$  & $n_5 = 1205.95$ & $\ln A_5 = -10594.8$\\
-&$\alpha_6 = 7.04353$   & $Q_6 = 59.2928$  & $n_6 =-446.166$ & $\ln A_6 = 4918.17$\\
-%\hdashline
-&$\alpha_0 = 0.0392338$ & $Q_0 = 0.437281$  & $n_0 = 4.3178$ & $\ln A_0 = 32.872$\\
-&$\alpha_1 =-0.323238$ & $Q_1 =-0.401528$ & $n_1 = 17.3196$ & $\ln A_1 = -32.2877$\\
-&$\alpha_2 = 2.38426$   & $Q_2 = 4.86745$ & $n_2 = -192.485$ & $\ln A_2 = 397.553$\\
-Extrapolation&$\alpha_3 = -9.04342$& $Q_3 = -33.2061$& $n_3 = 752.451$ & $\ln A_3 =-2725.91 $\\
-&$\alpha_4 = 18.34$   & $Q_4 = 95.0889$  & $n_4 = -1450.86$& $\ln A_4 = 7825.29$\\
-&$\alpha_5 = -18.8254$  & $Q_5 =-120.398$  & $n_5 = 1391.74$ & $\ln A_5 =-9924.46$\\
-&$\alpha_6 = 7.66332$   & $Q_6 = 56.2666$  & $n_6 =-530.417$ & $\ln A_6 = 4644.18$\\
+&$\alpha_0 = 0.03702$ & $Q_0 = 0.454825$  & $n_{20} = 4.49273$  & $\ln A_0 = 34.7431$\\
+&$\alpha_1 =-0.301107$& $Q_1 = -0.450492$ & $n_{21}=15.2803$    & $\ln A_1 =-36.826$\\
+&$\alpha_2 = 2.19877$ & $Q_2=4.76922 $    & $n_{22} =-170.126$  & $\ln A_2 =393.423$\\
+Values&$\alpha_3=-8.30819$&$Q_3 =-31.6016$& $n_{23} =651.241$   & $\ln A_3 =-2611.42$\\
+&$\alpha_4 = 16.823$  & $Q_4 = 89.8821$   & $n_{24} =-1225.15$  & $\ln A_4 =7436.98$\\
+&$\alpha_5 =-17.2732$ & $Q_5 =-113.829$   & $n_{25} =1143.54$   & $\ln A_5 =-9426.54$\\
+&$\alpha_6 =7.04342$  & $Q_6 = 53.3699$   & $n_{26} =-423.066$  & $\ln A_6 =4422.49$\\
 \hline
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/iCorrelationAR}
-\caption{Comparison between the experimental and predicted flow stresses by AR model for interpolation estimation}
+{newFigures/CompExpAR}
+\caption{Comparison between the experimental and predicted flow stresses by AR model}
 \label{fig:iCorrelationAR}
-\end{figure}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{newFigures/eCorrelationAR}
-\caption{Comparison between the experimental and predicted flow stresses by AR model for extrapolation estimation}
-\label{fig:eCorrelationAR}
 \end{figure}
@@
 %-------------------------------------------------------------------------
-\subsubsection{Proposed model (PTM model)\label{sec:ProposedModel}}
+\subsection{PTM model\label{sec:ProposedModel}}
 %--------------------------------------------------------------------------
@@
 The intrinsic functions of the model, which are the polynomial type functions, will determine the parameters of the model according to the degree of the polynomial, which provides a good fit for each function.
-The direct objective of this work being to demonstrate the ability of the neural network based model to override analytical models in the term of interpolation and extrapolation, it is important to point out that the PTM model can give better results than those presented in this work.
-For more details of this model we invite the reader to consult our previous work \cite{tize2022generalized}.
-The equation describing the PTM model is therefore given by:
+The equation describing the PTM model is therefore given by.
 \begin{equation}
@@
 \end{equation}
-where $A_i, B_j, C_k^l$ are the parameters of the model to be identified using the procedure proposed in  \cite{tize2022generalized}.
+where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM-parameters}) of the model to be identified using the procedure proposed in  \cite{tize2022generalized}.
 Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
 The larger these quantities are, the more parameters need to be identified for the PTM model.
+The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016-LNL} and for more details about this model  we invite the reader to read our previous work \cite{tize2022generalized}.
+Thus all the parametrers of this model are calcuted with $q=5$, $r=5$, $s=1$ and $t=5$.
 
-The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016-LNL} and according to the following three steps:
-\begin{itemize}
-\item \textbf{Step 1} : Determination of the two functions $I_1(\varepsilon^p)$ and $S_1(\varepsilon^p)$\\
-At the reference strain rate, \ie when $\mdot{\varepsilon}^p=\mdot{\varepsilon}_0$, Equation (\ref{eq:PTM-model}) is written as:
-\begin{equation}
-\sigma^y(\varepsilon^p,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right)
-\exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) \right]
-\end{equation}
-Taking the logarithm of each member of this equation we obtain:
-\begin{equation}
-\label{eq:I1S0}
-\ln \sigma^y(\varepsilon^p,T) = I_1(\varepsilon^p) + S_1(\varepsilon^p)\left(T-T_0\right)
-\end{equation}
-where:
-\begin{equation}
-\label{eq:I1S1}
-I_1(\varepsilon^p) = \ln\left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right)\qquad \text{and}\qquad S_1(\varepsilon^p) = \sum_{j=0}^{r}{B_j\varepsilon^{p^j}}
-\end{equation}
-Plotting the function $\ln \sigma^y(T)$ for a given value of $\varepsilon^p$ allows us to deduce $I_1(\varepsilon^p)$ and $S_1(\varepsilon^p)$ from the y-intercept and the slope, respectively.
-These functions are calculated for all plastic strain values $\varepsilon^p$ available in the experimental database.
-Analysis of those results allows us to propose some adequate values for the $q$ and $r$ quantities.
-Once those values have been selected, an identification procedure allow us to compute the $q$ parameters $A_i$ and $r$ parameters $B_j$ of the PTM model.
-\item \textbf{Step 2} : Determination of the function $S_2(\varepsilon^p,T)$ as polynomials depending on the temperature $T$\\
-Once the Step $1$ is done, it is possible to take the logarithm of the whole Equation (\ref{eq:PTM-model}) to obtain:
-\begin{equation}
-\ln \sigma^y(\varepsilon^p,\mdot{\varepsilon}^p,T) - I_1(\varepsilon^p) - S_1(\varepsilon^p)\left(T-T_0\right) = S_2(\varepsilon^p,T)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
-\label{eq:SlopeS2}
-\end{equation}
-where :
-\begin{equation}
-S_2 (\varepsilon^p,T)= \sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k
-\label{eq:S2_coefs}
-\end{equation}
-From this latter the plot of $\ln \sigma^y - I_1(\varepsilon^p) - S_1(\varepsilon^p)\left(T-T_0\right)$ versus $\ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows us to deduce $S_2(\varepsilon^p,T)$ as its slope for a given plastic strain value $\varepsilon^p$.
-The evolution of $S_2$ versus $\left(T-T_0\right)$ allows to find the same function for all plastic strains which is described in the polynomial forms of degree $k$ in Equation (\ref{eq:PTM-model}).
-The plastic strain $\varepsilon^p$ dependance of $S_2(\varepsilon^p,T)$ need to be evaluated.
-In the previous works \cite{Gao-2020-FBC, Yu-2020-FSM, Gurusamy-2017-PMZA, Samantaray-2009-CSJC, He-2014-MZA, Zhan-2014-CMF, Gupta-2013-CMP, Samantaray-2011-AMM} authors never took into account that step.
-\item \textbf{Step 3} : Determination of the coefficients of the function $S_2(\varepsilon^p,T)$ as polynomials depending on the plastic strain $\varepsilon^p$\\
-This step is a direct consequence of the previous one, which consists in determining each coefficient of the function $S_2(\varepsilon^p,T)$ as polynomial functions.
-Once we know the order of the polynomial that describes the function $S_2(\varepsilon^p,T)$, for each strain value the corresponding coefficients of  $S_2(\varepsilon^p,T)~\text{s}$hould be recorded in the empty lists initialized before.
-Thus, with the empty lists initialized, for a given strain value, it is necessary to go through all the temperatures and deduce the values of each coefficient of the function $S_2(\varepsilon^p,T)$ for this strain which will be recorded in the empty lists initialized at the beginning.
-Thus, an algorithm must be written which goes through all the values of the strains and adds to each list of coefficients of the polynomial $S_2(\varepsilon^p,T)$ the value deduced from the corresponding strain.
-It is therefore necessary to evaluate the dependence of each parameter (described by one list) on the strain in order to finally deduce its polynomial from which we also deduce its coefficients.
-This is how the operation is performed for all the lists.
-Finally, we calculate all the parameters of the proposed model.
-\end{itemize}
-Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM} and Figure \ref{fig:eCorrelationPTM}.
+Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}.
 The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$ the prediction in not quite good.
 The deviation between the predicted values and the experimental values is relatively good.
+\begin{table}[!h]
+\centering{}
+\caption{Parameters of PTM model\label{tab:PTM-parameters}}
+\scalebox{0.83}{
+\begin{tabular}{cc}
+\hline
+&   \\
+Parameters &Values\\
+&   \\
+\hline
+$A_0 (\text{MPa})$ & $62.314$ \\
+$A_1 (\text{MPa})$ & $559.827$ \\
+$A_2 (\text{MPa})$ & $-2160.03$ \\
+$A_3 (\text{MPa})$ & $4641.94,$ \\
+$A_4 (\text{MPa})$ & $-5193.06$ \\
+$A_5 (\text{MPa})$ & $2379.1$ \\
+$B_0 $   & $-0.0035805$\\
+$B_1 $   & $0.00282334$ \\
+$B_2 $   & $-0.00775301$\\
+$B_3 $   & $0.0085135$ \\
+$B_4 $   & $-0.00412815$\\
+$C_0^0 $ & $0.148304$ \\
+$C_0^1 $ & $-0.301958$ \\
+$C_0^2 $ & $2.2706$ \\
+$C_0^3 $ & $-5.33003$ \\
+$C_0^4 $ & $5.48971$ \\
+$C_0^5 $ & $-2.11566$\\
+$C_1^0 $ & $-3.74842\ \times10^{-7}$\\
+$C_1^1 $ & $0.00165233$\\
+$C_1^2 $ & $-0.00270485$ \\
+$C_1^3 $ & $-0.000483867$\\
+$C_1^4 $ & $0.00174818$ \\
+\hline
+\end{tabular}}
+\end{table}
 \begin{figure}[!ht]
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/iCorrelationPTM}
-\caption{Comparison between the experimental and predicted flow stresses by PTM model for interpolation estimation}
+{newFigures/CompExpPTM}
+\caption{Comparison between the experimental and predicted flow stresses by PTM model }
 \label{fig:iCorrelationPTM}
 \end{figure}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{newFigures/eCorrelationPTM}
-\caption{Comparison between the experimental and predicted flow stresses by PTM model for extrapolation estimation}
-\label{fig:eCorrelationPTM}
-\end{figure}
+\FloatBarrier
 
-\begin{table}[!h]
-\centering{}
-\caption{Parameters of the proposed model\label{tab:PTM-parameters}}
-\scalebox{1.2}{
-\begin{tabular}{ccc}
-\hline
-&  & \\
-Parameters & Interpolation &Extrapolation\\
-&  & \\
-\hline
-$A_0 (\text{MPa})$ & $62.314$ & $62.314$\\
-$A_1 (\text{MPa})$ & $559.827$ & $559.827$\\
-$A_2 (\text{MPa})$ & $-2160.03$ & $-2160.03$\\
-$A_3 (\text{MPa})$ & $4641.94,$ & $4641.94$\\
-$A_4 (\text{MPa})$ & $-5193.06$ & $-5193.06$\\
-$A_5 (\text{MPa})$ & $2379.1$ & $2379.1$\\
-$B_0 $ & $-0.0035805$ & $-0.0035805$\\
-$B_1 $ & $0.00282334$ & $0.00282334$\\
-$B_2 $ & $-0.00775301$ & $-0.00775301$\\
-$B_3 $ & $0.0085135$ & $0.0085135$\\
-$B_4 $ & $-0.00412815$ & $-0.00412815$\\
-$C_0^0 $ & $0.148539$ & $0.148766$\\
-$C_0^1 $ & $-0.302363$ & $-0.304798$\\
-$C_0^2 $ & $2.25845$ & $2.2891$\\
-$C_0^3 $ & $-5.2651$ & $-5.36673$\\
-$C_0^4 $ & $5.38382$ & $5.51053$\\
-$C_0^5 $ & $-2.05958$ & $-2.1115$\\
-$C_1^0 $ & $-4.3271\ \times10^{-7}$& $-9.92159\ \times10^{-7}$\\
-$C_1^1 $ & $0.00165983$& $0.00166581$\\
-$C_1^2 $ & $-0.00269801$ & $-0.00272071$\\
-$C_1^3 $ & $-0.000132085$& $-8.59293\ \times10^{-5}$\\
-$C_1^4 $ & $0.00182935$ & $0.00178989$\\
-\hline
-\end{tabular}}
-\end{table}
 %-------------------------------------------------------------------------
@@
 The architecture of the network used in this study is shown in Figure \ref{fig:ANN-scheme-2HL}.
-After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction as well as for interpolation and extrapolation where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot{\varepsilon}^p$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress.
+After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot{\varepsilon}^p$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress.
 The good performance of the model is found to be stable between $800$ and $1000$ epochs.
-This number was therefore used to train the model for both interpolation prediction and extrapolation.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]
+{newFigures/ANN-scheme-2HL}
+\caption{Multi-layer Artificial Neural Network architecture \cite{OPantale-2021-LGP}.}
+\label{fig:ANN-scheme-2HL}
+\end{figure}
 
@@
 $X_n$ is the normalized data of the corresponding $X$.
-The trained model once tested can be used to predict the behaviour of the AISI P20 alloy.
-Figure and Figure show a comparison between the predicted ﬂow stresses from ANN model and measured data from hot compression test as well as for interpolation prediction and extrapolation prediction.
-As shown from these two figures, the correlation between the experimental and the ANN prediction based is very good over the full range of data and the predicted data can well track the hardening and softening regions of the hot deforming material.
+The trained model once tested can be used to predict the behavior of the AISI P20 alloy.
+Figure \ref{fig:iCorrelationANN} show a comparison between the predicted ﬂow stresses from ANN model and measured data from hot compression test.
+As shown from this figures, the correlation between the experimental and the ANN prediction based is very good over the full range of data and the predicted data can well track the hardening and softening regions of the hot deforming material.
 Therefore, the ANN model can be used to simulate the hot deformation of this type of alloy.
@@
 The performance of this prediction will be much more appreciated when it comes to testing its ability to predict data that has not been used in either the training or the test data, but rather a full-fledged trial that we wish to validate the ANN prediction by experimental.
-This validation will be done both with a strain rate between those used in the training and in this case we will validate the interpolation and outside of the strain rates used in the training and in this case we will validate the extrapolation.
+This validation will be done both with a strain rate between and outside of those used for the training step.
 \begin{figure}[!ht]
 \centering
-\includegraphics[width=0.9\columnwidth]
-{newFigures/ANN-scheme-2HL}
-\caption{Multi-layer Artificial Neural Network architecture \cite{OPantale-2021-LGP}.}
-\label{fig:ANN-scheme-2HL}
+\includegraphics[width=1\columnwidth]
+{newFigures/CompExpANN}
+\caption{Comparison between the experimental and predicted flow stresses by ANN model }
+\label{fig:iCorrelationANN}
 \end{figure}
+\FloatBarrier
+%-------------------------------------------------------------------------
+\subsection{Comparison of analytical and ANN models\label{sec:Comparison}}
+%--------------------------------------------------------------------------
 \begin{figure}[!ht]
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/iCorrelationANN}
-\caption{Comparison between the experimental and predicted flow stresses by ANN model for interpolation estimation}
-\label{fig:iCorrelationANN}
+{newFigures/Correlation}
+\caption{Correlation coefficient ($R$) of models developped}
+\label{fig:Correlation}
 \end{figure}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{newFigures/eCorrelationANN}
-\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
-\label{fig:eCorrelationANN}
-\end{figure}
-
-%-------------------------------------------------------------------------
-\subsection{Comparison of analytical and ANN models\label{sec:Comparison}}
-%--------------------------------------------------------------------------
-%-------------------------------------------------------------------------
-\subsubsection{Identification results' comparison \label{sec:Interpolation}}
-%--------------------------------------------------------------------------
 The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($AARE$ generally known as $\AARE$ ) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($RMSE$) (Equation (\ref{eq:RMSE-expression})).
@@
 \label{eq:RMSE-expression}
-RMSE (\%) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2} \times 100
+RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2}
 \end{equation}
@@
 Indeed, they verify the predictability of a model term by term comparison of the relative error in relation to the real value of the variable \cite{srinivasulu2006comparative}.
-In the previous sections the correlations between the experimental flow stresses and those provided by the phenomenological and ANN models have been presented and the correlation coefficients $R$ for JC, MZA, HS, Arhenius, proposed and ANN models are $0.98405682$, $0.98786324$, $0.98413109$, $0.99829876$, $0.99524323$ and $0.99995003$, respectively in case of prediction for interpolation validation.
-These results show the Arrhenius-type, proposed and ANN models have better correlation between the experimental data and predicted results compared with the JC, MZA and HS models.
+Thus the correlation coefficients $R$ for JC, MZA, HS, Arhenius, proposed and ANN models are $0.98475$,  $0.99014$,  $0.98364$, $0.99839$, $0.99514$, and $0.99994$ respectively as shown on Figure \ref{fig:Correlation}.
+These results show that all models have a relatively good coefficient; this does not guarantee the validation of the prediction of these models.
+Hence the need to calculate the other two coefficients.
+All coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work are summarized in the Table \ref{tab:Coefsparams}.
 
-All coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work are summarized in the Table \ref{tab:Coefsparams}.
-From this Table, it can be seen that the ANN model has a good prediction than the analytical models.
-All this shows sufficiently that the ANN model is more effective in describing the behaviour of the AISI P20 alloy for high temperature deformation.
+From this table, it can be seen that the ANN model has a good prediction than the analytical models.
+All this shows sufficiently that the ANN model is more effective in describing the behavior of the AISI P20 alloy for high temperature deformation.
 This efficiency will therefore be validated on tests at two different selected strain rates.
 One between the minimum and the maximum strain rates used during identification or training for ANN model and another one outside higher than the maximum strain rate.
-This will validate the interpolation and extrapolation capability of the analytical and phenomenological models.
-The prediction results should lead to a better interpolation and extrapolation capability of the ANN model than phenomenological models as shown during identification step.
-The following sections will focus on this analysis.
-
-Another thing to be analysed from this table is the link between the values of the correlation coefficient $R$ and the values of $\AARE$.
+This will validate the interpolation and extrapolation capability of phenomenological and ANN models.
+The prediction results should lead to a better interpolation and extrapolation capability of the ANN model than phenomenological models as shown by identification.
+Another thing to be analysed from this table is the link between the values of the correlation coefficient $R$ and the values of $\AARE$ and $RMSE$.
 Indeed, as mentioned above, the $R$ coefficient does not necessarily mean a good prediction of the model but a good relationship of linearity between the experiment and the prediction.
 To ensure a good prediction of the model, it is necessary to add to $R$, the values of $\AARE$.
-For example and in the case of identification for the validation of the interpolation (the same analysis can be done for the validation of the extrapolation), let us observe carefully taht, the values of the coefficients $R$ are $99.0145\%$, $98.4131\%$ and those of $\AARE$ are $12.7939\%$ and $8.7309\%$ respectively for the MZA model and the HS model.
-This seems contradictory when the $R$ of HS is smaller than that of MZA, whereas for the $\AARE$ values it is the opposite case.
+From that table it can be seen the values of the coefficients $R$ are $99.014\%$, $98.364\%$, for $\AARE$ are $11.13020\%$ and $8.15103\%$ and those of $RMSE$ are $5.35079\ \text{MPa}$, and $6.45287\ \text{MPa}$ respectively for the MZA model and the HS model.
+This seems contradictory when the $R$ of HS is smaller than that of MZA, whereas for the $\AARE$ and $RMSE$ values it is the opposite case.
 This simply means that the HS model has a good prediction compared to the MZA model whereas in the framework of the linear correlation between the experiment and the prediction the MZA model makes it better.
-All this can be seen from the figures where we can observe the HS curves are indeed closer to the experimental than those of MZA while the points are scattered for HS model on the correlation curve.
-This validates the analysis made by \cite{phaniraj2003applicability, srinivasulu2006comparative} their works.
-The same analysis can be applied to the other results of the other models, although the ANN model is still the best for a good prediction.
+All this can be seen from the identification curves where we can observe the HS curves (Figure \ref{fig:iCorrelationHS}) are indeed closer to the experimental than those of MZA (Figure \ref{fig:iCorrelationMZA}) while the points are scattered for HS model on the correlation curve (Figure \ref{fig:Correlation}).
+This validates the analysis made by \cite{phaniraj2003applicability, srinivasulu2006comparative}.
+
 \begin{table}[h!]
 \centering{}
-\caption{Comparison of phenomenological an ANN models' accurary coefficients}
-\scalebox{0.88}{
-\begin{tabular}{lccccccc}
+\caption{Accurary coefficients of the developped models}
+\scalebox{0.92}{
+\begin{tabular}{lcccccc}
 \hline
-&		&		&         &             &		   &		  &						\\
-Coefficients&JC  & MZA  &HS  & Arhenius      & Proposed  &ANN &Expected predictions \\
-&				&				&         &             &		   &	     &	    \\
+&		&		&         &             &		   &		  		\\
+Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN  		    \\
+&				&				&         &             &		   &\\
 \hline
-$R(\%)$&$98.4057$&$99.0145$&$98.4131$&$99.8299$& $99.5243$&$99.9950$&Interpolation  \\
-$R(\%)$&$98.2519$&$98.7863$&$98.6493$&$99.7752$& $99.6527$&$99.9939$&Extrapolation  \\
-%\hdashline
-$\AARE(\%)$&$12.6421$&$12.7939$&$8.7309$&$3.7026$&$4.4781$&$0.6613$&Interpolation   \\
-$\AARE(\%)$&$12.7567$&$11.7289$&$7.6883$&$3.7875$&$3.9697$&$0.6219$&Extrapolation   \\
+$R(\%)$&$98.4745$&$99.0141$&$98.5682$&$99.839$& $99.5137$&$99.9994$ \\
+$\AARE(\%)$&$11.1667$&$11.13020$&$8.15103$&$3.30677$&$4.19549$&$0.81094$   \\
+$RMSE(\text{MPa})$&$6.30298$&$5.35079$&$6.45287$&$2.03275$&$3.59027$&$0.55158$\\
 \hline
@@
 \end{table}
+
 %-------------------------------------------------------------------------
-\subsubsection{Interpolation and extrapolation validation\label{sec:Extrapolation}}
+\section{Interpolation and extrapolation capability of phenomenological and ANN models \label{sec:inExtrapolation}}
 %--------------------------------------------------------------------------
-This section is devoted to the validation of the models developed in this study.
-To do so, let us briefly recall the purpose of this work in order to make it much clearly.
-Indeed, we have developed analytical models and a model based on the neural network for certain values of strain, strain rates and temperatures.
-The idea is therefore to randomly fix two strain rates while keeping the same values of strains and temperatures used for the development of the phenomenological and ANN models.
-Of these two strain rates, one must be between the minimum and maximum strain rate values already known and another must be higher.
-This is to test the interpolation and extrapolation capability of these models in order to validate them by experimental data.
-
+In this section we wish to test the performance of each identified model data interpolating and extrapolating data.
+Indeed, out of the $6$ strain rates used, one strain rate is voluntarily removed (while keeping the same values of strains and temperatures used for the development of the phenomenological and ANN models) so that it is inside or outside the other $5$ strain rates.
+For the strain rate which is between the minimum and the maximum of the $5$ other strain rates, we will thus test the capacity of each model to interpolate the data and for the one which is out of the $5$ other strain rates, the extrapolation capacity of the model is therefore validated.
+The validation procedure is as follows: $5$ strain rates are used to re-identify each model and once identified, it is used to predict the flow stress for the strain rate chosen for both interpolation and extrapolation.
+Validation is done with real data.
+The following subsections will highlight this procedure.
+\subsection{Interpolation validation}
 For the validation of the interpolation, the chosen strain rate is $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$.
@@
 This further shows the performance of the ANN model compared to the analytical models.
-All these results are summarised in Table \ref{tab:CoefInEx}.
+All these results are summarized in Table \ref{tab:inValid}.
 \begin{figure}[!ht]
@@
 {newFigures/inCombinaison1}
-\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
+\caption{Comparison between the experimental and predicted flow stresses by ANN model for interpolation estimation}
 \label{fig:inCombinaison1}
 \end{figure}
-For the validation of the extrapolation, the chosen strain rate is $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$.
-Figure \ref{fig:exCombinaison1} and Figure \ref{fig:exCombinaison2} show the comparison between the predictions  and the experimental.
-Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
-Again, the ANN model shows its ability to extrapolate data.
-This makes it possible to say that the ANN model remains the best tool to characterize the behaviour of a material subjected to certain deformation conditions.
-It can also be noted that the Arhenius and the proposed models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.78 \%$; which is not bad.
 \begin{figure}[!ht]
@@
 \end{figure}
-\FloatBarrier
 \begin{table}[h!]
 \centering{}
-\caption{Validatio of interpolation and extrapolation accurary coefficients}
+\caption{Accuracy coefficients of interpolation}
 \scalebox{0.92}{
-\begin{tabular}{lccccccc}
+\begin{tabular}{lcccccc}
 \hline
-&		&		&         &             &		   &		  &						\\
-Coefficients&JC  & MZA  &HS  & Arhenius      & Proposed  &ANN &Validations 		    \\
-&				&				&         &             &		   &	     &	    \\
+&		&		&         &             &		   &	\\
+Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN \\
+&				&				&         &             &	&\\
 \hline
-$R(\%)$&$99.0590$&$99.0821$&$97.6008$&$99.8417$& $99.8760$&$99.9439$&Interpolation  \\
-$R(\%)$&$99.2920$&$99.4879$&$93.9429$&$99.6870$& $99.7582$&$99.8047$&Extrapolation  \\
-%\hdashline
-$\AARE(\%)$&$4.2686$&$3.7440$&$6.1391$&$2.3321$&$2.7590$&$1.4018$&Interpolation   \\
-$\AARE(\%)$&$4.8988$&$3.4506$&$12.9939$&$3.2008$&$3.8845$&$1.7433$&Extrapolation   \\
+$R(\%)$&$99.0590$&$99.0821$&$97.6008$&$99.8417$& $99.8760$&$99.9439$  \\
+$\AARE(\%)$&$4.2686$&$3.7440$&$6.1391$&$2.3321$&$2.7590$&$1.4018$   \\
+$RMSE(\text{MPa})$&$4.1923$&$3.1856$&$82.6956$&$2.29891$&$2.4632$&$1.0228$ \\
 \hline
-\label{tab:CoefInEx}
+\label{tab:inValid}
+\end{tabular}}
+\end{table}
+\subsection{Extrapolation validation}
+For the validation of the extrapolation, the chosen strain rate is $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$.
+Figure \ref{fig:exCombinaison1} and Figure \ref{fig:exCombinaison2} show the comparison between the predictions  and the experimental.
+Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
+Again, the ANN model shows its ability to extrapolate data.
+This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions.
+It can also be noted that the Arhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
+\begin{table}[h!]
+\centering{}
+\caption{Accuracy coefficients of extrapolation}
+\scalebox{0.92}{
+\begin{tabular}{lcccccc}
+\hline
+&		&		&         &             &		   &	\\
+Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN \\
+&				&				&         &             &	&\\
+\hline
+$R(\%)$&$99.2920$&$99.4879$&$93.9429$&$99.6870$& $99.7582$&$99.8047$\\
+$\AARE(\%)$&$4.8988$&$3.4506$&$12.9939$&$3.2008$&$3.8845$&$1.7433$\\
+$RMSE(\text{MPa})$&$5.0943$&$4.3048$&$116.517$&$3.7035$&$4.3915$&$1.2513$ \\
+\hline
+\label{tab:exValid}
 \end{tabular}}
@@
 \FloatBarrier
-
 %---------------------------------------------------------------------
 \section{Conclusion \label{sec:Conclusion}}
-In order to describe the high temperature flow behaviour of the modified carbon alloy AISI P20, a comparative study between the phenomenologicalc(JC, MZA, HS, Arhenius and proposed) and ANN models was carried out.
-This study is done for temperatures ($1050$ -$1250^\circ$C ) and strain rates ($0.001 - 5.0\ \text{s}^{-1}$).
-Two fundamental works were compared in this study: on the one hand the flow stress prediction capacity of the studied models and on the other hand using these results to predict an interpolation test and another extrapolation test, all validated by experimental data.
-As a result of this study, the following conclusions were reached:
-\begin{itemize}
-\item The ﬂow stress increases with strain rate and decreases with the temperature, and strain has signiﬁcant inﬂuence on the ﬂow stress.
-Analytical models including JC, MZA, HS, Arhenius, proposed and ANN models were developed and a comparison of their predictions was made.
-Based on the prediction of those phenomenological models, JC and MZA models are not suitable for the AISI P20 alloy because their $\AARE$ are $12.64\%$ and $12.79\%$ respectively.
-But the Arhenius and proposed models can be used to describe the flow behabiour of this alloy because they have reduced $\AARE$ which are $3.78\%$ and $3.96\%$ respectively.
-For the ANN model, this coefficient is $0.62\%$.
-Regarding these results, the ANN model remains the best in terms of predicting the hot flow behaviour of the AISI P20 alloy to which can be added the Arhenius model and the proposed one.
-\item All models developed have been validated on interpolation and extrapolation tests.
-Based on these results, all models have a good prediction of the interpolation although the prediction of the ANN model remains the best.
-On the other hand, the analytical models do not have a good prediction of extrapolation compared to the ANN model.
-All these results are summarised in Table \ref{tab:CoefInEx}.
-\end{itemize}
-
+Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050^\circ$C - $1250^\circ$C, strains ($0.025$ - $0.7$), strain rates ($0.001\ \text{s}^{-1}$ - $5\ \text{s}^{-1}$) and the following conclusions were drawn.
+\begin{enumerate}
+\item The flow stress increases with decreasing temperature and increasing strain rate due to the competitive occurrence of dynamic softening and strain hardening mechanisms.
+The degree of DRX was discussed through the difference between the maximum and permanent stress, as well as the evolution of the microstructure which shows a partially complete DRX.
+At high strain rates it is difficult to visualise the DRX phenomenon on the flow curves due to the strain rate sensitivity of this phenomenon.
+A further study will focus on deep analysis of the microstructure of this steel alloy and its impact on mechanical properties.
+\item Five analytical models have been identified on this alloy and a model based on neural networks.
+Among the analytical models, the JC, HS and MZA models proved inappropriate for analysing the behavior of this material whereas the PTM and AR models showed their capacity since they have a relatively acceptable error ($ 3.2 \% $ and $ 3.8 \%$).
+As for the ANN model, it is largely reliable that the analytical models to predict the competitiveness of AISI P20.
+Therefore it may be advisable to use the ANN model when conducting a study involving this alloy under these experimental conditions.
+\item To test the performance of each model, a study is carried out to evaluate the interpolation and extrapolation capacity of the developed models.
+For the interpolation framework, all models have a good correlation with the experiment except the HS model but the ANN model shows a better correlation.
+For extrapolation of the data, the analytical models do not show good predictive capacity compared to the ANN model which still shows good extrapolation capacity.
+This further confirms what was demonstrated during his identification.
+\item As perspectives of this work, we will develop also an ANN model to characterize the microstructure in terms of DRX and phase formation such as fearrite, bainite and martensite as an example.
+This ANN model can therefore be compared to the most commonly used classical models such as the JMAK model.
+Therfore, this ANN model  will be implemented in FEM softwares such as Abaqus, Forge in order to validate it by doing a simulation.
+\end{enumerate}
 % \bibitem{}

### 2022-10-14 Article.tex
Clean directories and tracked files

@@
+% !TeX encoding = UTF-8
 \documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+\usepackage[utf8]{inputenc}
 \pagestyle{headings}
@@
 \usepackage{multirow}
+\usepackage{arydshln}
 \usepackage{xcolor}
 \usepackage{amssymb}
+\usepackage{subcaption}
+\usepackage{adjustbox}
+\usepackage{placeins}
+\usepackage[colorlinks = true]{hyperref}
 
@@
 % specify here the journal
-\journal{NAME OF THE JOURNAL}
+\journal{International Journal of Mechanical Sciences}
 
@@
 
-\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
-\newcommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
-\newcommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
-\newcommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
+%\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
+%\newcommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
+%\newcommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
+%\newcommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
 \newcommand{\dotp}{\boldsymbol{\cdot}}
-\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
+%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
 \newcommand{\e}[1]{\exp\left({#1}\right)}
@@
 \newcommand*{\eg}{e.g.,\@\xspace}
-\newcommand{\ERMS}{\text{E}_\text{RMS}}
+%\newcommand{\ERMS}{\text{E}_\text{RMS}}
 \newcommand{\AARE}{\text{E}_\text{AAR}}
-\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
-\DeclareMathOperator{\sech}{sech}
-\DeclareMathOperator{\sigmoid}{sig}
+\newcommand{\R}{\text{R}}
+%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
+%\DeclareMathOperator{\sech}{sech}
+%\DeclareMathOperator{\sigmoid}{sig}
 
+\usepackage{esvect}
 % Redefine the esvector shape to remove overlapping
-\usepackage{esvect}
 \def\traitfill@#1#2#3#4{%
@@
 \begin{document}
+\begin{frontmatter}
 
-\begin{frontmatter}{}
+\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation--extrapolation capacity validation}
 
-\title{TITLE}
-
+\author[LGP]{Pierre Tize Mha}
+\author[ETS]{Prashant Dhondapure}
+\author[LGP]{Amèvi Tongne}
+\author[ETS]{Mohammad Jahazi}
 \author[LGP]{Olivier Pantalé \corref{cor1}}
-
 \ead{Olivier.Pantale@enit.fr}
 \ead[url]{http://www.enit.fr}
-
-\author[LGP]{AUTHOR 2}
-
-\author[LGP]{AUTHOR 3}
 
@@
 \address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}
+\address[ETS]{Écolde de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}
 
 \begin{abstract}
-ABSTRACT
+The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$ ) and temperatures ($1050^\circ\text{C} -1250^\circ$C ).
+Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
+Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model.
+These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $AARE$ and the Root Mean Square Error ($RMSE$).
+From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy.
+For the strain rate ($\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050^\circ$C and $1100^\circ$C  while in the case of the PTM model, the strain rate  ($\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$) is not well described.
+This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high.
+Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot{\varepsilon}^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
+The results of the ANN model show a very good agreement between the predictions and the experiment.
+This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction.
+To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.
 \end{abstract}
+
 \begin{keyword}
-KEY1 \sep KEY2 \sep KEY3 \sep KEY4 \sep KEY5
+Zerilli--Armstrong flow law \sep Constitutive behavior \sep Arhenius--flow law \sep Hansel--Spittel flow law \sep Johnson--Cook flow law \sep interpolation \sep extrapolation \sep Artificial neural network
 \end{keyword}
 
-\end{frontmatter}{}
+\end{frontmatter}
+\linenumbers
 
-\section{SECTION 1\label{sec:SECTION1}}
+%--------------------------------------------------------------------------
+\section{Introduction\label{sec:Introduction}}
+%--------------------------------------------------------------------------
+Continuous casting and rolling mechanisms are an integral part of the technological methods of medium deformation through a continuous water-cooled crystalliser before entering a rolling mill.
+Some of the advantages of this method are increased metal yield, energy saving, improved quality of continuous casting and easier mechanisation and automation .
+Deformation being a very complex process involving both elastic and plastic deformation, is accompanied by high temperatures, high strain rates and complex and variable friction conditions \cite{he2013comparative}.
+However, a quantitative study and analysis of the deformation mechanism does not provide accurate analytical solutions .
+Moreover, conducting an experiment is not only time-consuming but also requires a high level of funding \cite{changizian2012high}.
+To mitigate these two factors (to name but a few), the Finite Element Method (FEM) is widely used in the analysis and optimisation of process parameters of various materials .
+FEM effectively compensates for the shortcomings of the analytical and experimental methods and plays an important role in the correct formulation of technological parameters, the improvement of product quality and the in-depth knowledge of the deformation mechanism.
+For example FEM has been widely used to simulate and analyse steel hot forming processes, such as forging, rolling, extrusion and casting but the accuracy of the numerical solution provided by FEM for this type of analysis strongly depends  on the accuracy of the constitutive equation of the concerned material \cite{qin2010modeling, mandal2009constitutive, ji2018constitutive}.
 
-BLA BLA \cite{mime}
+Indeed, hot forming processes are an essential step in the manufacturing of mechanical components and directly affect the ﬁnal quality of the products such as microstructure and mechanical properties \cite{ashtiani2012constitutive}.
+Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallisation), which very often occur during hot working, influence the quality of the deformation of materials.
+The complexity of the deformation behavior, however, leads to the fact that the deformation can only be calculated accurately by using a computer code to model the response of the material under the specified loading conditions.
+To this end, a mathematical formulation is often used to represent the flow behavior of materials in a form that can be used in finite element software \cite{lin2008prediction,wu2012flow}.
 
-\section{SECTION 2\label{sec:SECTION2}}
+Based on a thorough search of the literature many researchers have tried to predict the mechanical behavior of materials under hot working conditions using constitutive models.
+Therefore, various constitutive equations have been proposed to describe the flow behavior including phenomenological, physical and artiﬁcial neural network (ANN) models \cite{lin2011critical,shin2010phenomenological,rusinek2010thermo}.
+As for the semi-empirical models, they try to be at the border between the empirical and physical models.
+Among a large number of models, the Johnson--Cook (JC) \cite{Johnson-1983-Constitutive, Johnson-1985-Fracture} and the Zerilli--Armstrong (ZA) \cite{Zerilli-1987-Dislocation} models are the best known and available in finite element codes.
+The JC model is widely used because it is simple to use and has fewer constants to be determined \cite{Khan-2004-Quasi-static, NematNasser-2003-Thermomechanical}.
+However, this model, in its original state, contains some problems related to the phenomena describing the behavior of the material.
+We refer here to strain hardening, strain rate hardening, and thermal effects that are described separately in the JC model as analyzed by Jia \eal \cite{Jia-2021-Modified-JC}.
+To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998-Revised-JC, Vural-2003-Large, Lin-2010-Modified-JC, Lin-2012-Phenomenological, Li-2013-Modified-JC, Zhou-2019-Research, Zhang-2015-Modified-JC}.
+According to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988-Evaluation, Voyiadjis-2005-Microstructural, Dey-2007-Influence}.
+However, the drawbacks of this model are related to the temperature limit value of the test.
+Indeed, this model applies only to low strain rates and for temperatures limited to $0.6~T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005-Strain, Lee-2005-Strain, Chen-2007-Comparative, Lee-2006-Effects}.
+Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009-Thermo-viscoplastic}.
+In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{Nemat-2004-Plasticity, Lennon-2004-Influence, Muralli-2017-Performance, Cheng-2021-Modified-ZA, Muralli-2021-Finite}.
+The hyperbolic sine Arrhenius-type constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the microstructure of the studied material because   this model allows to estimate the deformation energy of the material \cite{jonas1969strength,zhang2012effect,mostafaei2012hot}.
+Its original formulation has been revised several times in order to properly describe the obtained experimental behavior.
+In order to increase the accuracy of the model, the effects of strain \cite{slooff2007constitutive, li2012flow, xu2013constitutive}, strain rate \cite{lin2008constitutive, mandal2009constitutive} have been considered by several researchers.
+For example, Sloof \eal \cite{slooff2007constitutive} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that their model could predict the high temperature flow behavior of a magnesium alloy.
+Lin \eal \cite{lin2008constitutive}, on the other hand, modified the model by introducing a strain rate compensation factor.
 
-BLA BLA
+The method based on artiﬁcial neural networks is an approach to predict the deformation behavior of materials under different conditions.
+ANN is in fact a method originally developed to simulate the biological processes of the human brain.
+And therefore it is not necessary to formulate a mathematical expresson and identify these parameters for this kind of model.
+The response of the deformation behavior of materials is highly non-linear at high temperatures, and many factors affecting the deformation behavior of materials are also non-linear; this makes the accuracy of the flow stress predicted by regression methods and the appropriate range is limited.
+Faced with these limitations, ANN models are therefore of interest.
+Indeed, ANNs are particularly suited to deal with complex and non-linear relationships; consequently, ANNs have been successfully applied to predict the deformation behavior of materials under hot working conditions.
+ANNs can provide a fundamentally different approach to statistical or numerical techniques for materials modelling and materials processing control.
 
-\section{SECTION 3\label{sec:SECTION3}}
-BLA BLA
+In this study, the high temperature deformation behavior of AISI P20 modified carbon steel subjected to compression tests will be highlighted.
+From the experimental data obtained, analytical models will be identified on the one hand in order to select the one that could better describe the behavior of this alloy and on the other hand, an ANN model is also developed and a comparative study between the analytical models and the ANN model will follow.
+A fundamental issue that will also be addressed in this work is the ability to interpolate and extrapolate of the developed models.
+Indeed, how do models behave when it comes to interpolating or extrapolating data that the model is never aware of ?
+the answer to this question will be well analyzed in this study.
 
+The main parts of this work are as follows: Section \ref{sec:Materials} presents the material et experimental procedure inverstigated in this study.
+Section \ref{sec:ConstLaws} is devoted to the presentation of the models developed and their comparative.
+Section \ref{sec:inExtrapolation} details the validation of interpolation and extrapolation capacity of each model developped.
+Conclusion and future works are detailed in Section \ref{sec:Conclusion}.
+
+%----------------------------------------------
+\section{ Materials and Experiments \label{sec:Materials}}
+%----------------------------------------------
+%----------------------------------------------
+\subsection{Experimental procedure}
+%----------------------------------------------
+The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table \ref{tab:Composition}.
+Cylindrical specimens were machined with an initial diameter of $10$ mm and a height of $15$ mm.
+Hot compression tests were conducted on a Gleeble-3800 thermo-simulator (Figure \ref{fig:Gleeble3800}), at temperatures of $1050^\circ$C,  $1050^\circ$C,  $1100^\circ$C,  $1150^\circ$C,  $1200^\circ$C and  $1250^\circ$C with strain rates of $0.001\ \text{s}^{-1}$, $0.01\ \text{s}^{-1}$, $0.1\ \text{s}^{-1}$, $1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$.
+Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during the tests.
+The samples were heated up to temperature $1260^\circ$C  and were held for $5$ min to eliminate thermal gradients.
+Then cooled to test temperature where the specimen is held $1$ minute before deformation.
+After compression the specimen is quencted rapidly for microstructure studies.
+The procedure of this test is illustrated in Figure \ref{fig:Heating} where $h_0$ and $R_0$ are the height and radius before compression; $h$, $R_M$, and $R_T$ are respectively the height, big radius and small radius of the specimen after compression.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]
+{newFigures/Gleeble-3}
+\caption{Gleeble 3800 simulator system}
+\label{fig:Gleeble3800}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]
+{newFigures/GleebleDesign}
+\caption{Schematic diagram of the experimental process.}
+\label{fig:Heating}
+\end{figure}
+\begin{table}[h!]
+\centering{}
+\caption{Chemical Composition of the AISI P20 Steel (Weight Percent)}
+\scalebox{0.9}{
+\begin{tabular}{lcccccccc}
+\hline
+C  &Mn & Mo   & Si   & Ni       &Cr& Cu & Other& Balance\\
+\hline
+ 0.30        &       0.89      &0.52		   &	0.34     &	 0.68          &1.86& 0.17& Microalloying& Iron\\
+\hline
+\label{tab:Composition}
+\end{tabular}}
+\end{table}
+%------------------------------------------------------------------------
+\subsection{Flow stress behavior}
+%------------------------------------------------------------------------
+The flow stress curves obtained from the compression tests performed on Gleeble-3800 simulator for each test condition are shown in Figure \ref{fig:rawData}.
+From these curves it can be seen that the flow stress increases with increasing strain rate but decreases with increasing temperature.
+It should be noted that the strain influences the flow stress.
+Indeed, for all strain values below $0.2$, the stress increases with strain before reaching a peak value at low strain rates and then decreases to maintain a stable value until the end of the test.
+The peak stress value increases with strain rate but decreases with temperature.
+For higher strain rates ($1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$) the flow stress increases throughout the test.
+The slight increase in stress at low strain rates when the strain is large is due to friction between the specimen and the grip during the test.
+For low strain rates, lubrication is lost over time and therefore friction occurs.
+This results in a progressive increase in stress.
+
+To explain the overall behavior of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX).
+At the beginning of the deformation, the amount of dislocations increases and they start to move, leading to a rapid increase in stress known as work-hardening.
+As the strain continues to increase, the dislocations are set in motion, leading to a stress relaxation phenomenon usually known as DRC.
+During this DRC mechanism, some of the dislocations are removed, due to their combination with another dislocation, or due to their integration into a grain boundary, and some of them are rearranged and formed as sub-grains within the initial grains.
+The combination of these dislocations moderates the increase of dislocations linked to strain hardening and thus controls the amount of energy stored in the material and manages the increase in flow stress.
+DRX consists of the germination of new grains, at the borders or inside the initial grains.
+These two phenomena therefore explain the different shapes of the flow stress curves observed for this alloy.
+As an example, the Figure \ref{fig:BeforeCompM} and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression.
+As observed on the flow curves, it can be seen that recrystallisation is almost complete for this temperature and strain rate.
+Indeed, most of the grain boundaries start to form new grains.
+The identification of the behavioral laws of these curves will be done in the next section in order to predict its behavior in any test condition.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/rawData}
+\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
+\label{fig:rawData}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]
+{newFigures/BeforeCompM}
+\caption{Optical micrograph of the AISI P20 steel before hot compression held during $5$ minutes at $1260^\circ$C}
+\label{fig:BeforeCompM}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]
+{newFigures/AfterCompM}
+\caption{Optical micrograph of AISI P20 alloy after howt compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
+\label{fig:AfterCompM}
+\end{figure}
+
+%-------------------------------------------------------------------------
+\section{Phenomenological constitutive flow laws\label{sec:ConstLaws}}
+%-------------------------------------------------------------------------
+The complete characterization of the thermomechanical behavior of a material is very important before its use in numerical simulations.
+This characterization usually involves experimental tests that serve as a basis for the development of constitutive laws.
+As mentioned in the introduction, many constitutive laws exist today, and selecting one of them based on explicit criteria hinders the development of computational models for new materials.
+Since the purpose of this work is to compare ANN model to analytical models it is important to justify the choice of the analytical models presented here among the many that exist in the literature.
+Among the most widely used analytical models nowadays, the Johnson-Cook (JC) model is the most used due to its simplicity of use linked to the number of its reduced and easy to obtain parameters.
+It should be noted that it is not the best model but the most integrated in finite element software.
+Hence the existence of several modified forms of this model.
+The Zerilli-Armstrong model, and particularly its modified form (MZA), is also widely known since it tries to provide solutions to the shortcomings of the JC model, particularly with regard to the coupling of physical parameters.
+Hence its use also in this study.
+In this perspective, the Hansel Spittel model (HS)is also one of the most widely used models in numerical simulation of casting and forging operations as it is integrated in the FORGE software.
+Also, the method of identifying its parameters is very simple to do as it is done in one step.
+Of course, it has its limitations as will be shown in the following sections.
+Furthermore, the Arrhenius model will be used in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter Q (the deformation activation energy coefficient) which is of great importance in the study related to the microstructural analysis of materials.
+The PTM model is also used in this study as it is a model whose formulation does not impose a number of parameters a priori and has proven its ability in our previous work and therefore we want to test it on this type of material as it is formulated to fit any material.
+%-------------------------------------------------------------------------
+\subsection{Johnson--Cook model\label{sec:JC}}
+%-------------------------------------------------------------------------
+The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature .
+However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
+Indeed, it is formulated by describing the effect of each physical parameter (strain, strain rate and temperature) separately as a factor in the mathematical expression of the model.
+Hence its inability to describe the phenomenon of temperature-induced softening.
+The equation that describes this model is given as follows \cite{johnson1985fracture}:
+\begin{equation}
+\label{eq: JCmodel}
+\sigma^y = \left(A + B\varepsilon^{p^n}\right)\left(1+C\ln\mdot{\varepsilon}^*\right)\left(1-T^{*^m}\right)
+\end{equation}
+Where $\sigma^y$ is the equivalent stress flow stress, $\varepsilon^p$ is the plastic strain, ($A=\sigma^y_0$) is the elastic limit of the material, $B$ is the strain hardening's coefficient, $n$ is the strain hardening's exponent.
+$C$ and $m$ are the material constants that describe the strain rate hardening and thermal softening exponent respectively.
+$\mdot{\varepsilon}^*$ is the dimensionless strain rate which is given by $\mdot{\varepsilon}^* = \mdot{\varepsilon^p}/\mdot{\varepsilon_0}$.
+$\mdot{\varepsilon^p}$ and $\mdot{\varepsilon_0}$ are strain rate and reference strain rate respectively.
+$T^{*^m} = (T-T_0)/(T_m - T_0)$ is homologous temperature where $T, T_m$ and $T_0$ are the déformation temperature, meltinng temperature (1460$^\circ$C in our case) and reference temperature respectively.
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050^\circ$C respectively and the value of $A$ is $43.0988$ MPa.
+Here after datailed the steps for determination of the JC model parameters.
+At the reference strain rate, Equation \ref{eq: JCmodel} becomes:
+\begin{equation}
+\label{eq: JCbn}
+\sigma^y = A + B\varepsilon^{p^n}
+\end{equation}
+Taking the natural logarithm on both sides of Equation \ref{eq: JCbn} we have:
+\begin{equation}
+\label{eq:JClog1}
+\ln\left(\sigma^y-A\right)= \ln(B) + n\ln\varepsilon^p
+\end{equation}
+By plotting $\ln(\sigma^y-A)$ \versus $\ln\varepsilon^p$ (Figure \ref{fig:JCSigmaAB}) from Equation \ref{eq:JClog1}, $n$ and $B$ can be obtained as slope and intercept respectively.
+Thus, for a strain value equal to $0.1$ the values of these two parameters are $n=0.313969$ and $B=114.518$.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]
+{newFigures/JCSigmaAB}
+\caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050^\circ$C and $0.1$}
+\label{fig:JCSigmaAB}
+\end{figure}
+\FloatBarrier
+Once the parameters $A$, $B$ and $n$ are known and at the reference temperature, the Equation \ref{eq: JCmodel} becomes:
+\begin{equation}
+\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 + C\ln\mdot{\varepsilon}^*
+\end{equation}
+From this equation one can easily obtain the parameter $C$ using the linear fitting method for each strain value and averaging all these values as shown in Figure \ref{fig:JCSigmaAB1} the value is $0.0995438$.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]
+{newFigures/JCSigmaAB1}
+\caption{Relationship between $\sigma^y/(A+ B\varepsilon^{p^n})$ and $\ln(\dot{\varepsilon}^*)$}
+\label{fig:JCSigmaAB1}
+\end{figure}
+The $m$ parameter is determined at the reference strain rate. Under this condition, the Equation \ref{eq: JCmodel} can be written as following:
+\begin{equation}
+\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 - T^{*^m}
+\end{equation}
+Taking the natural logarithm of both sides of that equation, we have:
+\begin{equation}
+\ln\left(1 - \frac{\sigma^y}{A + B\varepsilon^{p^n}}\right)  = m\ln T^*
+\end{equation}
+Plotting $\ln\left(1 - \frac{\sigma^y}{A + B\varepsilon^{p^n}}\right)$ as a function of $\ln T^*$ allows us to get the parameter $m$ as a slope for all values of the deformation by averaging them and the value is $0.898932$.
+Figure \ref{fig:JCSigmaT} illustrates this determination for some deformations.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.85\columnwidth]
+{newFigures/JCSigmaT}
+\caption{Relationship between $\ln\left(1 - \sigma^y/\left(A + B\varepsilon^{p^n}\right)\right)$ and $\ln T^*$}
+\label{fig:JCSigmaT}
+\end{figure}
+
+The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC}.
+The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates.
+The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates.
+All parameters of JC model are in Table \ref{tab: JCparameters}.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/CompExpJC}
+\caption{Comparison between the experimental and predicted flow stresses by JC model} 
+\label{fig:iCorrelationJC}
+\end{figure}
+\begin{table}[h!]
+\centering{}
+\caption{Parameters' constants of Johnson-Cook Model}
+\scalebox{1.2}{
+\begin{tabular}{lccccc}
+\hline
+&         &             &		   &		  &\\
+Parameters&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
+&         &             &		   &	     &	    \\
+\hline
+Values&$43.0988$&$114.518$& $0.313969$&$0.0995438$&$0.898932$\\
+\hline
+\label{tab: JCparameters}
+\end{tabular}}
+\end{table}
+%-------------------------------------------------------------------------
+\subsection{Modified Zerilli--Armstrong model\label{sec:MZA}}
+%-------------------------------------------------------------------------
+
+As mentioned earlier, Johnson--Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
+Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model \cite{Hull-2011-ITD}.
+But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic} proposed a modified form given by the following equation:
+\begin{equation}
+\label{eq:MZA-model}
+\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
+\end{equation}
+where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
+The formulation of the model can be found in \cite{Samantaray-2009-Thermo-viscoplastic} and determination of its parameters is sumarized as following.
+
+Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$.
+When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
+\begin{equation}
+\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
+\end{equation}
+Taking the logarithm of the previous relationship we have :
+\begin{equation}
+\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
+\end{equation}
+By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
+From the expression of $I_1$ we can write:
+\begin{equation}
+\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
+\end{equation}
+By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
+The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
+Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
+\begin{equation}
+\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
+\end{equation}
+with $S_2=C_5+C_6\left(T-T_0\right)$.
+Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
+The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}.
+It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
+The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
+That is aspect of the limitations of that model as presented in \cite{tize2022generalized}.
+\begin{table}[h!]
+\centering{}
+\caption{Parameters' constants of Modified--Zerilli-Armstrong Model}
+\scalebox{0.83}{
+\begin{tabular}{lllllllc}
+\hline
+&         &             &		   &		 &			   &&\\
+Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
+&         &             &		   &	     &	           &&\\
+\hline
+Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
+\hline
+\label{tab: MZAparameters}
+\end{tabular}}
+\end{table}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/CompExpMZA}
+\caption{Comparison between the experimental and predicted flow stresses by MZA model}
+\label{fig:iCorrelationMZA}
+\end{figure}
+\FloatBarrier
+
+%-------------------------------------------------------------------------
+\subsection{Hansel and Spittel\label{sec:HSmodel}}
+%-------------------------------------------------------------------------
+The Hansel-Spittel model is one of the least known models in terms of its  integration in software for finite element simulation although the determination of its parameters is easier than the JC model.
+A single programming command is sufficient for its identification.
+However, this model has some difficulties as it loses its accuracy when all parameters are taken into account.
+For this reason, several authors limit its use to $5$ or $6$ parameters \cite{chadha2018approach, rudnytskyj2020constitutive, el2015comparison}.
+In this paper the good predictions are with $5$ parameters summarized in Table \ref{tab: HSparameters}.
+The equation of the model is given by the following relation:
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/CompExpHS}
+\caption{Comparison between the experimental and predicted flow stresses by HS model}
+\label{fig:iCorrelationHS}
+\end{figure}
+\begin{equation}
+\sigma^y = Ae^{m_1T}\varepsilon^{p^{m_2}}\mdot{\varepsilon}^{p^{m_3}}e^{\frac{m_4}{\varepsilon^p}}(1+\varepsilon^p)^{m_5T}e^{m_6\varepsilon^p}\mdot{\varepsilon}^{p^{m_7T}}T^{m_8}
+\end{equation}
+Where $\sigma^y$ is the flow stess, $\varepsilon^p$ strain, $\mdot{\varepsilon}^p$ strain rate and $T$ temperature.
+The other coefficients $A$ and $m_j$ are model constants up to $m_5$ for our case.
+Comparison of predicted values of the HS model and experimental values is shown in Figure \ref{fig:iCorrelationHS}.
+It appears that this model as well as the previous ones do not predict the experimental well and the gap is relatively large.
+This shows that this model is not appropriate for the characterisation of this alloy.
+\begin{table}[h!]
+\centering{}
+\caption{Parameters' constants of Hansel and Spittel Model}
+\scalebox{0.9}{
+\begin{tabular}{llccccc}
+\hline
+&         &             &		   &		 &			   &\\
+Parameters&$A_0(\text{MPa})$    &$m_1$        & $m_2$     & $m_3$   & $m_4$       &$m_5$\\
+&         &             &		   &	     &	           &\\
+\hline
+Values&$9254.77$&$-0.00375057$& $0.208975$&$0.184238$&$-0.00287837$&$-0.000583287$\\
+\hline
+\label{tab: HSparameters}
+\end{tabular}}
+\end{table}
+%----------------------------------------------------------------------------------
+\subsection{Arrhenius model (AR model), \label{sec:ARmodel}}
+%----------------------------------------------------------------------------------
+The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material.
+Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot{\varepsilon}^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation.
+This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature.
+The following equations describe the Arrhenius model.
+\begin{equation}
+\label{eq:ARmodel1}
+\mdot{\varepsilon}^p = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)
+\end{equation}
+\begin{equation}
+\label{eq:ARmodel2}
+\mdot{\varepsilon}^p = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)
+\end{equation}
+\begin{equation}
+\label{eq:ARmodel}
+\mdot{\varepsilon}^p = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)
+\end{equation}
+Where $\mdot{\varepsilon}^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants.
+To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener--Hollomon parameter is introduced whose expression is given as follows:
+\begin{equation}
+\label{eq:Zparam}
+Z = \mdot{\varepsilon}^p\exp\left(\frac{Q}{RT}\right)
+\end{equation}
+By replacing the Equation (\ref{eq:ARmodel}) inton Equation (\ref{eq:Zparam}) it comes:
+\begin{equation}
+\label{eq:Zparam1}
+Z = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2} \qquad \Rightarrow \qquad \sinh(\alpha\sigma^y) = \left(\frac{Z}{A_3}\right)^{1/n_2}
+\end{equation}
+Furthermore, it is known that:
+\begin{equation}
+arc\sinh(x) = \ln\left(x + \sqrt{1+x^2}\right)
+\end{equation}
+Therefore Equation (\ref{eq:Zparam1}) becomes and which is actually the Arhenius model: 
+\begin{equation}
+\sigma^y = \frac{1}{\alpha}\ln\left\{\left(\frac{Z}{A_3}\right)^{1/n_2} + \left[1 + \left(\frac{Z}{A_3}\right)^{2/n_2}\right]^{1/2}\right\}
+\end{equation}
+To obtain the constitutive equation, all parameters $\alpha$, $Q$, $n_2$, and $A_3$ needed to be determined.
+The following part shows the calculation procedures of these material constants at $\varepsilon^p = 0.1$ as example.
+Taking the natural logarithm of Equations (\ref{eq:ARmodel1}) and (\ref{eq:ARmodel2}), the following relationships can be obtained:
+\begin{equation}
+\ln \sigma^y = \frac{1}{n_1}\ln \mdot{\varepsilon}^p -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}
+\end{equation}
+\begin{equation}
+\sigma^y = \frac{1}{\beta}\ln \mdot{\varepsilon}^p - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT} 
+\end{equation}
+From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot{\varepsilon}^p)$  and $\sigma^y = f(\ln\mdot{\varepsilon}^p)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$.
+It should be noted that later in this document all values of strain will be taken into account.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]{newFigures/LnAlp}
+\caption{Relationship between $\ln \sigma^y$ and $\ln \dot{\varepsilon}^p$}
+\label{fig:LnAlp}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhE0}
+\caption{Relationship between $\sigma^y$ and $\ln \dot{\varepsilon}^p$}
+\label{fig:LnSinhE0}
+\end{figure}
+The values of those parameters are therefore equal to $n_1=6.78177$ and $\beta=0.150563$ ($\alpha=\beta/n_1 = 0.0222011$). 
+From Equation (\ref{eq:ARmodel}), the following relationship can be obtained:
+\begin{equation}
+\label{eq:lnSinh}
+\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot{\varepsilon}^p  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
+\end{equation}
+By applying the chain derivative rule, we get the following relationship to calculate the energy activation coefficient $Q$.
+\begin{equation}
+\label{eq:parQ}
+Q = R\left[\frac{\partial \ln \mdot{\varepsilon}^p}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot{\varepsilon}^p}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
+\end{equation}
+From Equation (\ref{eq:lnSinh}) and Equation (\ref{eq:parQ}) we can deduce the parameters $n_2 $ and $Q $ from the slopes of the functions $\ln \sinh(\alpha\sigma^y) = f(\ln \dot{\varepsilon}^p)$ and $\ln \sinh(\alpha\sigma^y) = g(1/T)$ as shown in Figure \ref{fig:LnSinhE} and Figure \ref{fig:LnSinhT}.
+Thus those values are $4.94273$ and $437.385\ KJ.mol^{-1}$ respectively.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhE}
+\caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $\ln \dot{\varepsilon}^p$}
+\label{fig:LnSinhE}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhT}
+\caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $1/T$}
+\label{fig:LnSinhT}
+\end{figure}
+As these coefficients are calculated for a single strain value as example, it is possible to take into account their dependence on all strain values.
+Hence the need to find a function for each coefficient for all temperatures and strains.
+Figure  \ref{fig:ARparameters} shows the relationships between $\alpha$, $Q$, $n_2$, $\ln A$ and true strain $\varepsilon^p$ for AISI P20 alloy using leasquare method.
+For each parameter (whose strain dependant expressions are given by Equations \ref{eq:alpha}, \ref{eq:Q}, \ref{eq:n} and \ref{eq:lnA}), the values of constants are summarized in Table \ref{tab: ARparameters}.
+Figure \ref{fig:iCorrelationAR} is the comparison of predicted values of AR model and experimental values where the correlaton is good.
+The gap between experimental and prediction is small.
+But for the strain rate $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ and for the two low temperatures values, the AR model is not able to predict the softening.
+\begin{equation}
+\label{eq:alpha}
+\alpha(\varepsilon^p) = \alpha_0 + \alpha_1\varepsilon^{{p^1}} + \alpha_2\varepsilon^{p^2} + \alpha_3\varepsilon^{p^3} + \alpha_4\varepsilon^{p^4} + \alpha_5\varepsilon^{p^5} + \alpha_6\varepsilon^{p^6}
+\end{equation}
+\begin{equation}
+\label{eq:Q}
+Q(\varepsilon^p) = Q_0 + Q_1\varepsilon^{{p^1}} + Q_2\varepsilon^{p^2} + Q_3\varepsilon^{p^3} + Q_4\varepsilon^{p^4} + Q_5\varepsilon^{p^5} + Q_6\varepsilon^{p^6}
+\end{equation}
+\begin{equation}
+\label{eq:n}
+n_2(\varepsilon^p) = n_{20} + n_{21}\varepsilon^{{p^1}} + n_{22}\varepsilon^{p^2} + n_{23}\varepsilon^{p^3} + n_{24}\varepsilon^{p^4} + n_{25}\varepsilon^{p^5} + n_{26}\varepsilon^{p^6}
+\end{equation}
+\begin{equation}
+\label{eq:lnA}
+\ln A(\varepsilon^p) = \ln A_0 + \ln A_1\varepsilon^{{p^1}} + \ln A_2\varepsilon^{p^2} + \ln A_3\varepsilon^{p^3} + \ln A_4\varepsilon^{p^4} + \ln A_5\varepsilon^{p^5} + \ln A_6\varepsilon^{p^6}
+\end{equation}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]{newFigures/ARparameters}
+\caption{Relationships between $\alpha$ (a)  , $Q$ (b) , $n_2$ (c)  and $lnA$ (d)  with the plastic strain $\varepsilon^p$ by polynomial functions}
+\label{fig:ARparameters}
+\end{figure}
+\begin{table}[h!]
+\centering{}
+\caption{Parameters' constants of Arrhenius Model}
+\scalebox{0.95}{
+\begin{tabular}{lllll}
+\hline
+&					  &				      &				        &\\
+Parameters&$\alpha$   &$Q (MJ.mol^{-1})$ &$n_2$                &$\ln A$\\
+&					  &				      &				        &\\
+\hline
+&$\alpha_0 = 0.03702$ & $Q_0 = 0.454825$  & $n_{20} = 4.49273$  & $\ln A_0 = 34.7431$\\
+&$\alpha_1 =-0.301107$& $Q_1 = -0.450492$ & $n_{21}=15.2803$    & $\ln A_1 =-36.826$\\
+&$\alpha_2 = 2.19877$ & $Q_2=4.76922 $    & $n_{22} =-170.126$  & $\ln A_2 =393.423$\\
+Values&$\alpha_3=-8.30819$&$Q_3 =-31.6016$& $n_{23} =651.241$   & $\ln A_3 =-2611.42$\\
+&$\alpha_4 = 16.823$  & $Q_4 = 89.8821$   & $n_{24} =-1225.15$  & $\ln A_4 =7436.98$\\
+&$\alpha_5 =-17.2732$ & $Q_5 =-113.829$   & $n_{25} =1143.54$   & $\ln A_5 =-9426.54$\\
+&$\alpha_6 =7.04342$  & $Q_6 = 53.3699$   & $n_{26} =-423.066$  & $\ln A_6 =4422.49$\\
+\hline
+\label{tab: ARparameters}
+\end{tabular}}
+\end{table}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/CompExpAR}
+\caption{Comparison between the experimental and predicted flow stresses by AR model}
+\label{fig:iCorrelationAR}
+\end{figure}
+\FloatBarrier
+%-------------------------------------------------------------------------
+\subsection{PTM model\label{sec:ProposedModel}}
+%--------------------------------------------------------------------------
+The PTM model is a generalized formulation of the MZA model.
+Indeed, the shortcomings of the MZA model are taken into account in this formulation, which makes the model flexible for any type of studied material as it does not require a limited number of parameters.
+The intrinsic functions of the model, which are the polynomial type functions, will determine the parameters of the model according to the degree of the polynomial, which provides a good fit for each function.
+The equation describing the PTM model is therefore given by.
+\begin{equation}
+\label{eq:PTM-model}
+\sigma^y(\varepsilon^p,\mdot{\varepsilon}^p,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
+\end{equation}
+where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM-parameters}) of the model to be identified using the procedure proposed in  \cite{tize2022generalized}.
+Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
+The larger these quantities are, the more parameters need to be identified for the PTM model.
+The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016-LNL} and for more details about this model  we invite the reader to read our previous work \cite{tize2022generalized}.
+Thus all the parametrers of this model are calcuted with $q=5$, $r=5$, $s=1$ and $t=5$.
+
+Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}.
+The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$ the prediction in not quite good.
+The deviation between the predicted values and the experimental values is relatively good.
+\begin{table}[!h]
+\centering{}
+\caption{Parameters of PTM model\label{tab:PTM-parameters}}
+\scalebox{0.83}{
+\begin{tabular}{cc}
+\hline
+&   \\
+Parameters &Values\\
+&   \\
+\hline
+$A_0 (\text{MPa})$ & $62.314$ \\
+$A_1 (\text{MPa})$ & $559.827$ \\
+$A_2 (\text{MPa})$ & $-2160.03$ \\
+$A_3 (\text{MPa})$ & $4641.94,$ \\
+$A_4 (\text{MPa})$ & $-5193.06$ \\
+$A_5 (\text{MPa})$ & $2379.1$ \\
+$B_0 $   & $-0.0035805$\\
+$B_1 $   & $0.00282334$ \\
+$B_2 $   & $-0.00775301$\\
+$B_3 $   & $0.0085135$ \\
+$B_4 $   & $-0.00412815$\\
+$C_0^0 $ & $0.148304$ \\
+$C_0^1 $ & $-0.301958$ \\
+$C_0^2 $ & $2.2706$ \\
+$C_0^3 $ & $-5.33003$ \\
+$C_0^4 $ & $5.48971$ \\
+$C_0^5 $ & $-2.11566$\\
+$C_1^0 $ & $-3.74842\ \times10^{-7}$\\
+$C_1^1 $ & $0.00165233$\\
+$C_1^2 $ & $-0.00270485$ \\
+$C_1^3 $ & $-0.000483867$\\
+$C_1^4 $ & $0.00174818$ \\
+\hline
+\end{tabular}}
+\end{table}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/CompExpPTM}
+\caption{Comparison between the experimental and predicted flow stresses by PTM model }
+\label{fig:iCorrelationPTM}
+\end{figure}
+\FloatBarrier
+
+%-------------------------------------------------------------------------
+\subsection{Artificial neural network model\label{sec:ANNmodel}}
+%--------------------------------------------------------------------------
+The Artificial Neural Network model (ANN) is a mathematical formulation widely used in many fields today for better prediction.
+It is a model based on the principle of minimisation where it improves from the progressive decrease of the error during the learning process.
+Typically an ANN model contains an input layer, an output layer and hidden layers.
+Each hidden layer is connected to the one before it and the one after it via neurons.
+Indeed, all neurons in the $k$ layer are connected to each neuron in the ($k+1$ ) layer.
+To each layer is added another parameter called bias.
+As said the principle of the ANN model is therefore based on the minimisation of the difference between the value obtained from the output of the network and the expected value.
+Indeed, once the error is calculated, it is propagated back to the input layer in order to update the model parameters via the minimisation algorithms.
+In our case, the ADAM algorithm is used.
+The architecture of the network used in this study is shown in Figure \ref{fig:ANN-scheme-2HL}.
+After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot{\varepsilon}^p$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress.
+The good performance of the model is found to be stable between $800$ and $1000$ epochs.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.9\columnwidth]
+{newFigures/ANN-scheme-2HL}
+\caption{Multi-layer Artificial Neural Network architecture \cite{OPantale-2021-LGP}.}
+\label{fig:ANN-scheme-2HL}
+\end{figure}
+
+In this study $700$ of data were used; $80\%$ (560) are randomly selected for training and $20\%$ (140) for testing.
+Before learning, a normalisation of the data is required in order to have all data between $0$ and $1$.
+The Equation is widely used for normalization.
+\begin{equation}
+X_n = \frac{X - X_{min}}{X_{max} - X_{min}}
+\end{equation}
+Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot{\varepsilon}^p/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively.
+$X_n$ is the normalized data of the corresponding $X$.
+The trained model once tested can be used to predict the behavior of the AISI P20 alloy.
+Figure \ref{fig:iCorrelationANN} show a comparison between the predicted ﬂow stresses from ANN model and measured data from hot compression test.
+As shown from this figures, the correlation between the experimental and the ANN prediction based is very good over the full range of data and the predicted data can well track the hardening and softening regions of the hot deforming material.
+Therefore, the ANN model can be used to simulate the hot deformation of this type of alloy.
+This was not necessarily the case with the analytical models.
+The performance of this prediction will be much more appreciated when it comes to testing its ability to predict data that has not been used in either the training or the test data, but rather a full-fledged trial that we wish to validate the ANN prediction by experimental.
+This validation will be done both with a strain rate between and outside of those used for the training step.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1\columnwidth]
+{newFigures/CompExpANN}
+\caption{Comparison between the experimental and predicted flow stresses by ANN model }
+\label{fig:iCorrelationANN}
+\end{figure}
+\FloatBarrier
+%-------------------------------------------------------------------------
+\subsection{Comparison of analytical and ANN models\label{sec:Comparison}}
+%--------------------------------------------------------------------------
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/Correlation}
+\caption{Correlation coefficient ($R$) of models developped}
+\label{fig:Correlation}
+\end{figure}
+The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($AARE$ generally known as $\AARE$ ) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($RMSE$) (Equation (\ref{eq:RMSE-expression})).
+\begin{equation}
+\label{eq:R-expression}
+\R(\%) = \frac{\displaystyle\sum_{i=1}^{N}{\left(E_i - \overline{E}\right)\left(P_i - \overline{P}\right)}}{\sqrt{\displaystyle\sum_{i=1}^{N}\left(E_i - \overline{E}\right)^2 .\displaystyle\sum_{i=1}^{N}\left(P_i - \overline{P}\right)^2}}\times 100
+\end{equation}
+\begin{equation}
+\label{eq:AARE-expression}
+\AARE(\%) = \frac{1}{N}\displaystyle\sum_{i=1}^{N} \displaystyle\left\lvert\frac{E_i- P_i}{E_i} \right\rvert\times 100
+\end{equation}
+\begin{equation}
+\label{eq:RMSE-expression}
+RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2}
+\end{equation}
+Where $E_i$ is the experimental value and $P_i$ is the predicted value of the constitutive law (phenomenological and ANN models), $\overline{E}$ and $\overline{P}$ are the mean values of the experimental and predicted values, respectively.
+
+The correlation coefficient $R$ is generally used to show the degree of linearity between the experimental and predicted values.
+The model sometimes tends to be biased towards low and high values.
+Therefore, a good (high) value of $R$ does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction \cite{phaniraj2003applicability}.
+On the other hand, other coefficients ($\AARE$ and $RMSE$) are used to estimate the predictive capacity of the model because they are considered unbiased as well as for low and high values.
+Indeed, they verify the predictability of a model term by term comparison of the relative error in relation to the real value of the variable \cite{srinivasulu2006comparative}.
+Thus the correlation coefficients $R$ for JC, MZA, HS, Arhenius, proposed and ANN models are $0.98475$,  $0.99014$,  $0.98364$, $0.99839$, $0.99514$, and $0.99994$ respectively as shown on Figure \ref{fig:Correlation}.
+These results show that all models have a relatively good coefficient; this does not guarantee the validation of the prediction of these models.
+Hence the need to calculate the other two coefficients.
+All coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work are summarized in the Table \ref{tab:Coefsparams}.
+
+From this table, it can be seen that the ANN model has a good prediction than the analytical models.
+All this shows sufficiently that the ANN model is more effective in describing the behavior of the AISI P20 alloy for high temperature deformation.
+This efficiency will therefore be validated on tests at two different selected strain rates.
+One between the minimum and the maximum strain rates used during identification or training for ANN model and another one outside higher than the maximum strain rate.
+This will validate the interpolation and extrapolation capability of phenomenological and ANN models.
+The prediction results should lead to a better interpolation and extrapolation capability of the ANN model than phenomenological models as shown by identification.
+Another thing to be analysed from this table is the link between the values of the correlation coefficient $R$ and the values of $\AARE$ and $RMSE$.
+Indeed, as mentioned above, the $R$ coefficient does not necessarily mean a good prediction of the model but a good relationship of linearity between the experiment and the prediction.
+To ensure a good prediction of the model, it is necessary to add to $R$, the values of $\AARE$.
+From that table it can be seen the values of the coefficients $R$ are $99.014\%$, $98.364\%$, for $\AARE$ are $11.13020\%$ and $8.15103\%$ and those of $RMSE$ are $5.35079\ \text{MPa}$, and $6.45287\ \text{MPa}$ respectively for the MZA model and the HS model.
+This seems contradictory when the $R$ of HS is smaller than that of MZA, whereas for the $\AARE$ and $RMSE$ values it is the opposite case.
+This simply means that the HS model has a good prediction compared to the MZA model whereas in the framework of the linear correlation between the experiment and the prediction the MZA model makes it better.
+All this can be seen from the identification curves where we can observe the HS curves (Figure \ref{fig:iCorrelationHS}) are indeed closer to the experimental than those of MZA (Figure \ref{fig:iCorrelationMZA}) while the points are scattered for HS model on the correlation curve (Figure \ref{fig:Correlation}).
+This validates the analysis made by \cite{phaniraj2003applicability, srinivasulu2006comparative}.
+
+\begin{table}[h!]
+\centering{}
+\caption{Accurary coefficients of the developped models}
+\scalebox{0.92}{
+\begin{tabular}{lcccccc}
+\hline
+&		&		&         &             &		   &		  		\\
+Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN  		    \\
+&				&				&         &             &		   &\\
+\hline
+$R(\%)$&$98.4745$&$99.0141$&$98.5682$&$99.839$& $99.5137$&$99.9994$ \\
+$\AARE(\%)$&$11.1667$&$11.13020$&$8.15103$&$3.30677$&$4.19549$&$0.81094$   \\
+$RMSE(\text{MPa})$&$6.30298$&$5.35079$&$6.45287$&$2.03275$&$3.59027$&$0.55158$\\
+\hline
+\label{tab:Coefsparams}
+\end{tabular}}
+\end{table}
+
+%-------------------------------------------------------------------------
+\section{Interpolation and extrapolation capability of phenomenological and ANN models \label{sec:inExtrapolation}}
+%--------------------------------------------------------------------------
+In this section we wish to test the performance of each identified model data interpolating and extrapolating data.
+Indeed, out of the $6$ strain rates used, one strain rate is voluntarily removed (while keeping the same values of strains and temperatures used for the development of the phenomenological and ANN models) so that it is inside or outside the other $5$ strain rates.
+For the strain rate which is between the minimum and the maximum of the $5$ other strain rates, we will thus test the capacity of each model to interpolate the data and for the one which is out of the $5$ other strain rates, the extrapolation capacity of the model is therefore validated.
+The validation procedure is as follows: $5$ strain rates are used to re-identify each model and once identified, it is used to predict the flow stress for the strain rate chosen for both interpolation and extrapolation.
+Validation is done with real data.
+The following subsections will highlight this procedure.
+\subsection{Interpolation validation}
+For the validation of the interpolation, the chosen strain rate is $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$.
+The Figure \ref{fig:inCombinaison} shows the comparison between the predictions of the analytical and ANN models and the experiment.
+It appears from these Figures that all models have relatively good predictions but the ANN model remains the best because the value of its $\AARE$ is $1.4\%$ while it is between $2.33\%$ and $6.13\%$ for the analytical models.
+This further shows the performance of the ANN model compared to the analytical models.
+All these results are summarized in Table \ref{tab:inValid}.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1.02\columnwidth]
+{newFigures/inCombinaison}
+\caption{Comparison between the experimental and predicted flow stresses by ANN model for interpolation estimation}
+\label{fig:inCombinaison}
+\end{figure}
+\begin{table}[h!]
+\centering{}
+\caption{Accuracy coefficients of interpolation}
+\scalebox{0.92}{
+\begin{tabular}{lcccccc}
+\hline
+&		&		&         &             &		   &	\\
+Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN \\
+&				&				&         &             &	&\\
+\hline
+$R(\%)$&$99.0590$&$99.0821$&$97.6008$&$99.8417$& $99.8760$&$99.9439$  \\
+$\AARE(\%)$&$4.2686$&$3.7440$&$6.1391$&$2.3321$&$2.7590$&$1.4018$   \\
+$RMSE(\text{MPa})$&$4.1923$&$3.1856$&$82.6956$&$2.29891$&$2.4632$&$1.0228$ \\
+\hline
+\label{tab:inValid}
+\end{tabular}}
+\end{table}
+\subsection{Extrapolation validation}
+For the validation of the extrapolation, the chosen strain rate is $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$.
+Figure \ref{fig:exCombinaison} shows the comparison between the predictions  and the experimental.
+Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
+Again, the ANN model shows its ability to extrapolate data.
+This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions.
+It can also be noted that the Arhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
+\begin{table}[h!]
+\centering{}
+\caption{Accuracy coefficients of extrapolation}
+\scalebox{0.92}{
+\begin{tabular}{lcccccc}
+\hline
+&		&		&         &             &		   &	\\
+Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN \\
+&				&				&         &             &	&\\
+\hline
+$R(\%)$&$99.2920$&$99.4879$&$93.9429$&$99.6870$& $99.7582$&$99.8047$\\
+$\AARE(\%)$&$4.8988$&$3.4506$&$12.9939$&$3.2008$&$3.8845$&$1.7433$\\
+$RMSE(\text{MPa})$&$5.0943$&$4.3048$&$116.517$&$3.7035$&$4.3915$&$1.2513$ \\
+\hline
+\label{tab:exValid}
+\end{tabular}}
+\end{table}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.91\columnwidth]
+{newFigures/exCombinaison}
+\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
+\label{fig:exCombinaison}
+\end{figure}
+\FloatBarrier
+%---------------------------------------------------------------------
+\section{Conclusion \label{sec:Conclusion}}
+Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050^\circ$C - $1250^\circ$C, strains ($0.025$ - $0.7$), strain rates ($0.001\ \text{s}^{-1}$ - $5\ \text{s}^{-1}$) and the following conclusions were drawn.
+\begin{enumerate}
+\item The flow stress increases with decreasing temperature and increasing strain rate due to the competitive occurrence of dynamic softening and strain hardening mechanisms.
+The degree of DRX was discussed through the difference between the maximum and permanent stress, as well as the evolution of the microstructure which shows a partially complete DRX.
+At high strain rates it is difficult to visualise the DRX phenomenon on the flow curves due to the strain rate sensitivity of this phenomenon.
+A further study will focus on deep analysis of the microstructure of this steel alloy and its impact on mechanical properties.
+\item Five analytical models have been identified on this alloy and a model based on neural networks.
+Among the analytical models, the JC, HS and MZA models proved inappropriate for analysing the behavior of this material whereas the PTM and AR models showed their capacity since they have a relatively acceptable error ($ 3.2 \% $ and $ 3.8 \%$).
+As for the ANN model, it is largely reliable that the analytical models to predict the competitiveness of AISI P20.
+Therefore it may be advisable to use the ANN model when conducting a study involving this alloy under these experimental conditions.
+\item To test the performance of each model, a study is carried out to evaluate the interpolation and extrapolation capacity of the developed models.
+For the interpolation framework, all models have a good correlation with the experiment except the HS model but the ANN model shows a better correlation.
+For extrapolation of the data, the analytical models do not show good predictive capacity compared to the ANN model which still shows good extrapolation capacity.
+This further confirms what was demonstrated during his identification.
+\item As perspectives of this work, we will develop also an ANN model to characterize the microstructure in terms of DRX and phase formation such as fearrite, bainite and martensite as an example.
+This ANN model can therefore be compared to the most commonly used classical models such as the JMAK model.
+Therfore, this ANN model  will be implemented in FEM softwares such as Abaqus, Forge in order to validate it by doing a simulation.
+\end{enumerate}
+% \bibitem{}
 \bibliographystyle{elsarticle-num}
-\addcontentsline{toc}{section}{\refname}
-\bibliography{bibtex}
-
+\bibliography{Bibliography}
+%\end{thebibliography}
 \end{document}
+\endinput

### 2022-10-14 Article.tex
Initial clean of the TeX file

@@
 
-%\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
-%\newcommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
-%\newcommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
-%\newcommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
 \newcommand{\dotp}{\boldsymbol{\cdot}}
@@
 \newcommand*{\eg}{e.g.,\@\xspace}
-%\newcommand{\ERMS}{\text{E}_\text{RMS}}
+\newcommand{\RMSE}{\text{E}_\text{RMS}}
 \newcommand{\AARE}{\text{E}_\text{AAR}}
@@
 \begin{abstract}
-The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$ ) and temperatures ($1050^\circ\text{C} -1250^\circ$C ).
+The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050^\circ\text{C} -1250^\circ$C).
 Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
 Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model.
-These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $AARE$ and the Root Mean Square Error ($RMSE$).
+These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$).
 From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy.
@@
 \includegraphics[width=0.9\columnwidth]
-{newFigures/Gleeble-3}
+{Figures/Gleeble-3800}
 \caption{Gleeble 3800 simulator system}
@@
 \includegraphics[width=0.9\columnwidth]
-{newFigures/GleebleDesign}
+{Figures/GleebleDesign}
 \caption{Schematic diagram of the experimental process.}
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/rawData}
+{Figures/rawData}
 \caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
@@
 \includegraphics[width=0.9\columnwidth]
-{newFigures/BeforeCompM}
+{Figures/BeforeCompM}
 \caption{Optical micrograph of the AISI P20 steel before hot compression held during $5$ minutes at $1260^\circ$C}
@@
 \includegraphics[width=0.9\columnwidth]
-{newFigures/AfterCompM}
-\caption{Optical micrograph of AISI P20 alloy after howt compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
+{Figures/AfterCompM}
+\caption{Optical micrograph of AISI P20 alloy after hot compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
 \label{fig:AfterCompM}
@@
 \includegraphics[width=0.9\columnwidth]
-{newFigures/JCSigmaAB}
+{Figures/JCSigmaAB}
 \caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050^\circ$C and $0.1$}
@@
 \includegraphics[width=0.9\columnwidth]
-{newFigures/JCSigmaAB1}
+{Figures/JCSigmaAB1}
 \caption{Relationship between $\sigma^y/(A+ B\varepsilon^{p^n})$ and $\ln(\dot{\varepsilon}^*)$}
@@
 \includegraphics[width=0.85\columnwidth]
-{newFigures/JCSigmaT}
+{Figures/JCSigmaT}
 \caption{Relationship between $\ln\left(1 - \sigma^y/\left(A + B\varepsilon^{p^n}\right)\right)$ and $\ln T^*$}
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/CompExpJC}
+{Figures/CompExpJC}
 \caption{Comparison between the experimental and predicted flow stresses by JC model}
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/CompExpMZA}
+{Figures/CompExpMZA}
 \caption{Comparison between the experimental and predicted flow stresses by MZA model}
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/CompExpHS}
+{Figures/CompExpHS}
 \caption{Comparison between the experimental and predicted flow stresses by HS model}
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{newFigures/LnAlp}
+\includegraphics[width=0.9\columnwidth]{Figures/LnAlp}
 \caption{Relationship between $\ln \sigma^y$ and $\ln \dot{\varepsilon}^p$}
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhE0}
+\includegraphics[width=0.9\columnwidth]{Figures/LnSinhE0}
 \caption{Relationship between $\sigma^y$ and $\ln \dot{\varepsilon}^p$}
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhE}
+\includegraphics[width=0.9\columnwidth]{Figures/LnSinhE}
 \caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $\ln \dot{\varepsilon}^p$}
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhT}
+\includegraphics[width=0.9\columnwidth]{Figures/LnSinhT}
 \caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $1/T$}
@@
 \centering
-\includegraphics[width=1.02\columnwidth]{newFigures/ARparameters}
+\includegraphics[width=1.02\columnwidth]{Figures/ARparameters}
 \caption{Relationships between $\alpha$ (a)  , $Q$ (b) , $n_2$ (c)  and $lnA$ (d)  with the plastic strain $\varepsilon^p$ by polynomial functions}
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/CompExpAR}
+{Figures/CompExpAR}
 \caption{Comparison between the experimental and predicted flow stresses by AR model}
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/CompExpPTM}
+{Figures/CompExpPTM}
 \caption{Comparison between the experimental and predicted flow stresses by PTM model }
@@
 Each hidden layer is connected to the one before it and the one after it via neurons.
-Indeed, all neurons in the $k$ layer are connected to each neuron in the ($k+1$ ) layer.
+Indeed, all neurons in the $k$ layer are connected to each neuron in the ($k+1$) layer.
 To each layer is added another parameter called bias.
@@
 \centering
-\includegraphics[width=0.9\columnwidth]
-{newFigures/ANN-scheme-2HL}
+\includegraphics[width=0.7\columnwidth]
+{Figures/ANN-scheme-2HL}
 \caption{Multi-layer Artificial Neural Network architecture \cite{OPantale-2021-LGP}.}
@@
 \includegraphics[width=1\columnwidth]
-{newFigures/CompExpANN}
+{Figures/CompExpANN}
 \caption{Comparison between the experimental and predicted flow stresses by ANN model }
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/Correlation}
-\caption{Correlation coefficient ($R$) of models developped}
+{Figures/Correlation}
+\caption{Correlation coefficient ($R$) of models developed}
 \label{fig:Correlation}
 \end{figure}
-The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($AARE$ generally known as $\AARE$ ) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($RMSE$) (Equation (\ref{eq:RMSE-expression})).
+The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($\AARE$ generally known as $\AARE$) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($\RMSE$) (Equation (\ref{eq:RMSE-expression})).
 \begin{equation}
@@
 \label{eq:RMSE-expression}
-RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2}
+\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2}
 \end{equation}
@@
 Therefore, a good (high) value of $R$ does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction \cite{phaniraj2003applicability}.
-On the other hand, other coefficients ($\AARE$ and $RMSE$) are used to estimate the predictive capacity of the model because they are considered unbiased as well as for low and high values.
+On the other hand, other coefficients ($\AARE$ and $\RMSE$) are used to estimate the predictive capacity of the model because they are considered unbiased as well as for low and high values.
 Indeed, they verify the predictability of a model term by term comparison of the relative error in relation to the real value of the variable \cite{srinivasulu2006comparative}.
@@
 The prediction results should lead to a better interpolation and extrapolation capability of the ANN model than phenomenological models as shown by identification.
-Another thing to be analysed from this table is the link between the values of the correlation coefficient $R$ and the values of $\AARE$ and $RMSE$.
+Another thing to be analysed from this table is the link between the values of the correlation coefficient $R$ and the values of $\AARE$ and $\RMSE$.
 Indeed, as mentioned above, the $R$ coefficient does not necessarily mean a good prediction of the model but a good relationship of linearity between the experiment and the prediction.
 To ensure a good prediction of the model, it is necessary to add to $R$, the values of $\AARE$.
-From that table it can be seen the values of the coefficients $R$ are $99.014\%$, $98.364\%$, for $\AARE$ are $11.13020\%$ and $8.15103\%$ and those of $RMSE$ are $5.35079\ \text{MPa}$, and $6.45287\ \text{MPa}$ respectively for the MZA model and the HS model.
-This seems contradictory when the $R$ of HS is smaller than that of MZA, whereas for the $\AARE$ and $RMSE$ values it is the opposite case.
+From that table it can be seen the values of the coefficients $R$ are $99.014\%$, $98.364\%$, for $\AARE$ are $11.13020\%$ and $8.15103\%$ and those of $\RMSE$ are $5.35079\ \text{MPa}$, and $6.45287\ \text{MPa}$ respectively for the MZA model and the HS model.
+This seems contradictory when the $R$ of HS is smaller than that of MZA, whereas for the $\AARE$ and $\RMSE$ values it is the opposite case.
 This simply means that the HS model has a good prediction compared to the MZA model whereas in the framework of the linear correlation between the experiment and the prediction the MZA model makes it better.
@@
 $\AARE(\%)$&$11.1667$&$11.13020$&$8.15103$&$3.30677$&$4.19549$&$0.81094$   \\
-$RMSE(\text{MPa})$&$6.30298$&$5.35079$&$6.45287$&$2.03275$&$3.59027$&$0.55158$\\
+$\RMSE(\text{MPa})$&$6.30298$&$5.35079$&$6.45287$&$2.03275$&$3.59027$&$0.55158$\\
 \hline
@@
 \includegraphics[width=1.02\columnwidth]
-{newFigures/inCombinaison}
+{Figures/inCombinaison}
 \caption{Comparison between the experimental and predicted flow stresses by ANN model for interpolation estimation}
@@
 $\AARE(\%)$&$4.2686$&$3.7440$&$6.1391$&$2.3321$&$2.7590$&$1.4018$   \\
-$RMSE(\text{MPa})$&$4.1923$&$3.1856$&$82.6956$&$2.29891$&$2.4632$&$1.0228$ \\
+$\RMSE(\text{MPa})$&$4.1923$&$3.1856$&$82.6956$&$2.29891$&$2.4632$&$1.0228$ \\
 \hline
@@
 \includegraphics[width=0.91\columnwidth]
-{newFigures/exCombinaison}
+{Figures/exCombinaison}
 \caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}

### 2022-10-14 Article.tex
Remove scalebox in Latex
Update and clean of bibliography. Remove doubles

@@
 Some of the advantages of this method are increased metal yield, energy saving, improved quality of continuous casting and easier mechanisation and automation .
-Deformation being a very complex process involving both elastic and plastic deformation, is accompanied by high temperatures, high strain rates and complex and variable friction conditions \cite{he2013comparative}.
+Deformation being a very complex process involving both elastic and plastic deformation, is accompanied by high temperatures, high strain rates and complex and variable friction conditions \cite{He-2013}.
 However, a quantitative study and analysis of the deformation mechanism does not provide accurate analytical solutions .
-Moreover, conducting an experiment is not only time-consuming but also requires a high level of funding \cite{changizian2012high}.
+Moreover, conducting an experiment is not only time-consuming but also requires a high level of funding \cite{Changizian-2012}.
 To mitigate these two factors (to name but a few), the Finite Element Method (FEM) is widely used in the analysis and optimisation of process parameters of various materials .
 FEM effectively compensates for the shortcomings of the analytical and experimental methods and plays an important role in the correct formulation of technological parameters, the improvement of product quality and the in-depth knowledge of the deformation mechanism.
-For example FEM has been widely used to simulate and analyse steel hot forming processes, such as forging, rolling, extrusion and casting but the accuracy of the numerical solution provided by FEM for this type of analysis strongly depends  on the accuracy of the constitutive equation of the concerned material \cite{qin2010modeling, mandal2009constitutive, ji2018constitutive}.
+For example FEM has been widely used to simulate and analyse steel hot forming processes, such as forging, rolling, extrusion and casting but the accuracy of the numerical solution provided by FEM for this type of analysis strongly depends  on the accuracy of the constitutive equation of the concerned material \cite{Qin-2010, Mandal-2009, Ji-2018}.
 
-Indeed, hot forming processes are an essential step in the manufacturing of mechanical components and directly affect the ﬁnal quality of the products such as microstructure and mechanical properties \cite{ashtiani2012constitutive}.
+Indeed, hot forming processes are an essential step in the manufacturing of mechanical components and directly affect the ﬁnal quality of the products such as microstructure and mechanical properties \cite{Ashtiani-2012}.
 Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallisation), which very often occur during hot working, influence the quality of the deformation of materials.
 The complexity of the deformation behavior, however, leads to the fact that the deformation can only be calculated accurately by using a computer code to model the response of the material under the specified loading conditions.
-To this end, a mathematical formulation is often used to represent the flow behavior of materials in a form that can be used in finite element software \cite{lin2008prediction,wu2012flow}.
+To this end, a mathematical formulation is often used to represent the flow behavior of materials in a form that can be used in finite element software \cite{Lin-2008-P,Wu-2012}.
 
 Based on a thorough search of the literature many researchers have tried to predict the mechanical behavior of materials under hot working conditions using constitutive models.
-Therefore, various constitutive equations have been proposed to describe the flow behavior including phenomenological, physical and artiﬁcial neural network (ANN) models \cite{lin2011critical,shin2010phenomenological,rusinek2010thermo}.
+Therefore, various constitutive equations have been proposed to describe the flow behavior including phenomenological, physical and artiﬁcial neural network (ANN) models \cite{Lin-2011,Shin-2010,Rusinek-2010}.
 As for the semi-empirical models, they try to be at the border between the empirical and physical models.
-Among a large number of models, the Johnson--Cook (JC) \cite{Johnson-1983-Constitutive, Johnson-1985-Fracture} and the Zerilli--Armstrong (ZA) \cite{Zerilli-1987-Dislocation} models are the best known and available in finite element codes.
-The JC model is widely used because it is simple to use and has fewer constants to be determined \cite{Khan-2004-Quasi-static, NematNasser-2003-Thermomechanical}.
+Among a large number of models, the Johnson--Cook (JC) \cite{Johnson-1983, Johnson-1985} and the Zerilli--Armstrong (ZA) \cite{Zerilli-1987} models are the best known and available in finite element codes.
+The JC model is widely used because it is simple to use and has fewer constants to be determined \cite{Khan-2004, NematNasser-2003}.
 However, this model, in its original state, contains some problems related to the phenomena describing the behavior of the material.
-We refer here to strain hardening, strain rate hardening, and thermal effects that are described separately in the JC model as analyzed by Jia \eal \cite{Jia-2021-Modified-JC}.
-To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998-Revised-JC, Vural-2003-Large, Lin-2010-Modified-JC, Lin-2012-Phenomenological, Li-2013-Modified-JC, Zhou-2019-Research, Zhang-2015-Modified-JC}.
-According to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988-Evaluation, Voyiadjis-2005-Microstructural, Dey-2007-Influence}.
+We refer here to strain hardening, strain rate hardening, and thermal effects that are described separately in the JC model as analyzed by Jia \eal \cite{Jia-2021}.
+To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}.
+According to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
 However, the drawbacks of this model are related to the temperature limit value of the test.
-Indeed, this model applies only to low strain rates and for temperatures limited to $0.6~T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005-Strain, Lee-2005-Strain, Chen-2007-Comparative, Lee-2006-Effects}.
-Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009-Thermo-viscoplastic}.
-In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{Nemat-2004-Plasticity, Lennon-2004-Influence, Muralli-2017-Performance, Cheng-2021-Modified-ZA, Muralli-2021-Finite}.
-The hyperbolic sine Arrhenius-type constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the microstructure of the studied material because   this model allows to estimate the deformation energy of the material \cite{jonas1969strength,zhang2012effect,mostafaei2012hot}.
+Indeed, this model applies only to low strain rates and for temperatures limited to $0.6~T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}.
+Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
+In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.
+The hyperbolic sine Arrhenius-type constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the microstructure of the studied material because   this model allows to estimate the deformation energy of the material \cite{Jonas-1969,Zhang-2012,Mostafaei-2012}.
 Its original formulation has been revised several times in order to properly describe the obtained experimental behavior.
-In order to increase the accuracy of the model, the effects of strain \cite{slooff2007constitutive, li2012flow, xu2013constitutive}, strain rate \cite{lin2008constitutive, mandal2009constitutive} have been considered by several researchers.
-For example, Sloof \eal \cite{slooff2007constitutive} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that their model could predict the high temperature flow behavior of a magnesium alloy.
-Lin \eal \cite{lin2008constitutive}, on the other hand, modified the model by introducing a strain rate compensation factor.
+In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several researchers.
+For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that their model could predict the high temperature flow behavior of a magnesium alloy.
+Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.
 
@@
 \caption{Chemical Composition of the AISI P20 Steel (Weight Percent)}
-\scalebox{0.9}{
 \begin{tabular}{lcccccccc}
@@
 \label{tab:Composition}
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 Hence its inability to describe the phenomenon of temperature-induced softening.
-The equation that describes this model is given as follows \cite{johnson1985fracture}:
+The equation that describes this model is given as follows \cite{Johnson-1985}:
 \begin{equation}
@@
 \caption{Parameters' constants of Johnson-Cook Model}
-\scalebox{1.2}{
 \begin{tabular}{lccccc}
@@
 \label{tab: JCparameters}
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 As mentioned earlier, Johnson--Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
-Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model \cite{Hull-2011-ITD}.
-But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009-Thermo-viscoplastic} proposed a modified form given by the following equation:
+Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model \cite{Hull-2011}.
+But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
 \begin{equation}
@@
 where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
-The formulation of the model can be found in \cite{Samantaray-2009-Thermo-viscoplastic} and determination of its parameters is sumarized as following.
+The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.
 
@@
 The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
-That is aspect of the limitations of that model as presented in \cite{tize2022generalized}.
+That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
 \begin{table}[h!]
@@
 \caption{Parameters' constants of Modified--Zerilli-Armstrong Model}
-\scalebox{0.83}{
 \begin{tabular}{lllllllc}
@@
 \label{tab: MZAparameters}
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 However, this model has some difficulties as it loses its accuracy when all parameters are taken into account.
-For this reason, several authors limit its use to $5$ or $6$ parameters \cite{chadha2018approach, rudnytskyj2020constitutive, el2015comparison}.
+For this reason, several authors limit its use to $5$ or $6$ parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.
 In this paper the good predictions are with $5$ parameters summarized in Table \ref{tab: HSparameters}.
@@
 \caption{Parameters' constants of Hansel and Spittel Model}
-\scalebox{0.9}{
 \begin{tabular}{llccccc}
@@
 \label{tab: HSparameters}
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 \caption{Parameters' constants of Arrhenius Model}
-\scalebox{0.95}{
 \begin{tabular}{lllll}
@@
 \label{tab: ARparameters}
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 \end{equation}
-where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM-parameters}) of the model to be identified using the procedure proposed in  \cite{tize2022generalized}.
+where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM-parameters}) of the model to be identified using the procedure proposed in  \cite{TizeMha-2022}.
 Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
 The larger these quantities are, the more parameters need to be identified for the PTM model.
-The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016-LNL} and for more details about this model  we invite the reader to read our previous work \cite{tize2022generalized}.
+The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016} and for more details about this model  we invite the reader to read our previous work \cite{TizeMha-2022}.
 Thus all the parametrers of this model are calcuted with $q=5$, $r=5$, $s=1$ and $t=5$.
@@
 \caption{Parameters of PTM model\label{tab:PTM-parameters}}
-\scalebox{0.83}{
 \begin{tabular}{cc}
@@
 \hline
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 {Figures/ANN-scheme-2HL}
-\caption{Multi-layer Artificial Neural Network architecture \cite{OPantale-2021-LGP}.}
+\caption{Multi-layer Artificial Neural Network architecture \cite{Pantale-2021}.}
 \label{fig:ANN-scheme-2HL}
@@
 The model sometimes tends to be biased towards low and high values.
-Therefore, a good (high) value of $R$ does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction \cite{phaniraj2003applicability}.
+Therefore, a good (high) value of $R$ does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction \cite{Phaniraj-2003}.
 On the other hand, other coefficients ($\AARE$ and $\RMSE$) are used to estimate the predictive capacity of the model because they are considered unbiased as well as for low and high values.
-Indeed, they verify the predictability of a model term by term comparison of the relative error in relation to the real value of the variable \cite{srinivasulu2006comparative}.
+Indeed, they verify the predictability of a model term by term comparison of the relative error in relation to the real value of the variable \cite{Srinivasulu-2006}.
 Thus the correlation coefficients $R$ for JC, MZA, HS, Arhenius, proposed and ANN models are $0.98475$,  $0.99014$,  $0.98364$, $0.99839$, $0.99514$, and $0.99994$ respectively as shown on Figure \ref{fig:Correlation}.
@@
 All this can be seen from the identification curves where we can observe the HS curves (Figure \ref{fig:iCorrelationHS}) are indeed closer to the experimental than those of MZA (Figure \ref{fig:iCorrelationMZA}) while the points are scattered for HS model on the correlation curve (Figure \ref{fig:Correlation}).
-This validates the analysis made by \cite{phaniraj2003applicability, srinivasulu2006comparative}.
+This validates the analysis made by \cite{Phaniraj-2003, Srinivasulu-2006}.
 
@@
 \caption{Accurary coefficients of the developped models}
-\scalebox{0.92}{
 \begin{tabular}{lcccccc}
@@
 \label{tab:Coefsparams}
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 \caption{Accuracy coefficients of interpolation}
-\scalebox{0.92}{
 \begin{tabular}{lcccccc}
@@
 \label{tab:inValid}
-\end{tabular}}
+\end{tabular}
 \end{table}
@@
 \caption{Accuracy coefficients of extrapolation}
-\scalebox{0.92}{
 \begin{tabular}{lcccccc}
@@
 \label{tab:exValid}
-\end{tabular}}
+\end{tabular}
 \end{table}

### 2022-10-17 Article.tex
Correction of Introduction chapter

@@
 \usepackage{amsthm}
-\usepackage{gensymb}
+%\usepackage{gensymb}
 \usepackage{xspace}
@@
 
+% This is used to add comments into the text
+\usepackage{soul} %Can also be used to highlight text with \hl{highlighted text}
+\usepackage{color}
+\definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
+\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:}\\#1}}\endgroup} }
+
 \begin{document}
@@
 
-\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation--extrapolation capacity validation}
+\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation-extrapolation capacity validation}
 
@@
 \address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}
-\address[ETS]{Écolde de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}
+\address[ETS]{École de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}
 
@@
 \begin{keyword}
-Zerilli--Armstrong flow law \sep Constitutive behavior \sep Arhenius--flow law \sep Hansel--Spittel flow law \sep Johnson--Cook flow law \sep interpolation \sep extrapolation \sep Artificial neural network
+Zerilli-Armstrong flow law \sep Constitutive behavior \sep Arhenius flow law \sep Hansel-Spittel flow law \sep Johnson-Cook flow law \sep interpolation \sep extrapolation \sep Artificial neural network
 \end{keyword}
@@
 %--------------------------------------------------------------------------
-Continuous casting and rolling mechanisms are an integral part of the technological methods of medium deformation through a continuous water-cooled crystalliser before entering a rolling mill.
-Some of the advantages of this method are increased metal yield, energy saving, improved quality of continuous casting and easier mechanisation and automation .
-Deformation being a very complex process involving both elastic and plastic deformation, is accompanied by high temperatures, high strain rates and complex and variable friction conditions \cite{He-2013}.
-However, a quantitative study and analysis of the deformation mechanism does not provide accurate analytical solutions .
-Moreover, conducting an experiment is not only time-consuming but also requires a high level of funding \cite{Changizian-2012}.
-To mitigate these two factors (to name but a few), the Finite Element Method (FEM) is widely used in the analysis and optimisation of process parameters of various materials .
-FEM effectively compensates for the shortcomings of the analytical and experimental methods and plays an important role in the correct formulation of technological parameters, the improvement of product quality and the in-depth knowledge of the deformation mechanism.
-For example FEM has been widely used to simulate and analyse steel hot forming processes, such as forging, rolling, extrusion and casting but the accuracy of the numerical solution provided by FEM for this type of analysis strongly depends  on the accuracy of the constitutive equation of the concerned material \cite{Qin-2010, Mandal-2009, Ji-2018}.
+Continuous casting and rolling techniques are an integral part of material forming methods.
+Advantages of this method include increased process efficiency, energy savings, improved casting quality and easier mechanization and automation.
+Deformation, a complex process involving simultaneous elastic and plastic deformation, is accompanied by high temperatures, high strain rates, and complex and variable frictional conditions \cite{He-2013}, for which, analytical methods are not available for quantitative study and analysis of the deformation mechanism.
+On the other hand, conducting experimental tests is not only time-consuming but also requires a high financial investment \cite{Changizian-2012}.
+As an alternative approach to the previous two, the Finite Element Method (FEM) is widely used as a tool for analysis and optimization of process parameters in the processing of various materials.
+Finite element modeling effectively compensates for the shortcomings of analytical and experimental methods and is playing an increasingly important role in determining process parameters, improving product quality, and gaining in-depth knowledge of deformation mechanisms.
+For example, FEM has been widely used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Qin-2010, Mandal-2009, Ji-2018}.
 
-Indeed, hot forming processes are an essential step in the manufacturing of mechanical components and directly affect the ﬁnal quality of the products such as microstructure and mechanical properties \cite{Ashtiani-2012}.
-Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallisation), which very often occur during hot working, influence the quality of the deformation of materials.
-The complexity of the deformation behavior, however, leads to the fact that the deformation can only be calculated accurately by using a computer code to model the response of the material under the specified loading conditions.
-To this end, a mathematical formulation is often used to represent the flow behavior of materials in a form that can be used in finite element software \cite{Lin-2008-P,Wu-2012}.
+Hot forming processes are an essential step in the manufacture of mechanical components and directly affect the final quality of the products through their strong influence on the micro-structure and mechanical properties \cite{Ashtiani-2012}.
+Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and re-crystallization), which very often occur during hot working, influence the behavior and deformation of materials.
+The complexity of the thermomechanical behavior usually leads to the fact that it can only be taken into account accurately by using a numerical approach to obtain the response of the material under the specified loading conditions.
+To this end, a mathematical formulation is typically used to represent the flow of a material in a form that can be used in finite element software \cite{Lin-2008-P, Wu-2012}.
 
-Based on a thorough search of the literature many researchers have tried to predict the mechanical behavior of materials under hot working conditions using constitutive models.
-Therefore, various constitutive equations have been proposed to describe the flow behavior including phenomenological, physical and artiﬁcial neural network (ANN) models \cite{Lin-2011,Shin-2010,Rusinek-2010}.
-As for the semi-empirical models, they try to be at the border between the empirical and physical models.
-Among a large number of models, the Johnson--Cook (JC) \cite{Johnson-1983, Johnson-1985} and the Zerilli--Armstrong (ZA) \cite{Zerilli-1987} models are the best known and available in finite element codes.
-The JC model is widely used because it is simple to use and has fewer constants to be determined \cite{Khan-2004, NematNasser-2003}.
-However, this model, in its original state, contains some problems related to the phenomena describing the behavior of the material.
-We refer here to strain hardening, strain rate hardening, and thermal effects that are described separately in the JC model as analyzed by Jia \eal \cite{Jia-2021}.
-To overcome this difficulty, several modified forms of the Johnson--Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}.
-According to its more physical formulation, the ZA model is preferred over the JC model because it allows for the coupling between strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
-However, the drawbacks of this model are related to the temperature limit value of the test.
-Indeed, this model applies only to low strain rates and for temperatures limited to $0.6~T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}.
+For several years, many researchers have developed methods to predict the thermomechanical behavior of materials under hot working conditions using constitutive models.
+Thus, various forms of constitutive equations have been proposed to describe the flow of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Lin-2011, Shin-2010, Rusinek-2010, Pantale-2021}.
+Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983, Johnson-1985} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in finite element codes.
+The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{Khan-2004, NematNasser-2003}.
+However, this model, in its original state, has some shortcomings related to nonlinear coupling phenomena not taken into account in the material behavior.
+We refer here to strain hardening, strain rate hardening and thermal effects that are taken into account in a non-coupled manner in the JC model as analyzed by Jia \eal \cite{Jia-2021}.
+To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}.
+Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
+However, this model has other drawbacks related to the limit value of the test temperature.
+Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}.
 Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
-In order to reduce these shortcomings (\eg applying this model over a wider temperature range) of the ZA model, Modified Zerilli--Armstrong forms (MZA) have been proposed by several authors over the last past years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.
-The hyperbolic sine Arrhenius-type constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the microstructure of the studied material because   this model allows to estimate the deformation energy of the material \cite{Jonas-1969,Zhang-2012,Mostafaei-2012}.
-Its original formulation has been revised several times in order to properly describe the obtained experimental behavior.
-In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several researchers.
-For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that their model could predict the high temperature flow behavior of a magnesium alloy.
+In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed by several authors in recent years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.
+
+The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the deformation energy of the material \cite{Jonas-1969, Zhang-2012, Mostafaei-2012}.
+Its original formulation has been revised several times to correctly describe the resulting experimental behavior.
+In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several authors.
+For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that his model could predict the high-temperature flow of a magnesium alloy.
 Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.
 
-The method based on artiﬁcial neural networks is an approach to predict the deformation behavior of materials under different conditions.
-ANN is in fact a method originally developed to simulate the biological processes of the human brain.
-And therefore it is not necessary to formulate a mathematical expresson and identify these parameters for this kind of model.
-The response of the deformation behavior of materials is highly non-linear at high temperatures, and many factors affecting the deformation behavior of materials are also non-linear; this makes the accuracy of the flow stress predicted by regression methods and the appropriate range is limited.
-Faced with these limitations, ANN models are therefore of interest.
-Indeed, ANNs are particularly suited to deal with complex and non-linear relationships; consequently, ANNs have been successfully applied to predict the deformation behavior of materials under hot working conditions.
-ANNs can provide a fundamentally different approach to statistical or numerical techniques for materials modelling and materials processing control.
+\OP{You must add here two paragraphs concerning a brief introduction to the Hansel-Spittel and the PTM models.}
 
-In this study, the high temperature deformation behavior of AISI P20 modified carbon steel subjected to compression tests will be highlighted.
-From the experimental data obtained, analytical models will be identified on the one hand in order to select the one that could better describe the behavior of this alloy and on the other hand, an ANN model is also developed and a comparative study between the analytical models and the ANN model will follow.
-A fundamental issue that will also be addressed in this work is the ability to interpolate and extrapolate of the developed models.
-Indeed, how do models behave when it comes to interpolating or extrapolating data that the model is never aware of ?
-the answer to this question will be well analyzed in this study.
+Behavior modeling based on an artificial neural network is an approach to predict the flow of materials without requiring a mathematical formulation of the flow law.
+It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
+Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress by an analytical model whose parameters are identified by a classical regression method is limited.
+Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
+Consequently, ANNs have been successfully applied to predict the flow of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB, Pantale-2021}.
+They provide a fundamentally different approach to statistical or numerical techniques for modeling materials.
 
-The main parts of this work are as follows: Section \ref{sec:Materials} presents the material et experimental procedure inverstigated in this study.
-Section \ref{sec:ConstLaws} is devoted to the presentation of the models developed and their comparative.
-Section \ref{sec:inExtrapolation} details the validation of interpolation and extrapolation capacity of each model developped.
-Conclusion and future works are detailed in Section \ref{sec:Conclusion}.
+In this work, the high-temperature thermomechanical behavior of AISI P20 modified carbon steel subjected to compression tests in a Gleeble thermomechanical simulator was studied.
+From the experimental data obtained from the compression tests, five analytical models were identified in order to select the one that best describes the behavior of this alloy.
+A flow model based on an artificial neural network was also developed and identified, and a comparative study between the five analytical models and the ANN model is proposed.
+A fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.
+
+The main parts of this work are as follows: Section \ref{sec:Materials} presents the hardware (Gleeble thermomechanical simulator), the experimental procedure, the material and the results of the compression tests performed for this study.
+Section \ref{sec:ConstLaws} is devoted to the presentation of the five analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models.
+Section \ref{sec:inExtrapolation} details the interpolation and extrapolation capabilities of each model proposed in this paper.
+Conclusions and future work are detailed in Section \ref{sec:Conclusion}.
 
@@
 %-------------------------------------------------------------------------
-The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature .
+The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature.
 However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
@@
 %-------------------------------------------------------------------------
-\subsection{Modified Zerilli--Armstrong model\label{sec:MZA}}
+\subsection{Modified Zerilli-Armstrong model\label{sec:MZA}}
 %-------------------------------------------------------------------------
 
-As mentioned earlier, Johnson--Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
-Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli--Armstrong (ZA) model \cite{Hull-2011}.
+As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
+Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}.
 But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
@@
 \centering{}
-\caption{Parameters' constants of Modified--Zerilli-Armstrong Model}
+\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
 \begin{tabular}{lllllllc}
@@
 Where $\mdot{\varepsilon}^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants.
-To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener--Hollomon parameter is introduced whose expression is given as follows:
+To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:
 \begin{equation}

### 2022-10-17 Article.tex
Two new paragraphs added to the intro part and one new ref in Biblio

@@
 
-\OP{You must add here two paragraphs concerning a brief introduction to the Hansel-Spittel and the PTM models.}
+\textcolor{red}{Another model widely used in the Forge software is the model developed by Hansel and Spittel \cite{hensel1978kraft}, commonly known as the HS model, which is a thermo-visco-plastic model and whose formulation is a product of the dependent functions of three physical variables.
+Unlike the JC model, this formulation does not imply an independence of the three physical variables since they are determined simultaneously.
+This model is simple to use and has $8$ coefficients that are easy to determine.
+The limitation of this model is that it loses its accuracy in some cases when all $8$ parameters have to be used.
+Hence many works limit its use very often to $5$ or $6$ parameters.
+This has been verified in our study where the smallest error of the model is found with $5$ parameters}.
+
+\textcolor{purple}{The fixed and few number of parameters imposed by each analytical model as presented above has both advantages and disadvantages.
+The advantages are related to the fact that the models have few parameters and are therefore easy to identify, but the disadvantage is when the model has to be applied to a different material than the one for which it was developed and in this case the model loses its performance as in the case of the HS model.
+To try to solve this problem P.
+Tize Mha \eal \cite{TizeMha-2022} proposed a formulation where the number of parameters is not known in advance.
+Indeed, the idea is to make an analytical model formulation flexible so that it can be adapted to a large number of materials.
+This formulation is based on MZA model and polynomial functions are used allowing to find its final form from the functions intrinsic to the model.
+Another way to describe the flow behavior of material is to use neural network tool due to its capacity to solve complex problems}.
 
@@
 {Figures/ANN-scheme-2HL}
-\caption{Multi-layer Artificial Neural Network architecture \cite{Pantale-2021}.}
+\caption{Multi-layer Artificial Neural Network architecture}
 \label{fig:ANN-scheme-2HL}

### 2022-10-18 Article.tex
Correction of two additional paragraphs in the Introduction

--- 2022-10-17 Article.tex
@@
 
-\OP{You must add here two paragraphs concerning a brief introduction to the Hansel-Spittel and the PTM models.}
+Users of the Forge software make extensive use of the model developed by Hansel and Spittel \cite{Hensel-1978}, commonly referred to as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on the three physical variables.
+Unlike the JC model, this formulation is based on parameters that are determined simultaneously.
+This model is simple to use and has $8$ parameters that are easy to determine.
+The limitation of this model is its loss of accuracy in some cases when the $8$ parameters are defined.
+This is why many works often limit its identification to only $5$ or $6$ parameters.
+This has been verified in our study where the smallest error of the model is obtained with only $5$ parameters identified.
+
+The fixed and limited number of parameters imposed by each analytical model as presented above has both advantages and disadvantages.
+These models have few parameters and are therefore easy to identify, but when these models have to be applied to a material different from the one for which they were initially developed they lose their performance as in the case of the HS model.
+To try to solve this problem, Tize Mha \eal \cite{TizeMha-2022} has proposed a formulation where the number of parameters is not known in advance.
+The idea is to make the formulation of an analytical model flexible so that it can be adapted to many materials.
+This formulation is based on the MZA model and polynomial functions of undefined order are used in the identification phase.
 

### 2022-10-18 Article.tex
Correction of Section 2

@@
 \definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
-\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:}\\#1}}\endgroup} }
+\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:}#1}}\endgroup} }
 
@@
 \begin{abstract}
-The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050^\circ\text{C} -1250^\circ$C).
+The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050\text{°C}-1250\text{°C}$).
 Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
@@
 From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy.
-For the strain rate ($\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050^\circ$C and $1100^\circ$C  while in the case of the PTM model, the strain rate  ($\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$) is not well described.
+For the strain rate ($\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050$°C and $1100$°C  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$) is not well described.
 This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high.
-Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot{\varepsilon}^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
+Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
 The results of the ANN model show a very good agreement between the predictions and the experiment.
@@
 %----------------------------------------------
-\section{ Materials and Experiments \label{sec:Materials}}
+\section{Materials and Experiments\label{sec:Materials}}
 %----------------------------------------------
+
 %----------------------------------------------
@@
 %----------------------------------------------
-The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table \ref{tab:Composition}.
-Cylindrical specimens were machined with an initial diameter of $10$ mm and a height of $15$ mm.
-Hot compression tests were conducted on a Gleeble-3800 thermo-simulator (Figure \ref{fig:Gleeble3800}), at temperatures of $1050^\circ$C,  $1050^\circ$C,  $1100^\circ$C,  $1150^\circ$C,  $1200^\circ$C and  $1250^\circ$C with strain rates of $0.001\ \text{s}^{-1}$, $0.01\ \text{s}^{-1}$, $0.1\ \text{s}^{-1}$, $1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$.
-Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during the tests.
-The samples were heated up to temperature $1260^\circ$C  and were held for $5$ min to eliminate thermal gradients.
-Then cooled to test temperature where the specimen is held $1$ minute before deformation.
-After compression the specimen is quencted rapidly for microstructure studies.
-The procedure of this test is illustrated in Figure \ref{fig:Heating} where $h_0$ and $R_0$ are the height and radius before compression; $h$, $R_M$, and $R_T$ are respectively the height, big radius and small radius of the specimen after compression.
-\begin{figure}[!ht]
+
+The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
+Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm.
+A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050$°C, $1100$°C, $1150$°C, $1200$°C and $1250$°C with the six strain rates of $0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$, $1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$ and $5.0~\text{s}^{-1}$.
+
+\begin{table}[h!]
 \centering
-\includegraphics[width=0.9\columnwidth]
-{Figures/Gleeble-3800}
-\caption{Gleeble 3800 simulator system}
-\label{fig:Gleeble3800}
-\end{figure}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.9\columnwidth]
-{Figures/GleebleDesign}
-\caption{Schematic diagram of the experimental process.}
-\label{fig:Heating}
-\end{figure}
-\begin{table}[h!]
-\centering{}
-\caption{Chemical Composition of the AISI P20 Steel (Weight Percent)}
-\begin{tabular}{lcccccccc}
+\caption{Chemical composition of AISI P20 steel, Fe = balance.}
+\begin{tabular}{lccccccc}
 \hline
-C  &Mn & Mo   & Si   & Ni       &Cr& Cu & Other& Balance\\
-\hline
- 0.30        &       0.89      &0.52		   &	0.34     &	 0.68          &1.86& 0.17& Microalloying& Iron\\
-\hline
+Element & C & Mn & Mo & Si & Ni & Cr & Cu\\ \hline
+Wt~\% & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17\\ \hline
 \label{tab:Composition}
@@
 \end{table}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
+\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
+\label{fig:Gleeble3800}
+\end{figure}
+
+Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
+As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260$°C with a heating rate of $2$°C/s and held at this temperature for $5$~min to eliminate thermal gradients.
+They were then cooled with a rate of $1$°C/s to the test temperature and then held at constant temperature for $1$~min before deformation.
+During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
+After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
+Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $R_0$ are the height and radius before compression and $h$, $R_M$ and $R_T$ are the height, large radius and small radius of the specimen after compression, respectively.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
+\caption{Schematic diagram of the experimental process.}
+\label{fig:GleebleProcess}
+\end{figure}
+
 %------------------------------------------------------------------------
-\subsection{Flow stress behavior}
+\subsection{Compression tests results}
 %------------------------------------------------------------------------
-The flow stress curves obtained from the compression tests performed on Gleeble-3800 simulator for each test condition are shown in Figure \ref{fig:rawData}.
-From these curves it can be seen that the flow stress increases with increasing strain rate but decreases with increasing temperature.
-It should be noted that the strain influences the flow stress.
-Indeed, for all strain values below $0.2$, the stress increases with strain before reaching a peak value at low strain rates and then decreases to maintain a stable value until the end of the test.
-The peak stress value increases with strain rate but decreases with temperature.
-For higher strain rates ($1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$) the flow stress increases throughout the test.
-The slight increase in stress at low strain rates when the strain is large is due to friction between the specimen and the grip during the test.
-For low strain rates, lubrication is lost over time and therefore friction occurs.
-This results in a progressive increase in stress.
 
-To explain the overall behavior of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX).
-At the beginning of the deformation, the amount of dislocations increases and they start to move, leading to a rapid increase in stress known as work-hardening.
-As the strain continues to increase, the dislocations are set in motion, leading to a stress relaxation phenomenon usually known as DRC.
-During this DRC mechanism, some of the dislocations are removed, due to their combination with another dislocation, or due to their integration into a grain boundary, and some of them are rearranged and formed as sub-grains within the initial grains.
-The combination of these dislocations moderates the increase of dislocations linked to strain hardening and thus controls the amount of energy stored in the material and manages the increase in flow stress.
-DRX consists of the germination of new grains, at the borders or inside the initial grains.
-These two phenomena therefore explain the different shapes of the flow stress curves observed for this alloy.
-As an example, the Figure \ref{fig:BeforeCompM} and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression.
-As observed on the flow curves, it can be seen that recrystallisation is almost complete for this temperature and strain rate.
-Indeed, most of the grain boundaries start to form new grains.
-The identification of the behavioral laws of these curves will be done in the next section in order to predict its behavior in any test condition.
+The set of flow stress $\sigma^y$ versus plastic strain $\varepsilon^p$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
+The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon^p$ but decreases with increasing temperature $T$.
+It should be noted that the plastic strain also influences the flow stress.
+Indeed, for the lowest strain rates $\mdot\varepsilon^p$, the flow stress $\sigma^y$ increases with the plastic strain $\varepsilon^p$ until a value of about $\varepsilon^p=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
+For the highest strain rates ($1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$, and $5.0~\text{s}^{-1}$), the flow stress increases throughout the test.
+One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
+For low strain rates, the effect of lubrication decreases over time and thus friction increases.
+This results in a progressive increase of the flow stress.
+
 \begin{figure}[!ht]
@@
 \end{figure}
+
+To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX).
+At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
+As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRC.
+This DRC mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
+Some of these dislocations reorganize and then form sub-grains within the initial grains of the material.
+The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
+The dynamic recrystallization concerns the germination of new grains, at the borders or inside the initial grains.
+These two phenomena explain the different shapes of the flow stress curves observed for this alloy.
+As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260$°C before and after the compression phase.
+As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample \OP{What are the temperature and strain rate related with this micrography}.
+From the results reported in Figure \ref{fig:rawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.
+
 \begin{figure}[!ht]
 \centering
-\includegraphics[width=0.9\columnwidth]
-{Figures/BeforeCompM}
-\caption{Optical micrograph of the AISI P20 steel before hot compression held during $5$ minutes at $1260^\circ$C}
-\label{fig:BeforeCompM}
-\end{figure}
-\begin{figure}[!ht]
+\begin{subfigure}[b]{0.45\textwidth}
 \centering
-\includegraphics[width=0.9\columnwidth]
-{Figures/AfterCompM}
-\caption{Optical micrograph of AISI P20 alloy after hot compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
-\label{fig:AfterCompM}
+\includegraphics[width=\textwidth]{Figures/BeforeCompM}
+\caption{Before hot compression}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{Figures/AfterCompM}
+\caption{After hot compression}
+\end{subfigure}
+\caption{Optical micrographs of the AISI P20 steel before and after hot compression.}
+\label{fig:Micrography}
 \end{figure}
@@
 \label{eq: JCmodel}
-\sigma^y = \left(A + B\varepsilon^{p^n}\right)\left(1+C\ln\mdot{\varepsilon}^*\right)\left(1-T^{*^m}\right)
+\sigma^y = \left(A + B\varepsilon^{p^n}\right)\left(1+C\ln\mdot\varepsilon^*\right)\left(1-T^{*^m}\right)
 \end{equation}
@@
 $C$ and $m$ are the material constants that describe the strain rate hardening and thermal softening exponent respectively.
-$\mdot{\varepsilon}^*$ is the dimensionless strain rate which is given by $\mdot{\varepsilon}^* = \mdot{\varepsilon^p}/\mdot{\varepsilon_0}$.
-$\mdot{\varepsilon^p}$ and $\mdot{\varepsilon_0}$ are strain rate and reference strain rate respectively.
-$T^{*^m} = (T-T_0)/(T_m - T_0)$ is homologous temperature where $T, T_m$ and $T_0$ are the déformation temperature, meltinng temperature (1460$^\circ$C in our case) and reference temperature respectively.
-For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050^\circ$C respectively and the value of $A$ is $43.0988$ MPa.
+$\mdot\varepsilon^*$ is the dimensionless strain rate which is given by $\mdot\varepsilon^* = \mdot\varepsilon^p/\mdot\varepsilon_0$.
+$\mdot\varepsilon^p$ and $\mdot\varepsilon_0$ are strain rate and reference strain rate respectively.
+$T^{*^m} = (T-T_0)/(T_m - T_0)$ is homologous temperature where $T, T_m$ and $T_0$ are the déformation temperature, meltinng temperature ($1460$°C in our case) and reference temperature respectively.
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050$°C respectively and the value of $A$ is $43.0988$ MPa.
 Here after datailed the steps for determination of the JC model parameters.
@@
 {Figures/JCSigmaAB}
-\caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050^\circ$C and $0.1$}
+\caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050$°C and $0.1$}
 \label{fig:JCSigmaAB}
@@
 \begin{equation}
-\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 + C\ln\mdot{\varepsilon}^*
+\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 + C\ln\mdot\varepsilon^*
 \end{equation}
@@
 \label{eq:MZA-model}
-\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
+\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)\right]
 \end{equation}
@@
 
-Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$.
-When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
+Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon^p=\mdot{\varepsilon}_0)$.
+When the current strain rate $\mdot\varepsilon^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
 \begin{equation}
@@
 \begin{equation}
-\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
+\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)
 \end{equation}
 with $S_2=C_5+C_6\left(T-T_0\right)$.
-Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
+Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
 The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}.
@@
 \begin{equation}
-\sigma^y = Ae^{m_1T}\varepsilon^{p^{m_2}}\mdot{\varepsilon}^{p^{m_3}}e^{\frac{m_4}{\varepsilon^p}}(1+\varepsilon^p)^{m_5T}e^{m_6\varepsilon^p}\mdot{\varepsilon}^{p^{m_7T}}T^{m_8}
+\sigma^y = Ae^{m_1T}\varepsilon^{p^{m_2}}\mdot\varepsilon^{p^{m_3}}e^{\frac{m_4}\varepsilon^p}(1+\varepsilon^p)^{m_5T}e^{m_6\varepsilon^p}\mdot\varepsilon^{p^{m_7T}}T^{m_8}
 \end{equation}
-Where $\sigma^y$ is the flow stess, $\varepsilon^p$ strain, $\mdot{\varepsilon}^p$ strain rate and $T$ temperature.
+Where $\sigma^y$ is the flow stess, $\varepsilon^p$ strain, $\mdot\varepsilon^p$ strain rate and $T$ temperature.
 The other coefficients $A$ and $m_j$ are model constants up to $m_5$ for our case.
@@
 The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material.
-Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot{\varepsilon}^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation.
+Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot\varepsilon^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation.
 This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature.
@@
 \label{eq:ARmodel1}
-\mdot{\varepsilon}^p = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)
+\mdot\varepsilon^p = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)
 \end{equation}
@@
 \label{eq:ARmodel2}
-\mdot{\varepsilon}^p = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)
+\mdot\varepsilon^p = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)
 \end{equation}
@@
 \label{eq:ARmodel}
-\mdot{\varepsilon}^p = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)
+\mdot\varepsilon^p = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)
 \end{equation}
-Where $\mdot{\varepsilon}^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants.
+Where $\mdot\varepsilon^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants.
 To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:
@@
 \label{eq:Zparam}
-Z = \mdot{\varepsilon}^p\exp\left(\frac{Q}{RT}\right)
+Z = \mdot\varepsilon^p\exp\left(\frac{Q}{RT}\right)
 \end{equation}
@@
 \begin{equation}
-\ln \sigma^y = \frac{1}{n_1}\ln \mdot{\varepsilon}^p -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}
+\ln \sigma^y = \frac{1}{n_1}\ln \mdot\varepsilon^p -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}
 \end{equation}
 \begin{equation}
-\sigma^y = \frac{1}{\beta}\ln \mdot{\varepsilon}^p - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}
+\sigma^y = \frac{1}{\beta}\ln \mdot\varepsilon^p - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}
 \end{equation}
-From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot{\varepsilon}^p)$  and $\sigma^y = f(\ln\mdot{\varepsilon}^p)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$.
+From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot\varepsilon^p)$  and $\sigma^y = f(\ln\mdot\varepsilon^p)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$.
 It should be noted that later in this document all values of strain will be taken into account.
@@
 \label{eq:lnSinh}
-\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot{\varepsilon}^p  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
+\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot\varepsilon^p  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
 \end{equation}
@@
 \label{eq:parQ}
-Q = R\left[\frac{\partial \ln \mdot{\varepsilon}^p}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot{\varepsilon}^p}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
+Q = R\left[\frac{\partial \ln \mdot\varepsilon^p}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot\varepsilon^p}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
 \end{equation}
@@
 The gap between experimental and prediction is small.
-But for the strain rate $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ and for the two low temperatures values, the AR model is not able to predict the softening.
+But for the strain rate $\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$ and for the two low temperatures values, the AR model is not able to predict the softening.
 \begin{equation}
@@
 \label{eq:PTM-model}
-\sigma^y(\varepsilon^p,\mdot{\varepsilon}^p,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
+\sigma^y(\varepsilon^p,\mdot\varepsilon^p,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)\right]
 \end{equation}
@@
 Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}.
-The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$ the prediction in not quite good.
+The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$ the prediction in not quite good.
 The deviation between the predicted values and the experimental values is relatively good.
@@
 The architecture of the network used in this study is shown in Figure \ref{fig:ANN-scheme-2HL}.
-After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot{\varepsilon}^p$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress.
+After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon^p$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress.
 The good performance of the model is found to be stable between $800$ and $1000$ epochs.
@@
 \end{equation}
-Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot{\varepsilon}^p/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively.
+Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot\varepsilon^p/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively.
 $X_n$ is the normalized data of the corresponding $X$.
@@
 \subsection{Interpolation validation}
-For the validation of the interpolation, the chosen strain rate is $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$.
+For the validation of the interpolation, the chosen strain rate is $\mdot\varepsilon^p = 1.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot\varepsilon^p = 0.001\ \text{s}^{-1}$ , $\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$ , $\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$, $\mdot\varepsilon^p = 2.0\ \text{s}^{-1}$  and $\mdot\varepsilon^p = 5.0\ \text{s}^{-1}$.
 The Figure \ref{fig:inCombinaison} shows the comparison between the predictions of the analytical and ANN models and the experiment.
@@
 \subsection{Extrapolation validation}
-For the validation of the extrapolation, the chosen strain rate is $\mdot{\varepsilon}^p = 5.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot{\varepsilon}^p = 0.001\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$ , $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$, $\mdot{\varepsilon}^p = 1.0\ \text{s}^{-1}$  and $\mdot{\varepsilon}^p = 2.0\ \text{s}^{-1}$.
+For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon^p = 5.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot\varepsilon^p = 0.001\ \text{s}^{-1}$ , $\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$ , $\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$, $\mdot\varepsilon^p = 1.0\ \text{s}^{-1}$  and $\mdot\varepsilon^p = 2.0\ \text{s}^{-1}$.
 Figure \ref{fig:exCombinaison} shows the comparison between the predictions  and the experimental.
@@
 \section{Conclusion \label{sec:Conclusion}}
-Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050^\circ$C - $1250^\circ$C, strains ($0.025$ - $0.7$), strain rates ($0.001\ \text{s}^{-1}$ - $5\ \text{s}^{-1}$) and the following conclusions were drawn.
+Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050$°C - $1250$°C, strains ($0.025$ - $0.7$), strain rates ($0.001\ \text{s}^{-1}$ - $5\ \text{s}^{-1}$) and the following conclusions were drawn.
 \begin{enumerate}

### 2022-10-18 Article.tex
Remove Johnson-Cook 1985

@@
 Thus, various forms of constitutive equations have been proposed to describe the flow of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Lin-2011, Shin-2010, Rusinek-2010, Pantale-2021}.
-Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983, Johnson-1985} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in finite element codes.
+Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in finite element codes.
 The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{Khan-2004, NematNasser-2003}.
@@
 Hence its inability to describe the phenomenon of temperature-induced softening.
-The equation that describes this model is given as follows \cite{Johnson-1985}:
+The equation that describes this model is given as follows \cite{Johnson-1983}:
 \begin{equation}

### 2022-10-18 Article.tex
Rewrite part concerning JC identification

@@
 \definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
-\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:}#1}}\endgroup} }
+\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:} #1}}\endgroup} }
 
@@
 \centering
-\includegraphics[width=1.02\columnwidth]
-{Figures/rawData}
+\includegraphics[width=1.02\columnwidth]{Figures/rawData}
 \caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
@@
 %-------------------------------------------------------------------------
-\section{Phenomenological constitutive flow laws\label{sec:ConstLaws}}
+\section{Identification of constitutive flow laws parameters\label{sec:ConstLaws}}
 %-------------------------------------------------------------------------
-The complete characterization of the thermomechanical behavior of a material is very important before its use in numerical simulations.
+
+The complete characterization of the thermomechanical behavior of a material through the identification of its flow law is very important before its modeling in numerical simulations.
 This characterization usually involves experimental tests that serve as a basis for the development of constitutive laws.
-As mentioned in the introduction, many constitutive laws exist today, and selecting one of them based on explicit criteria hinders the development of computational models for new materials.
-Since the purpose of this work is to compare ANN model to analytical models it is important to justify the choice of the analytical models presented here among the many that exist in the literature.
-Among the most widely used analytical models nowadays, the Johnson-Cook (JC) model is the most used due to its simplicity of use linked to the number of its reduced and easy to obtain parameters.
-It should be noted that it is not the best model but the most integrated in finite element software.
-Hence the existence of several modified forms of this model.
-The Zerilli-Armstrong model, and particularly its modified form (MZA), is also widely known since it tries to provide solutions to the shortcomings of the JC model, particularly with regard to the coupling of physical parameters.
-Hence its use also in this study.
-In this perspective, the Hansel Spittel model (HS)is also one of the most widely used models in numerical simulation of casting and forging operations as it is integrated in the FORGE software.
-Also, the method of identifying its parameters is very simple to do as it is done in one step.
-Of course, it has its limitations as will be shown in the following sections.
-Furthermore, the Arrhenius model will be used in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter Q (the deformation activation energy coefficient) which is of great importance in the study related to the microstructural analysis of materials.
-The PTM model is also used in this study as it is a model whose formulation does not impose a number of parameters a priori and has proven its ability in our previous work and therefore we want to test it on this type of material as it is formulated to fit any material.
+As mentioned in the introduction, many constitutive laws exist today, and the selection of one of them on the basis of explicit criteria makes the development of computational models for new materials with new types of behavior challenging.
+Since the purpose of this work is to compare the ANN model to analytical models, it is important to justify the choice of analytical models selected for this study among the many that exist in the literature.
+Among the analytical models, the Johnson-Cook (JC) model \cite{Johnson-1983} is the most used because of its simplicity of implementation linked to the reduced number of its parameters and the ease to identify them.
+It should be noted that it is not the best model but the most integrated in the Finite Elements softwares.
+This also explains the existence of several modified forms of this model.
+The Zerilli-Armstrong model, and in particular its modified forms (MZA) \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, is also widely used because it attempts to provide solutions to the shortcomings of the JC model, particularly with regard to the coupling of physical parameters.
+It is therefore also part of this study.
+The Hansel Spittel (HS) model \cite{Hensel-1978} is also one of the most widely used models in numerical simulation of casting and forging operations because it is natively integrated in the Forge software.
+Moreover, the method of identifying its parameters is very simple to perform since it is done in one step.
+It also has limitations as we will show in the following sections.
+The Arrhenius model was also chosen in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter $Q$ (the deformation activation energy coefficient) which is of great importance in the microstructural analyses of materials.
+The PTM model \cite{TizeMha-2022} is also used in this study because it is a model whose formulation does not impose a priori a number of parameters and which proved its ability in our previous works.
+We selected it to test it on this type of material because it is normally formulated to fit any type of material.
+
 %-------------------------------------------------------------------------
-\subsection{Johnson--Cook model\label{sec:JC}}
+\subsection{Johnson-Cook model\label{sec:JC}}
 %-------------------------------------------------------------------------
-The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature.
+
+The JC model, as mentioned above, is one of the most widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon^p$, strain rate $\mdot\varepsilon^p$, and temperature $T$.
 However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
-Indeed, it is formulated by describing the effect of each physical parameter (strain, strain rate and temperature) separately as a factor in the mathematical expression of the model.
-Hence its inability to describe the phenomenon of temperature-induced softening.
+Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon^p$, $\mdot\varepsilon^p$ and $T$) separately as a factor in the mathematical expression of the model.
+Hence its inability to describe the phenomenon of softening induced by temperature.
 The equation that describes this model is given as follows \cite{Johnson-1983}:
+
 \begin{equation}
-\label{eq: JCmodel}
-\sigma^y = \left(A + B\varepsilon^{p^n}\right)\left(1+C\ln\mdot\varepsilon^*\right)\left(1-T^{*^m}\right)
+\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon^p}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
 \end{equation}
-Where $\sigma^y$ is the equivalent stress flow stress, $\varepsilon^p$ is the plastic strain, ($A=\sigma^y_0$) is the elastic limit of the material, $B$ is the strain hardening's coefficient, $n$ is the strain hardening's exponent.
-$C$ and $m$ are the material constants that describe the strain rate hardening and thermal softening exponent respectively.
-$\mdot\varepsilon^*$ is the dimensionless strain rate which is given by $\mdot\varepsilon^* = \mdot\varepsilon^p/\mdot\varepsilon_0$.
-$\mdot\varepsilon^p$ and $\mdot\varepsilon_0$ are strain rate and reference strain rate respectively.
-$T^{*^m} = (T-T_0)/(T_m - T_0)$ is homologous temperature where $T, T_m$ and $T_0$ are the déformation temperature, meltinng temperature ($1460$°C in our case) and reference temperature respectively.
-For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050$°C respectively and the value of $A$ is $43.0988$ MPa.
-Here after datailed the steps for determination of the JC model parameters.
-At the reference strain rate, Equation \ref{eq: JCmodel} becomes:
-\begin{equation}
-\label{eq: JCbn}
-\sigma^y = A + B\varepsilon^{p^n}
-\end{equation}
-Taking the natural logarithm on both sides of Equation \ref{eq: JCbn} we have:
-\begin{equation}
-\label{eq:JClog1}
-\ln\left(\sigma^y-A\right)= \ln(B) + n\ln\varepsilon^p
-\end{equation}
-By plotting $\ln(\sigma^y-A)$ \versus $\ln\varepsilon^p$ (Figure \ref{fig:JCSigmaAB}) from Equation \ref{eq:JClog1}, $n$ and $B$ can be obtained as slope and intercept respectively.
-Thus, for a strain value equal to $0.1$ the values of these two parameters are $n=0.313969$ and $B=114.518$.
+where $\sigma^y$ is the flow stress, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
+The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460$°C in our case) and the reference temperature, respectively.
+
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\text{s}^{-1}$ and $T_0=1050$°C respectively.
+
+The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
+This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
+Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=11.76$~MPa.
+For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
+Thus, here, $B=23.51$~MPa and $n=0.066$.
+Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.352$.
+Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.696$.
+All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.
+
+\begin{table}[h!]
+\centering{}
+\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
+\begin{tabular}{lccccc}
+\hline
+Parameters & $A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\ \hline
+Values & $43.0988$ & $114.518$ &  $0.313969$ & $0.0995438$ & $0.898932$\\ \hline
+\label{tab:JCparams}
+\end{tabular}
+\end{table}
+
+The values predicted by the Johnson-Cook flow law (solid line) and the experimental values (dots) are compared in Figure \ref{fig:iCorrelationJC}.
+The JC model is not able to describe the evolution of the flow stress of AISI P20 for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
+The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
+As expected, the mathematical formulation of the Johnson-Cook flow law is unable to represent the stress drop at low strain rates, the JC model being only monotonically increasing with strain.
+Since most of the parameters are identified at low strain rates ($A$, $B$ and $n$), this results in a very poor fit of the model to the experimental data.
+
 \begin{figure}[!ht]
 \centering
-\includegraphics[width=0.9\columnwidth]
-{Figures/JCSigmaAB}
-\caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050$°C and $0.1$}
-\label{fig:JCSigmaAB}
-\end{figure}
-\FloatBarrier
-Once the parameters $A$, $B$ and $n$ are known and at the reference temperature, the Equation \ref{eq: JCmodel} becomes:
-\begin{equation}
-\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 + C\ln\mdot\varepsilon^*
-\end{equation}
-From this equation one can easily obtain the parameter $C$ using the linear fitting method for each strain value and averaging all these values as shown in Figure \ref{fig:JCSigmaAB1} the value is $0.0995438$.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.9\columnwidth]
-{Figures/JCSigmaAB1}
-\caption{Relationship between $\sigma^y/(A+ B\varepsilon^{p^n})$ and $\ln(\dot{\varepsilon}^*)$}
-\label{fig:JCSigmaAB1}
-\end{figure}
-The $m$ parameter is determined at the reference strain rate. Under this condition, the Equation \ref{eq: JCmodel} can be written as following:
-\begin{equation}
-\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 - T^{*^m}
-\end{equation}
-Taking the natural logarithm of both sides of that equation, we have:
-\begin{equation}
-\ln\left(1 - \frac{\sigma^y}{A + B\varepsilon^{p^n}}\right)  = m\ln T^*
-\end{equation}
-Plotting $\ln\left(1 - \frac{\sigma^y}{A + B\varepsilon^{p^n}}\right)$ as a function of $\ln T^*$ allows us to get the parameter $m$ as a slope for all values of the deformation by averaging them and the value is $0.898932$.
-Figure \ref{fig:JCSigmaT} illustrates this determination for some deformations.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.85\columnwidth]
-{Figures/JCSigmaT}
-\caption{Relationship between $\ln\left(1 - \sigma^y/\left(A + B\varepsilon^{p^n}\right)\right)$ and $\ln T^*$}
-\label{fig:JCSigmaT}
+\includegraphics[width=1.02\columnwidth]{Figures/CompExpJC}
+\caption{Comparison between the experimental and predicted flow stresses by JC model.}
+\label{fig:iCorrelationJC}
 \end{figure}
 
-The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC}.
-The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates.
-The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates.
-All parameters of JC model are in Table \ref{tab: JCparameters}.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{Figures/CompExpJC}
-\caption{Comparison between the experimental and predicted flow stresses by JC model}
-\label{fig:iCorrelationJC}
-\end{figure}
-\begin{table}[h!]
-\centering{}
-\caption{Parameters' constants of Johnson-Cook Model}
-\begin{tabular}{lccccc}
-\hline
-&         &             &		   &		  &\\
-Parameters&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
-&         &             &		   &	     &	    \\
-\hline
-Values&$43.0988$&$114.518$& $0.313969$&$0.0995438$&$0.898932$\\
-\hline
-\label{tab: JCparameters}
-\end{tabular}
-\end{table}
 %-------------------------------------------------------------------------

### 2022-10-19 Article.tex
Update of Johnson-Cook parameters and script

@@
 \usepackage{amsthm}
-%\usepackage{gensymb}
+\usepackage{gensymb}
 \usepackage{xspace}
@@
 \begin{abstract}
-The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050\text{°C}-1250\text{°C}$).
+The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050\celsius-1250\celsius$).
 Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
@@
 From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy.
-For the strain rate ($\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050$°C and $1100$°C  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$) is not well described.
+For the strain rate ($\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050\celsius$ and $1100\celsius$  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$) is not well described.
 This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high.
@@
 Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm.
-A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050$°C, $1100$°C, $1150$°C, $1200$°C and $1250$°C with the six strain rates of $0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$, $1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$ and $5.0~\text{s}^{-1}$.
+A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$, $1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$ and $5.0~\text{s}^{-1}$.
 
@@
 Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
-As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260$°C with a heating rate of $2$°C/s and held at this temperature for $5$~min to eliminate thermal gradients.
-They were then cooled with a rate of $1$°C/s to the test temperature and then held at constant temperature for $1$~min before deformation.
+As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2\celsius$/s and held at this temperature for $5$~min to eliminate thermal gradients.
+They were then cooled with a rate of $1\celsius$/s to the test temperature and then held at constant temperature for $1$~min before deformation.
 During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
@@
 Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $R_0$ are the height and radius before compression and $h$, $R_M$ and $R_T$ are the height, large radius and small radius of the specimen after compression, respectively.
-
 \begin{figure}[!ht]
@@
 
+\OP{Here, a part concerning the treatment of the Gleeble data is missing.
+You introduce the notions of $h_0$, $R_0$, $h$, $R_M$ and $R_T$ and we have no idea what they are for.
+How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}
 %------------------------------------------------------------------------
@@
 The set of flow stress $\sigma^y$ versus plastic strain $\varepsilon^p$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
-The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon^p$ but decreases with increasing temperature $T$.
+\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...} The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon^p$ but decreases with increasing temperature $T$.
 It should be noted that the plastic strain also influences the flow stress.
@@
 These two phenomena explain the different shapes of the flow stress curves observed for this alloy.
-As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260$°C before and after the compression phase.
-As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample \OP{What are the temperature and strain rate related with this micrography}.
+As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
+As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample.
+\OP{What are the temperature and strain rate related with this micrography}
 From the results reported in Figure \ref{fig:rawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.
@@
 where $\sigma^y$ is the flow stress, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
-The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460$°C in our case) and the reference temperature, respectively.
+The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
 
-For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\text{s}^{-1}$ and $T_0=1050$°C respectively.
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\text{s}^{-1}$ and $T_0=1050\celsius$ respectively.
 
@@
 This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
-Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=11.76$~MPa.
+Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=(11.758$~MPa.
 For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
-Thus, here, $B=23.51$~MPa and $n=0.066$.
-Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.352$.
-Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.696$.
+Thus, here, $B=25.563$~MPa and $n=0.139$.
+Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.338$.
+Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.730$.
 All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.
@@
 Parameters & $A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\ \hline
-Values & $43.0988$ & $114.518$ &  $0.313969$ & $0.0995438$ & $0.898932$\\ \hline
+Values & $11.758$ & $25.563$ &  $0.139$ & $0.338$ & $0.730$\\ \hline
 \label{tab:JCparams}
@@
 \section{Conclusion \label{sec:Conclusion}}
-Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050$°C - $1250$°C, strains ($0.025$ - $0.7$), strain rates ($0.001\ \text{s}^{-1}$ - $5\ \text{s}^{-1}$) and the following conclusions were drawn.
+Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050\celsius$ - $1250\celsius$, strains ($0.025$ - $0.7$), strain rates ($0.001\ \text{s}^{-1}$ - $5\ \text{s}^{-1}$) and the following conclusions were drawn.
 \begin{enumerate}

### 2022-10-19 Article.tex
Starting updating MZA model

@@
 %-------------------------------------------------------------------------
-
+\OP{This introduction paragraph is entirely copied from the WJET publication}
 As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.

### 2022-10-21 Article.tex
Correction of HS model

@@
 \begin{table}[h!]
-\centering{}
+\centering
 \caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
-\begin{tabular}{lccccc}
+\begin{tabular}{ccccc}
 \hline
-Parameters & $A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\ \hline
-Values & $11.758$ & $25.563$ &  $0.139$ & $0.338$ & $0.730$\\ \hline
+$A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
+$11.758$ & $25.563$ &  $0.139$ & $0.338$ & $0.730$\\ \hline
 \label{tab:JCparams}
@@
 %-------------------------------------------------------------------------
-The Hansel-Spittel model is one of the least known models in terms of its  integration in software for finite element simulation although the determination of its parameters is easier than the JC model.
-A single programming command is sufficient for its identification.
-However, this model has some difficulties as it loses its accuracy when all parameters are taken into account.
-For this reason, several authors limit its use to $5$ or $6$ parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.
-In this paper the good predictions are with $5$ parameters summarized in Table \ref{tab: HSparameters}.
-The equation of the model is given by the following relation:
+
+\OP{Are you absolutely sure that the HS model takes into account the plastic strain $\varepsilon^p$ and not the strain $\varepsilon$ ?
+I don't think that it is the plastic strain, so I changed the mathematical expression of $\sigma^y$}
+The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in finite element simulation software, although the determination of its parameters is easier than that of the JC or MZA model.
+The programming of a simple identification script is sufficient to identify its parameters for a given material. 
+The equation of the HS model is given by the following relation:
+\begin{equation}
+\sigma^y = A~e^{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~e^{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~e^{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8}\label{eq:HS}
+\end{equation}
+where $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature as proposed earlier. 
+The coefficients $A$ and $m_i$ are the parameters of the model to be identified. 
+However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification. 
+For its identification, several authors restrict its expression to a reduced number of $5$ or $6$ $m_i$ parameters only by truncating its expression according to the number of parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.
+
+In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
+From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab: HSparameters}.
+\begin{table}[h!]
+\centering
+\caption{Parameters' values of the Hansel and Spittel flow law for the P20 steel.}
+\begin{tabular}{ccccc}
+\hline
+$A~(\text{MPa})$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
+$5954.043$ & $-3.358\times10^{-3}$ & $2.641\times10^{-1}$ & $-8.678\times10^{-2}$ & $2.269\times10^{-4}$\\\hline
+& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
+& $-4.216\times10^{-4}$ & $-5.613\times10^{-2}$ & $2.264\times10^{-4}$ & $0$\\\hline
+\label{tab: HSparameters}
+\end{tabular}
+\end{table}
+
+The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS}. 
+It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important. 
+This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate. 
+The DRX phenomena cannot be reproduced by this type of model.
+
 \begin{figure}[!ht]
@@
 \end{figure}
-\begin{equation}
-\sigma^y = Ae^{m_1T}\varepsilon^{p^{m_2}}\mdot\varepsilon^{p^{m_3}}e^{\frac{m_4}\varepsilon^p}(1+\varepsilon^p)^{m_5T}e^{m_6\varepsilon^p}\mdot\varepsilon^{p^{m_7T}}T^{m_8}
-\end{equation}
-Where $\sigma^y$ is the flow stess, $\varepsilon^p$ strain, $\mdot\varepsilon^p$ strain rate and $T$ temperature.
-The other coefficients $A$ and $m_j$ are model constants up to $m_5$ for our case.
-Comparison of predicted values of the HS model and experimental values is shown in Figure \ref{fig:iCorrelationHS}.
-It appears that this model as well as the previous ones do not predict the experimental well and the gap is relatively large.
-This shows that this model is not appropriate for the characterisation of this alloy.
-\begin{table}[h!]
-\centering{}
-\caption{Parameters' constants of Hansel and Spittel Model}
-\begin{tabular}{llccccc}
-\hline
-&         &             &		   &		 &			   &\\
-Parameters&$A_0(\text{MPa})$    &$m_1$        & $m_2$     & $m_3$   & $m_4$       &$m_5$\\
-&         &             &		   &	     &	           &\\
-\hline
-Values&$9254.77$&$-0.00375057$& $0.208975$&$0.184238$&$-0.00287837$&$-0.000583287$\\
-\hline
-\label{tab: HSparameters}
-\end{tabular}
-\end{table}
+
 %----------------------------------------------------------------------------------

### 2022-10-21 Article.tex
Update of whole Article concerning plastic strain

@@
 \newcommand{\R}{\text{R}}
+\newcommand{\ps}{\text{s}^{-1}}
 %\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
@@
 \begin{abstract}
-The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050\celsius-1250\celsius$).
+The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \ps - 5\ \ps$) and temperatures ($1050\celsius-1250\celsius$).
 Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
@@
 From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy.
-For the strain rate ($\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050\celsius$ and $1100\celsius$  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$) is not well described.
+For the strain rate ($\mdot\varepsilon = 0.01\ \ps$)  the AR model fails to describe the flow for temperatures $1050\celsius$ and $1100\celsius$  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon = 0.1\ \ps$) is not well described.
 This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high.
-Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
+Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
 The results of the ANN model show a very good agreement between the predictions and the experiment.
@@
 Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm.
-A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$, $1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$ and $5.0~\text{s}^{-1}$.
+A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1.0~\ps$, $2.0~\ps$ and $5.0~\ps$.
 
@@
 
-The set of flow stress $\sigma^y$ versus plastic strain $\varepsilon^p$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
-\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...} The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon^p$ but decreases with increasing temperature $T$.
-It should be noted that the plastic strain also influences the flow stress.
-Indeed, for the lowest strain rates $\mdot\varepsilon^p$, the flow stress $\sigma^y$ increases with the plastic strain $\varepsilon^p$ until a value of about $\varepsilon^p=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
-For the highest strain rates ($1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$, and $5.0~\text{s}^{-1}$), the flow stress increases throughout the test.
+The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
+\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...} The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
+It should be noted that the strain also influences the flow stress.
+Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
+For the highest strain rates ($1.0~\ps$, $2.0~\ps$, and $5.0~\ps$), the flow stress increases throughout the test.
 One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
@@
 
-The JC model, as mentioned above, is one of the most widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon^p$, strain rate $\mdot\varepsilon^p$, and temperature $T$.
+The JC model, as mentioned above, is one of the most widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon$, strain rate $\mdot\varepsilon$, and temperature $T$.
 However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
-Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon^p$, $\mdot\varepsilon^p$ and $T$) separately as a factor in the mathematical expression of the model.
+Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model.
 Hence its inability to describe the phenomenon of softening induced by temperature.
@@
 \begin{equation}
-\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon^p}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
+\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
 \end{equation}
-where $\sigma^y$ is the flow stress, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
+where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
 The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
 
-For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\text{s}^{-1}$ and $T_0=1050\celsius$ respectively.
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$ respectively.
 
@@
 This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
-Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=(11.758$~MPa.
+Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=11.758$~MPa.
 For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
@@
 \label{eq:MZA-model}
-\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)\right]
+\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
 \end{equation}
@@
 
-Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon^p=\mdot{\varepsilon}_0)$.
-When the current strain rate $\mdot\varepsilon^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
+Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$.
+When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
 \begin{equation}
@@
 \begin{equation}
-\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)
+\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
 \end{equation}
 with $S_2=C_5+C_6\left(T-T_0\right)$.
-Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
+Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
 The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}.
@@
 However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification. 
-For its identification, several authors restrict its expression to a reduced number of $5$ or $6$ $m_i$ parameters only by truncating its expression according to the number of parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.
+For its identification, several authors restrict its expression to a reduced number of $5$ or $6$ $m_i$ parameters only, by forcing a zero value for the other parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.
 
@@
 
-The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS}. 
-It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important. 
+The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS} where the dots represent the experimental values and the solid lines are the values predicted by the HS flow law.
+It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1.0~\ps$. 
 This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate. 
@@
 The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material.
-Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot\varepsilon^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation.
+Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot\varepsilon$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation.
 This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature.
@@
 \label{eq:ARmodel1}
-\mdot\varepsilon^p = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)
+\mdot\varepsilon = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)
 \end{equation}
@@
 \label{eq:ARmodel2}
-\mdot\varepsilon^p = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)
+\mdot\varepsilon = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)
 \end{equation}
@@
 \label{eq:ARmodel}
-\mdot\varepsilon^p = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)
+\mdot\varepsilon = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)
 \end{equation}
-Where $\mdot\varepsilon^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants.
+Where $\mdot\varepsilon$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants.
 To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:
@@
 \label{eq:Zparam}
-Z = \mdot\varepsilon^p\exp\left(\frac{Q}{RT}\right)
+Z = \mdot\varepsilon\exp\left(\frac{Q}{RT}\right)
 \end{equation}
@@
 \begin{equation}
-\ln \sigma^y = \frac{1}{n_1}\ln \mdot\varepsilon^p -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}
+\ln \sigma^y = \frac{1}{n_1}\ln \mdot\varepsilon -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}
 \end{equation}
 \begin{equation}
-\sigma^y = \frac{1}{\beta}\ln \mdot\varepsilon^p - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}
+\sigma^y = \frac{1}{\beta}\ln \mdot\varepsilon - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}
 \end{equation}
-From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot\varepsilon^p)$  and $\sigma^y = f(\ln\mdot\varepsilon^p)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$.
+From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot\varepsilon)$  and $\sigma^y = f(\ln\mdot\varepsilon)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$.
 It should be noted that later in this document all values of strain will be taken into account.
@@
 \label{eq:lnSinh}
-\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot\varepsilon^p  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
+\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot\varepsilon  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
 \end{equation}
@@
 \label{eq:parQ}
-Q = R\left[\frac{\partial \ln \mdot\varepsilon^p}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot\varepsilon^p}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
+Q = R\left[\frac{\partial \ln \mdot\varepsilon}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot\varepsilon}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
 \end{equation}
@@
 The gap between experimental and prediction is small.
-But for the strain rate $\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$ and for the two low temperatures values, the AR model is not able to predict the softening.
+But for the strain rate $\mdot\varepsilon = 0.01\ \ps$ and for the two low temperatures values, the AR model is not able to predict the softening.
 \begin{equation}
@@
 \label{eq:PTM-model}
-\sigma^y(\varepsilon^p,\mdot\varepsilon^p,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)\right]
+\sigma^y(\varepsilon^p,\mdot\varepsilon,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
 \end{equation}
@@
 Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}.
-The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$ the prediction in not quite good.
+The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot\varepsilon = 0.1\ \ps$ the prediction in not quite good.
 The deviation between the predicted values and the experimental values is relatively good.
@@
 The architecture of the network used in this study is shown in Figure \ref{fig:ANN-scheme-2HL}.
-After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon^p$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress.
+After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress.
 The good performance of the model is found to be stable between $800$ and $1000$ epochs.
@@
 \end{equation}
-Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot\varepsilon^p/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively.
+Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot\varepsilon/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively.
 $X_n$ is the normalized data of the corresponding $X$.
@@
 \subsection{Interpolation validation}
-For the validation of the interpolation, the chosen strain rate is $\mdot\varepsilon^p = 1.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot\varepsilon^p = 0.001\ \text{s}^{-1}$ , $\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$ , $\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$, $\mdot\varepsilon^p = 2.0\ \text{s}^{-1}$  and $\mdot\varepsilon^p = 5.0\ \text{s}^{-1}$.
+For the validation of the interpolation, the chosen strain rate is $\mdot\varepsilon = 1.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 2.0\ \ps$  and $\mdot\varepsilon = 5.0\ \ps$.
 The Figure \ref{fig:inCombinaison} shows the comparison between the predictions of the analytical and ANN models and the experiment.
@@
 \subsection{Extrapolation validation}
-For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon^p = 5.0\ \text{s}^{-1}$ and those used for identification (training for ANN) are $\mdot\varepsilon^p = 0.001\ \text{s}^{-1}$ , $\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$ , $\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$, $\mdot\varepsilon^p = 1.0\ \text{s}^{-1}$  and $\mdot\varepsilon^p = 2.0\ \text{s}^{-1}$.
+For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 1.0\ \ps$  and $\mdot\varepsilon = 2.0\ \ps$.
 Figure \ref{fig:exCombinaison} shows the comparison between the predictions  and the experimental.
@@
 \section{Conclusion \label{sec:Conclusion}}
-Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050\celsius$ - $1250\celsius$, strains ($0.025$ - $0.7$), strain rates ($0.001\ \text{s}^{-1}$ - $5\ \text{s}^{-1}$) and the following conclusions were drawn.
+Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050\celsius$ - $1250\celsius$, strains ($0.025$ - $0.7$), strain rates ($0.001\ \ps$ - $5\ \ps$) and the following conclusions were drawn.
 \begin{enumerate}

### 2022-10-21 Article.tex
Update text and figures to remove plastic strain reference

@@
 %-------------------------------------------------------------------------
-\OP{This introduction paragraph is entirely copied from the WJET publication}
+\OP{This introduction paragraph is entirely copied from the WJET publication, P.T.M. must rewrite this part of the text !}
 As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
@@
 
-\OP{Are you absolutely sure that the HS model takes into account the plastic strain $\varepsilon^p$ and not the strain $\varepsilon$ ?
-I don't think that it is the plastic strain, so I changed the mathematical expression of $\sigma^y$}
 The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in finite element simulation software, although the determination of its parameters is easier than that of the JC or MZA model.

### 2022-10-25 Article.tex
.texFile updated

@@
 You introduce the notions of $h_0$, $R_0$, $h$, $R_M$ and $R_T$ and we have no idea what they are for.
-How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}
+How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}\textcolor{red}{The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A\ \text{and}\ \varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
+As there are noises from raw data, filter method is applied to remove noise and have more smooth data.
+For further usage of  data in numerical simulation elastic parts have been removed}.
 %------------------------------------------------------------------------
@@
 The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
-\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...} The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
+\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}\textcolor{red}{almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
+We have decided to limit the identification up to $0.7$ because for strain rates $2$ and $5$, stresses are note good}.
+The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
 It should be noted that the strain also influences the flow stress.
@@
 As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
-As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample.
+As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample \textcolor{red}{held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$}.
 \OP{What are the temperature and strain rate related with this micrography}
@@
 \OP{This introduction paragraph is entirely copied from the WJET publication, P.T.M. must rewrite this part of the text !}
-As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
-Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}.
-But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
+\textcolor{red}{The MZA which is the modified form of ZA model, as the JC model is one of widely used models and implemented in many sofwares like Abaqus.
+The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experimental.
+Indeed, in the JC model, those parameters are considered separately where they are simultaneaously considered in MZA and for that formulation MZA is prefered to JC model} \cite{Hull-2011}.
+But the original form of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
 \begin{equation}
@@
 
-In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
+In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}\textcolor{red}{already done}.
 From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab: HSparameters}.

### 2022-10-31 Article.tex
First modifications on HS models

--- 2022-10-21 Article.tex
@@
 %\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
-\newcommand{\e}[1]{\exp\left({#1}\right)}
+%\newcommand{\e}[1]{\exp\left({#1}\right)}
+\newcommand{\e}[1]{{\rm e}^{#1}}
 \newcommand{\lay}[1]{^{(#1)}}
@@
 %-------------------------------------------------------------------------
-\subsection{Hansel and Spittel\label{sec:HSmodel}}
+\subsection{Hansel and Spittel model\label{sec:HSmodel}}
 %-------------------------------------------------------------------------
@@
 \begin{equation}
-\sigma^y = A~e^{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~e^{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~e^{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8}\label{eq:HS}
+\sigma^y = A~\e{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~\e{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~\e{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8} \label{eq:HS}
 \end{equation}
@@
 \centering
-\caption{Parameters' values of the Hansel and Spittel flow law for the P20 steel.}
+\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
 \begin{tabular}{ccccc}
@@
 
-The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS} where the dots represent the experimental values and the solid lines are the values predicted by the HS flow law.
+The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
 It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1.0~\ps$.
@@
 %----------------------------------------------------------------------------------
-\subsection{Arrhenius model (AR model), \label{sec:ARmodel}}
+\subsection{Arrhenius model\label{sec:ARmodel}}
 %----------------------------------------------------------------------------------
-The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material.
-Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot\varepsilon$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation.
-This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature.
-The following equations describe the Arrhenius model.
+
+The Arrhenius type model \cite{Sellars-1966} is one of the most used models in the framework of material forming, especially when it comes to studying the microstructure of the material.
+Indeed, this model takes into account the physical phenomena that describe the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ expressed as power law, exponential law and hyperbolic sine.
+This makes it easier to describe the softening phenomenon observed in the material due to increasing temperature. 
+The following equations describe the Arrhenius model:
 \begin{equation}
-\label{eq:ARmodel1}
-\mdot\varepsilon = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)
+\mdot\varepsilon =
+\begin{cases}
+A_1 \sigma^{y^{n_1}} \exp{\left(-\frac{Q}{RT}\right)} & \alpha\sigma^y < 0.8\\
+A_2 \exp(\beta\sigma^y) \exp{\left(-\frac{Q}{RT}\right)} & \alpha\sigma^y > 1.2\\
+A_3 \left[\sinh{\left(\alpha\sigma^y\right)}\right]^{n_2} \exp{\left(-\frac{Q}{RT}\right)} & \text{for all }\sigma^y
+\end{cases}
+\label{eq:ArDef}
+\end{equation}
+with:
+\begin{equation}
+Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}
+\end{equation}
+where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha n_1$ are dependent of the material.
+The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperature by regression method.
+Combination of Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allow expressing the flow stress $\sigma^y$ as a function of the $Z$ parameter:
+\begin{equation}
+\sigma^y = \frac{1}{\alpha} \ln\left\{\left(\frac{Z}{A}\right)^{1/n} + \left[1 + \left(\frac{Z}{A}\right)^{2/n}\right]^{1/2}\right\}
+\end{equation}
+
+To obtain the constitutive equation, it is necessary to determine all the parameters $A$, $Q$ $\alpha$ and $n$ for a given material. 
+The strain has a significant non-linear influence on the behavior of the material by the mechanism of strain hardening and softening at high values of deformation. 
+A compensation in strain must therefore be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$ $\alpha$ and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
+\begin{equation}
+A(\varepsilon) = \exp{\left[\ln A_0 + \ln A_1\varepsilon + \ln A_2\varepsilon^2 + \ln A_3\varepsilon^3 + \cdots + \ln A_m\varepsilon^m\right]}
+\label{eq:ArA}
 \end{equation}
 \begin{equation}
-\label{eq:ARmodel2}
-\mdot\varepsilon = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)
+Q(\varepsilon) = Q_0 + Q_1\varepsilon + Q_2\varepsilon^2 + Q_3\varepsilon^3 + \cdots + Q_m\varepsilon^m
+\label{eq:ArQ}
 \end{equation}
 \begin{equation}
-\label{eq:ARmodel}
-\mdot\varepsilon = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)
+\alpha(\varepsilon) = \alpha_0 + \alpha_1\varepsilon + \alpha_2\varepsilon^2 + \alpha_3\varepsilon^3 + \cdots + \alpha_m\varepsilon^m
+\label{eq:Aralpha}
 \end{equation}
-Where $\mdot\varepsilon$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants.
-To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:
 \begin{equation}
-\label{eq:Zparam}
-Z = \mdot\varepsilon\exp\left(\frac{Q}{RT}\right)
+n(\varepsilon) = n_0 + n_1\varepsilon + n_2\varepsilon^2 + n_3\varepsilon^3 + \cdots + n_m\varepsilon^m
+\label{eq:Arn}
 \end{equation}
-By replacing the Equation (\ref{eq:ARmodel}) inton Equation (\ref{eq:Zparam}) it comes:
+
+The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
+The values $\ln A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
+This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates.
+Equation (\ref{eq:ArStress}) is finally used:
 \begin{equation}
-\label{eq:Zparam1}
-Z = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2} \qquad \Rightarrow \qquad \sinh(\alpha\sigma^y) = \left(\frac{Z}{A_3}\right)^{1/n_2}
+\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
+\label{eq:ArStress}
 \end{equation}
-Furthermore, it is known that:
-\begin{equation}
-arc\sinh(x) = \ln\left(x + \sqrt{1+x^2}\right)
-\end{equation}
-Therefore Equation (\ref{eq:Zparam1}) becomes and which is actually the Arhenius model:
-\begin{equation}
-\sigma^y = \frac{1}{\alpha}\ln\left\{\left(\frac{Z}{A_3}\right)^{1/n_2} + \left[1 + \left(\frac{Z}{A_3}\right)^{2/n_2}\right]^{1/2}\right\}
-\end{equation}
-To obtain the constitutive equation, all parameters $\alpha$, $Q$, $n_2$, and $A_3$ needed to be determined.
-The following part shows the calculation procedures of these material constants at $\varepsilon^p = 0.1$ as example.
+
+The following part shows the calculation procedures of these material constants at $\varepsilon = 0.1$ as example. 
 Taking the natural logarithm of Equations (\ref{eq:ARmodel1}) and (\ref{eq:ARmodel2}), the following relationships can be obtained:
@@
 %-------------------------------------------------------------------------
-\subsection{Artificial neural network model\label{sec:ANNmodel}}
+\subsection{Artificial Neural Network model\label{sec:ANNmodel}}
 %--------------------------------------------------------------------------

### 2022-10-31 Article.tex

@@
 From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab: HSparameters}.
+
 \begin{table}[h!]

### 2022-11-07 Article.tex
Modification and finalization of the AR model

@@
 \caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
-\begin{tabular}{lllllllc}
+\begin{tabular}{llllllc}
 \hline
-&         &             &		   &		 &			   &&\\
-Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
-&         &             &		   &	     &	           &&\\
-\hline
-Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
+$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
+$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
 \hline
@@
 In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
-From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab: HSparameters}.
+From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HSparameters}.
 
@@
 & $-4.216\times10^{-4}$ & $-5.613\times10^{-2}$ & $2.264\times10^{-4}$ & $0$\\\hline
-\label{tab: HSparameters}
+\label{tab:HSparameters}
 \end{tabular}
@@
 \begin{equation}
-A(\varepsilon) = \exp{\left[\ln A_0 + \ln A_1\varepsilon + \ln A_2\varepsilon^2 + \ln A_3\varepsilon^3 + \cdots + \ln A_m\varepsilon^m\right]}
+A(\varepsilon) = \exp{\left[\ln\!A_0 + \ln\!A_1\varepsilon + \ln\!A_2\varepsilon^2 + \ln\!A_3\varepsilon^3 + \cdots + \ln\!A_m\varepsilon^m\right]}
 \label{eq:ArA}
@@
 The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
-The values $\ln A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
+The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method. 
+Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:ARparameters}. 
+\begin{table}[h!]
+\centering
+\caption{Parameters' values of the Arrhenius flow law for the P20 steel}
+\begin{tabular}{llll}
+\hline
+$\alpha_i~(\text{MPa}^{-1})$ & $Q_i~(\text{MJ.mol}^{-1})$ & $\ln\!A_i~(\ps)$ & $n_i$\\
+\hline
+$\alpha_0=0.0392$ & $Q_0=0.467$ & $\ln\!A_0=35.8092$ & $n_0=4.8216$ \\
+$\alpha_1=-0.4092$ & $Q_1=-0.6516$ & $\ln\!A_1=-58.8219$ & $n_1=3.2813$ \\
+$\alpha_2=3.9229$ & $Q_2=7.6084$ & $\ln\!A_2=740.3302$ & $n_2=71.5963$ \\
+$\alpha_3=-20.713$ & $Q_3=-48.016$ & $\ln\!A_3=-5049.2979$ & $n_3=-1956.1871$ \\
+$\alpha_4=62.1376$ & $Q_4=66.795$ & $\ln\!A_4=11305.3573$ & $n_4=14460.9217$ \\
+$\alpha_5=-99.9999$ & $Q_5=468.8898$ & $\ln\!A_5=20220.008$ & $n_5=-54309.8814$ \\
+$\alpha_6=58.7108$ & $Q_6=-2303.1535$ & $\ln\!A_6=-153871.1135$ & $n_6=117612.0374$ \\
+$\alpha_7=54.3688$ & $Q_7=4370.6566$ & $\ln\!A_7=317981.5396$ & $n_7=-148819.8996$ \\
+$\alpha_8=-99.9999$ & $Q_8=-3939.3826$ & $\ln\!A_8=-297254.899$ & $n_8=102387.2537$ \\
+$\alpha_9=42.5233$ & $Q_9=1397.0283$ & $\ln\!A_9=107585.17$ & $n_9=-29621.1293$ \\
+\hline
+\label{tab:ARparameters}
+\end{tabular}
+\end{table}
 This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates. 
-Equation (\ref{eq:ArStress}) is finally used:
+Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$: 
 \begin{equation}
@@
 
-The following part shows the calculation procedures of these material constants at $\varepsilon = 0.1$ as example. 
-Taking the natural logarithm of Equations (\ref{eq:ARmodel1}) and (\ref{eq:ARmodel2}), the following relationships can be obtained:
-\begin{equation}
-\ln \sigma^y = \frac{1}{n_1}\ln \mdot\varepsilon -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}
-\end{equation}
-\begin{equation}
-\sigma^y = \frac{1}{\beta}\ln \mdot\varepsilon - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}
-\end{equation}
-From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot\varepsilon)$  and $\sigma^y = f(\ln\mdot\varepsilon)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$.
-It should be noted that later in this document all values of strain will be taken into account.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.9\columnwidth]{Figures/LnAlp}
-\caption{Relationship between $\ln \sigma^y$ and $\ln \dot{\varepsilon}^p$}
-\label{fig:LnAlp}
-\end{figure}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.9\columnwidth]{Figures/LnSinhE0}
-\caption{Relationship between $\sigma^y$ and $\ln \dot{\varepsilon}^p$}
-\label{fig:LnSinhE0}
-\end{figure}
-The values of those parameters are therefore equal to $n_1=6.78177$ and $\beta=0.150563$ ($\alpha=\beta/n_1 = 0.0222011$).
-From Equation (\ref{eq:ARmodel}), the following relationship can be obtained:
-\begin{equation}
-\label{eq:lnSinh}
-\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot\varepsilon  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
-\end{equation}
-By applying the chain derivative rule, we get the following relationship to calculate the energy activation coefficient $Q$.
-\begin{equation}
-\label{eq:parQ}
-Q = R\left[\frac{\partial \ln \mdot\varepsilon}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot\varepsilon}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
-\end{equation}
-From Equation (\ref{eq:lnSinh}) and Equation (\ref{eq:parQ}) we can deduce the parameters $n_2 $ and $Q $ from the slopes of the functions $\ln \sinh(\alpha\sigma^y) = f(\ln \dot{\varepsilon}^p)$ and $\ln \sinh(\alpha\sigma^y) = g(1/T)$ as shown in Figure \ref{fig:LnSinhE} and Figure \ref{fig:LnSinhT}.
-Thus those values are $4.94273$ and $437.385\ KJ.mol^{-1}$ respectively.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.9\columnwidth]{Figures/LnSinhE}
-\caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $\ln \dot{\varepsilon}^p$}
-\label{fig:LnSinhE}
-\end{figure}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.9\columnwidth]{Figures/LnSinhT}
-\caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $1/T$}
-\label{fig:LnSinhT}
-\end{figure}
-As these coefficients are calculated for a single strain value as example, it is possible to take into account their dependence on all strain values. 
-Hence the need to find a function for each coefficient for all temperatures and strains. 
-Figure  \ref{fig:ARparameters} shows the relationships between $\alpha$, $Q$, $n_2$, $\ln A$ and true strain $\varepsilon^p$ for AISI P20 alloy using leasquare method. 
-For each parameter (whose strain dependant expressions are given by Equations \ref{eq:alpha}, \ref{eq:Q}, \ref{eq:n} and \ref{eq:lnA}), the values of constants are summarized in Table \ref{tab: ARparameters}.
-Figure \ref{fig:iCorrelationAR} is the comparison of predicted values of AR model and experimental values where the correlaton is good. 
-The gap between experimental and prediction is small. 
-But for the strain rate $\mdot\varepsilon = 0.01\ \ps$ and for the two low temperatures values, the AR model is not able to predict the softening.
-\begin{equation}
-\label{eq:alpha}
-\alpha(\varepsilon^p) = \alpha_0 + \alpha_1\varepsilon^{{p^1}} + \alpha_2\varepsilon^{p^2} + \alpha_3\varepsilon^{p^3} + \alpha_4\varepsilon^{p^4} + \alpha_5\varepsilon^{p^5} + \alpha_6\varepsilon^{p^6}
-\end{equation}
-\begin{equation}
-\label{eq:Q}
-Q(\varepsilon^p) = Q_0 + Q_1\varepsilon^{{p^1}} + Q_2\varepsilon^{p^2} + Q_3\varepsilon^{p^3} + Q_4\varepsilon^{p^4} + Q_5\varepsilon^{p^5} + Q_6\varepsilon^{p^6}
-\end{equation}
-\begin{equation}
-\label{eq:n}
-n_2(\varepsilon^p) = n_{20} + n_{21}\varepsilon^{{p^1}} + n_{22}\varepsilon^{p^2} + n_{23}\varepsilon^{p^3} + n_{24}\varepsilon^{p^4} + n_{25}\varepsilon^{p^5} + n_{26}\varepsilon^{p^6}
-\end{equation}
-\begin{equation}
-\label{eq:lnA}
-\ln A(\varepsilon^p) = \ln A_0 + \ln A_1\varepsilon^{{p^1}} + \ln A_2\varepsilon^{p^2} + \ln A_3\varepsilon^{p^3} + \ln A_4\varepsilon^{p^4} + \ln A_5\varepsilon^{p^5} + \ln A_6\varepsilon^{p^6}
-\end{equation}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]{Figures/ARparameters}
-\caption{Relationships between $\alpha$ (a)  , $Q$ (b) , $n_2$ (c)  and $lnA$ (d)  with the plastic strain $\varepsilon^p$ by polynomial functions}
-\label{fig:ARparameters}
-\end{figure}
-\begin{table}[h!]
-\centering{}
-\caption{Parameters' constants of Arrhenius Model}
-\begin{tabular}{lllll}
-\hline
-&					  &				      &				        &\\
-Parameters&$\alpha$   &$Q (MJ.mol^{-1})$ &$n_2$                &$\ln A$\\
-&					  &				      &				        &\\
-\hline
-&$\alpha_0 = 0.03702$ & $Q_0 = 0.454825$  & $n_{20} = 4.49273$  & $\ln A_0 = 34.7431$\\
-&$\alpha_1 =-0.301107$& $Q_1 = -0.450492$ & $n_{21}=15.2803$    & $\ln A_1 =-36.826$\\
-&$\alpha_2 = 2.19877$ & $Q_2=4.76922 $    & $n_{22} =-170.126$  & $\ln A_2 =393.423$\\
-Values&$\alpha_3=-8.30819$&$Q_3 =-31.6016$& $n_{23} =651.241$   & $\ln A_3 =-2611.42$\\
-&$\alpha_4 = 16.823$  & $Q_4 = 89.8821$   & $n_{24} =-1225.15$  & $\ln A_4 =7436.98$\\
-&$\alpha_5 =-17.2732$ & $Q_5 =-113.829$   & $n_{25} =1143.54$   & $\ln A_5 =-9426.54$\\
-&$\alpha_6 =7.04342$  & $Q_6 = 53.3699$   & $n_{26} =-423.066$  & $\ln A_6 =4422.49$\\
-\hline
-\label{tab: ARparameters}
-\end{tabular}
-\end{table}
+Figure \ref{fig:iCorrelationAR} shows the comparison of the values predicted by the Arrhenius model and the experimental values. 
+The difference between the experimental and predicted values is small. 
+But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
+
 \begin{figure}[!ht]

### 2022-11-07 Article.tex
Update PTM model

@@
 \hline
-$\alpha_i~(\text{MPa}^{-1})$ & $Q_i~(\text{MJ.mol}^{-1})$ & $\ln\!A_i~(\ps)$ & $n_i$\\
+\multicolumn{1}{c}{$\alpha_i~(\text{MPa}^{-1})$} & \multicolumn{1}{c}{$Q_i~(\text{MJ.mol}^{-1})$} & \multicolumn{1}{c}{$\ln\!A_i~(\ps)$} & \multicolumn{1}{c}{$n_i$}\\
 \hline
@@
 \end{figure}
-\FloatBarrier
+
 %-------------------------------------------------------------------------
-\subsection{PTM model\label{sec:ProposedModel}}
+\subsection{PTM model\label{sec:PTM}}
 %--------------------------------------------------------------------------
-The PTM model is a generalized formulation of the MZA model. 
-Indeed, the shortcomings of the MZA model are taken into account in this formulation, which makes the model flexible for any type of studied material as it does not require a limited number of parameters.
-The intrinsic functions of the model, which are the polynomial type functions, will determine the parameters of the model according to the degree of the polynomial, which provides a good fit for each function.
-The equation describing the PTM model is therefore given by.
+
+The PTM model \cite{TizeMha-2022} is a generalized formulation of the MZA model presented in Section \ref{sec:MZA}.
+When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to make the PTM model flexible for any type of material studied because there is no need for a limited number of parameters as in the MZA model.
+Its construction is based on the use of polynomial functions as in the AR model.
+Thus, the intrinsic functions of the model, of polynomial type, allow to adjust the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
+The equation describing the PTM model is therefore given by :
 \begin{equation}
 \label{eq:PTM-model}
-\sigma^y(\varepsilon^p,\mdot\varepsilon,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
+\sigma^y = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
 \end{equation}
@@
 The deviation between the predicted values and the experimental values is relatively good.
-\begin{table}[!h]
-\centering{}
-\caption{Parameters of PTM model\label{tab:PTM-parameters}}
-\begin{tabular}{cc}
+
+\begin{table}[h!]
+\centering
+\caption{Parameters' values of the PTM flow law for the P20 steel}
+\begin{tabular}{llll}
 \hline
-&   \\
-Parameters &Values\\
-&   \\
+\multicolumn{1}{c}{$A_i$} & \multicolumn{1}{c}{$B_i$} & \multicolumn{1}{c}{$C_0^i$} & \multicolumn{1}{c}{$C_1^i$}\\
 \hline
-$A_0 (\text{MPa})$ & $62.314$ \\
-$A_1 (\text{MPa})$ & $559.827$ \\
-$A_2 (\text{MPa})$ & $-2160.03$ \\
-$A_3 (\text{MPa})$ & $4641.94,$ \\
-$A_4 (\text{MPa})$ & $-5193.06$ \\
-$A_5 (\text{MPa})$ & $2379.1$ \\
-$B_0 $   & $-0.0035805$\\
-$B_1 $   & $0.00282334$ \\
-$B_2 $   & $-0.00775301$\\
-$B_3 $   & $0.0085135$ \\
-$B_4 $   & $-0.00412815$\\
-$C_0^0 $ & $0.148304$ \\
-$C_0^1 $ & $-0.301958$ \\
-$C_0^2 $ & $2.2706$ \\
-$C_0^3 $ & $-5.33003$ \\
-$C_0^4 $ & $5.48971$ \\
-$C_0^5 $ & $-2.11566$\\
-$C_1^0 $ & $-3.74842\ \times10^{-7}$\\
-$C_1^1 $ & $0.00165233$\\
-$C_1^2 $ & $-0.00270485$ \\
-$C_1^3 $ & $-0.000483867$\\
-$C_1^4 $ & $0.00174818$ \\
+$A_0=16.8528$ & $B_0=-0.0035$ & $C_0^0=0.1607$ & $C_1^0=0.0$\\
+$A_1=340.6451$ & $B_1=-0.0131$ & $C_0^1=-0.6201$ & $C_1^1=0.0026$\\
+$A_2=-1959.4041$ & $B_2=-0.0044$ & $C_0^2=4.9515$ & $C_1^2=-0.0035$\\
+$A_3=4835.9698$ & $B_3=0.2217$ & $C_0^3=-13.1693$ & $C_1^3=-0.0222$\\
+$A_4=-5517.6094$ & $B_4=-0.4988$ & $C_0^4=15.2499$ & $C_1^4=0.0608$\\
+$A_5=2405.8399$ & $B_5=0.3211$ & $C_0^5=-6.5869$ & $C_1^5=-0.0412$\\
 \hline
+\label{tab:PTM-parameters}
 \end{tabular}
 \end{table}
+
 \begin{figure}[!ht]

### 2022-11-09 Article.tex
Update of main tex

@@
 This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
-Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=11.758$~MPa.
+Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=13.5143$~MPa.
 For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
-Thus, here, $B=25.563$~MPa and $n=0.139$.
-Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.338$.
-Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.730$.
+Thus, here, $B=21.816$~MPa and $n=0.0746$.
+Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
+Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
 All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.
@@
 $A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
-$11.758$ & $25.563$ &  $0.139$ & $0.338$ & $0.730$\\ \hline
+$13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\ \hline
 \label{tab:JCparams}
@@
 \centering
-\includegraphics[width=1.02\columnwidth]{Figures/CompExpJC}
+\includegraphics[width=1.02\columnwidth]{Figures/CompExp-JC-6}
 \caption{Comparison between the experimental and predicted flow stresses by JC model.}
@@
 %-------------------------------------------------------------------------
-\OP{This introduction paragraph is entirely copied from the WJET publication, P.T.M. must rewrite this part of the text !}
+\OP{This introduction paragraph is entirely copied from the WJET publication, P.T.M.
+must rewrite this part of the text !}
 \textcolor{red}{The MZA which is the modified form of ZA model, as the JC model is one of widely used models and implemented in many sofwares like Abaqus.
@@
 \caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
-\begin{tabular}{llllllc}
+\begin{tabular}{ccccccc}
 \hline
-$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
-$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
+$C_1$ & $C_2$ & $C_3$ & $C_4$ & $C_5$ & $C_6$ & $n$\\
+$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$\\
 \hline
@@
 \includegraphics[width=1.02\columnwidth]
-{Figures/CompExpMZA}
+{Figures/CompExp-MZA-6}
 \caption{Comparison between the experimental and predicted flow stresses by MZA model}
@@
 \hline
-$A~(\text{MPa})$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
-$5954.043$ & $-3.358\times10^{-3}$ & $2.641\times10^{-1}$ & $-8.678\times10^{-2}$ & $2.269\times10^{-4}$\\\hline
+$A$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
+$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$ & $-0.0868$ & $2.2688\times10^{-4}$\\\hline
 & $m_5$ & $m_6$ & $m_7$ & $m_8$\\
-& $-4.216\times10^{-4}$ & $-5.613\times10^{-2}$ & $2.264\times10^{-4}$ & $0$\\\hline
+& $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$\\\hline
 \label{tab:HSparameters}
@@
 \includegraphics[width=1.02\columnwidth]
-{Figures/CompExpHS}
+{Figures/CompExp-HS-6}
 \caption{Comparison between the experimental and predicted flow stresses by HS model}
@@
 \hline
-\multicolumn{1}{c}{$\alpha_i~(\text{MPa}^{-1})$} & \multicolumn{1}{c}{$Q_i~(\text{MJ.mol}^{-1})$} & \multicolumn{1}{c}{$\ln\!A_i~(\ps)$} & \multicolumn{1}{c}{$n_i$}\\
+\multicolumn{1}{c}{$\alpha_i$} & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}\\
 \hline
-$\alpha_0=0.0392$ & $Q_0=0.467$ & $\ln\!A_0=35.8092$ & $n_0=4.8216$ \\
-$\alpha_1=-0.4092$ & $Q_1=-0.6516$ & $\ln\!A_1=-58.8219$ & $n_1=3.2813$ \\
-$\alpha_2=3.9229$ & $Q_2=7.6084$ & $\ln\!A_2=740.3302$ & $n_2=71.5963$ \\
-$\alpha_3=-20.713$ & $Q_3=-48.016$ & $\ln\!A_3=-5049.2979$ & $n_3=-1956.1871$ \\
-$\alpha_4=62.1376$ & $Q_4=66.795$ & $\ln\!A_4=11305.3573$ & $n_4=14460.9217$ \\
-$\alpha_5=-99.9999$ & $Q_5=468.8898$ & $\ln\!A_5=20220.008$ & $n_5=-54309.8814$ \\
-$\alpha_6=58.7108$ & $Q_6=-2303.1535$ & $\ln\!A_6=-153871.1135$ & $n_6=117612.0374$ \\
-$\alpha_7=54.3688$ & $Q_7=4370.6566$ & $\ln\!A_7=317981.5396$ & $n_7=-148819.8996$ \\
-$\alpha_8=-99.9999$ & $Q_8=-3939.3826$ & $\ln\!A_8=-297254.899$ & $n_8=102387.2537$ \\
-$\alpha_9=42.5233$ & $Q_9=1397.0283$ & $\ln\!A_9=107585.17$ & $n_9=-29621.1293$ \\
+$\alpha_0=0.0407$ & $Q_0=0.467$ & $A_0=35.8092$ & $n_0=4.8217$\\
+$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & $A_1=-58.822$ & $n_1=3.2814$\\
+$\alpha_2=6.3912$ & $Q_2=7.6084$ & $A_2=740.3303$ & $n_2=71.5963$\\
+$\alpha_3=-47.3364$ & $Q_3=-48.016$ & $A_3=-5.0493\times 10^{3}$ & $n_3=-1.9562\times 10^{3}$\\
+$\alpha_4=220.0014$ & $Q_4=66.795$ & $A_4=1.1305\times 10^{4}$ & $n_4=1.4461\times 10^{4}$\\
+$\alpha_5=-654.4553$ & $Q_5=468.8898$ & $A_5=2.022\times 10^{4}$ & $n_5=-5.431\times 10^{4}$\\
+$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & $A_6=-1.5387\times 10^{5}$ & $n_6=1.1761\times 10^{5}$\\
+$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & $A_7=3.1798\times 10^{5}$ & $n_7=-1.4882\times 10^{5}$\\
+$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$\\
+$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$\\
 \hline
@@
 \includegraphics[width=1.02\columnwidth]
-{Figures/CompExpAR}
+{Figures/CompExp-AR-6}
 \caption{Comparison between the experimental and predicted flow stresses by AR model}
@@
 \hline
-$A_0=16.8528$ & $B_0=-0.0035$ & $C_0^0=0.1607$ & $C_1^0=0.0$\\
-$A_1=340.6451$ & $B_1=-0.0131$ & $C_0^1=-0.6201$ & $C_1^1=0.0026$\\
-$A_2=-1959.4041$ & $B_2=-0.0044$ & $C_0^2=4.9515$ & $C_1^2=-0.0035$\\
-$A_3=4835.9698$ & $B_3=0.2217$ & $C_0^3=-13.1693$ & $C_1^3=-0.0222$\\
-$A_4=-5517.6094$ & $B_4=-0.4988$ & $C_0^4=15.2499$ & $C_1^4=0.0608$\\
-$A_5=2405.8399$ & $B_5=0.3211$ & $C_0^5=-6.5869$ & $C_1^5=-0.0412$\\
+$A_0=16.8529$ & $B_0=-3.5418\times 10^{-3}$ & $C_0^0=0.1608$ & $C_1^0=-1.9037\times 10^{-5}$\\
+$A_1=340.6451$ & $B_1=-0.0132$ & $C_0^1=-0.6202$ & $C_1^1=2.67\times 10^{-3}$\\
+$A_2=-1.9594\times 10^{3}$ & $B_2=-4.4888\times 10^{-3}$ & $C_0^2=4.9516$ & $C_1^2=-3.5788\times 10^{-3}$\\
+$A_3=4.836\times 10^{3}$ & $B_3=0.2218$ & $C_0^3=-13.1694$ & $C_1^3=-0.0222$\\
+$A_4=-5.5176\times 10^{3}$ & $B_4=-0.4988$ & $C_0^4=15.25$ & $C_1^4=0.0609$\\
+$A_5=2.4058\times 10^{3}$ & $B_5=0.3211$ & $C_0^5=-6.587$ & $C_1^5=-0.0413$\\
 \hline
@@
 \includegraphics[width=1.02\columnwidth]
-{Figures/CompExpPTM}
-\caption{Comparison between the experimental and predicted flow stresses by PTM model }
+{Figures/CompExp-PTM-6}
+\caption{Comparison between the experimental and predicted flow stresses by PTM model}
 \label{fig:iCorrelationPTM}
@@
 \includegraphics[width=1\columnwidth]
-{Figures/CompExpANN}
-\caption{Comparison between the experimental and predicted flow stresses by ANN model }
+{Figures/CompExp-3-15-7-1-sigmoid}
+\caption{Comparison between the experimental and predicted flow stresses by the 3-15-7-1-sigmoid ANN model}
 \label{fig:iCorrelationANN}
@@
 %--------------------------------------------------------------------------
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]
-{Figures/Correlation}
-\caption{Correlation coefficient ($R$) of models developed}
-\label{fig:Correlation}
-\end{figure}
+
 The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($\AARE$ generally known as $\AARE$) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($\RMSE$) (Equation (\ref{eq:RMSE-expression})).

### 2022-11-10 Article.tex
Update text of the ANN-6 model

@@
 
+\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
 \newcommand{\dotp}{\boldsymbol{\cdot}}
@@
 \newcommand{\ps}{\text{s}^{-1}}
+\DeclareMathOperator{\ANN2}{sig}
 %\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
 %\DeclareMathOperator{\sech}{sech}
-%\DeclareMathOperator{\sigmoid}{sig}
+%\DeclareMathOperator{\ANN2}{sig}
 
@@
 For further usage of  data in numerical simulation elastic parts have been removed}.
+
 %------------------------------------------------------------------------
-\subsection{Compression tests results}
+\subsection{Compression tests results\label{sec:ComTestResults}}
 %------------------------------------------------------------------------
@@
 
+The accuracy and predictive ability of the models are usually assessed by certain coefficients such as the Mean Absolute Relative Error ($\AARE$) defined by Equation (\ref{eq:AARE}) and the Root Mean Square Error ($\RMSE$) defined by Equation (\ref{eq:RMSE}).
+\begin{equation}
+\AARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100 \label{eq:AARE}
+\end{equation}
+\begin{equation}
+\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2} \label{eq:RMSE}
+\end{equation}
+where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the predicted value using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21000$).
+For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\text{MPa}$.
+The correlation coefficient ($R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
+Therefore, a good (high) value of $R$ (close to $1$) does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction \cite{Phaniraj-2003}.
+
 %-------------------------------------------------------------------------
@@
 The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
+For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model.
 That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
@@
 \end{figure}
-\FloatBarrier
 
@@
 The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
+For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\text{MPa}$.
 It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1.0~\ps$.
@@
 But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
+For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\text{MPa}$.
 
@@
 Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}.
-The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot\varepsilon = 0.1\ \ps$ the prediction in not quite good.
-The deviation between the predicted values and the experimental values is relatively good.
+The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction in not quite good.
+The deviation between the predicted values and the experimental values for other strain rates is relatively good.
+For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\text{MPa}$ this shows an overall worse performance than the AR model.
 
@@
 %--------------------------------------------------------------------------
-The Artificial Neural Network model (ANN) is a mathematical formulation widely used in many fields today for better prediction.
-It is a model based on the principle of minimisation where it improves from the progressive decrease of the error during the learning process.
-Typically an ANN model contains an input layer, an output layer and hidden layers.
-Each hidden layer is connected to the one before it and the one after it via neurons.
-Indeed, all neurons in the $k$ layer are connected to each neuron in the ($k+1$) layer.
-To each layer is added another parameter called bias.
-As said the principle of the ANN model is therefore based on the minimisation of the difference between the value obtained from the output of the network and the expected value.
-Indeed, once the error is calculated, it is propagated back to the input layer in order to update the model parameters via the minimisation algorithms.
-In our case, the ADAM algorithm is used.
-The architecture of the network used in this study is shown in Figure \ref{fig:ANN-scheme-2HL}.
-After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress.
-The good performance of the model is found to be stable between $800$ and $1000$ epochs.
+Because of their predictive capacity and their adaptability, Artificial Neural Networks (ANNs) are more and more widely used today in many scientific fields.
+Their operation is based on a learning process during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine learning process.
 
+There are generally two uses of neural networks: classification and regression.
+The first is the ability to classify data into different groups and for example to distinguish between images of cats and dogs.
+The second one corresponds to the capacity of universal approximator of these neural networks, which interests us in this application, and thus to the ability after learning to predict the values of the flow stress $\sigma^y$ according to the input data, as do the analytical models previously identified.
+The main difference is that this approximation is not linked to a fixed mathematical formulation (JC, MZA, AR, HS, PTM model), but is only dependent on the data used for training, the number of layers, the number of neurons per layer and the activation functions associated with the neurons of the network.
+A feed-forward ANN, as used in our application, contains an input layer, an output layer and a number of hidden layers ($2$ in our case).
+Each layer of neurons is connected to the one before it and the one after it by weighted connections.
+Thus, all the neurons of the $k$ layer are connected to all the neurons of the ($k-1$) layer as shown in Figure \ref{fig:ANN-scheme-2HL}.
 \begin{figure}[!ht]
@@
 
-In this study $700$ of data were used; $80\%$ (560) are randomly selected for training and $20\%$ (140) for testing.
-Before learning, a normalisation of the data is required in order to have all data between $0$ and $1$.
-The Equation is widely used for normalization.
+Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately previous layer $(k-1)$, containing $m$ neurons, given by the following equation:
 \begin{equation}
-X_n = \frac{X - X_{min}}{X_{max} - X_{min}}
+y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k}\label{eq:ANN1}
 \end{equation}
-Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot\varepsilon/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively.
-$X_n$ is the normalized data of the corresponding $X$.
-The trained model once tested can be used to predict the behavior of the AISI P20 alloy.
-Figure \ref{fig:iCorrelationANN} show a comparison between the predicted ﬂow stresses from ANN model and measured data from hot compression test.
-As shown from this figures, the correlation between the experimental and the ANN prediction based is very good over the full range of data and the predicted data can well track the hardening and softening regions of the hot deforming material.
-Therefore, the ANN model can be used to simulate the hot deformation of this type of alloy.
-This was not necessarily the case with the analytical models.
-The performance of this prediction will be much more appreciated when it comes to testing its ability to predict data that has not been used in either the training or the test data, but rather a full-fledged trial that we wish to validate the ANN prediction by experimental.
-This validation will be done both with a strain rate between and outside of those used for the training step.
+where $y_i\lay{k}$ is the entry of the $i^{th}$ neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j^{th}$ neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i^{th}$ neuron of layer $k$ and the $j^{th}$ neuron of layer $(k-1)$ and $b_i\lay{k}$ is the associated bias of the $i^{th}$ neuron of layer $k$.
+Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN that we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021}.
+For the proposed model, we have selected the ANN2 activation function, so that, each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
+\begin{equation}
+\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
+\end{equation}
+No activation function is used for the output neuron of the ANN.
+
+After some tests of different types of network architecture and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer give the best compromise between prediction, learning time and model compactness.
+From the global architecture point of view, the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
+This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second and $8$ for the output).
+
+The Python program used for training the neural network was developed using the specialized Python library Tensorflow \cite{Abadi-2016}.
+The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
+The training data are those from the tests presented in section \ref{sec:ComTestResults} and composed of $21000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
+The learning is performed on the basis of $5000$ epochs of the experimental data set.
+Fourty minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GiB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
+Figure \ref{fig:ANN-6-conv} show the evolution of the training error defined by the $\log_{10}$ of the Root Mean Square Error during the training phase.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.7\columnwidth]
+{Figures/Conv-ANN-6}
+\caption{Convergence of the ANN model during the training phase.}
+\label{fig:ANN-6-conv}
+\end{figure}
+As we can see on this figure, after $5000$ epoch, we can consider that we have reached a stationary state of the model learning and that it is useless to continue the learning phase.
+
+Once the learning phase is over, the trained model can be used to predict the behavior of the AISI P20 alloy as a function of the input data in the same way as is done with the analytical models.
+One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}) which can be implemented in any language (e.g.
+in FORTRAN for use on the Abaqus Explicit FEM code) as proposed in Pantalé \eal \cite{Pantale-2021}.
+For reasons of compactness, the parameters of the ANN model are not reported in this paper.
+
+As for the analytical models presented previously, Figure \ref{fig:iCorrelationANN} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
 \begin{figure}[!ht]
@@
 \end{figure}
-\FloatBarrier
+The correlation between the experimental data and the ANN prediction is very good over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
+For the ANN model, $\AARE=0.62~\%$ and $\RMSE=0.38~\text{MPa}$ which is excellent.
+This model can be used to simulate the hot deformation of this type of alloy with much greater fidelity to the actual material behavior than the analytical models presented previously.
+
 %-------------------------------------------------------------------------
@@
 
-The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($\AARE$ generally known as $\AARE$) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($\RMSE$) (Equation (\ref{eq:RMSE-expression})).
-\begin{equation}
-\label{eq:R-expression}
-\R(\%) = \frac{\displaystyle\sum_{i=1}^{N}{\left(E_i - \overline{E}\right)\left(P_i - \overline{P}\right)}}{\sqrt{\displaystyle\sum_{i=1}^{N}\left(E_i - \overline{E}\right)^2 .\displaystyle\sum_{i=1}^{N}\left(P_i - \overline{P}\right)^2}}\times 100
-\end{equation}
-\begin{equation}
-\label{eq:AARE-expression}
-\AARE(\%) = \frac{1}{N}\displaystyle\sum_{i=1}^{N} \displaystyle\left\lvert\frac{E_i- P_i}{E_i} \right\rvert\times 100
-\end{equation}
-\begin{equation}
-\label{eq:RMSE-expression}
-\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2}
-\end{equation}
-Where $E_i$ is the experimental value and $P_i$ is the predicted value of the constitutive law (phenomenological and ANN models), $\overline{E}$ and $\overline{P}$ are the mean values of the experimental and predicted values, respectively.
+On the other hand, other coefficients ($\AARE$ and $\RMSE$) are used to estimate the predictive capacity of the model because they are considered unbiased as well as for low and high values.
 
-The correlation coefficient $R$ is generally used to show the degree of linearity between the experimental and predicted values.
-The model sometimes tends to be biased towards low and high values.
-Therefore, a good (high) value of $R$ does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction \cite{Phaniraj-2003}.
-On the other hand, other coefficients ($\AARE$ and $\RMSE$) are used to estimate the predictive capacity of the model because they are considered unbiased as well as for low and high values.
 Indeed, they verify the predictability of a model term by term comparison of the relative error in relation to the real value of the variable \cite{Srinivasulu-2006}.
+
 Thus the correlation coefficients $R$ for JC, MZA, HS, Arhenius, proposed and ANN models are $0.98475$,  $0.99014$,  $0.98364$, $0.99839$, $0.99514$, and $0.99994$ respectively as shown on Figure \ref{fig:Correlation}.
@@
 \end{figure}
-\FloatBarrier
+
 %---------------------------------------------------------------------

### 2022-11-10 Article.tex
Update text of Comparison section

@@
 
-The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
+The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:RawData}.
 \OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}\textcolor{red}{almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
@@
 \caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
-\label{fig:rawData}
+\label{fig:RawData}
 \end{figure}
@@
 \OP{What are the temperature and strain rate related with this micrography}
-From the results reported in Figure \ref{fig:rawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.
+From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.
 
@@
 Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
-All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.
+All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.
 
@@
 $13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\ \hline
-\label{tab:JCparams}
+\label{tab:JC}
 \end{tabular}
@@
 
-The values predicted by the Johnson-Cook flow law (solid line) and the experimental values (dots) are compared in Figure \ref{fig:iCorrelationJC}.
+The values predicted by the Johnson-Cook flow law (solid line) and the experimental values (dots) are compared in Figure \ref{fig:CompExp-JC-6}.
 The JC model is not able to describe the evolution of the flow stress of AISI P20 for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
@@
 \caption{Comparison between the experimental and predicted flow stresses by JC model.}
-\label{fig:iCorrelationJC}
+\label{fig:CompExp-JC-6}
 \end{figure}
@@
 Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
-The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}.
+The parameters of MZA model are given in the Table \ref{tab:MZA} while its prediction are shown in Figure \ref{fig:CompExp-MZA-6}.
 It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
@@
 \hline
-\label{tab: MZAparameters}
+\label{tab:MZA}
 \end{tabular}
@@
 \caption{Comparison between the experimental and predicted flow stresses by MZA model}
-\label{fig:iCorrelationMZA}
+\label{fig:CompExp-MZA-6}
 \end{figure}
@@
 In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
-From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HSparameters}.
+From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HS}.
 
@@
 & $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$\\\hline
-\label{tab:HSparameters}
+\label{tab:HS}
 \end{tabular}
@@
 
-The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
+The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
 For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\text{MPa}$.
@@
 \caption{Comparison between the experimental and predicted flow stresses by HS model}
-\label{fig:iCorrelationHS}
+\label{fig:CompExp-HS-6}
 \end{figure}
@@
 The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
-Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:ARparameters}.
+Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:AR}.
 \begin{table}[h!]
@@
 \hline
-\label{tab:ARparameters}
+\label{tab:AR}
 \end{tabular}
@@
 
-Figure \ref{fig:iCorrelationAR} shows the comparison of the values predicted by the Arrhenius model and the experimental values.
+Figure \ref{fig:CompExp-AR-6} shows the comparison of the values predicted by the Arrhenius model and the experimental values.
 The difference between the experimental and predicted values is small.
@@
 \caption{Comparison between the experimental and predicted flow stresses by AR model}
-\label{fig:iCorrelationAR}
+\label{fig:CompExp-AR-6}
 \end{figure}
@@
 \end{equation}
-where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM-parameters}) of the model to be identified using the procedure proposed in  \cite{TizeMha-2022}.
+where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM}) of the model to be identified using the procedure proposed in  \cite{TizeMha-2022}.
 Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
@@
 The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016} and for more details about this model  we invite the reader to read our previous work \cite{TizeMha-2022}.
-Thus all the parametrers of this model are calcuted with $q=5$, $r=5$, $s=1$ and $t=5$.
+Thus, all the parameters of this model are calculated with $q=5$, $r=5$, $s=1$ and $t=5$.
 
-Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}.
+Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
 The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction in not quite good.
@@
 \hline
-\label{tab:PTM-parameters}
+\label{tab:PTM}
 \end{tabular}
@@
 \caption{Comparison between the experimental and predicted flow stresses by PTM model}
-\label{fig:iCorrelationPTM}
+\label{fig:CompExp-PTM-6}
 \end{figure}
@@
 Each layer of neurons is connected to the one before it and the one after it by weighted connections.
-Thus, all the neurons of the $k$ layer are connected to all the neurons of the ($k-1$) layer as shown in Figure \ref{fig:ANN-scheme-2HL}.
+Thus, all the neurons of the $k$ layer are connected to all the neurons of the ($k-1$) layer as shown in Figure \ref{fig:ANN-2HL}.
 \begin{figure}[!ht]
@@
 \caption{Multi-layer Artificial Neural Network architecture}
-\label{fig:ANN-scheme-2HL}
+\label{fig:ANN-2HL}
 \end{figure}
@@
 Once the learning phase is over, the trained model can be used to predict the behavior of the AISI P20 alloy as a function of the input data in the same way as is done with the analytical models.
-One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}) which can be implemented in any language (e.g.
-in FORTRAN for use on the Abaqus Explicit FEM code) as proposed in Pantalé \eal \cite{Pantale-2021}.
+One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}) which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code) as proposed in Pantalé \eal \cite{Pantale-2021}.
 For reasons of compactness, the parameters of the ANN model are not reported in this paper.
 
-As for the analytical models presented previously, Figure \ref{fig:iCorrelationANN} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
+As for the analytical models presented previously, Figure \ref{fig:CompExp-3-15-7-1-sigmoid} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
 \begin{figure}[!ht]
@@
 \caption{Comparison between the experimental and predicted flow stresses by the 3-15-7-1-sigmoid ANN model}
-\label{fig:iCorrelationANN}
+\label{fig:CompExp-3-15-7-1-sigmoid}
 \end{figure}
@@
 
-On the other hand, other coefficients ($\AARE$ and $\RMSE$) are used to estimate the predictive capacity of the model because they are considered unbiased as well as for low and high values.
-
-Indeed, they verify the predictability of a model term by term comparison of the relative error in relation to the real value of the variable \cite{Srinivasulu-2006}.
-
-Thus the correlation coefficients $R$ for JC, MZA, HS, Arhenius, proposed and ANN models are $0.98475$,  $0.99014$,  $0.98364$, $0.99839$, $0.99514$, and $0.99994$ respectively as shown on Figure \ref{fig:Correlation}.
-These results show that all models have a relatively good coefficient; this does not guarantee the validation of the prediction of these models.
-Hence the need to calculate the other two coefficients.
-All coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work are summarized in the Table \ref{tab:Coefsparams}.
-
-From this table, it can be seen that the ANN model has a good prediction than the analytical models.
-All this shows sufficiently that the ANN model is more effective in describing the behavior of the AISI P20 alloy for high temperature deformation.
-This efficiency will therefore be validated on tests at two different selected strain rates.
-One between the minimum and the maximum strain rates used during identification or training for ANN model and another one outside higher than the maximum strain rate.
-This will validate the interpolation and extrapolation capability of phenomenological and ANN models.
-The prediction results should lead to a better interpolation and extrapolation capability of the ANN model than phenomenological models as shown by identification.
-Another thing to be analysed from this table is the link between the values of the correlation coefficient $R$ and the values of $\AARE$ and $\RMSE$.
-Indeed, as mentioned above, the $R$ coefficient does not necessarily mean a good prediction of the model but a good relationship of linearity between the experiment and the prediction.
-To ensure a good prediction of the model, it is necessary to add to $R$, the values of $\AARE$.
-From that table it can be seen the values of the coefficients $R$ are $99.014\%$, $98.364\%$, for $\AARE$ are $11.13020\%$ and $8.15103\%$ and those of $\RMSE$ are $5.35079\ \text{MPa}$, and $6.45287\ \text{MPa}$ respectively for the MZA model and the HS model.
-This seems contradictory when the $R$ of HS is smaller than that of MZA, whereas for the $\AARE$ and $\RMSE$ values it is the opposite case.
-This simply means that the HS model has a good prediction compared to the MZA model whereas in the framework of the linear correlation between the experiment and the prediction the MZA model makes it better.
-All this can be seen from the identification curves where we can observe the HS curves (Figure \ref{fig:iCorrelationHS}) are indeed closer to the experimental than those of MZA (Figure \ref{fig:iCorrelationMZA}) while the points are scattered for HS model on the correlation curve (Figure \ref{fig:Correlation}).
-This validates the analysis made by \cite{Phaniraj-2003, Srinivasulu-2006}.
-
+A summary of the coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work is reported in Table \ref{tab:Errors}.
 \begin{table}[h!]
-\centering{}
-\caption{Accurary coefficients of the developped models}
+\centering
+\caption{Accuracy coefficients for all the analyzed models.}
 \begin{tabular}{lcccccc}
 \hline
-&		&		&         &             &		   &		  		\\
-Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN  		    \\
-&				&				&         &             &		   &\\
+Coefficients & JC & MZA & HS & Arhenius & PTM & ANN\\
 \hline
-$R(\%)$&$98.4745$&$99.0141$&$98.5682$&$99.839$& $99.5137$&$99.9994$ \\
-$\AARE(\%)$&$11.1667$&$11.13020$&$8.15103$&$3.30677$&$4.19549$&$0.81094$   \\
-$\RMSE(\text{MPa})$&$6.30298$&$5.35079$&$6.45287$&$2.03275$&$3.59027$&$0.55158$\\
+$\AARE(\%)$ & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$\\
+$\RMSE(\text{MPa})$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$\\
 \hline
-\label{tab:Coefsparams}
+\label{tab:Errors}
 \end{tabular}
 \end{table}
+From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally $6$ times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.
+
+The ANN, Arrhenius and PTM models are the only models that take into account the softening with the deformation of AISI P20 at low strain rate, unlike the other three models that only present an increase of the flow stress with the strain, whatever the strain rate and temperature, hence their poor performance in predicting the behavior of this material and more particularly at low strain rates.
+The parameters reported in Table \ref{tab:Errors}, the correlations visible in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow us to conclude here that the ANN model is the most efficient of all the models presented to describe the behavior of the AISI P20 alloy for high temperature deformation applications.
 
@@
 For the validation of the interpolation, the chosen strain rate is $\mdot\varepsilon = 1.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 2.0\ \ps$  and $\mdot\varepsilon = 5.0\ \ps$.
-The Figure \ref{fig:inCombinaison} shows the comparison between the predictions of the analytical and ANN models and the experiment.
+The Figure \ref{fig:IntComp} shows the comparison between the predictions of the analytical and ANN models and the experiment.
 It appears from these Figures that all models have relatively good predictions but the ANN model remains the best because the value of its $\AARE$ is $1.4\%$ while it is between $2.33\%$ and $6.13\%$ for the analytical models.
 This further shows the performance of the ANN model compared to the analytical models.
-All these results are summarized in Table \ref{tab:inValid}.
+All these results are summarized in Table \ref{tab:IntVal}.
 \begin{figure}[!ht]
@@
 \caption{Comparison between the experimental and predicted flow stresses by ANN model for interpolation estimation}
-\label{fig:inCombinaison}
+\label{fig:IntComp}
 \end{figure}
@@
 \hline
-\label{tab:inValid}
+\label{tab:IntVal}
 \end{tabular}
@@
 For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 1.0\ \ps$  and $\mdot\varepsilon = 2.0\ \ps$.
-Figure \ref{fig:exCombinaison} shows the comparison between the predictions  and the experimental.
+Figure \ref{fig:ExtComp} shows the comparison between the predictions  and the experimental.
 Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
@@
 \hline
-\label{tab:exValid}
+\label{tab:ExtVal}
 \end{tabular}
@@
 \caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
-\label{fig:exCombinaison}
+\label{fig:ExtComp}
 \end{figure}

### 2022-11-10 Article.tex
Add Appendix to the paper

@@
 One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}) which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code) as proposed in Pantalé \eal \cite{Pantale-2021}.
-For reasons of compactness, the parameters of the ANN model are not reported in this paper.
+For reasons of compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix \ref{sec:Appendix} at the end of this paper.
 
@@
 \end{enumerate}
+
+\section{Appendix\label{sec:Appendix}}
+In order to complete this paper, we report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
+In order to use this model we describe here after the procedure to compute the flow stress $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$.
+This process can be decomposed in $3$ phases:
+\begin{itemize}
+\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, Lu-2011-ANN}.
+Therefore, the three components of the input are obtained from the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$ and the temperature $T$ using the following expressions:
+\begin{equation}
+\begin{cases}
+x_1 = \frac{\varepsilon^p - [\varepsilon^p]_{min}}{[\varepsilon^p]_{max} - [\varepsilon^p]_{min}}\\
+x_2 = \frac{\ln(\mdot{\varepsilon}/\mdot{\varepsilon_0})-[\ln(\mdot{\varepsilon}/\mdot{\varepsilon_0})]_{min}}{[\ln(\mdot{\varepsilon}/\mdot{\varepsilon_0})]_{max}-[\ln(\mdot{\varepsilon}/\mdot{\varepsilon_0})]_{min}}\label{eq:CR1}\\
+x_3 = \frac{T-[T]_{min}}{[T]_{max}-[T]_{min}}
+\end{cases}
+\end{equation}
+where $[~]_{min}$ and $[~]_{max}$  are the boundaries of the range of the corresponding field: $\varepsilon^p\!\in\!\left[0.0,0.7\right]$, $\mdot{\varepsilon}\!\in\!\left[0.001,5.0\right]$, $T\!\in\!\left[1050,1250\right]$ and $\sigma\!\in\!\left[1.311,153.739\right]$.
+The reference strain rate is $\mdot{\varepsilon_0} = 0.001$.
+\item Then we compute the output $s$ of the ANN from the input vector $\overrightarrow{x}$ using the three following equations.
+\begin{equation}
+\overrightarrow{y}_1 = \left[1 + \exp{\left(- \w_1 \dotp \overrightarrow{x}- \overrightarrow{b}_1\right)}\right]^{-1}
+\end{equation}
+\begin{equation}
+\overrightarrow{y}_2 = \left[1 + \exp{\left(- \w_2 \dotp \overrightarrow{y}_1- \overrightarrow{b}_2\right)}\right]^{-1}
+\end{equation}
+\begin{equation}
+s = \overrightarrow{w}^T \dotp \overrightarrow{y}_2 + b
+\end{equation}
+\item Finally, the flow stress $\sigma^y$ can be obtained from the output $s$ of the ANN using the following equation:
+\begin{equation}
+\sigma^y =  \left([\sigma]_{max}-[\sigma]_{min}\right)s + [\sigma]_{min} \label{eq:CR2}
+\end{equation}
+\end{itemize}
+
+Conforming to the computing process proposed by Equations (\ref{eq:CR1}-\ref{eq:CR2}), we report hereafter the $180$ coefficients of the ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
+
+\begin{equation*}
+\w_1^T = \left[
+\begin{array}{rrr}
+2.2206 & -3.7555 & -6.7246\\ 
+-4.8598 & 5.7431 & -5.8538\\ 
+2.3099 & 3.3325 & -5.1795\\ 
+2.0475 & 0.8006 & -1.4259\\ 
+8.8358 & -6.0362 & 0.8226\\ 
+-1.2613 & -0.9274 & -2.3725\\ 
+-0.3561 & 6.5032 & -10.7573\\ 
+-11.7226 & -2.0455 & 1.2248\\ 
+3.1066 & 26.5580 & 18.6540\\ 
+-0.5150 & -5.6922 & 1.0104\\ 
+-6.4755 & 8.4888 & -2.4459\\ 
+-1.8791 & -0.5380 & 2.2295\\ 
+-6.0206 & 1.2776 & 0.2169\\ 
+0.2619 & -4.7974 & -1.1282\\ 
+-27.1456 & -0.5327 & -0.5303\\ 
+\end{array}\right]
+\end{equation*}
+\begin{equation*}
+\overrightarrow{b}_1 = \left[
+\begin{array}{r}
+5.9164\\ 
+-1.9074\\ 
+-2.6837\\ 
+-1.0954\\ 
+-0.9509\\ 
+3.1682\\ 
+-4.3964\\ 
+0.6343\\ 
+-5.0676\\ 
+2.0228\\ 
+1.1267\\ 
+-0.9671\\ 
+-0.6263\\ 
+2.3110\\ 
+-0.3037\\ 
+\end{array}\right]
+\end{equation*}
+\begin{equation*}
+\w_2 = \left[
+\begin{array}{rrrrrrr}
+-0.5783 & 1.2724 & 0.5747 & 0.6449 & -4.2203 & -0.2380 & 0.2591\\ 
+-0.4852 & 5.2807 & 0.8888 & -8.2324 & -2.0075 & -0.6474 & -1.0787\\ 
+4.4499 & -0.0137 & 0.1657 & 0.3198 & 4.9765 & -1.2503 & 0.8219\\ 
+1.7571 & 0.7730 & 0.0208 & -1.3316 & -0.8945 & -0.7284 & -0.1831\\ 
+-1.0866 & 0.1330 & -0.8615 & -0.1283 & 0.2218 & -0.1772 & -2.7458\\ 
+-0.3925 & 1.3994 & 0.0630 & -1.8397 & -1.1047 & -1.9839 & 0.5767\\ 
+-0.2121 & 0.9977 & 1.2028 & -9.6525 & 0.5520 & 0.1062 & -0.0409\\ 
+-1.1518 & -1.6402 & -4.1501 & -1.0759 & 0.4749 & -2.8350 & 0.9225\\ 
+-1.1453 & -0.2173 & -0.1382 & 0.8264 & -0.5125 & 0.1882 & -0.8654\\ 
+-4.3301 & -0.3711 & -7.4305 & 3.5926 & -9.6217 & -1.2375 & 1.6171\\ 
+2.3907 & -1.0085 & -0.8828 & -1.1891 & 0.9947 & 1.1178 & -1.0953\\ 
+-1.5955 & 1.6313 & 0.4916 & 0.1906 & -1.9216 & -1.4140 & 1.3827\\ 
+-1.6985 & 1.4277 & -3.4462 & -8.3777 & -1.2132 & -1.2158 & 2.8512\\ 
+-1.9954 & -2.0159 & -8.3455 & -0.5205 & 0.2942 & -1.3337 & 0.2026\\ 
+4.3040 & -0.7164 & -1.0859 & 3.4294 & -23.8003 & 12.5859 & 7.3721\\ 
+\end{array}\right]
+\end{equation*}
+\begin{equation*}
+\overrightarrow{b}_2 = \left[
+\begin{array}{r}
+0.7534\\ 
+0.9473\\ 
+0.6055\\ 
+-0.7793\\ 
+-1.0305\\ 
+-1.5779\\ 
+-0.1471\\ 
+\end{array}\right]
+\end{equation*}
+\begin{equation*}
+\overrightarrow{w}_3 = \left[
+\begin{array}{r}
+0.1920\\ 
+0.3406\\ 
+0.3839\\ 
+-0.2880\\ 
+1.2047\\ 
+-1.4126\\ 
+-0.2215\\ 
+\end{array}\right]
+\end{equation*}
+\begin{equation*}
+b_3 = 0.1178 
+\end{equation*}
+
 % \bibitem{}

### 2022-11-10 Article.tex
Move Appendix to the end of the paper

@@
 One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}) which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code) as proposed in Pantalé \eal \cite{Pantale-2021}.
-For reasons of compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix \ref{sec:Appendix} at the end of this paper.
+For reasons of compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix.
 
@@
 
-\section{Appendix\label{sec:Appendix}}
+\bibliographystyle{elsarticle-num}
+\bibliography{Bibliography}
+
+\section*{Appendix\label{sec:Appendix}}
 In order to complete this paper, we report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
@@
 
-% \bibitem{}
-\bibliographystyle{elsarticle-num}
-\bibliography{Bibliography}
-%\end{thebibliography}
 \end{document}
-\endinput

### 2022-11-14 Article.tex
updating the texFile

@@
 \begin{abstract}
-The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \ps - 5\ \ps$) and temperatures ($1050\celsius-1250\celsius$).
+A concept for analysing and using of both analytical and neural network based models is proposed in this study to investigate the high-temperature deformation behavior of the AISI P20 alloy by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \ps - 5\ \ps$) and temperatures ($1050\celsius-1250\celsius$).
 Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
@@
 The limitation of this model is its loss of accuracy in some cases when the $8$ parameters are defined.
-This is why many works often limit its identification to only $5$ or $6$ parameters.
-This has been verified in our study where the smallest error of the model is obtained with only $5$ parameters identified.
+This is why many works often limit its identification to only $5$, $6$ or $7$ parameters.
+This has been verified in our study where the smallest error of the model is obtained with only $7$ parameters identified.
 
@@
 The idea is to make the formulation of an analytical model flexible so that it can be adapted to many materials.
-This formulation is based on the MZA model and polynomial functions of undefined order are used in the identification phase.
+This formulation is based on the MZA model and polynomial functions of undefined order are used during the identification.
 
@@
 As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2\celsius$/s and held at this temperature for $5$~min to eliminate thermal gradients.
-They were then cooled with a rate of $1\celsius$/s to the test temperature and then held at constant temperature for $1$~min before deformation.
+They were then cooled down with a rate of $1\celsius$/s to the test temperature and then held at constant temperature for $1$~min before deformation.
 During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
@@
 
-\OP{Here, a part concerning the treatment of the Gleeble data is missing.
-You introduce the notions of $h_0$, $R_0$, $h$, $R_M$ and $R_T$ and we have no idea what they are for.
-How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}\textcolor{red}{The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A\ \text{and}\ \varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
-As there are noises from raw data, filter method is applied to remove noise and have more smooth data.
-For further usage of  data in numerical simulation elastic parts have been removed}.
+The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A\ \text{and}\ \varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
+As there are noises from raw data, filter method is applied to remove noise and have more smooth data. For further usage of  data in numerical simulation elastic parts have been removed.
 
@@
 The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:RawData}.
-\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}\textcolor{red}{almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
-We have decided to limit the identification up to $0.7$ because for strain rates $2$ and $5$, stresses are note good}.
+Almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
+We have decided to limit the identification up to $0.7$ because for strain rates $2$ and $5$, stresses are note good.
 The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
@@
 
-To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX).
+To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRV) and Dynamic Recrystallization (DRX).
 At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
-As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRC.
-This DRC mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
+As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRV.
+This DRV mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
 Some of these dislocations reorganize and then form sub-grains within the initial grains of the material.
@@
 As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
-As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample \textcolor{red}{held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$}.
-\OP{What are the temperature and strain rate related with this micrography}
+As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$.
 From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.
@@
 The Arrhenius model was also chosen in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter $Q$ (the deformation activation energy coefficient) which is of great importance in the microstructural analyses of materials.
-The PTM model \cite{TizeMha-2022} is also used in this study because it is a model whose formulation does not impose a priori a number of parameters and which proved its ability in our previous works.
+The PTM model \cite{TizeMha-2022} is also used in this study because it is a model whose formulation does not impose a priori a number of parameters and which proved its ability in our previous works \cite{TizeMha-2022}.
 We selected it to test it on this type of material because it is normally formulated to fit any type of material.
@@
 %-------------------------------------------------------------------------
-\OP{This introduction paragraph is entirely copied from the WJET publication, P.T.M.
-must rewrite this part of the text !}
-\textcolor{red}{The MZA which is the modified form of ZA model, as the JC model is one of widely used models and implemented in many sofwares like Abaqus.
+The MZA which is the modified form of ZA model, as the JC model is one of widely used models and implemented in many sofwares like Abaqus.
 The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experimental.
-Indeed, in the JC model, those parameters are considered separately where they are simultaneaously considered in MZA and for that formulation MZA is prefered to JC model} \cite{Hull-2011}.
+Indeed, in the JC model, those parameters are considered separately where they are simultaneaously considered in MZA and for that formulation MZA is prefered to JC model \cite{Hull-2011}.
 But the original form of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
@@
 
-In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
+In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.
 From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HS}.
@@
 \end{equation}
-where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha n_1$ are dependent of the material.
+where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha/ n_1$ are dependent of the material.
 The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperature by regression method.
@@
 Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
-The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction in not quite good.
+The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
 The deviation between the predicted values and the experimental values for other strain rates is relatively good.
-For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\text{MPa}$ this shows an overall worse performance than the AR model.
+For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\text{MPa}$ and this shows an overall worse performance than the AR model.
 

### 2022-11-15 Article.tex
Update Appendix

--- 2022-11-10 Article.tex
@@
 Conforming to the computing process proposed by Equations (\ref{eq:CR1}-\ref{eq:CR2}), we report hereafter the $180$ coefficients of the ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
-
+The weight matrix for the first hidden layer $\w_1$ is a $15\times3$ matrix:
 \begin{equation*}
-\w_1^T = \left[
+\w_1 = \left[
 \begin{array}{rrr}
@@
 \end{equation*}
+The biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$ components vector:
 \begin{equation*}
@@
 \end{equation*}
+The weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
 \begin{equation*}
-\w_2 = \left[
+\w_2^T = \left[
 \begin{array}{rrrrrrr}
@@
 \end{equation*}
+The biases of the second hidden layer $\overrightarrow{b_2}$ is a $7$ components vector:
 \begin{equation*}
@@
 \end{equation*}
+The weight vector for the output layer $\overrightarrow{w}_3$ is a $7$ components vector:
 \begin{equation*}
@@
 \end{equation*}
+The bias of the output layer $b_3$ is a scalar:
 \begin{equation*}

### 2022-11-15 Article.tex
Update of Article after merge

@@
 
+\OP{Here, a part concerning the treatment of the Gleeble data is missing.
+You introduce the notions of $h_0$, $R_0$, $h$, $R_M$ and $R_T$ and we have no idea what they are for.
+How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}
 The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A\ \text{and}\ \varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
-As there are noises from raw data, filter method is applied to remove noise and have more smooth data. For further usage of  data in numerical simulation elastic parts have been removed.
+As there are noises from raw data, filter method is applied to remove noise and have more smooth data.
+For further usage of  data in numerical simulation elastic parts have been removed.
 
@@
 The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:RawData}.
+\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}
 Almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
@@
 As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$.
+\OP{What are the temperature and strain rate related with this micrography}
 From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.
@@
 \end{equation}
-where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha/ n_1$ are dependent of the material.
+where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent of the material.
 The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperature by regression method.

### 2022-11-17 Article.tex
Update of the Final part of the paper

@@
 \newcommand{\ps}{\text{s}^{-1}}
-\DeclareMathOperator{\ANN2}{sig}
+%\DeclareMathOperator{\ANN2}{sig}
+\newcommand{\mr}[2]{\multirow{#1}{*}{#2}}
 %\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
@@
 \hline
-Coefficients & JC & MZA & HS & Arhenius & PTM & ANN\\
+Coefficients & JC & MZA & HS & AR & PTM & ANN\\
 \hline
@@
 \includegraphics[width=1.02\columnwidth]
-{Figures/inCombinaison}
+{Figures/CompInt}
 \caption{Comparison between the experimental and predicted flow stresses by ANN model for interpolation estimation}
@@
 \caption{Accuracy coefficients of interpolation}
-\begin{tabular}{lcccccc}
+\begin{tabular}{llcccccc}
 \hline
-&		&		&         &             &		   &	\\
-Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN \\
-&				&				&         &             &	&\\
+$\mdot\varepsilon$           & Coefficients        & JC      & MZA     & HS     & AR     & PTM    & ANN\\
 \hline
-$R(\%)$&$99.0590$&$99.0821$&$97.6008$&$99.8417$& $99.8760$&$99.9439$  \\
-$\AARE(\%)$&$4.2686$&$3.7440$&$6.1391$&$2.3321$&$2.7590$&$1.4018$   \\
-$\RMSE(\text{MPa})$&$4.1923$&$3.1856$&$82.6956$&$2.29891$&$2.4632$&$1.0228$ \\
+\mr{2}{all}                  & $\AARE(\%)$         & $13.97$ & $21.49$ & $7.76$ & $3.54$ & $4.78$ & $0.78$\\
+                             & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $0.71$\\\hline
+\mr{2}{$\mdot\varepsilon=1$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $1.40$\\
+                             & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $1.52$\\
 \hline
@@
 \caption{Accuracy coefficients of extrapolation}
-\begin{tabular}{lcccccc}
+\begin{tabular}{llcccccc}
 \hline
-&		&		&         &             &		   &	\\
-Coefficients&JC  & MZA  &HS  & Arhenius      & PTM  &ANN \\
-&				&				&         &             &	&\\
+$\mdot\varepsilon$           & Coefficients        & JC      & MZA     & HS     & AR     & PTM     & ANN\\
 \hline
-$R(\%)$&$99.2920$&$99.4879$&$93.9429$&$99.6870$& $99.7582$&$99.8047$\\
-$\AARE(\%)$&$4.8988$&$3.4506$&$12.9939$&$3.2008$&$3.8845$&$1.7433$\\
-$RMSE(\text{MPa})$&$5.0943$&$4.3048$&$116.517$&$3.7035$&$4.3915$&$1.2513$ \\
+\mr{2}{all}                  & $\AARE(\%)$         & $14.27$ & $19.96$ & $7.37$ & $3.95$ & $5.53$  & $1.15$\\
+                             & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$\\\hline
+\mr{2}{$\mdot\varepsilon=5$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.37$ & $3.53$ & $11.46$ & $3.87$\\
+                             & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$\\
 \hline
@@
 \includegraphics[width=0.91\columnwidth]
-{Figures/exCombinaison}
+{Figures/CompExt}
 \caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
@@
 \item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, Lu-2011-ANN}.
-Therefore, the three components of the input are obtained from the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$ and the temperature $T$ using the following expressions:
+Therefore, the three components of the input vector $\overrightarrow{x}$ are obtained from the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$ and the temperature $T$ using the following expressions:
 \begin{equation}
+\overrightarrow{x}=
 \begin{cases}
@@
 \end{equation*}
-The weight vector for the output layer $\overrightarrow{w}_3$ is a $7$ components vector:
+The weight vector for the output layer $\overrightarrow{w}$ is a $7$ components vector:
 \begin{equation*}
-\overrightarrow{w}_3 = \left[
+\overrightarrow{w} = \left[
 \begin{array}{r}
@@
 \end{equation*}
-The bias of the output layer $b_3$ is a scalar:
+The bias of the output layer $b$ is a scalar:
 \begin{equation*}
-b_3 = 0.1178 
+b = 0.1178 
 \end{equation*}

### 2022-11-18 Article.tex
Modified newcommands to DeclareRobustCommand for bug in captions
Update the int and ext sections

@@
 
-\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
-\newcommand{\dotp}{\boldsymbol{\cdot}}
+\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
+\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
 %\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
 %\newcommand{\e}[1]{\exp\left({#1}\right)}
-\newcommand{\e}[1]{{\rm e}^{#1}}
-\newcommand{\lay}[1]{^{(#1)}}
-\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
-\newcommand*{\ie}{\emph{i.e.}\@\xspace}
-\newcommand*{\versus}{\emph{vs.}\@\xspace}
-\newcommand*{\eal}{et \emph{al.}\@\xspace}
-\newcommand*{\eg}{e.g.,\@\xspace}
-\newcommand{\RMSE}{\text{E}_\text{RMS}}
-\newcommand{\AARE}{\text{E}_\text{AAR}}
-\newcommand{\R}{\text{R}}
-\newcommand{\ps}{\text{s}^{-1}}
+\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
+\DeclareRobustCommand{\lay}[1]{^{(#1)}}
+\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
+\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
+\DeclareRobustCommand{\versus}{\emph{vs.}\@\xspace}
+\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
+\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
+\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
+\DeclareRobustCommand{\AARE}{\text{E}_\text{AAR}}
+\DeclareRobustCommand{\R}{\text{R}}
+\DeclareRobustCommand{\ps}{\text{s}^{-1}}
 %\DeclareMathOperator{\ANN2}{sig}
-\newcommand{\mr}[2]{\multirow{#1}{*}{#2}}
+\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
 %\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
@@
 This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high.
-Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
+Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains 7 neurons and the input layer contains 3 neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
 The results of the ANN model show a very good agreement between the predictions and the experiment.
@@
 Unlike the JC model, this formulation is based on parameters that are determined simultaneously.
-This model is simple to use and has $8$ parameters that are easy to determine.
-The limitation of this model is its loss of accuracy in some cases when the $8$ parameters are defined.
-This is why many works often limit its identification to only $5$, $6$ or $7$ parameters.
-This has been verified in our study where the smallest error of the model is obtained with only $7$ parameters identified.
+This model is simple to use and has 8 parameters that are easy to determine.
+The limitation of this model is its loss of accuracy in some cases when the 8 parameters are defined.
+This is why many works often limit its identification to only 5, 6 or 7 parameters.
+This has been verified in our study where the smallest error of the model is obtained with only 7 parameters identified.
 
@@
 Section \ref{sec:ConstLaws} is devoted to the presentation of the five analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models.
-Section \ref{sec:inExtrapolation} details the interpolation and extrapolation capabilities of each model proposed in this paper.
+Section \ref{sec:IntExt} details the interpolation and extrapolation capabilities of each model proposed in this paper.
 Conclusions and future work are detailed in Section \ref{sec:Conclusion}.
@@
 Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm.
-A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1.0~\ps$, $2.0~\ps$ and $5.0~\ps$.
+A batch of 30 hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
 
@@
 Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
-As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2\celsius$/s and held at this temperature for $5$~min to eliminate thermal gradients.
-They were then cooled down with a rate of $1\celsius$/s to the test temperature and then held at constant temperature for $1$~min before deformation.
+As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
+They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
 During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
@@
 
-The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:RawData}.
+The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
 \OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}
-Almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
-We have decided to limit the identification up to $0.7$ because for strain rates $2$ and $5$, stresses are note good.
+Almost all data are around $21030$ or less than and the amplitude of deformation is between $0.7$ and $0.85$.
+We have decided to limit the identification up to $0.7$ because for strain rates $\mdot\varepsilon=2$ and $\mdot\varepsilon=5$, stresses are note good.
 The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
@@
 Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
-For the highest strain rates ($1.0~\ps$, $2.0~\ps$, and $5.0~\ps$), the flow stress increases throughout the test.
+For the highest strain rates ($1~\ps$, $2.0~\ps$, and $5~\ps$), the flow stress increases throughout the test.
 One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
@@
 As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
-As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$.
+As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$.
 \OP{What are the temperature and strain rate related with this micrography}
@@
 The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
-This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
+This method allows obtaining one after the other the 5 parameters in the order $A$, $B$, $n$, $C$ and $m$.
 Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=13.5143$~MPa.
@@
 \end{equation}
-where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
+where the 7 coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
 The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.
@@
 However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification.
-For its identification, several authors restrict its expression to a reduced number of $5$ or $6$ $m_i$ parameters only, by forcing a zero value for the other parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.
+For its identification, several authors restrict its expression to a reduced number of 5 or 6 $m_i$ parameters only, by forcing a zero value for the other parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.
 
-In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.
+In the present study, the best results were obtained by taking the model defined by only the first 7 $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.
 From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HS}.
@@
 For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\text{MPa}$.
-It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1.0~\ps$.
+It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1~\ps$.
 This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate.
@@
 
-After some tests of different types of network architecture and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer give the best compromise between prediction, learning time and model compactness.
+After some tests of different types of network architecture and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and 7 neurons for the second layer give the best compromise between prediction, learning time and model compactness.
 From the global architecture point of view, the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
-This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second and $8$ for the output).
+This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second and 8 for the output).
 
@@
 \end{table}
-From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally $6$ times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.
+From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally 6 times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.
 
@@
 %-------------------------------------------------------------------------
-\section{Interpolation and extrapolation capability of phenomenological and ANN models \label{sec:inExtrapolation}}
+\section{Interpolation and extrapolation capability of analytical and ANN models \label{sec:IntExt}}
 %--------------------------------------------------------------------------
-In this section we wish to test the performance of each identified model data interpolating and extrapolating data.
-Indeed, out of the $6$ strain rates used, one strain rate is voluntarily removed (while keeping the same values of strains and temperatures used for the development of the phenomenological and ANN models) so that it is inside or outside the other $5$ strain rates.
-For the strain rate which is between the minimum and the maximum of the $5$ other strain rates, we will thus test the capacity of each model to interpolate the data and for the one which is out of the $5$ other strain rates, the extrapolation capacity of the model is therefore validated.
-The validation procedure is as follows: $5$ strain rates are used to re-identify each model and once identified, it is used to predict the flow stress for the strain rate chosen for both interpolation and extrapolation.
-Validation is done with real data.
-The following subsections will highlight this procedure.
+
+In order to better compare the performances of the models presented previously (the 5 analytical models and the neural network based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
+The identification of the models performed without the section is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
+In order to test the learning capabilities and fidelity of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
+
+Thus, one of the omitted strain rates ($\mdot\varepsilon=1~\ps$) is within the range of strain rates for model identification ($0.001~\ps\text{ to }5~\ps$), so we can test the ability of the models to interpolate the results from the other 5 strain rates and be able to quantify the deviation from the experimental values.
+On the other hand, the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates of identification of the models ($0.001~\ps\text{ to }2~\ps$), we will then test the ability of the models to extrapolate the results and also be able to quantify the deviation with the experimental values.
+
 \subsection{Interpolation validation}
-For the validation of the interpolation, the chosen strain rate is $\mdot\varepsilon = 1.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 2.0\ \ps$  and $\mdot\varepsilon = 5.0\ \ps$.
-The Figure \ref{fig:IntComp} shows the comparison between the predictions of the analytical and ANN models and the experiment.
-It appears from these Figures that all models have relatively good predictions but the ANN model remains the best because the value of its $\AARE$ is $1.4\%$ while it is between $2.33\%$ and $6.13\%$ for the analytical models.
-This further shows the performance of the ANN model compared to the analytical models.
-All these results are summarized in Table \ref{tab:IntVal}.
+
+For the validation of the interpolation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for ANN) are the 5 other, \ie $\mdot\varepsilon=[0.001, 0.
+01, 0.
+1, 2, 5]~\ps$.
+All models were re-identified from the same experimental data on a data set corresponding to 5 strain rates and 5 temperatures.
+
+Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
 \begin{figure}[!ht]
@@
 {Figures/CompInt}
-\caption{Comparison between the experimental and predicted flow stresses by ANN model for interpolation estimation}
-\label{fig:IntComp}
+\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
+\label{fig:CompInt}
 \end{figure}
+Table \ref{tab:IntVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=1~\ps$.
 \begin{table}[h!]
 \centering{}
-\caption{Accuracy coefficients of interpolation}
+\caption{Accuracy coefficients of interpolation for all models $\mdot\varepsilon=1~\ps$}
 \begin{tabular}{llcccccc}
@@
                                  & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $0.71$\\\hline
-\mr{2}{$\mdot\varepsilon=1$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $1.40$\\
+\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $1.40$\\
                                  & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $1.52$\\
@@
 \end{table}
+
+In Figure \ref{fig:CompInt} it can be seen that the first two models (JC and MZA), presented in this study do not have the ability to reproduce the behavior of the material for the strain rate $\mdot\varepsilon=1~\ps$.
+Overall, the JC model gives better results than the MZA model for $\mdot\varepsilon=1~\ps$, which is reflected in Table \ref{tab:IntVal} by a lower value of $\AARE$ and $\RMSE$ for JC than for MZA.
+Nevertheless, these values are higher than $10\%$ for the JC model and $20\%$ for the MZA model, which reflects the poor ability of these models to correctly model the behavior of this material. 
+This finding is in agreement with the previous findings of Sections \ref{sec:JC} and \ref{sec:MZA} which showed the inability of these models to take into account the softening of the behavior visible at low strain rates and low temperatures.
+
+From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models. 
+Table \ref{tab:IntVal} shows the quantitative comparison on all the deformation speeds and on $\mdot\varepsilon=1~\ps$ for these 4 models. 
+It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.78\%$ and $\RMSE=0.71~\text{MPa}$ respectively, that is to say values approximately 3 times lower for the ANN model compared to the AR model.
+
+This shows the superior fidelity of the ANN model compared to the 5 analytical models presented in this study both in the interpolation capability of the model and in the overall behavior.
+
 \subsection{Extrapolation validation}
-For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 1.0\ \ps$  and $\mdot\varepsilon = 2.0\ \ps$.
-Figure \ref{fig:ExtComp} shows the comparison between the predictions  and the experimental.
-Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
-Again, the ANN model shows its ability to extrapolate data.
-This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions.
-It can also be noted that the Arhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
+
+For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0.
+01, 0.
+1, 1, 2]~\ps$.
+The strain rate omitted in this analysis is therefore the highest value, which restricts the learning domain.
+
+In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.91\columnwidth]
+{Figures/CompExt}
+\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
+\label{fig:CompExt}
+\end{figure}
+Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
+%For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 1.0\ \ps$  and $\mdot\varepsilon = 2.0\ \ps$.
+%Figure \ref{fig:CompExt} shows the comparison between the predictions  and the experimental.
+%Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
+%Again, the ANN model shows its ability to extrapolate data.
+%This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions.
+%It can also be noted that the Arhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
 \begin{table}[h!]
 \centering{}
-\caption{Accuracy coefficients of extrapolation}
+\caption{Accuracy coefficients of extrapolation for all models $\mdot\varepsilon=5~\ps$}
 \begin{tabular}{llcccccc}
@@
 \hline
-\mr{2}{all}                  & $\AARE(\%)$         & $14.27$ & $19.96$ & $7.37$ & $3.95$ & $5.53$  & $1.15$\\
+\mr{2}{all}                      & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.37$ & $3.95$ & $5.53$  & $1.15$\\
                                  & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$\\\hline
-\mr{2}{$\mdot\varepsilon=5$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.37$ & $3.53$ & $11.46$ & $3.87$\\
+\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.37$ & $3.53$ & $11.46$ & $3.87$\\
                                  & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$\\
@@
 \end{table}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.91\columnwidth]
-{Figures/CompExt}
-\caption{Comparison between the experimental and predicted flow stresses by ANN model for extrapolation estimation}
-\label{fig:ExtComp}
-\end{figure}
+
+As presented in the previous section regarding the interpolation capability of the models, in Figure \ref{fig:CompExt} it can be seen that the first two models, JC and MZA, in this study again do not have the ability to correctly reproduce the material behavior for the strain rate $\mdot\varepsilon=5~\ps$.
+The JC model performs better than the MZA model for $\mdot\varepsilon=5~\ps$, which is reflected in Table \ref{tab:ExtVal} by a lower value of $\AARE$ and $\RMSE$ for JC than for MZA.
+Nevertheless, these values are too large for proper use.
+It is again the inability of these models to take into account the softening of the behavior at low strain rates and low temperatures that is at the origin of these values.
+
+The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models compared to the other two models. 
+Table \ref{tab:ExtVal} shows the comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 4 models. 
+The HS model performs worse on extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\AARE$ and $\RMSE$ superior to $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
+The two models AR and ANN give the best results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$. 
+The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.15\%$ and $\RMSE=2.40~\text{MPa}$ respectively.
+
+We can therefore conclude from this part of the study that the AR model is the best performing of the 5 analytical models presented, which is in agreement with the fact that it is widely used for thermomechanical processing, but the ANN model approach has advantages over the AR model approach in that, overall, the ANN model is more faithful to the experimental data than the AR model for all strain rates.
 
@@
 In order to use this model we describe here after the procedure to compute the flow stress $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$.
-This process can be decomposed in $3$ phases:
+This process can be decomposed in 3 phases:
 \begin{itemize}
@@
 \end{equation*}
-The biases of the second hidden layer $\overrightarrow{b_2}$ is a $7$ components vector:
+The biases of the second hidden layer $\overrightarrow{b_2}$ is a 7 components vector:
 \begin{equation*}
@@
 \end{equation*}
-The weight vector for the output layer $\overrightarrow{w}$ is a $7$ components vector:
+The weight vector for the output layer $\overrightarrow{w}$ is a 7 components vector:
 \begin{equation*}

### 2022-11-18 Article.tex
Update Conclusion

@@
 \begin{abstract}
-A concept for analysing and using of both analytical and neural network based models is proposed in this study to investigate the high-temperature deformation behavior of the AISI P20 alloy by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \ps - 5\ \ps$) and temperatures ($1050\celsius-1250\celsius$).
+A concept for analysing and using of both analytical and neural network based models is proposed in this study to investigate the high-temperature deformation behavior of the AISI P20 alloy by performing hot compression tests over a wide range of strains ($0.0 - 0.7$),  strain rates ($0.001~\ps - 5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
 Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
@@
 From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy.
-For the strain rate ($\mdot\varepsilon = 0.01\ \ps$)  the AR model fails to describe the flow for temperatures $1050\celsius$ and $1100\celsius$  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon = 0.1\ \ps$) is not well described.
+For the strain rate ($\mdot\varepsilon = 0.01~\ps$)  the AR model fails to describe the flow for temperatures $1050\celsius$ and $1100\celsius$  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon = 0.1~\ps$) is not well described.
 This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high.
@@
 \hline
-Element & C & Mn & Mo & Si & Ni & Cr & Cu\\ \hline
-Wt~\% & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17\\ \hline
+Element & C & Mn & Mo & Si & Ni & Cr & Cu\\\hline
+Wt~\% & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17\\\hline
 \label{tab:Composition}
@@
 How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}
-The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A\ \text{and}\ \varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
+The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A~\text{and}~\varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
 As there are noises from raw data, filter method is applied to remove noise and have more smooth data.
@@
 As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
-As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$.
+As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
 \OP{What are the temperature and strain rate related with this micrography}
@@
 $A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
-$13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\ \hline
+$13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\\hline
 \label{tab:JC}
@@
 Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
-%For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 1.0\ \ps$  and $\mdot\varepsilon = 2.0\ \ps$.
+%For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0~\ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001~\ps$ , $\mdot\varepsilon = 0.01~\ps$ , $\mdot\varepsilon = 0.1~\ps$, $\mdot\varepsilon = 1.0~\ps$  and $\mdot\varepsilon = 2.0~\ps$.
 %Figure \ref{fig:CompExt} shows the comparison between the predictions  and the experimental.
@@
 
-%---------------------------------------------------------------------
-\section{Conclusion \label{sec:Conclusion}}
-Experiments were conducted on modified AISI P20 carbon alloy to study the applicability and predictive accuracy of five analytical models and one neural network model over a range of temperatures ($1050\celsius$ - $1250\celsius$, strains ($0.025$ - $0.7$), strain rates ($0.001\ \ps$ - $5\ \ps$) and the following conclusions were drawn.
-\begin{enumerate}
-\item The flow stress increases with decreasing temperature and increasing strain rate due to the competitive occurrence of dynamic softening and strain hardening mechanisms.
-The degree of DRX was discussed through the difference between the maximum and permanent stress, as well as the evolution of the microstructure which shows a partially complete DRX.
-At high strain rates it is difficult to visualise the DRX phenomenon on the flow curves due to the strain rate sensitivity of this phenomenon.
-A further study will focus on deep analysis of the microstructure of this steel alloy and its impact on mechanical properties.
-\item Five analytical models have been identified on this alloy and a model based on neural networks.
-Among the analytical models, the JC, HS and MZA models proved inappropriate for analysing the behavior of this material whereas the PTM and AR models showed their capacity since they have a relatively acceptable error ($ 3.2 \% $ and $ 3.8 \%$).
-As for the ANN model, it is largely reliable that the analytical models to predict the competitiveness of AISI P20.
-Therefore it may be advisable to use the ANN model when conducting a study involving this alloy under these experimental conditions.
-\item To test the performance of each model, a study is carried out to evaluate the interpolation and extrapolation capacity of the developed models.
-For the interpolation framework, all models have a good correlation with the experiment except the HS model but the ANN model shows a better correlation.
-For extrapolation of the data, the analytical models do not show good predictive capacity compared to the ANN model which still shows good extrapolation capacity.
-This further confirms what was demonstrated during his identification.
-\item As perspectives of this work, we will develop also an ANN model to characterize the microstructure in terms of DRX and phase formation such as fearrite, bainite and martensite as an example.
-This ANN model can therefore be compared to the most commonly used classical models such as the JMAK model.
-Therfore, this ANN model  will be implemented in FEM softwares such as Abaqus, Forge in order to validate it by doing a simulation.
-\end{enumerate}
+%--------------------------------------------------------------------------
+\section{Conclusions and future work\label{sec:Conclusion}}
+%--------------------------------------------------------------------------
+
+Experimental tests were performed on a Gleeble thermomechanical simulator for a modified AISI P20 carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
+The analytical models selected for this study are the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model  \cite{TizeMha-2022}.
+Analysis of the data from the Gleeble trials, and comparison of the 6 models proposed in this study against the experiments, led to the following conclusions.
+
+From an experimental point of view, it appears from the tests carried out that the flow stress $\sigma^y$ increases with the decrease of the temperature $T$ and the increase of the strain rate $\mdot\varepsilon$ due to the competitive appearance of the dynamic softening and work hardening mechanisms.
+The dynamic recrystallization (DRX) phenomenon, introduced through the difference between the maximum and permanent strain, shows a partially complete microstructure evolution. 
+Thus, at high strain rates, it is difficult to visualize the DRX phenomenon on the flow curves due to the sensitivity of this phenomenon to the strain rate. 
+A study focused on an in-depth analysis of the microstructure of this steel alloy and its impact on mechanical properties is currently underway.
+
+Five analytical models have been identified for this alloy, as well as an Artificial Neural Network based model. 
+Among the analytical models, the JC and MZA models proved to be inappropriate to reproduce the behavior of this material, while the HS, PTM and AR models showed their capabilities since they present an acceptable $\AARE$ error (from $3.5\%$ to $7.7\%$), with a superiority of the AR model ($3.56\%$) over the other two which confirms its use in thermomechanical processes.
+The ANN model, is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of the AISI P20 with a value of $\AARE=0.62\%$.
+
+To test the performance of each proposed model, a study was conducted to evaluate the interpolation and extrapolation capability of the developed models. 
+In the case of interpolation, the HS, PTM and AR models have a good correlation with the experiment, but the ANN model shows superiority with an error factor 5 times lower than the AR model. 
+For the extrapolation of the data, the HS, PTM and AR models have again a good correlation with the experiment, but the ANN model is again globally better performing.
+These two parts of the study confirm what was demonstrated in the model identifications.
+
+Identifying the parameters of an ANN model from experimental data requires more time than identifying the parameters of analytical models (about 40 minutes on a working laptop), but as shown by Pantalé \eal \cite{Pantale-2021}, implementing an ANN model in a computational code is straightforward.
+Therefore, we recommend using the ANN model when conducting a study involving this alloy under these experimental conditions.
+
+As part of the perspectives of this work, we will develop another ANN model to characterize this time the microstructure in terms of DRX and formation of phases such as ferrite, bainite and martensite for example.
+This ANN model can then be compared to the most commonly used classical models such as the JMAK model. 
+Then, these ANN models will be implemented in FEM software such as Abaqus or Forge in order to validate them.
 

### 2022-11-18 Article.tex
Update Abstract

@@
 \begin{abstract}
-A concept for analysing and using of both analytical and neural network based models is proposed in this study to investigate the high-temperature deformation behavior of the AISI P20 alloy by performing hot compression tests over a wide range of strains ($0.0 - 0.7$),  strain rates ($0.001~\ps - 5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy.
-Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model.
-These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$).
-From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy.
-For the strain rate ($\mdot\varepsilon = 0.01~\ps$)  the AR model fails to describe the flow for temperatures $1050\celsius$ and $1100\celsius$  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon = 0.1~\ps$) is not well described.
-This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high.
-Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains 7 neurons and the input layer contains 3 neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$).
-The results of the ANN model show a very good agreement between the predictions and the experiment.
-This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction.
-To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.
+An analysis of the use of analytical models and Artificial Neural Networks (ANN) is proposed in this paper to study the high-temperature deformation behavior of AISI P20 alloy during hot compression tests, on a Gleeble thermomechanical simulator, over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
+From the experimental data (stress-strain curves), 5 analytical models such as Johnson-Cook (JC), Modified Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arrhenius (AR) and PTM on the one hand, and an ANN model with 3 inputs, 2 hidden layers of 15 and 7 neurons respectively and 1 output, on the other hand, have been identified to predict the flow of this alloy.
+The comparison between the analytical models, the ANN model and the experimental results, carried out on the basis of the Mean Absolute Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$), allowed us to qualify the fidelity of these models.
+We were able to show that the JC and MZA models are not suitable to predict the high temperature behavior of the AISI P20 alloy, while the HS, PTM and AR models can be used to predict the behavior of this alloy with an acceptable error.
+On the other hand, the ANN model results show excellent agreement between the predicted flow stresses $\sigma^y$ and experiment with very low error.
+To validate the performance of these models, their ability to interpolate and extrapolate the experimental data was also tested. 
+The HS, PTM and AR analytical models have shown a good interpolation and extrapolation capacity with a notable superiority for the AR model compared to the other two. 
+The ANN model is still superior to the AR model from the point of view of its global behavior and its performance.
 \end{abstract}
@@
 \begin{keyword}
-Zerilli-Armstrong flow law \sep Constitutive behavior \sep Arhenius flow law \sep Hansel-Spittel flow law \sep Johnson-Cook flow law \sep interpolation \sep extrapolation \sep Artificial neural network
+Johnson-Cook \sep Zerilli-Armstrong \sep Arrhenius \sep Hansel-Spittel \sep Artificial Neural Network
 \end{keyword}

### 2022-11-18 Article.tex
Final modification before sharing

@@
 \DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
-%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
-%\newcommand{\e}[1]{\exp\left({#1}\right)}
 \DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
@@
 \DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
-\DeclareRobustCommand{\versus}{\emph{vs.}\@\xspace}
 \DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
@@
 \DeclareRobustCommand{\ps}{\text{s}^{-1}}
-%\DeclareMathOperator{\ANN2}{sig}
 \DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
-%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
-%\DeclareMathOperator{\sech}{sech}
-%\DeclareMathOperator{\ANN2}{sig}
-
-\usepackage{esvect}
-% Redefine the esvector shape to remove overlapping
-\def\traitfill@#1#2#3#4{%
-  $\m@th\mkern2mu\relax#4#1\mkern-1.5mu %on met \relbaredd au d\'ebut
-   \cleaders\hbox{$#4\mkern-0.3mu#2\mkern-0.3mu$}\hfill %remplit avec relbareda
-   \mkern-1.5mu#3$%
-}
-\renewcommand{\overrightarrow}{\vv}
 
 % This is used to add comments into the text
-\usepackage{soul} %Can also be used to highlight text with \hl{highlighted text}
+%
+% Will have to be removed from final version
+%
+\usepackage{soul}
 \usepackage{color}
-\definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
-\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:} #1}}\endgroup} }
+\definecolor{VWyellow}{RGB}{255,251,150}
+\DeclareRobustCommand{\OP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
+\DeclareRobustCommand{\OPP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
 
@@
 
-\title{Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and  interpolation-extrapolation capacity validation}
+\title{Comparison of Analytical and Artificial Neural Network models in predicting hot deformation behavior of AISI P20}
 
@@
 \author[ETS]{Mohammad Jahazi}
-\author[LGP]{Olivier Pantalé \corref{cor1}}
+\author[LGP]{Olivier Pantalé\corref{cor1}}
 \ead{Olivier.Pantale@enit.fr}
@@
 
-\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, France 65016}
-\address[ETS]{École de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3}
+\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, 65016, France}
+\address[ETS]{École de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3, Canada}
 
@@
 An analysis of the use of analytical models and Artificial Neural Networks (ANN) is proposed in this paper to study the high-temperature deformation behavior of AISI P20 alloy during hot compression tests, on a Gleeble thermomechanical simulator, over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-From the experimental data (stress-strain curves), 5 analytical models such as Johnson-Cook (JC), Modified Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arrhenius (AR) and PTM on the one hand, and an ANN model with 3 inputs, 2 hidden layers of 15 and 7 neurons respectively and 1 output, on the other hand, have been identified to predict the flow of this alloy.
-The comparison between the analytical models, the ANN model and the experimental results, carried out on the basis of the Mean Absolute Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$), allowed us to qualify the fidelity of these models.
+From the experimental data (stress-strain curves), 5 analytical models such as Johnson-Cook (JC), Modified Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arrhenius (AR) and PTM on the one hand, and an ANN model with 3 inputs, 2 hidden layers of 15 and 7 neurons respectively and 1 output, on the other hand, have been identified to predict the flow stress $\sigma^y$ of this alloy.
+The comparison between the analytical models, the ANN model and the experimental results, carried out on the basis of the Mean Absolute Relative Error ($\AARE$) and the Root Mean Square Error ($\RMSE$), allowed us to qualify these models.
 We were able to show that the JC and MZA models are not suitable to predict the high temperature behavior of the AISI P20 alloy, while the HS, PTM and AR models can be used to predict the behavior of this alloy with an acceptable error.
@@
 
-%--------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 \section{Introduction\label{sec:Introduction}}
-%--------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
+
 Continuous casting and rolling techniques are an integral part of material forming methods.
@@
 Finite element modeling effectively compensates for the shortcomings of analytical and experimental methods and is playing an increasingly important role in determining process parameters, improving product quality, and gaining in-depth knowledge of deformation mechanisms.
-For example, FEM has been widely used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Qin-2010, Mandal-2009, Ji-2018}.
+For example, FEM has been widely used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Mandal-2009, Qin-2010, Ji-2018}.
 
-Hot forming processes are an essential step in the manufacture of mechanical components and directly affect the final quality of the products through their strong influence on the micro-structure and mechanical properties \cite{Ashtiani-2012}.
-Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and re-crystallization), which very often occur during hot working, influence the behavior and deformation of materials.
+Hot forming processes are an essential step in the manufacture of mechanical components and directly affect the final quality of the products through their strong influence on the micro-structure and mechanical properties as reported by Ashtiani \eal \cite{Ashtiani-2012}.
+Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallization), which very often occur during hot working, influence the behavior and deformation of materials.
 The complexity of the thermomechanical behavior usually leads to the fact that it can only be taken into account accurately by using a numerical approach to obtain the response of the material under the specified loading conditions.
-To this end, a mathematical formulation is typically used to represent the flow of a material in a form that can be used in finite element software \cite{Lin-2008-P, Wu-2012}.
+To this end, a mathematical formulation is typically used to represent the flow stress $\sigma^y$ of a material from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ in a form that can be used in finite element software \cite{Lin-2008-P, Wu-2012}.
 
 For several years, many researchers have developed methods to predict the thermomechanical behavior of materials under hot working conditions using constitutive models.
-Thus, various forms of constitutive equations have been proposed to describe the flow of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Lin-2011, Shin-2010, Rusinek-2010, Pantale-2021}.
-Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in finite element codes.
-The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{Khan-2004, NematNasser-2003}.
+Thus, various forms of constitutive equations have been proposed to describe the flow stress of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021}.
+Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEM codes.
+The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{NematNasser-2003, Khan-2004}.
 However, this model, in its original state, has some shortcomings related to nonlinear coupling phenomena not taken into account in the material behavior.
 We refer here to strain hardening, strain rate hardening and thermal effects that are taken into account in a non-coupled manner in the JC model as analyzed by Jia \eal \cite{Jia-2021}.
-To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}.
+To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhang-2015, Zhou-2019}.
 Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
 However, this model has other drawbacks related to the limit value of the test temperature.
-Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}.
+Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Lee-2006, Chen-2007}.
 Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
@@
 
-The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the deformation energy of the material \cite{Jonas-1969, Zhang-2012, Mostafaei-2012}.
+The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the deformation energy of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
 Its original formulation has been revised several times to correctly describe the resulting experimental behavior.
 In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several authors.
-For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arhenius model so that his model could predict the high-temperature flow of a magnesium alloy.
+For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arrhenius model so that his model could predict the high-temperature flow of a magnesium alloy.
 Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.
 
-Users of the Forge software make extensive use of the model developed by Hansel and Spittel \cite{Hensel-1978}, commonly referred to as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on the three physical variables.
+Users of the Forge software make extensive use of the model developed by Hansel and Spittel \cite{Hensel-1978}, commonly referred to as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on $\varepsilon$, $\mdot\varepsilon$ and $T$.
 Unlike the JC model, this formulation is based on parameters that are determined simultaneously.
@@
 
-Behavior modeling based on an artificial neural network is an approach to predict the flow of materials without requiring a mathematical formulation of the flow law.
+Behavior modeling based on an Artificial Neural Network is an approach to predict the flow stress of materials without requiring a mathematical formulation of the flow law.
 It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
@@
 From the experimental data obtained from the compression tests, five analytical models were identified in order to select the one that best describes the behavior of this alloy.
-A flow model based on an artificial neural network was also developed and identified, and a comparative study between the five analytical models and the ANN model is proposed.
+A flow model based on an ANN was also developed and identified, and a comparative study between the 5 analytical models and the ANN model is proposed.
 A fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.
@@
 The main parts of this work are as follows: Section \ref{sec:Materials} presents the hardware (Gleeble thermomechanical simulator), the experimental procedure, the material and the results of the compression tests performed for this study.
-Section \ref{sec:ConstLaws} is devoted to the presentation of the five analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models.
+Section \ref{sec:ConstLaws} is devoted to the presentation of the 5 analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models with regard to the experimental results.
 Section \ref{sec:IntExt} details the interpolation and extrapolation capabilities of each model proposed in this paper.
@@
 
-%----------------------------------------------
+%----------------------------------------------------------------------------------
 \section{Materials and Experiments\label{sec:Materials}}
-%----------------------------------------------
+%----------------------------------------------------------------------------------
 
-%----------------------------------------------
+%----------------------------------------------------------------------------------
 \subsection{Experimental procedure}
-%----------------------------------------------
+%----------------------------------------------------------------------------------
 
 The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
-Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm.
-A batch of 30 hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
-
 \begin{table}[h!]
@@
 	\hline
-Element & C & Mn & Mo & Si & Ni & Cr & Cu\\\hline
-Wt~\% & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17\\\hline
+	Element &  C   &  Mn  &  Mo  &  Si  &  Ni  &  Cr  &  Cu  \\ \hline
+	Wt~\%   & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17 \\ \hline
 	\label{tab:Composition}
@@
 \end{table}
+Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
+A batch of 30 hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
 \begin{figure}[!ht]
@@
 \end{figure}
-
 Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
@@
 After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
-Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $R_0$ are the height and radius before compression and $h$, $R_M$ and $R_T$ are the height, large radius and small radius of the specimen after compression, respectively.
+Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
 \begin{figure}[!ht]
@@
 
-\OP{Here, a part concerning the treatment of the Gleeble data is missing.
-You introduce the notions of $h_0$, $R_0$, $h$, $R_M$ and $R_T$ and we have no idea what they are for.
-How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}
-The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A~\text{and}~\varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
-As there are noises from raw data, filter method is applied to remove noise and have more smooth data.
-For further usage of  data in numerical simulation elastic parts have been removed.
+The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as true stress and true strain according to L-gauge where the formula to get those curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2r_0$ and $F$ is the force as measured by Gleeble load cell.\OPP{those formulas seems incomplete.}
+As there are noises from raw data, filter method is applied to remove noise and have more smooth data.\OPP{what is the filtering method used ?}
+For further usage of data in numerical simulation elastic parts have been removed. \OPP{you must explain how.}
 
-%------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 \subsection{Compression tests results\label{sec:ComTestResults}}
-%------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 
 The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
-\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}
-Almost all data are around $21030$ or less than and the amplitude of deformation is between $0.7$ and $0.85$.
-We have decided to limit the identification up to $0.7$ because for strain rates $\mdot\varepsilon=2$ and $\mdot\varepsilon=5$, stresses are note good.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\columnwidth]{Figures/rawData}
+\caption{Stress-strain curves of AISI P20 alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
+\label{fig:RawData}
+\end{figure}
+All data curve contains $700$ equidistant strain values up-to $\varepsilon=0.7$.
+So, as we have 6 strain rates and 5 temperatures, the database consists of $21~000$ data points.
 The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
@@
 Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
-For the highest strain rates ($1~\ps$, $2.0~\ps$, and $5~\ps$), the flow stress increases throughout the test.
+For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
 One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
@@
 This results in a progressive increase of the flow stress.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]{Figures/rawData}
-\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
-\label{fig:RawData}
-\end{figure}
 
@@
 These two phenomena explain the different shapes of the flow stress curves observed for this alloy.
-As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
-As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
-\OP{What are the temperature and strain rate related with this micrography}
-From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.
-
+As an example, Figure \ref{fig:Micrography} shows the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
 \begin{figure}[!ht]
 \centering
-\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{0.45\columnwidth}
 \centering
-\includegraphics[width=\textwidth]{Figures/BeforeCompM}
+\includegraphics[width=\columnwidth]{Figures/BeforeCompM}
 \caption{Before hot compression}
@@
 \hfill
-\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{0.45\columnwidth}
 \centering
-\includegraphics[width=\textwidth]{Figures/AfterCompM}
+\includegraphics[width=\columnwidth]{Figures/AfterCompM}
 \caption{After hot compression}
 \end{subfigure}
-\caption{Optical micrographs of the AISI P20 steel before and after hot compression.}
+\caption{Optical micrographs of the AISI P20 steel before (a) and after (b) hot compression.}
 \label{fig:Micrography}
 \end{figure}
+As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
+From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the 6 proposed flow laws will be presented in the next section in order to predict the behavior of the material in any test condition.
 
-%-------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 \section{Identification of constitutive flow laws parameters\label{sec:ConstLaws}}
-%-------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 
-The complete characterization of the thermomechanical behavior of a material through the identification of its flow law is very important before its modeling in numerical simulations.
+The complete characterization of the thermomechanical behavior of a material through the identification of the parameters of its flow law is very important for an accurate modeling in numerical simulations.
 This characterization usually involves experimental tests that serve as a basis for the development of constitutive laws.
 As mentioned in the introduction, many constitutive laws exist today, and the selection of one of them on the basis of explicit criteria makes the development of computational models for new materials with new types of behavior challenging.
-Since the purpose of this work is to compare the ANN model to analytical models, it is important to justify the choice of analytical models selected for this study among the many that exist in the literature.
+Since the purpose of this work is to compare the ANN model to some analytical models, it is important to justify the choice of the analytical models selected for this study among the many that exist in the literature.
 Among the analytical models, the Johnson-Cook (JC) model \cite{Johnson-1983} is the most used because of its simplicity of implementation linked to the reduced number of its parameters and the ease to identify them.
-It should be noted that it is not the best model but the most integrated in the Finite Elements softwares.
+It should be noted that it is not the best model but the most integrated in the Finite Elements softwares such as Abaqus for example.
 This also explains the existence of several modified forms of this model.
@@
 It is therefore also part of this study.
-The Hansel Spittel (HS) model \cite{Hensel-1978} is also one of the most widely used models in numerical simulation of casting and forging operations because it is natively integrated in the Forge software.
+The Hansel-Spittel (HS) model \cite{Hensel-1978} is also one of the most widely used models in numerical simulation of casting and forging operations because it is integrated in the Forge software.
 Moreover, the method of identifying its parameters is very simple to perform since it is done in one step.
@@
 The Arrhenius model was also chosen in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter $Q$ (the deformation activation energy coefficient) which is of great importance in the microstructural analyses of materials.
-The PTM model \cite{TizeMha-2022} is also used in this study because it is a model whose formulation does not impose a priori a number of parameters and which proved its ability in our previous works \cite{TizeMha-2022}.
+The PTM model \cite{TizeMha-2022} is also used in this study because it is a model whose formulation does not impose a given number of parameters and which proved its ability in our previous works \cite{TizeMha-2022}.
 We selected it to test it on this type of material because it is normally formulated to fit any type of material.
 
-%-------------------------------------------------------------------------
-\subsection{Johnson-Cook model\label{sec:JC}}
-%-------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
+\subsection{The Johnson-Cook model\label{sec:JC}}
+%----------------------------------------------------------------------------------
 
@@
 The equation that describes this model is given as follows \cite{Johnson-1983}:
-
 \begin{equation}
@@
 The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
-
 For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$ respectively.
@@
 This method allows obtaining one after the other the 5 parameters in the order $A$, $B$, $n$, $C$ and $m$.
-Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=13.5143$~MPa.
+Thus, according to our experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143$~MPa.
 For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
@@
 The values predicted by the Johnson-Cook flow law (solid line) and the experimental values (dots) are compared in Figure \ref{fig:CompExp-JC-6}.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\columnwidth]{Figures/CompExp-JC-6}
+\caption{Comparison between the experimental and predicted flow stresses by JC model.}
+\label{fig:CompExp-JC-6}
+\end{figure}
 The JC model is not able to describe the evolution of the flow stress of AISI P20 for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1.02\columnwidth]{Figures/CompExp-JC-6}
-\caption{Comparison between the experimental and predicted flow stresses by JC model.}
-\label{fig:CompExp-JC-6}
-\end{figure}
+The accuracy and predictive ability of the models are usually assessed by certain coefficients such as the Mean Absolute Relative Error ($\AARE$) defined by Equation (\ref{eq:AARE}):
+\begin{equation}
+\AARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
+\end{equation}
+and the Root Mean Square Error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
+\begin{equation}
+\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
+\end{equation}
+where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the predicted value using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
+For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\text{MPa}$.
+As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
+Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction we avoided its use in our analysis.
 
-The accuracy and predictive ability of the models are usually assessed by certain coefficients such as the Mean Absolute Relative Error ($\AARE$) defined by Equation (\ref{eq:AARE}) and the Root Mean Square Error ($\RMSE$) defined by Equation (\ref{eq:RMSE}).
-\begin{equation}
-\AARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100 \label{eq:AARE}
-\end{equation}
-\begin{equation}
-\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2} \label{eq:RMSE}
-\end{equation}
-where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the predicted value using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21000$).
-For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\text{MPa}$.
-The correlation coefficient ($R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
-Therefore, a good (high) value of $R$ (close to $1$) does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction \cite{Phaniraj-2003}.
+%----------------------------------------------------------------------------------
+\subsection{The Modified Zerilli-Armstrong model\label{sec:MZA}}
+%----------------------------------------------------------------------------------
 
-%-------------------------------------------------------------------------
-\subsection{Modified Zerilli-Armstrong model\label{sec:MZA}}
-%-------------------------------------------------------------------------
-The MZA which is the modified form of ZA model, as the JC model is one of widely used models and implemented in many sofwares like Abaqus.
+The MZA which is the modified form of ZA model, as the JC model is one of widely used models and implemented in many FEM codes like Abaqus.
 The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experimental.
-Indeed, in the JC model, those parameters are considered separately where they are simultaneaously considered in MZA and for that formulation MZA is prefered to JC model \cite{Hull-2011}.
+Indeed, in the JC model, those parameters are considered separately where they are simultaneously considered in MZA and for that formulation MZA is preferred to JC model \cite{Hull-2011}.
 But the original form of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
@@
 \label{eq:MZA-model}
-\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
+\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right],
 \end{equation}
 where the 7 coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
-The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.
+The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is summarized as following.
 
-Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$.
-When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
-\begin{equation}
-\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
-\end{equation}
-Taking the logarithm of the previous relationship we have :
+\OP{See again how to summarize this part, since this method is already published.}
+
+Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced directly from $\sigma^y(0,T_0,\mdot{\varepsilon}_0)$.
+When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, taking the logarithm of the Equation (\ref{eq:MZA-model}) leads to:
 \begin{equation}
@@
 \end{equation}
+
 By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
@@
 \end{equation}
+
 By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
@@
 \begin{equation}
-\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
+\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right),
 \end{equation}
@@
 Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
-The parameters of MZA model are given in the Table \ref{tab:MZA} while its prediction are shown in Figure \ref{fig:CompExp-MZA-6}.
-It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
-The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
-For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model.
-That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
+The parameters of MZA model are given in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
 \begin{table}[h!]
@@
 \centering
-\includegraphics[width=1.02\columnwidth]
+\includegraphics[width=\columnwidth]
 {Figures/CompExp-MZA-6}
@@
 \end{figure}
+It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
+The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
+For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.
 
-%-------------------------------------------------------------------------
-\subsection{Hansel and Spittel model\label{sec:HSmodel}}
-%-------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
+\subsection{The Hansel-Spittel model\label{sec:HSmodel}}
+%----------------------------------------------------------------------------------
 
-The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in finite element simulation software, although the determination of its parameters is easier than that of the JC or MZA model.
+The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEM codes, although the determination of its parameters is easier than that of the JC or MZA model.
 The programming of a simple identification script is sufficient to identify its parameters for a given material.
@@
 \begin{equation}
-\sigma^y = A~\e{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~\e{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~\e{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8} \label{eq:HS}
+\sigma^y = A~\e{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~\e{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~\e{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8}, \label{eq:HS}
 \end{equation}
-where $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature as proposed earlier.
-The coefficients $A$ and $m_i$ are the parameters of the model to be identified.
+where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature as proposed earlier.
+The coefficients $A$ and $m_i$ are the 9 parameters of the model to be identified.
 However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification.
-For its identification, several authors restrict its expression to a reduced number of 5 or 6 $m_i$ parameters only, by forcing a zero value for the other parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.
+For its identification, several authors restrict its expression to a reduced number of 5 or 6 $m_i$ parameters only, by forcing a zero value for the other parameters \cite{Chadha-2018, Mehtedi-2015, Rudnytskyj-2020}.
 
@@
 \centering
-\includegraphics[width=1.02\columnwidth]
+\includegraphics[width=\columnwidth]
 {Figures/CompExp-HS-6}
@@
 %----------------------------------------------------------------------------------
-\subsection{Arrhenius model\label{sec:ARmodel}}
+\subsection{The Arrhenius model\label{sec:ARmodel}}
 %----------------------------------------------------------------------------------
@@
 \begin{equation}
-Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}
+Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)}, \label{eq:ArZ}
 \end{equation}
@@
 The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
-The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
+The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
 Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:AR}.
@@
 \centering
-\caption{Parameters' values of the Arrhenius flow law for the P20 steel}
+\caption{Parameters' values of the Arrhenius flow law for the P20 steel.}
 \begin{tabular}{llll}
@@
 \centering
-\includegraphics[width=1.02\columnwidth]
+\includegraphics[width=\columnwidth]
 {Figures/CompExp-AR-6}
@@
 
-%-------------------------------------------------------------------------
-\subsection{PTM model\label{sec:PTM}}
-%--------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
+\subsection{The PTM model\label{sec:PTM}}
+%----------------------------------------------------------------------------------
 
@@
 Its construction is based on the use of polynomial functions as in the AR model.
-Thus, the intrinsic functions of the model, of polynomial type, allow to adjust the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
+Thus, the intrinsic functions of the model, of polynomial type, allow adjusting the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
 The equation describing the PTM model is therefore given by :
@@
 \centering
-\caption{Parameters' values of the PTM flow law for the P20 steel}
+\caption{Parameters' values of the PTM flow law for the P20 steel.}
 \begin{tabular}{llll}
 	\hline
-\multicolumn{1}{c}{$A_i$} & \multicolumn{1}{c}{$B_i$} & \multicolumn{1}{c}{$C_0^i$} & \multicolumn{1}{c}{$C_1^i$}\\
-\hline
-$A_0=16.8529$ & $B_0=-3.5418\times 10^{-3}$ & $C_0^0=0.1608$ & $C_1^0=-1.9037\times 10^{-5}$\\
-$A_1=340.6451$ & $B_1=-0.0132$ & $C_0^1=-0.6202$ & $C_1^1=2.67\times 10^{-3}$\\
-$A_2=-1.9594\times 10^{3}$ & $B_2=-4.4888\times 10^{-3}$ & $C_0^2=4.9516$ & $C_1^2=-3.5788\times 10^{-3}$\\
-$A_3=4.836\times 10^{3}$ & $B_3=0.2218$ & $C_0^3=-13.1694$ & $C_1^3=-0.0222$\\
-$A_4=-5.5176\times 10^{3}$ & $B_4=-0.4988$ & $C_0^4=15.25$ & $C_1^4=0.0609$\\
-$A_5=2.4058\times 10^{3}$ & $B_5=0.3211$ & $C_0^5=-6.587$ & $C_1^5=-0.0413$\\
-\hline
+	\multicolumn{1}{c}{$A_i$}  & \multicolumn{1}{c}{$B_i$}   & \multicolumn{1}{c}{$C_0^i$} & \multicolumn{1}{c}{$C_1^i$}   \\ \hline
+	$A_0=16.8529$              & $B_0=-3.5418\times 10^{-3}$ & $C_0^0=0.1608$              & $C_1^0=-1.9037\times 10^{-5}$ \\
+	$A_1=340.6451$             & $B_1=-0.0132$               & $C_0^1=-0.6202$             & $C_1^1=2.67\times 10^{-3}$    \\
+	$A_2=-1.9594\times 10^{3}$ & $B_2=-4.4888\times 10^{-3}$ & $C_0^2=4.9516$              & $C_1^2=-3.5788\times 10^{-3}$ \\
+	$A_3=4.836\times 10^{3}$   & $B_3=0.2218$                & $C_0^3=-13.1694$            & $C_1^3=-0.0222$               \\
+	$A_4=-5.5176\times 10^{3}$ & $B_4=-0.4988$               & $C_0^4=15.25$               & $C_1^4=0.0609$                \\
+	$A_5=2.4058\times 10^{3}$  & $B_5=0.3211$                & $C_0^5=-6.587$              & $C_1^5=-0.0413$               \\ \hline
 	\label{tab:PTM}
@@
 \centering
-\includegraphics[width=1.02\columnwidth]
+\includegraphics[width=\columnwidth]
 {Figures/CompExp-PTM-6}
@@
 
-%-------------------------------------------------------------------------
-\subsection{Artificial Neural Network model\label{sec:ANNmodel}}
-%--------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
+\subsection{The Artificial Neural Network model\label{sec:ANNmodel}}
+%----------------------------------------------------------------------------------
+
 Because of their predictive capacity and their adaptability, Artificial Neural Networks (ANNs) are more and more widely used today in many scientific fields.
@@
 \begin{equation}
-y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k}\label{eq:ANN1}
+y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
 \end{equation}
@@
 Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN that we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021}.
-For the proposed model, we have selected the ANN2 activation function, so that, each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
+For the proposed model, we have selected the Sigmoid activation function, so that, each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
 \begin{equation}
@@
 From the global architecture point of view, the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
-This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second and 8 for the output).
+This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second layer and 8 for the output layer).
 
@@
 The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
-The training data are those from the tests presented in section \ref{sec:ComTestResults} and composed of $21000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
-The learning is performed on the basis of $5000$ epochs of the experimental data set.
+The training data are those from the tests presented in section \ref{sec:ComTestResults} and composed of $21~000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
+The learning is performed on the basis of $5~000$ epochs of the experimental data set.
 Fourty minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GiB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
-Figure \ref{fig:ANN-6-conv} show the evolution of the training error defined by the $\log_{10}$ of the Root Mean Square Error during the training phase.
+Figure \ref{fig:ANN-6-conv} show the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$  during the training phase.
 \begin{figure}[!ht]
@@
 \end{figure}
-As we can see on this figure, after $5000$ epoch, we can consider that we have reached a stationary state of the model learning and that it is useless to continue the learning phase.
+As we can see on this figure, after $5~000$ epoch, we can consider that we have reached a stationary state of the model learning and that it is useless to continue the learning phase.
 
@@
 \centering
-\includegraphics[width=1\columnwidth]
+\includegraphics[width=\columnwidth]
 {Figures/CompExp-3-15-7-1-sigmoid}
@@
 
-%-------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 \subsection{Comparison of analytical and ANN models\label{sec:Comparison}}
-%--------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 
@@
 
-%-------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 \section{Interpolation and extrapolation capability of analytical and ANN models \label{sec:IntExt}}
-%--------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------
 \subsection{Interpolation validation}
+%----------------------------------------------------------------------------------
 
@@
 \centering
-\includegraphics[width=1.02\columnwidth]
+\includegraphics[width=\columnwidth]
 {Figures/CompInt}
@@
 
+%----------------------------------------------------------------------------------
 \subsection{Extrapolation validation}
+%----------------------------------------------------------------------------------
 
@@
 \centering
-\includegraphics[width=0.91\columnwidth]
+\includegraphics[width=\columnwidth]
 {Figures/CompExt}
@@
 %This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions.
-%It can also be noted that the Arhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
+%It can also be noted that the Arrhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
 \begin{table}[h!]
@@
 
-%--------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 \section{Conclusions and future work\label{sec:Conclusion}}
-%--------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------
 \section*{Appendix\label{sec:Appendix}}
+%----------------------------------------------------------------------------------
+
 In order to complete this paper, we report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.

### 2022-11-24 Article.tex
Add two lines in final tables

@@
 \centering{}
-\caption{Accuracy coefficients of interpolation for all models $\mdot\varepsilon=1~\ps$}
+\caption{Accuracy coefficients of interpolation for all models with  $\mdot\varepsilon=1~\ps$}
 \begin{tabular}{llcccccc}
 	\hline
-$\mdot\varepsilon$               & Coefficients        & JC      & MZA     & HS     & AR     & PTM    & ANN\\
-\hline
-\mr{2}{all}                      & $\AARE(\%)$         & $13.97$ & $21.49$ & $7.76$ & $3.54$ & $4.78$ & $0.78$\\
-                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $0.71$\\\hline
-\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $1.40$\\
-                                 & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $1.52$\\
-\hline
-\label{tab:IntVal}
+	$\mdot\varepsilon$               & Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
+	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
+	                                 & $\RMSE(\text{MPa})$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
+	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
+	                                 & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
+	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
+	                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
+	\label{tab:IntVal}               &
 \end{tabular}
@@
 From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
-Table \ref{tab:IntVal} shows the quantitative comparison on all the deformation speeds and on $\mdot\varepsilon=1~\ps$ for these 4 models.
-It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.78\%$ and $\RMSE=0.71~\text{MPa}$ respectively, that is to say values approximately 3 times lower for the ANN model compared to the AR model.
+Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates, on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
+It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\text{MPa}$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.
 
@@
 Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
-%For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0~\ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001~\ps$ , $\mdot\varepsilon = 0.01~\ps$ , $\mdot\varepsilon = 0.1~\ps$, $\mdot\varepsilon = 1.0~\ps$  and $\mdot\varepsilon = 2.0~\ps$.
-%Figure \ref{fig:CompExt} shows the comparison between the predictions  and the experimental.
-%Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
-%Again, the ANN model shows its ability to extrapolate data.
-%This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions.
-%It can also be noted that the Arrhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
 \begin{table}[h!]
 \centering{}
-\caption{Accuracy coefficients of extrapolation for all models $\mdot\varepsilon=5~\ps$}
+\caption{Accuracy coefficients of extrapolation for all models with  $\mdot\varepsilon=5~\ps$}
 \begin{tabular}{llcccccc}
@@
 \hline
-\mr{2}{all}                      & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.37$ & $3.95$ & $5.53$  & $1.15$\\
+\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$\\
+                                 & $\RMSE(\text{MPa})$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$\\\hline
+\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$\\
+                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$\\\hline
+\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$\\
                                  & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$\\\hline
-\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.37$ & $3.53$ & $11.46$ & $3.87$\\
-                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$\\
-\hline
 \label{tab:ExtVal}
@@
 The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models compared to the other two models.
-Table \ref{tab:ExtVal} shows the comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 4 models.
+Table \ref{tab:ExtVal} shows the comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
 The HS model performs worse on extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\AARE$ and $\RMSE$ superior to $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
 The two models AR and ANN give the best results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
-The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.15\%$ and $\RMSE=2.40~\text{MPa}$ respectively.
+The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.09\%$ and $\RMSE=2.40~\text{MPa}$ respectively.
 

### 2022-11-25 Article.tex
Move misplaced Tables labels

@@
 	Wt~\%   & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17 \\ \hline
+\end{tabular}
 \label{tab:Composition}
-\end{tabular}
 \end{table}
@@
 	\hline
-$A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
-$13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\\hline
+	$A~(\text{MPa})$ & $B~(\text{MPa})$ &   $n$    &   $C$    &   $m$    \\
+	   $13.5143$     &     $21.816$     & $0.0746$ & $0.3404$ & $0.7057$ \\ \hline
+\end{tabular}
 \label{tab:JC}
-\end{tabular}
 \end{table}
@@
 	\hline
-$C_1$ & $C_2$ & $C_3$ & $C_4$ & $C_5$ & $C_6$ & $n$\\
-$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$\\
-\hline
+	  $C_1$   &   $C_2$   &         $C_3$          &         $C_4$          &  $C_5$   &         $C_6$         &   $n$    \\
+	$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$ \\ \hline
+\end{tabular}
 \label{tab:MZA}
-\end{tabular}
 \end{table}
@@
 	\hline
-$A$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
-$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$ & $-0.0868$ & $2.2688\times10^{-4}$\\\hline
-& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
-& $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$\\\hline
+	        $A$          &         $m_1$          &   $m_2$   &        $m_3$         &         $m_4$         \\
+	$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$  &      $-0.0868$       & $2.2688\times10^{-4}$ \\ \hline
+	                     &         $m_5$          &   $m_6$   &        $m_7$         &         $m_8$         \\
+	                     & $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ &          $0$          \\ \hline
+\end{tabular}
 \label{tab:HS}
-\end{tabular}
 \end{table}
@@
 	\hline
-\multicolumn{1}{c}{$\alpha_i$} & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}\\
-\hline
-$\alpha_0=0.0407$ & $Q_0=0.467$ & $A_0=35.8092$ & $n_0=4.8217$\\
-$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & $A_1=-58.822$ & $n_1=3.2814$\\
-$\alpha_2=6.3912$ & $Q_2=7.6084$ & $A_2=740.3303$ & $n_2=71.5963$\\
-$\alpha_3=-47.3364$ & $Q_3=-48.016$ & $A_3=-5.0493\times 10^{3}$ & $n_3=-1.9562\times 10^{3}$\\
-$\alpha_4=220.0014$ & $Q_4=66.795$ & $A_4=1.1305\times 10^{4}$ & $n_4=1.4461\times 10^{4}$\\
-$\alpha_5=-654.4553$ & $Q_5=468.8898$ & $A_5=2.022\times 10^{4}$ & $n_5=-5.431\times 10^{4}$\\
-$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & $A_6=-1.5387\times 10^{5}$ & $n_6=1.1761\times 10^{5}$\\
-$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & $A_7=3.1798\times 10^{5}$ & $n_7=-1.4882\times 10^{5}$\\
-$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$\\
-$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$\\
-\hline
+	\multicolumn{1}{c}{$\alpha_i$}  & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}  \\ \hline
+	$\alpha_0=0.0407$               & $Q_0=0.467$                                & $A_0=35.8092$                  & $n_0=4.8217$               \\
+	$\alpha_1=-0.5167$              & $Q_1=-0.6517$                              & $A_1=-58.822$                  & $n_1=3.2814$               \\
+	$\alpha_2=6.3912$               & $Q_2=7.6084$                               & $A_2=740.3303$                 & $n_2=71.5963$              \\
+	$\alpha_3=-47.3364$             & $Q_3=-48.016$                              & $A_3=-5.0493\times 10^{3}$     & $n_3=-1.9562\times 10^{3}$ \\
+	$\alpha_4=220.0014$             & $Q_4=66.795$                               & $A_4=1.1305\times 10^{4}$      & $n_4=1.4461\times 10^{4}$  \\
+	$\alpha_5=-654.4553$            & $Q_5=468.8898$                             & $A_5=2.022\times 10^{4}$       & $n_5=-5.431\times 10^{4}$  \\
+	$\alpha_6=1.2421\times 10^{3}$  & $Q_6=-2.3032\times 10^{3}$                 & $A_6=-1.5387\times 10^{5}$     & $n_6=1.1761\times 10^{5}$  \\
+	$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$                  & $A_7=3.1798\times 10^{5}$      & $n_7=-1.4882\times 10^{5}$ \\
+	$\alpha_8=952.0619$             & $Q_8=-3.9394\times 10^{3}$                 & $A_8=-2.9725\times 10^{5}$     & $n_8=1.0239\times 10^{5}$  \\
+	$\alpha_9=-267.4994$            & $Q_9=1.397\times 10^{3}$                   & $A_9=1.0759\times 10^{5}$      & $n_9=-2.9621\times 10^{4}$ \\ \hline
+\end{tabular}
 \label{tab:AR}
-\end{tabular}
 \end{table}
@@
 	$A_5=2.4058\times 10^{3}$  & $B_5=0.3211$                & $C_0^5=-6.587$              & $C_1^5=-0.0413$               \\ \hline
+\end{tabular}
 \label{tab:PTM}
-\end{tabular}
 \end{table}
@@
 	\hline
-Coefficients & JC & MZA & HS & AR & PTM & ANN\\
-\hline
-$\AARE(\%)$ & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$\\
-$\RMSE(\text{MPa})$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$\\
-\hline
+	Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
+	$\AARE(\%)$         & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
+	$\RMSE(\text{MPa})$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \hline
+\end{tabular}
 \label{tab:Errors}
-\end{tabular}
 \end{table}
@@
 	\hline
-	$\mdot\varepsilon$               & Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
+	Strain rate                      & Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
 	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
@@
 	                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
-	\label{tab:IntVal}               &
 \end{tabular}
+\label{tab:IntVal}
 \end{table}
@@
 From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
-Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates, on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
+Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates (named id.
+$\mdot\varepsilon$), on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
 It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\text{MPa}$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.
@@
 	\hline
-$\mdot\varepsilon$               & Coefficients        & JC      & MZA     & HS     & AR     & PTM     & ANN\\
-\hline
-\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$\\
-                                 & $\RMSE(\text{MPa})$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$\\\hline
-\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$\\
-                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$\\\hline
-\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$\\
-                                 & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$\\\hline
+	Strain rate                      & Coefficients        &   JC    &   MZA   &   HS   &   AR   &   PTM   &  ANN   \\ \hline
+	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$ \\
+	                                 & $\RMSE(\text{MPa})$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$ \\ \hline
+	\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$ \\
+	                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ \hline
+	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$ \\
+	                                 & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$ \\ \hline
+\end{tabular}
 \label{tab:ExtVal}
-\end{tabular}
 \end{table}

### 2022-11-25 Article.tex
Small corrections to main Article

@@
 \DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
+\DeclareRobustCommand{\MPa}{\text{MPa}}
 
@@
 As there are noises from raw data, filter method is applied to remove noise and have more smooth data.\OPP{what is the filtering method used ?}
-For further usage of data in numerical simulation elastic parts have been removed. \OPP{you must explain how.}
+For further usage of data in numerical simulation elastic parts have been removed.
+\OPP{you must explain how.}
 
@@
 This method allows obtaining one after the other the 5 parameters in the order $A$, $B$, $n$, $C$ and $m$.
-Thus, according to our experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143$~MPa.
+Thus, according to our experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
 For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
-Thus, here, $B=21.816$~MPa and $n=0.0746$.
+Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
 Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
@@
 	\hline
-	$A~(\text{MPa})$ & $B~(\text{MPa})$ &   $n$    &   $C$    &   $m$    \\
+	$A~(\MPa)$ & $B~(\MPa)$ &   $n$    &   $C$    &   $m$    \\
 	   $13.5143$     &     $21.816$     & $0.0746$ & $0.3404$ & $0.7057$ \\ \hline
@@
 \begin{equation}
-\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
+\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
 \end{equation}
 where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the predicted value using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
-For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\text{MPa}$.
+For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
 As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
@@
 The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
-For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.
+For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\MPa$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.
 
@@
 The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
-For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\text{MPa}$.
+For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\MPa$.
 It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1~\ps$.
@@
 But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
-For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\text{MPa}$.
+For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\MPa$.
 
@@
 Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
-The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
+The PTM model is suitable to describe the flow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
 The deviation between the predicted values and the experimental values for other strain rates is relatively good.
-For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\text{MPa}$ and this shows an overall worse performance than the AR model.
+For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\MPa$ and this shows an overall worse performance than the AR model.
 
@@
 The learning is performed on the basis of $5~000$ epochs of the experimental data set.
-Fourty minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GiB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
+Fourty minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
 Figure \ref{fig:ANN-6-conv} show the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$  during the training phase.
@@
 The correlation between the experimental data and the ANN prediction is very good over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
-For the ANN model, $\AARE=0.62~\%$ and $\RMSE=0.38~\text{MPa}$ which is excellent.
+For the ANN model, $\AARE=0.62~\%$ and $\RMSE=0.38~\MPa$ which is excellent.
 This model can be used to simulate the hot deformation of this type of alloy with much greater fidelity to the actual material behavior than the analytical models presented previously.
@@
 	$\AARE(\%)$         & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
-	$\RMSE(\text{MPa})$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \hline
+	$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \hline
 \end{tabular}
@@
 
-For the validation of the interpolation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for ANN) are the 5 other, \ie $\mdot\varepsilon=[0.001, 0.
-01, 0.
-1, 2, 5]~\ps$.
+For the validation of the interpolation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for ANN) are the 5 other, \ie $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
 All models were re-identified from the same experimental data on a data set corresponding to 5 strain rates and 5 temperatures.
@@
 	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
-	                                 & $\RMSE(\text{MPa})$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
+	                                 & $\RMSE(\MPa)$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
 	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
-	                                 & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
+	                                 & $\RMSE(\MPa)$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
 	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
-	                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
+	                                 & $\RMSE(\MPa)$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
 \end{tabular}
@@
 $\mdot\varepsilon$), on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
-It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\text{MPa}$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.
+It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.
 
@@
 
-For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0.
-01, 0.
-1, 1, 2]~\ps$.
+For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0.01, 0.1, 1, 2]~\ps$.
 The strain rate omitted in this analysis is therefore the highest value, which restricts the learning domain.
@@
 	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$ \\
-	                                 & $\RMSE(\text{MPa})$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$ \\ \hline
+	                                 & $\RMSE(\MPa)$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$ \\ \hline
 	\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$ \\
-	                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ \hline
+	                                 & $\RMSE(\MPa)$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ \hline
 	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$ \\
-	                                 & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$ \\ \hline
+	                                 & $\RMSE(\MPa)$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$ \\ \hline
 \end{tabular}
@@
 The two models AR and ANN give the best results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
-The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.09\%$ and $\RMSE=2.40~\text{MPa}$ respectively.
+The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.09\%$ and $\RMSE=2.40~\MPa$ respectively.
 
@@
 \end{equation}
-where $[~]_{min}$ and $[~]_{max}$  are the boundaries of the range of the corresponding field: $\varepsilon^p\!\in\!\left[0.0,0.7\right]$, $\mdot{\varepsilon}\!\in\!\left[0.001,5.0\right]$, $T\!\in\!\left[1050,1250\right]$ and $\sigma\!\in\!\left[1.311,153.739\right]$.
-The reference strain rate is $\mdot{\varepsilon_0} = 0.001$.
+where $[~]_{min}$ and $[~]_{max}$  are the boundaries of the range of the corresponding field: $\varepsilon^p\!\in\!\left[0.0,0.7\right]$, $\mdot{\varepsilon}\!\in\!\left[0.001~\ps,5.0~\ps\right]$, $T\!\in\!\left[1050~\celsius,1250~\celsius\right]$ and $\sigma\!\in\!\left[1.311~\MPa,153.739~\MPa\right]$.
+The reference strain rate is $\mdot{\varepsilon_0} = 0.001~\ps$.
 \item Then we compute the output $s$ of the ANN from the input vector $\overrightarrow{x}$ using the three following equations.

### 2022-12-14 Article.tex
texFile and Bib updated

@@
 
-\title{Comparison of Analytical and Artificial Neural Network models in predicting hot deformation behavior of AISI P20}
+\title{\textcolor{red}{Interpolation and extrapolation based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}}
 
@@
 \begin{abstract}
-An analysis of the use of analytical models and Artificial Neural Networks (ANN) is proposed in this paper to study the high-temperature deformation behavior of AISI P20 alloy during hot compression tests, on a Gleeble thermomechanical simulator, over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-From the experimental data (stress-strain curves), 5 analytical models such as Johnson-Cook (JC), Modified Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arrhenius (AR) and PTM on the one hand, and an ANN model with 3 inputs, 2 hidden layers of 15 and 7 neurons respectively and 1 output, on the other hand, have been identified to predict the flow stress $\sigma^y$ of this alloy.
-The comparison between the analytical models, the ANN model and the experimental results, carried out on the basis of the Mean Absolute Relative Error ($\AARE$) and the Root Mean Square Error ($\RMSE$), allowed us to qualify these models.
-We were able to show that the JC and MZA models are not suitable to predict the high temperature behavior of the AISI P20 alloy, while the HS, PTM and AR models can be used to predict the behavior of this alloy with an acceptable error.
-On the other hand, the ANN model results show excellent agreement between the predicted flow stresses $\sigma^y$ and experiment with very low error.
+\textcolor{purple}{An analysis of the use of analytical models and Artificial Neural Networks is proposed in this paper to study the high-temperature deformation behavior of medium carbon steel alloy during hot compression tests, on a Gleeble thermomechanical simulator, over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
+From the experimental data (stress-true strain curves), 5 analytical models such as Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius and PTM on the one hand, and an Artificial Neural Networks model with 3 inputs, 2 hidden layers of 15 and 7 neurons respectively and 1 output, on the other hand, have been identified to predict the flow stress $\sigma^y$ of this alloy.
+The comparison between the analytical models, the Artificial Neural Networks model and the experimental results, carried out on the basis of the Mean Absolute Relative Error ($\AARE$) and the Root Mean Square Error ($\RMSE$), were used to quantify these models.
+It is shown that the Johnson-Cook and  Modified Zerilli-Armstrong models are not suitable to predict the high temperature behavior of this medium carbon steel alloy, while the Hansel-Spittel, PTM and Arrhenius models can be used to predict the behavior of this alloy with an acceptable error.
+On the other hand, the Artificial Neural Networks model results show excellent agreement between the predicted flow stresses $\sigma^y$ and experiment with comparatively significantly lower error.
 To validate the performance of these models, their ability to interpolate and extrapolate the experimental data was also tested.
 The HS, PTM and AR analytical models have shown a good interpolation and extrapolation capacity with a notable superiority for the AR model compared to the other two.
-The ANN model is still superior to the AR model from the point of view of its global behavior and its performance.
+The Artificial Neural Networks model is still superior to the AR model from the point of view of its global behavior and its performance}.
+\textcolor{red}{An approach for a better usage of these models on unknown data is proposed where each constitutive law must be multiplied by a factor $\lambda$ only for models whose correlation with experience is acceptable}.
 \end{abstract}
@@
 \begin{keyword}
-Johnson-Cook \sep Zerilli-Armstrong \sep Arrhenius \sep Hansel-Spittel \sep Artificial Neural Network
+Johnson-Cook \sep Zerilli-Armstrong \sep Arrhenius \sep Hansel-Spittel \sep Artificial Neural Network  \sep interpolation  \sep extrapolation 
 \end{keyword}
@@
 %----------------------------------------------------------------------------------
+\textcolor{purple}{Due to their excellent weldability, high machinability, good wear resistance, medium carbon steels nowadays are widely used in industrial fields.
+In addition, the hardening of these alloys through a heat treatment process and their high forgeability are very important characteristics that can be used for manufacturing large structures.
+As application, many automotive parts for steering, engines, suspensions and transmissions are made from these steels.
+Indeed, the medium carbon steels come to substitute quench-temper steels in different automative parts previously used as connecting rods produced by hot forging of low carbone steel alloys \cite{murugesan2019two, murugesan2019hybrid, tavakoli2019ferrite, ebrahimi2017flow}.
+Several metallurgical phenomena such as work hardening (WH) and dynamic softening (dynamic recovery (DRV) and recrystallization (DRX)), which very often occur during hot deformation, influence the microstructure evolution of materials during hot deformation.
+The processes involved in hot deformation are highly critical to the quality and workability of the final product \cite{Ashtiani-2012}.
+In order to estimate the influence of the different parameters involved in hot deformation before the experiment, numerical simulation like Finite Element Method (FEM) is widely used \cite{He-2013, Changizian-2012}.
+For example, FEM has been used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Mandal-2009, Qin-2010, Ji-2018}.
+To this end, a mathematical formulation is typically used to represent the flow stress $\sigma^y$ of a material from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ in a form that can be used in FEM software \cite{Lin-2008-P, Wu-2012}}.
 
-Continuous casting and rolling techniques are an integral part of material forming methods.
-Advantages of this method include increased process efficiency, energy savings, improved casting quality and easier mechanization and automation.
-Deformation, a complex process involving simultaneous elastic and plastic deformation, is accompanied by high temperatures, high strain rates, and complex and variable frictional conditions \cite{He-2013}, for which, analytical methods are not available for quantitative study and analysis of the deformation mechanism.
-On the other hand, conducting experimental tests is not only time-consuming but also requires a high financial investment \cite{Changizian-2012}.
-As an alternative approach to the previous two, the Finite Element Method (FEM) is widely used as a tool for analysis and optimization of process parameters in the processing of various materials.
-Finite element modeling effectively compensates for the shortcomings of analytical and experimental methods and is playing an increasingly important role in determining process parameters, improving product quality, and gaining in-depth knowledge of deformation mechanisms.
-For example, FEM has been widely used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Mandal-2009, Qin-2010, Ji-2018}.
-
-Hot forming processes are an essential step in the manufacture of mechanical components and directly affect the final quality of the products through their strong influence on the micro-structure and mechanical properties as reported by Ashtiani \eal \cite{Ashtiani-2012}.
-Several metallurgical phenomena such as work hardening and dynamic softening (dynamic recovery and recrystallization), which very often occur during hot working, influence the behavior and deformation of materials.
-The complexity of the thermomechanical behavior usually leads to the fact that it can only be taken into account accurately by using a numerical approach to obtain the response of the material under the specified loading conditions.
-To this end, a mathematical formulation is typically used to represent the flow stress $\sigma^y$ of a material from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ in a form that can be used in finite element software \cite{Lin-2008-P, Wu-2012}.
-
-For several years, many researchers have developed methods to predict the thermomechanical behavior of materials under hot working conditions using constitutive models.
-Thus, various forms of constitutive equations have been proposed to describe the flow stress of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021}.
+\textcolor{purple}{Various forms of constitutive equations have been proposed to describe the flow stress of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021}.
 Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEM codes.
@@
 In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed by several authors in recent years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.
-
-The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the deformation energy of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
-Its original formulation has been revised several times to correctly describe the resulting experimental behavior.
+The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the activation energy for deformation \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
+Its original formulation has been revised several times for a more accurate description of the high temperature deformation behavior.
 In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several authors.
@@
 Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.
-
-Users of the Forge software make extensive use of the model developed by Hansel and Spittel \cite{Hensel-1978}, commonly referred to as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on $\varepsilon$, $\mdot\varepsilon$ and $T$.
+Another form of model developed by Hansel and Spittel \cite{Hensel-1978}, commonly named as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on $\varepsilon$, $\mdot\varepsilon$ and $T$.
 Unlike the JC model, this formulation is based on parameters that are determined simultaneously.
@@
 The limitation of this model is its loss of accuracy in some cases when the 8 parameters are defined.
-This is why many works often limit its identification to only 5, 6 or 7 parameters.
-This has been verified in our study where the smallest error of the model is obtained with only 7 parameters identified.
+This is why many works often limit its identification to only 5, 6 or 7 parameters}.
 
@@
 These models have few parameters and are therefore easy to identify, but when these models have to be applied to a material different from the one for which they were initially developed they lose their performance as in the case of the HS model.
-To try to solve this problem, Tize Mha \eal \cite{TizeMha-2022} has proposed a formulation where the number of parameters is not known in advance.
+To try to solve this problem, Tize Mha \eal \cite{TizeMha-2022} recently proposed a formulation where the number of parameters is not known in advance.
 The idea is to make the formulation of an analytical model flexible so that it can be adapted to many materials.
-This formulation is based on the MZA model and polynomial functions of undefined order are used during the identification.
+This formulation is based on the MZA model and polynomial functions of undefined order are used during the identification but the problem with this model is the high order of the polynomial function that can affect its accuracy.
+Therefore a good choice of order of polynomial functions is important during its identification.
+Another identification technique is that based on artificial intelligence.
 
-Behavior modeling based on an Artificial Neural Network is an approach to predict the flow stress of materials without requiring a mathematical formulation of the flow law.
+Artificial Neural Network (ANN) is an approach to predict the flow stress of materials without requiring a mathematical formulation of the flow law.
 It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
@@
 
-In this work, the high-temperature thermomechanical behavior of AISI P20 modified carbon steel subjected to compression tests in a Gleeble thermomechanical simulator was studied.
+\textcolor{red}{From all the work previously presented on both analytical and ANN models, a remark on the performance of these models emerges.
+Indeed, a model is considered appropriate to describe the behavior of a material when its predictions and experience correlate well.
+First an experiment is carried out, then the data from this experiment are used to determine the parameters of the model, and based on these parameters the predictions of this model and the initial data are displayed to see the correlation between predictions and experience.
+It is questionable whether a model that correctly describes the behavior of a material can be used to generate data for conditions different from those on which it was identified ?
+And in the event that we use it, how can we reassure ourselves of the relevance of what it predicts ?
+To answer these questions the interpolation and extrapolation techniques \cite{wahab2017interpolation,luo2019interpolation,stinis2019enforcing} widely used in several fields are extended to the constitutive laws in this work where the variable is the strain rate and this can be applied as well as to strain to the temperature.
+It is a question of choosing a strain rate different from those used during the identification of the model both inside and outside the range of known strain rates.
+An experiment is therefore carried out for this strain rate in order to validate the prediction of the models.}
+
+In this work, the high-temperature thermomechanical behavior of medium carbon steel alloy subjected to compression tests in a Gleeble thermomechanical simulator was studied.
 From the experimental data obtained from the compression tests, five analytical models were identified in order to select the one that best describes the behavior of this alloy.
 A flow model based on an ANN was also developed and identified, and a comparative study between the 5 analytical models and the ANN model is proposed.
-A fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.
+As presented previously a fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.
 
@@
 
-The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
+The material used in this study is a \textcolor{red}{medium carbon steel} whose chemical composition is given in Table \ref{tab:Composition}.
 \begin{table}[h!]
 \centering
-\caption{Chemical composition of AISI P20 steel, Fe = balance.}
+\caption{Chemical composition of medium carbon steel, Fe = balance.}
 \begin{tabular}{lccccccc}
@@
 Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
-A batch of 30 hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
+\textcolor{red}{Hot compression} tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
 \begin{figure}[!ht]
@@
 
-The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as true stress and true strain according to L-gauge where the formula to get those curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2r_0$ and $F$ is the force as measured by Gleeble load cell.\OPP{those formulas seems incomplete.}
-As there are noises from raw data, filter method is applied to remove noise and have more smooth data.\OPP{what is the filtering method used ?}
+The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as true stress and true strain according to L-gauge where the formula to get those curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2r_0$ and $F$ is the force as measured by Gleeble load cell.
+As there are noises from raw data, savgolfilter method from scipy library is used to remove noise and have more smooth data.
 For further usage of data in numerical simulation elastic parts have been removed.
-\OPP{you must explain how.}
 
@@
 \includegraphics[width=\columnwidth]{Figures/rawData}
-\caption{Stress-strain curves of AISI P20 alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
+\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
 \label{fig:RawData}
@@
 The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
-The dynamic recrystallization concerns the germination of new grains, at the borders or inside the initial grains.
-These two phenomena explain the different shapes of the flow stress curves observed for this alloy.
-As an example, Figure \ref{fig:Micrography} shows the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
+The DRX concerns the germination of new grains, at the borders or inside the initial grains.
+In addition to the softening phenomena hardening such as deformation induced precipitation and phase transformation that could take place and therefore affect the material behavior.
+All these phenomena explain the different flow stress curves observed for this alloy.
+As an example, Figure \ref{fig:Micrography} shows the microstructures of medium carbon held during $5$~min at $1260\celsius$ before and after the compression phase.
 \begin{figure}[!ht]
@@
 \end{subfigure}
-\caption{Optical micrographs of the AISI P20 steel before (a) and after (b) hot compression.}
+\caption{Optical micrographs of a medium carbon steel before (a) and after (b) hot compression.}
 \label{fig:Micrography}
@@
 %----------------------------------------------------------------------------------
-
-The complete characterization of the thermomechanical behavior of a material through the identification of the parameters of its flow law is very important for an accurate modeling in numerical simulations.
-This characterization usually involves experimental tests that serve as a basis for the development of constitutive laws.
-As mentioned in the introduction, many constitutive laws exist today, and the selection of one of them on the basis of explicit criteria makes the development of computational models for new materials with new types of behavior challenging.
-Since the purpose of this work is to compare the ANN model to some analytical models, it is important to justify the choice of the analytical models selected for this study among the many that exist in the literature.
-Among the analytical models, the Johnson-Cook (JC) model \cite{Johnson-1983} is the most used because of its simplicity of implementation linked to the reduced number of its parameters and the ease to identify them.
-It should be noted that it is not the best model but the most integrated in the Finite Elements softwares such as Abaqus for example.
-This also explains the existence of several modified forms of this model.
-The Zerilli-Armstrong model, and in particular its modified forms (MZA) \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, is also widely used because it attempts to provide solutions to the shortcomings of the JC model, particularly with regard to the coupling of physical parameters.
-It is therefore also part of this study.
-The Hansel-Spittel (HS) model \cite{Hensel-1978} is also one of the most widely used models in numerical simulation of casting and forging operations because it is integrated in the Forge software.
-Moreover, the method of identifying its parameters is very simple to perform since it is done in one step.
-It also has limitations as we will show in the following sections.
-The Arrhenius model was also chosen in this study because it is one of the models that not only provides a good prediction of the flow stress but also takes into account the physical parameter $Q$ (the deformation activation energy coefficient) which is of great importance in the microstructural analyses of materials.
-The PTM model \cite{TizeMha-2022} is also used in this study because it is a model whose formulation does not impose a given number of parameters and which proved its ability in our previous works \cite{TizeMha-2022}.
-We selected it to test it on this type of material because it is normally formulated to fit any type of material.
-
 %----------------------------------------------------------------------------------
@@
 \end{figure}
-The JC model is not able to describe the evolution of the flow stress of AISI P20 for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
+The JC model is not able to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
 The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
@@
 where the 7 coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
-The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is summarized as following.
-
-\OP{See again how to summarize this part, since this method is already published.}
-
-Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced directly from $\sigma^y(0,T_0,\mdot{\varepsilon}_0)$.
-When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, taking the logarithm of the Equation (\ref{eq:MZA-model}) leads to:
-\begin{equation}
-\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
-\end{equation}
-
-By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
-From the expression of $I_1$ we can write:
-\begin{equation}
-\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
-\end{equation}
-
-By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
-The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
-Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
-\begin{equation}
-\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right),
-\end{equation}
-with $S_2=C_5+C_6\left(T-T_0\right)$.
-Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
-The parameters of MZA model are given in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
+To get the parameters of the MZA model we apply the medod proposed by \cite{Samantaray-2009} and those parameters are summurizedin in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
 \begin{table}[h!]
@@
 \end{equation}
-where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent of the material.
+Where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent of the material.
 The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperature by regression method.
@@
 Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
-The PTM model is suitable to describe the flow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
+The PTM model is suitable to describe the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
 The deviation between the predicted values and the experimental values for other strain rates is relatively good.
@@
 
-Once the learning phase is over, the trained model can be used to predict the behavior of the AISI P20 alloy as a function of the input data in the same way as is done with the analytical models.
+Once the learning phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data in the same way as is done with the analytical models.
 One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}) which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code) as proposed in Pantalé \eal \cite{Pantale-2021}.
@@
 
-A summary of the coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work is reported in Table \ref{tab:Errors}.
+A summary of the coefficients for evaluating the high-temperature flow stress prediction capability of the medium carbon alloy for all models presented in this work is reported in Table \ref{tab:Errors}.
 \begin{table}[h!]
@@
 
-The ANN, Arrhenius and PTM models are the only models that take into account the softening with the deformation of AISI P20 at low strain rate, unlike the other three models that only present an increase of the flow stress with the strain, whatever the strain rate and temperature, hence their poor performance in predicting the behavior of this material and more particularly at low strain rates.
-The parameters reported in Table \ref{tab:Errors}, the correlations visible in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow us to conclude here that the ANN model is the most efficient of all the models presented to describe the behavior of the AISI P20 alloy for high temperature deformation applications.
+The ANN, Arrhenius and PTM models are the only models that take into account the softening with the deformation of medium carbon at low strain rate, unlike the other three models that only present an increase of the flow stress with the strain, whatever the strain rate and temperature, hence their poor performance in predicting the behavior of this material and more particularly at low strain rates.
+The parameters reported in Table \ref{tab:Errors}, the correlations visible in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow us to conclude here that the ANN model is the most efficient of all the models presented to describe the behavior of the medium carbon alloy for high temperature deformation applications.
 
@@
 %----------------------------------------------------------------------------------
+\subsection{Proposed technique for better interpolation}
+%----------------------------------------------------------------------------------
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\columnwidth]
+{Figures/Performance}
+\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
+\label{fig:Performance}
+\end{figure}
+In this part a technique is proposed to have a better interpolation of data.
+Indeed, as mentioned in the introduction, it is important to know how to reassure oneself of the effectiveness of the model that well describes the behavior of a material for a good use on new data.
+It is therefore a question of choosing models that have a good correlation with experience and proposing a formula for a good use of their parameters on unknown data.
+The AR, HS, PTM and ANN models are therefore chosen and it emerges that each model must be multiplied by a lambda factor whose formula is given as follows.
+\begin{equation}
+ \lambda = \left(\frac{\dot{\varepsilon}_{max} - \dot{\varepsilon}_{p} }{\dot{\varepsilon}_{p} - \dot{\varepsilon}_{min}}\right)^{\frac{\dot{\varepsilon}_p}{m}}
+\end{equation}
+Where $\dot{\varepsilon}_{p}$ is the unkown strain rate and $m\in[50-300]$
+Applaying this formule the new figures are plotted in Figure \ref{fig:Performance}. From these results we can see clearly that the results are better that the initial ones. 
 \section{Conclusions and future work\label{sec:Conclusion}}
@@
 
-Experimental tests were performed on a Gleeble thermomechanical simulator for a modified AISI P20 carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
+Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
 The analytical models selected for this study are the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model  \cite{TizeMha-2022}.
@@
 Among the analytical models, the JC and MZA models proved to be inappropriate to reproduce the behavior of this material, while the HS, PTM and AR models showed their capabilities since they present an acceptable $\AARE$ error (from $3.5\%$ to $7.7\%$), with a superiority of the AR model ($3.56\%$) over the other two which confirms its use in thermomechanical processes.
-The ANN model, is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of the AISI P20 with a value of $\AARE=0.62\%$.
+The ANN model, is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of the medium carbon with a value of $\AARE=0.62\%$.
 

### 2022-12-28 Article.tex
PriorEditionVersion

@@
 
-\title{\textcolor{red}{Interpolation and extrapolation based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}}
+\title{Interpolation and extrapolation based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}
 
@@
 \begin{abstract}
-\textcolor{purple}{An analysis of the use of analytical models and Artificial Neural Networks is proposed in this paper to study the high-temperature deformation behavior of medium carbon steel alloy during hot compression tests, on a Gleeble thermomechanical simulator, over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-From the experimental data (stress-true strain curves), 5 analytical models such as Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius and PTM on the one hand, and an Artificial Neural Networks model with 3 inputs, 2 hidden layers of 15 and 7 neurons respectively and 1 output, on the other hand, have been identified to predict the flow stress $\sigma^y$ of this alloy.
-The comparison between the analytical models, the Artificial Neural Networks model and the experimental results, carried out on the basis of the Mean Absolute Relative Error ($\AARE$) and the Root Mean Square Error ($\RMSE$), were used to quantify these models.
-It is shown that the Johnson-Cook and  Modified Zerilli-Armstrong models are not suitable to predict the high temperature behavior of this medium carbon steel alloy, while the Hansel-Spittel, PTM and Arrhenius models can be used to predict the behavior of this alloy with an acceptable error.
-On the other hand, the Artificial Neural Networks model results show excellent agreement between the predicted flow stresses $\sigma^y$ and experiment with comparatively significantly lower error.
-To validate the performance of these models, their ability to interpolate and extrapolate the experimental data was also tested.
-The HS, PTM and AR analytical models have shown a good interpolation and extrapolation capacity with a notable superiority for the AR model compared to the other two.
-The Artificial Neural Networks model is still superior to the AR model from the point of view of its global behavior and its performance}.
-\textcolor{red}{An approach for a better usage of these models on unknown data is proposed where each constitutive law must be multiplied by a factor $\lambda$ only for models whose correlation with experience is acceptable}.
+\textcolor{red}{In the present work, a critical analysis of the most commonly used analytical models as well as recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them}.
+To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Geleeble $3800$ thermomechanical simulator.
+The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
+The Mean Absolute Relative Error (MARE) and the Root Mean Square Error (RMSE) values were used to quantify the predictive accuracy of the analyzed models.
+The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented significant error, MARRE of  $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with about $3.56\%$ error.
+The Artificial Neural Network model, on the other hand, showed excellent agreement, less than $0.62\%$ error, between the predicted and experimental flow curves.
+To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
+The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability with a notable superiority for the Arrhenius model compared to the other two.
+The Artificial Neural Networks model was however, still the most performant compared to all the models.
+A correlation factor is proposed to extend the applicability of some of the investigated models to deformation conditions not included in the original experimental plan.
 \end{abstract}
@@
 %----------------------------------------------------------------------------------
-\textcolor{purple}{Due to their excellent weldability, high machinability, good wear resistance, medium carbon steels nowadays are widely used in industrial fields.
-In addition, the hardening of these alloys through a heat treatment process and their high forgeability are very important characteristics that can be used for manufacturing large structures.
-As application, many automotive parts for steering, engines, suspensions and transmissions are made from these steels.
-Indeed, the medium carbon steels come to substitute quench-temper steels in different automative parts previously used as connecting rods produced by hot forging of low carbone steel alloys \cite{murugesan2019two, murugesan2019hybrid, tavakoli2019ferrite, ebrahimi2017flow}.
-Several metallurgical phenomena such as work hardening (WH) and dynamic softening (dynamic recovery (DRV) and recrystallization (DRX)), which very often occur during hot deformation, influence the microstructure evolution of materials during hot deformation.
-The processes involved in hot deformation are highly critical to the quality and workability of the final product \cite{Ashtiani-2012}.
-In order to estimate the influence of the different parameters involved in hot deformation before the experiment, numerical simulation like Finite Element Method (FEM) is widely used \cite{He-2013, Changizian-2012}.
-For example, FEM has been used to simulate and analyze hot forming processes of steel, such as forging, rolling, extrusion and casting, but the quality of the numerical solution provided by this method is highly dependent on the constitutive equation of the modeled material \cite{Mandal-2009, Qin-2010, Ji-2018}.
-To this end, a mathematical formulation is typically used to represent the flow stress $\sigma^y$ of a material from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ in a form that can be used in FEM software \cite{Lin-2008-P, Wu-2012}}.
+The manufacturing of large size forged blocks made of high-strength steels (as medium carbon alloy steel) is a process whose first step is ingot casting, followed by forging, quenching, and tempering operations.
+These forged blocks are used in automative industry  as die materials for the production of plastic injection components \cite{chadha2017deformation,chadha2018influence,murugesan2019two, murugesan2019hybrid}.
+For more industrial applications, requirements such as chemical homogeneity, uniform hardness and grain size inside these large size forged blocks are importants.
+The ingot breakdown which is the first step of the deformation process, is carried out generally to get the above requirements and strengthening or weakening of alloy may result.
+Work hardening (WH), phase transformation, and precipitation are those that often have strengthening effects while dynamic recovery (DRV), metadynamic recristallization (MDRX), dynamic recristallization (DRX), static recovery and static recristallization occur in the material softening.
+Strengthening or weakening effects strongly depends on three macroscopic quantities \ie the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ and impact the mechanical properties of the final product \cite{tavakoli2019ferrite, ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}.
+As conducting an experiment is very expensive and time consuming, numerical simulation such as the Finite Element Analysis (FEA), where a good result depends on the behavior laws of the materials, is widely used nowadays to reduce experimental errors \cite{Mandal-2009, Qin-2010, Ji-2018,Lin-2008-P, Wu-2012}.
 
-\textcolor{purple}{Various forms of constitutive equations have been proposed to describe the flow stress of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021}.
-Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEM codes.
-The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{NematNasser-2003, Khan-2004}.
-However, this model, in its original state, has some shortcomings related to nonlinear coupling phenomena not taken into account in the material behavior.
-We refer here to strain hardening, strain rate hardening and thermal effects that are taken into account in a non-coupled manner in the JC model as analyzed by Jia \eal \cite{Jia-2021}.
-To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhang-2015, Zhou-2019}.
+To predict the flow stress behavior during the breakdown process of ingots, many constitutive models have been proposed to simulate the thermomechanical process among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021}.
+Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
+The JC model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{NematNasser-2003, Khan-2004}.
+However, this model, in its original state, has some shortcomings due to non-coupling effect of strain, strain rate and temperature as analyzed by Jia \eal \cite{Jia-2021}.
+To circumvent these shortcomings, several modified forms of the JC model have been developed \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhang-2015, Zhou-2019}.
 Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
@@
 Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Lee-2006, Chen-2007}.
-Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
-In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed by several authors in recent years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.
+Moreover, the ZA model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
+In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.
 The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the activation energy for deformation \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
@@
 Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.
-Another form of model developed by Hansel and Spittel \cite{Hensel-1978}, commonly named as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on $\varepsilon$, $\mdot\varepsilon$ and $T$.
-Unlike the JC model, this formulation is based on parameters that are determined simultaneously.
+Another form of model is developed by Hansel and Spittel \cite{Hensel-1978} whose formulation is based on a product of functions dependent on $\varepsilon$, $\mdot\varepsilon$ and $T$.
 This model is simple to use and has 8 parameters that are easy to determine.
 The limitation of this model is its loss of accuracy in some cases when the 8 parameters are defined.
-This is why many works often limit its identification to only 5, 6 or 7 parameters}.
+This is why many works often limit its identification to only 5, 6 or 7 parameters.
 
-The fixed and limited number of parameters imposed by each analytical model as presented above has both advantages and disadvantages.
-These models have few parameters and are therefore easy to identify, but when these models have to be applied to a material different from the one for which they were initially developed they lose their performance as in the case of the HS model.
-To try to solve this problem, Tize Mha \eal \cite{TizeMha-2022} recently proposed a formulation where the number of parameters is not known in advance.
-The idea is to make the formulation of an analytical model flexible so that it can be adapted to many materials.
+Most of the developed models are related to a specific material or alloy and where they are used for other materials, their efficiency is not good.
+To overcome this issue, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model whose formulation can be adapt to any kind of material or alloys.
 This formulation is based on the MZA model and polynomial functions of undefined order are used during the identification but the problem with this model is the high order of the polynomial function that can affect its accuracy.
 Therefore a good choice of order of polynomial functions is important during its identification.
-Another identification technique is that based on artificial intelligence.
+Another model is that based on artificial intelligence method where parameters identification step of analytical models is replaced by training step.
 
-Artificial Neural Network (ANN) is an approach to predict the flow stress of materials without requiring a mathematical formulation of the flow law.
+Artificial Neural Network (ANN) is an approach to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
 It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
-Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress by an analytical model whose parameters are identified by a classical regression method is limited.
+Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
 Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
-Consequently, ANNs have been successfully applied to predict the flow of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB, Pantale-2021}.
-They provide a fundamentally different approach to statistical or numerical techniques for modeling materials.
+Consequently, ANNs have been successfully applied to predict the flow stress behavio of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB, Pantale-2021}.
 
-\textcolor{red}{From all the work previously presented on both analytical and ANN models, a remark on the performance of these models emerges.
-Indeed, a model is considered appropriate to describe the behavior of a material when its predictions and experience correlate well.
-First an experiment is carried out, then the data from this experiment are used to determine the parameters of the model, and based on these parameters the predictions of this model and the initial data are displayed to see the correlation between predictions and experience.
-It is questionable whether a model that correctly describes the behavior of a material can be used to generate data for conditions different from those on which it was identified ?
-And in the event that we use it, how can we reassure ourselves of the relevance of what it predicts ?
-To answer these questions the interpolation and extrapolation techniques \cite{wahab2017interpolation,luo2019interpolation,stinis2019enforcing} widely used in several fields are extended to the constitutive laws in this work where the variable is the strain rate and this can be applied as well as to strain to the temperature.
+Although progress has been made in improvement of constitutive models to better predict the flow stress behavior of materials, there is still a problem with the efficiency of the model.
+Indeed, a model is considered appropriate to the prediction of the material's behavior when its predictions and experience correlate well.
+It is questionable whether a model that correctly describes the behavior of a material can be used to generate data for conditions different from those on which it was identified and how to know the relevance of what it predicts.
+Interpolation and extrapolation techniques \cite{wahab2017interpolation,luo2019interpolation,stinis2019enforcing} widely used in several fields are extended to the constitutive models in this work where the variable is the strain rate and this can be applied as well as to strain to the temperature.
 It is a question of choosing a strain rate different from those used during the identification of the model both inside and outside the range of known strain rates.
-An experiment is therefore carried out for this strain rate in order to validate the prediction of the models.}
-
-In this work, the high-temperature thermomechanical behavior of medium carbon steel alloy subjected to compression tests in a Gleeble thermomechanical simulator was studied.
-From the experimental data obtained from the compression tests, five analytical models were identified in order to select the one that best describes the behavior of this alloy.
+An experiment is therefore carried out for this strain rate in order to validate the prediction of the models.
+For this purpose, the high-temperature thermomechanical behavior of medium carbon steel alloy subjected to compression tests in a Gleeble thermomechanical simulator was studied.
+From the experimental data, five analytical models were identified in order to select the one that best describes the behavior of the studied material.
 A flow model based on an ANN was also developed and identified, and a comparative study between the 5 analytical models and the ANN model is proposed.
@@
 
-The material used in this study is a \textcolor{red}{medium carbon steel} whose chemical composition is given in Table \ref{tab:Composition}.
+The material used in this study is a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
 \begin{table}[h!]
@@
 Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
-\textcolor{red}{Hot compression} tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
+Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
 \begin{figure}[!ht]

### 2023-01-11 Article.tex
Restore Correct versions of Article

@@
 \usepackage{placeins}
+\usepackage{ulem}
 \usepackage[colorlinks = true]{hyperref}
@@
 %----------------------------------------------------------------------------------
-The manufacturing of large size forged blocks made of high-strength steels (as medium carbon alloy steel) is a process whose first step is ingot casting, followed by forging, quenching, and tempering operations.
-These forged blocks are used in automative industry  as die materials for the production of plastic injection components \cite{chadha2017deformation,chadha2018influence,murugesan2019two, murugesan2019hybrid}.
-For more industrial applications, requirements such as chemical homogeneity, uniform hardness and grain size inside these large size forged blocks are importants.
-The ingot breakdown which is the first step of the deformation process, is carried out generally to get the above requirements and strengthening or weakening of alloy may result.
-Work hardening (WH), phase transformation, and precipitation are those that often have strengthening effects while dynamic recovery (DRV), metadynamic recristallization (MDRX), dynamic recristallization (DRX), static recovery and static recristallization occur in the material softening.
-Strengthening or weakening effects strongly depends on three macroscopic quantities \ie the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ and impact the mechanical properties of the final product \cite{tavakoli2019ferrite, ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}.
-As conducting an experiment is very expensive and time consuming, numerical simulation such as the Finite Element Analysis (FEA), where a good result depends on the behavior laws of the materials, is widely used nowadays to reduce experimental errors \cite{Mandal-2009, Qin-2010, Ji-2018,Lin-2008-P, Wu-2012}.
+Large size forged blocks made of medium carbon high-strength steels are extensively used in automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
+The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and quench $\&$ temper heat treatment process to achieve the desired mechanical properties  \cite{chadha2017deformation,chadha2018influence,murugesan2019two}.
+In recent years, in order to respond to the market demand, larger size forgings need to be produced.
+In parallel, more stringent condition on chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block are required.
+Among the three manufacturing steps (casting, forging, heat treatment), forging is the one where the most important microstructural changes take place and influences the final properties that could be achieved \cite{murugesan2019hybrid,chadha2020microstructure,sripada2022effect}.
+Open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, concomitantly take place with softening phenomena such as   recovery and recrystallization under static and/or dynamic \cite{tian2022deformation,tavakoli2019ferrite}.
+It has also been reported that phase transformation could take place during deformation.
+The extent and intensity of the above strengthening or softening phenomena strongly depend on three macroscopic quantities \ie the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$  \cite{ ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}.
 
-To predict the flow stress behavior during the breakdown process of ingots, many constitutive models have been proposed to simulate the thermomechanical process among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021}.
-Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
-The JC model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{NematNasser-2003, Khan-2004}.
-However, this model, in its original state, has some shortcomings due to non-coupling effect of strain, strain rate and temperature as analyzed by Jia \eal \cite{Jia-2021}.
-To circumvent these shortcomings, several modified forms of the JC model have been developed \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhang-2015, Zhou-2019}.
-Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
-However, this model has other drawbacks related to the limit value of the test temperature.
-Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Lee-2006, Chen-2007}.
-Moreover, the ZA model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
-In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.
-The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the activation energy for deformation \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
-Its original formulation has been revised several times for a more accurate description of the high temperature deformation behavior.
-In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several authors.
-For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arrhenius model so that his model could predict the high-temperature flow of a magnesium alloy.
-Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor.
-Another form of model is developed by Hansel and Spittel \cite{Hensel-1978} whose formulation is based on a product of functions dependent on $\varepsilon$, $\mdot\varepsilon$ and $T$.
-This model is simple to use and has 8 parameters that are easy to determine.
-The limitation of this model is its loss of accuracy in some cases when the 8 parameters are defined.
-This is why many works often limit its identification to only 5, 6 or 7 parameters.
-
-Most of the developed models are related to a specific material or alloy and where they are used for other materials, their efficiency is not good.
-To overcome this issue, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model whose formulation can be adapt to any kind of material or alloys.
-This formulation is based on the MZA model and polynomial functions of undefined order are used during the identification but the problem with this model is the high order of the polynomial function that can affect its accuracy.
-Therefore a good choice of order of polynomial functions is important during its identification.
-Another model is that based on artificial intelligence method where parameters identification step of analytical models is replaced by training step.
+Considering the large size of the blocks, a purely experimental approach, based on trial and error, could not be used by industry and reliable predictive tools, such a Finite Element analysis (FEA) codes have been developed and are commercially available.
+However, the prediction reliability of such analyses is dependent on the accuracy of the material constitutive model, which describes the mutual interactions between strain, strain rate, and temperature during deformation.
+Precipitation and phase changes as mentioned above are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
+Hence most of the constitutive models depend on macroscopic parameters that influence the hardening and softening of the material.
+A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed among them, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
+Despite their simplicity, each of them suffer from shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from lack of non-coupling between strain, strain rate and temperature  while the HS model is better adapted for higher strain rate deformation conditions \cite{chadha2018approach}.
+To circumvent these shortcomings, several modified forms of models have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
+However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, could not be accurately predicted and none of the models is able to accurately predict flow behavior outside the experimental testing interval that was used to determine the model constants.
+Due to its more physics-based formulation, the ZA model and its modified form, MZA, \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021} and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS  models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
+The Arrhenius formulation has been revised several times for a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
+To overcome the strong dependency of the models to a specific alloy, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
+This formulation is based on the MZA model and polynomial functions of undefined order that are used during the identification.
+However, in the PTM model, the high order of the polynomial function (up to $10$ in some cases) can affect its accuracy.
 
@@
 Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
-Consequently, ANNs have been successfully applied to predict the flow stress behavio of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB, Pantale-2021}.
+Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
+Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software as reported by Pantalé \eal \cite{Pantale-2021}.
+In fact, the implementation of constitutive model in a FEA code requires the derivatives of this model with respect to strain, strain rate and temperature.
 
-Although progress has been made in improvement of constitutive models to better predict the flow stress behavior of materials, there is still a problem with the efficiency of the model.
-Indeed, a model is considered appropriate to the prediction of the material's behavior when its predictions and experience correlate well.
-It is questionable whether a model that correctly describes the behavior of a material can be used to generate data for conditions different from those on which it was identified and how to know the relevance of what it predicts.
-Interpolation and extrapolation techniques \cite{wahab2017interpolation,luo2019interpolation,stinis2019enforcing} widely used in several fields are extended to the constitutive models in this work where the variable is the strain rate and this can be applied as well as to strain to the temperature.
-It is a question of choosing a strain rate different from those used during the identification of the model both inside and outside the range of known strain rates.
-An experiment is therefore carried out for this strain rate in order to validate the prediction of the models.
-For this purpose, the high-temperature thermomechanical behavior of medium carbon steel alloy subjected to compression tests in a Gleeble thermomechanical simulator was studied.
-From the experimental data, five analytical models were identified in order to select the one that best describes the behavior of the studied material.
-A flow model based on an ANN was also developed and identified, and a comparative study between the 5 analytical models and the ANN model is proposed.
-As presented previously a fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.
+Although progress has been made in improvement of constitutive models to better predict the flow stress behavior of materials, there is still a problem with the efficiency of all the above models.
+Indeed, a model is considered appropriate to the prediction of the material's behavior when its predictions and experimental results correlate well.
+It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those it was identified for.
+In other words, can interpolation and extrapolation techniques be used to extent the applicability of a constitutive equation for different materials and processing windows?
 
-The main parts of this work are as follows: Section \ref{sec:Materials} presents the hardware (Gleeble thermomechanical simulator), the experimental procedure, the material and the results of the compression tests performed for this study.
-Section \ref{sec:ConstLaws} is devoted to the presentation of the 5 analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models with regard to the experimental results.
-Section \ref{sec:IntExt} details the interpolation and extrapolation capabilities of each model proposed in this paper.
-Conclusions and future work are detailed in Section \ref{sec:Conclusion}.
+The present work aims to address the above question using a combination of the recently introduced PTM model and ANN.
+To this end, initially, hot compression tests, simulating the open die forging process, were carried out and the generated flow curves were modeled using the above mentioned constitutive equations and an ANN model developed in this work.
+Then the interpolation and extrapolation capabilities of each model is evaluated and a solution is proposed that responds to the main question of the paper.
+The results are validated based on experimental work carried out in the present work and data obtained from the literature.
 
@@
 All data curve contains $700$ equidistant strain values up-to $\varepsilon=0.7$.
-So, as we have 6 strain rates and 5 temperatures, the database consists of $21~000$ data points.
+So, there are $6$ strain rates and $5$ temperatures, the database consists of $21~000$ data points.
 The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
@@
 For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
-One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
-For low strain rates, the effect of lubrication decreases over time and thus friction increases.
-This results in a progressive increase of the flow stress.
-
-To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRV) and Dynamic Recrystallization (DRX).
-At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
-As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRV.
-This DRV mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
-Some of these dislocations reorganize and then form sub-grains within the initial grains of the material.
-The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
-The DRX concerns the germination of new grains, at the borders or inside the initial grains.
-In addition to the softening phenomena hardening such as deformation induced precipitation and phase transformation that could take place and therefore affect the material behavior.
-All these phenomena explain the different flow stress curves observed for this alloy.
+The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{buckley2001deformation}.
+The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time and thus friction increases.
+The increase of stresses observed at the beginning of the deformation up to $0.1$ is due to the work hardening (WH).
+After $0.1$ up to $0.2$ the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of work-hardening rate.
+This behavior describes that thermal softening becomes more and more predominant until it exceeds WH.
+At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening.
+This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$ except those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and strain rate of $0.1$ $\text{s}^{-1}$ ; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
+Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates.
+In contrast, at higher strain rates and lower temperatures, the higher work hardening rate slows down the rate of softening due to DRX, and therefore, both the peak stress and the onset of steady-state flow are shifted to higher strain levels.
+In fact, the drop observed in
+stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$.
 As an example, Figure \ref{fig:Micrography} shows the microstructures of medium carbon held during $5$~min at $1260\celsius$ before and after the compression phase.
@@
 {Figures/Performance}
-\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
+\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
 \label{fig:Performance}

### 2023-01-17 ArticleAE.tex
Version of the article after edition

--- 2023-01-11 Article.tex
@@
 \begin{abstract}
-\textcolor{red}{In the present work, a critical analysis of the most commonly used analytical models as well as recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them}.
-To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Geleeble $3800$ thermomechanical simulator.
-The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
+In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
+To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble $3800$ thermomechanical simulator.
+The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
 The Mean Absolute Relative Error (MARE) and the Root Mean Square Error (RMSE) values were used to quantify the predictive accuracy of the analyzed models.
-The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented significant error, MARRE of  $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with about $3.56\%$ error.
-The Artificial Neural Network model, on the other hand, showed excellent agreement, less than $0.62\%$ error, between the predicted and experimental flow curves.
+The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented significant error, MARRE of  $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
+The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
 To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
-The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability with a notable superiority for the Arrhenius model compared to the other two.
-The Artificial Neural Networks model was however, still the most performant compared to all the models.
-A correlation factor is proposed to extend the applicability of some of the investigated models to deformation conditions not included in the original experimental plan.
+The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability with the notable superiority of the Arrhenius model over the other two.
+The Artificial Neural Networks model was however, still the most performant among all the models.
+A correlation factor was proposed to extend the applicability of some of the investigated models to deformation conditions not included in the original experimental plan.
 \end{abstract}
@@
 %----------------------------------------------------------------------------------
-Large size forged blocks made of medium carbon high-strength steels are extensively used in automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
-The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and quench $\&$ temper heat treatment process to achieve the desired mechanical properties  \cite{chadha2017deformation,chadha2018influence,murugesan2019two}.
-In recent years, in order to respond to the market demand, larger size forgings need to be produced.
-In parallel, more stringent condition on chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block are required.
-Among the three manufacturing steps (casting, forging, heat treatment), forging is the one where the most important microstructural changes take place and influences the final properties that could be achieved \cite{murugesan2019hybrid,chadha2020microstructure,sripada2022effect}.
-Open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, concomitantly take place with softening phenomena such as   recovery and recrystallization under static and/or dynamic \cite{tian2022deformation,tavakoli2019ferrite}.
-It has also been reported that phase transformation could take place during deformation.
-The extent and intensity of the above strengthening or softening phenomena strongly depend on three macroscopic quantities \ie the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$  \cite{ ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}.
+Large size forged blocks made of medium carbon high-strength steels are extensively used in the automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
+The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and a quench and temper heat treatment process to achieve the desired mechanical properties  \cite{chadha2017deformation,chadha2018influence,murugesan2019two}.
+In recent years, in order to respond to the market demand, larger size forgings have had to be produced.
+In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block have been required.
+Of the three manufacturing steps (casting, forging and heat treatment), forging is where the most important microstructural changes take place, and which greatly influences the final properties that can be achieved \cite{murugesan2019hybrid,chadha2020microstructure,sripada2022effect}.
+The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation,  take place concomitantly with softening phenomena such as   recovery and recrystallization under static and/or dynamic \cite{tian2022deformation,tavakoli2019ferrite}.
+It has also been reported that phase transformation can occur during deformation.
+The extent and intensity of the above phenomena strongly depend on three macroscopic quantities namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$  \cite{ ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}.
 
-Considering the large size of the blocks, a purely experimental approach, based on trial and error, could not be used by industry and reliable predictive tools, such a Finite Element analysis (FEA) codes have been developed and are commercially available.
-However, the prediction reliability of such analyses is dependent on the accuracy of the material constitutive model, which describes the mutual interactions between strain, strain rate, and temperature during deformation.
-Precipitation and phase changes as mentioned above are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
-Hence most of the constitutive models depend on macroscopic parameters that influence the hardening and softening of the material.
-A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed among them, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
-Despite their simplicity, each of them suffer from shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from lack of non-coupling between strain, strain rate and temperature  while the HS model is better adapted for higher strain rate deformation conditions \cite{chadha2018approach}.
-To circumvent these shortcomings, several modified forms of models have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
-However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, could not be accurately predicted and none of the models is able to accurately predict flow behavior outside the experimental testing interval that was used to determine the model constants.
-Due to its more physics-based formulation, the ZA model and its modified form, MZA, \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021} and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS  models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
-The Arrhenius formulation has been revised several times for a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
-To overcome the strong dependency of the models to a specific alloy, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
-This formulation is based on the MZA model and polynomial functions of undefined order that are used during the identification.
+Considering the large size of blocks, a purely experimental approach, based on trial and error, can not be used by industry, and  therefore, reliable predictive tools, such a Finite Element analysis (FEA) codes, have been developed, and are commercially available.
+However, the prediction reliability of such analyses is a function of the accuracy of the material constitutive model, which describes the mutual interactions between the strain, the strain rate, and the temperature during deformation.
+As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
+Hence, most constitutive models depend on macroscopic parameters which influence the hardening and softening of the material.
+A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed.
+Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
+Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature,  while the HS model is better adapted for higher strain rate deformation conditions \cite{chadha2018approach}.
+To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
+However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, can not be accurately predicted and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
+Due to its more physics-based formulation, the ZA model and its modified form, MZA, \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS  models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
+The Arrhenius formulation has been revised to achieve a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
+To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
+This formulation is based on the MZA model and the polynomial functions of undefined order that are used during the identification.
 However, in the PTM model, the high order of the polynomial function (up to $10$ in some cases) can affect its accuracy.
 
-Artificial Neural Network (ANN) is an approach to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
+The Artificial Neural Network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
 It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
-Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
+Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
 Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
 Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
-Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software as reported by Pantalé \eal \cite{Pantale-2021}.
-In fact, the implementation of constitutive model in a FEA code requires the derivatives of this model with respect to strain, strain rate and temperature.
+Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021}.
+In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to strain, strain rate and temperature.
 
-Although progress has been made in improvement of constitutive models to better predict the flow stress behavior of materials, there is still a problem with the efficiency of all the above models.
-Indeed, a model is considered appropriate to the prediction of the material's behavior when its predictions and experimental results correlate well.
-It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those it was identified for.
-In other words, can interpolation and extrapolation techniques be used to extent the applicability of a constitutive equation for different materials and processing windows?
+Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problem still persist with the model's efficiency.
+Indeed, a model is considered appropriate for predicting the material's behavior if its predictions and experimental results correlate well.
+It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those for which it was identified.
+In other words, the question is whether interpolation and extrapolation techniques can be used to extend the applicability of a constitutive equation for different materials and processing windows.
 
-The present work aims to address the above question using a combination of the recently introduced PTM model and ANN.
-To this end, initially, hot compression tests, simulating the open die forging process, were carried out and the generated flow curves were modeled using the above mentioned constitutive equations and an ANN model developed in this work.
-Then the interpolation and extrapolation capabilities of each model is evaluated and a solution is proposed that responds to the main question of the paper.
-The results are validated based on experimental work carried out in the present work and data obtained from the literature.
+The present work aims to address the preceding question using a combination of the recently introduced PTM model and ANN.
+To this end, initially, hot compression tests, simulating the open die forging process, are carried out and the flow curves  generated are modeled using the above--mentioned constitutive equations and an ANN model developed in this work.
+Then, the interpolation and extrapolation capabilities of each model are evaluated and a solution proposed, responding to the main question of the paper.
+The results are validated based on experimental work carried out here in and on data obtained from the literature.
 
@@
 
-The material used in this study is a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
+The material used in this study consists of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
 \begin{table}[h!]
@@
 Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
-Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
+Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
 \begin{figure}[!ht]
@@
 \end{figure}
-Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
+Thin tantalum sheets were used as lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
 As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
@@
 
-The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as true stress and true strain according to L-gauge where the formula to get those curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2r_0$ and $F$ is the force as measured by Gleeble load cell.
-As there are noises from raw data, savgolfilter method from scipy library is used to remove noise and have more smooth data.
-For further usage of data in numerical simulation elastic parts have been removed.
+The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge,  having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
+As raw data contains noises, savgol$\_$filter method from the scipy library is used to remove noise and provide smoother data.
+To allow further use of the data in numerical simulations, elastic parts are removed.
 
@@
 \end{figure}
-All data curve contains $700$ equidistant strain values up-to $\varepsilon=0.7$.
-So, there are $6$ strain rates and $5$ temperatures, the database consists of $21~000$ data points.
+All data curves contain $700$ equidistant strain values up-to $\varepsilon=0.7$.
+Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of $21~000$ data points.
 The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
 It should be noted that the strain also influences the flow stress.
-Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
+Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, and then decreases to maintain a more or less constant value until the end of the test.
 For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
 The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{buckley2001deformation}.
-The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time and thus friction increases.
-The increase of stresses observed at the beginning of the deformation up to $0.1$ is due to the work hardening (WH).
-After $0.1$ up to $0.2$ the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of work-hardening rate.
-This behavior describes that thermal softening becomes more and more predominant until it exceeds WH.
+The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time, and friction thus increases.
+The increase of stress observed at the beginning of the deformation and up to $0.1$ is due to work hardening (WH).
+After $0.1$ and up to $0.2$, the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of the work-hardening rate.
+This behavior indicates that thermal softening becomes more and more predominant until it exceeds WH.
 At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening.
-This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$ except those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and strain rate of $0.1$ $\text{s}^{-1}$ ; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
+This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$, except for those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and a $0.1$ $\text{s}^{-1}$  strain rate ; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
 Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates.
@@
 stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$.
-As an example, Figure \ref{fig:Micrography} shows the microstructures of medium carbon held during $5$~min at $1260\celsius$ before and after the compression phase.
+As an example, Figure \ref{fig:Micrography} shows the medium carbon microstructure held for $5$~min at $1260\celsius$ before and after the compression phase.
 \begin{figure}[!ht]
@@
 \end{subfigure}
-\caption{Optical micrographs of a medium carbon steel before (a) and after (b) hot compression.}
+\caption{Optical micrographs of a medium carbon steel (a) before  and (b) after hot compression.}
 \label{fig:Micrography}
 \end{figure}
-As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
-From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the 6 proposed flow laws will be presented in the next section in order to predict the behavior of the material in any test condition.
+As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get austenitized grain on the one hand, and on the other hand, held for $1$ minute at $1150^\circ$C before compression with a $0.001~\text{s}^{-1}$ strain rate.
+The results reported in Figure \ref{fig:RawData},will be used in the next section to identify the parameters of the $6$  proposed flow laws in order to see which mode will matches with experimental.
 
 %----------------------------------------------------------------------------------
-\section{Identification of constitutive flow laws parameters\label{sec:ConstLaws}}
+\section{Identification of Constitutive Flow Laws Parameters\label{sec:ConstLaws}}
 %----------------------------------------------------------------------------------
@@
 However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
-Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model.
-Hence its inability to describe the phenomenon of softening induced by temperature.
+Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model, hence its inability to describe the phenomenon of softening induced by temperature.
 The equation that describes this model is given as follows \cite{Johnson-1983}:
@@
 \end{equation}
-where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
-The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
+where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
+The other values are reference values: $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and thus $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
 For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$ respectively.
 
-The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
-This method allows obtaining one after the other the 5 parameters in the order $A$, $B$, $n$, $C$ and $m$.
-Thus, according to our experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
-For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
+The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
+This method allows sequentially obtaining the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
+Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
+For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then determined by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
 Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
-Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
-Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
+Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering that all the curves at $T=T_0$ then gives $C=0.3404$.
+Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the previous parameters and gives $m=0.7057$.
 All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.
@@
 \centering
-\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
+\caption{Parameter' values of the Johnson-Cook flow law for a medium carbon steel.}
 \begin{tabular}{ccccc}
@@
 \includegraphics[width=\columnwidth]{Figures/CompExp-JC-6}
-\caption{Comparison between the experimental and predicted flow stresses by JC model.}
+\caption{Comparison between the experimental flow stresses and those by JC model.}
 \label{fig:CompExp-JC-6}
 \end{figure}
-The JC model is not able to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
+The JC model is unable to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several strain rates values.
 The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
-As expected, the mathematical formulation of the Johnson-Cook flow law is unable to represent the stress drop at low strain rates, the JC model being only monotonically increasing with strain.
+As expected, the mathematical formulation of the Johnson-Cook flow law is unable to represent the stress drop at low strain rates, with the JC model increasing only monotonically with the strain.
 Since most of the parameters are identified at low strain rates ($A$, $B$ and $n$), this results in a very poor fit of the model to the experimental data.
 
-The accuracy and predictive ability of the models are usually assessed by certain coefficients such as the Mean Absolute Relative Error ($\AARE$) defined by Equation (\ref{eq:AARE}):
+The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the Mean Absolute Relative Error ($\AARE$) defined by Equation (\ref{eq:AARE}):
 \begin{equation}
@@
 \end{equation}
-where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the predicted value using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
+where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
 For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
@@
 
-The MZA which is the modified form of ZA model, as the JC model is one of widely used models and implemented in many FEM codes like Abaqus.
-The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experimental.
-Indeed, in the JC model, those parameters are considered separately where they are simultaneously considered in MZA and for that formulation MZA is preferred to JC model \cite{Hull-2011}.
-But the original form of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
+The MZA which is the modified form of the ZA model, as the JC model is one of widely used models and implemented into many FEM codes like Abaqus software.
+The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experiments.
+In the JC model, the parameters are considered separately, while in MZA, they are  considered simultaneously and for that formulation, MZA is preferred to the JC model \cite{Hull-2011}.
+However, the original form of the ZA model has some limitations due to the fact that it is considered as two terms (thermal and athermal functions), and to improvre formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
 \begin{equation}
@@
 \end{equation}
-where the 7 coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
-To get the parameters of the MZA model we apply the medod proposed by \cite{Samantaray-2009} and those parameters are summurizedin in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
+where the $7$ coefficients($C_i$ and $n$) are the parameters of the model to be identified for a given material.
+To get the parameters of the MZA model, we apply the method proposed by \cite{Samantaray-2009} and the parameters are summarized in in Table \ref{tab:MZA,} while their predictions are plotted in Figure \ref{fig:CompExp-MZA-6}.
 \begin{table}[h!]
 \centering{}
-\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
+\caption{Parameters' constants of Modified-Zerilli-Armstrong model}
 \begin{tabular}{ccccccc}
@@
 {Figures/CompExp-MZA-6}
-\caption{Comparison between the experimental and predicted flow stresses by MZA model}
+\caption{Comparison between the experimental flow stresses and those predicted by the MZA model}
 \label{fig:CompExp-MZA-6}
 \end{figure}
-It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
-The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
-For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\MPa$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.
+It can be seen from the figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
+The deviation between the predicted values and the experimental values is large because this model has problem correctly describing the softening in its formulation.
+For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.
 
@@
 
-The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEM codes, although the determination of its parameters is easier than that of the JC or MZA model.
-The programming of a simple identification script is sufficient to identify its parameters for a given material.
+The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEM codes, although its parameters can more easily be determined than those of the JC or MZA models.
+Programming a simple identification script is sufficient to identify its parameters for a given material.
 The equation of the HS model is given by the following relation:
@@
 However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification.
-For its identification, several authors restrict its expression to a reduced number of 5 or 6 $m_i$ parameters only, by forcing a zero value for the other parameters \cite{Chadha-2018, Mehtedi-2015, Rudnytskyj-2020}.
+For its identification, several authors restrict its expression to a reduced number of only $5$ or $6$ $m_i$ parameters, by forcing a zero value for the other parameters \cite{Chadha-2018, Mehtedi-2015, Rudnytskyj-2020}.
 
 In the present study, the best results were obtained by taking the model defined by only the first 7 $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.
-From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HS}.
+From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} allowed to compute the parameters reported in Table
+ \ref{tab:HS}.
 
@@
 \centering
-\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
+\caption{Parameters' values of the Hansel-Spittel flow law for the medium carbon steel.}
 \begin{tabular}{ccccc}
@@
 
-The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
+A comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6}, where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
 For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\MPa$.
-It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1~\ps$.
-This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate.
-The DRX phenomena cannot be reproduced by this type of model.
+It appears that both this model and the previous ones do not adequately predict the experimental one, and the difference is relatively significant for all strain rates below $1~\ps$.
+This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong non-linear the behavior observed for low strain rate values.
+The DRX phenomenon cannot be reproduced by this type of model.
 
@@
 {Figures/CompExp-HS-6}
-\caption{Comparison between the experimental and predicted flow stresses by HS model}
+\caption{Comparison between the experimental flow stresses and those predicted by the HS model}
 \label{fig:CompExp-HS-6}
@@
 
-The Arrhenius type model \cite{Sellars-1966} is one of the most used models in the framework of material forming, especially when it comes to studying the microstructure of the material.
-Indeed, this model takes into account the physical phenomena that describe the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ expressed as power law, exponential law and hyperbolic sine.
+The Arrhenius type model \cite{Sellars-1966} is one of the most used models in the framework of material forming, especially when it comes to studying the material microstructure.
+The model takes into account the physical phenomena describing the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ expressed as power law, exponential law and hyperbolic sine.
 This makes it easier to describe the softening phenomenon observed in the material due to increasing temperature.
@@
 \end{equation}
-Where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent of the material.
-The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperature by regression method.
-Combination of Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allow expressing the flow stress $\sigma^y$ as a function of the $Z$ parameter:
+Where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent on the material.
+The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperatures by the regression method.
+Combining Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allows to express the flow stress $\sigma^y$ as a function of the $Z$ parameter:
 \begin{equation}
@@
 
-To obtain the constitutive equation, it is necessary to determine all the parameters $A$, $Q$ $\alpha$ and $n$ for a given material.
-The strain has a significant non-linear influence on the behavior of the material by the mechanism of strain hardening and softening at high values of deformation.
-A compensation in strain must therefore be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$ $\alpha$ and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
+To obtain the constitutive equation, all the parameters $A$, $Q$ $\alpha$ and $n$must be determined for a given material.
+The strain has a significant non-linear influence on the behavior of the material by the  strain hardening and softening mechanisms at high values of deformation.
+A strain dependent factor must therefore be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$ $\alpha$ and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
 \begin{equation}
@@
 The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
-The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
+The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials used to determine using a regression method.
 Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:AR}.
@@
 \centering
-\caption{Parameters' values of the Arrhenius flow law for the P20 steel.}
+\caption{Parameters' values of the Arrhenius flow law for the medium carbon steel.}
 \begin{tabular}{llll}
@@
 \end{table}
-This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates.
+This modified form of the Arrhenius behavior law allows an accurate and reliable prediction over a wide range of temperatures and strain rates.
 Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$:
@@
 
-Figure \ref{fig:CompExp-AR-6} shows the comparison of the values predicted by the Arrhenius model and the experimental values.
+Figure \ref{fig:CompExp-AR-6} shows a comparison of the values predicted by the Arrhenius model and the experimental values.
 The difference between the experimental and predicted values is small.
-But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
+However for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is unable to predict the softening.
 For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\MPa$.
-
 \begin{figure}[!ht]
@@
 {Figures/CompExp-AR-6}
-\caption{Comparison between the experimental and predicted flow stresses by AR model}
+\caption{Comparison between the experimental flow stresses and those predicted flow stresses by the AR model}
 \label{fig:CompExp-AR-6}
@@
 The PTM model \cite{TizeMha-2022} is a generalized formulation of the MZA model presented in Section \ref{sec:MZA}.
-When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to make the PTM model flexible for any type of material studied because there is no need for a limited number of parameters as in the MZA model.
-Its construction is based on the use of polynomial functions as in the AR model.
-Thus, the intrinsic functions of the model, of polynomial type, allow adjusting the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
+When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to render the PTM model flexible for any type of material studied because it removes need for a limited number of parameters as in the MZA model.
+Its construction is based on the use of polynomial functions, as is the case in the AR model.
+Thus, the physical parameters' dependent intrinsic functions of the PTM model, allow adjusting the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
 The equation describing the PTM model is therefore given by :
@@
 Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
-The larger these quantities are, the more parameters need to be identified for the PTM model.
-The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016} and for more details about this model  we invite the reader to read our previous work \cite{TizeMha-2022}.
+The larger these quantities, the greater the number of parameters needing to be identified for the PTM model.
+The determination of the parameters of this model is calculated thanks to the LMFIT Python library \cite{Newville-2016} (for more details about this model  we refer the reader to our previous work \cite{TizeMha-2022}).
 Thus, all the parameters of this model are calculated with $q=5$, $r=5$, $s=1$ and $t=5$.
 
-Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
-The PTM model is suitable to describe the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
-The deviation between the predicted values and the experimental values for other strain rates is relatively good.
-For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\MPa$ and this shows an overall worse performance than the AR model.
+\ref{fig:CompExp-PTM-6} presents a Comparison of values predicted by the PTM model and experimental values.
+The PTM model is suitable for describing the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$, the prediction is not very good.
+The deviation between the predicted values and the experimental values for other strain rates is relatively low.
+For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\MPa$, which is an overall worse performance than the AR model.
 
@@
 {Figures/CompExp-PTM-6}
-\caption{Comparison between the experimental and predicted flow stresses by PTM model}
+\caption{Comparison between the experimental flow stresses and those predicted the PTM model}
 \label{fig:CompExp-PTM-6}
@@
 
-Because of their predictive capacity and their adaptability, Artificial Neural Networks (ANNs) are more and more widely used today in many scientific fields.
+Because of their predictive capacity and adaptability, Artificial Neural Networks (ANNs) are increasingly widely used today in many scientific fields.
 Their operation is based on a learning process during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine learning process.
 
-There are generally two uses of neural networks: classification and regression.
+Neural networks generally have two uses: classification and regression.
 The first is the ability to classify data into different groups and for example to distinguish between images of cats and dogs.
-The second one corresponds to the capacity of universal approximator of these neural networks, which interests us in this application, and thus to the ability after learning to predict the values of the flow stress $\sigma^y$ according to the input data, as do the analytical models previously identified.
+The second corresponds to the universal approximation capacity of these neural networks, which if of interest to us here in, and thus, to the ability, after learning to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by  the previously identified analytical models.
 The main difference is that this approximation is not linked to a fixed mathematical formulation (JC, MZA, AR, HS, PTM model), but is only dependent on the data used for training, the number of layers, the number of neurons per layer and the activation functions associated with the neurons of the network.
@@
 
-Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately previous layer $(k-1)$, containing $m$ neurons, given by the following equation:
+Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following equation:
 \begin{equation}
@@
 where $y_i\lay{k}$ is the entry of the $i^{th}$ neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j^{th}$ neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i^{th}$ neuron of layer $k$ and the $j^{th}$ neuron of layer $(k-1)$ and $b_i\lay{k}$ is the associated bias of the $i^{th}$ neuron of layer $k$.
-Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN that we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021}.
-For the proposed model, we have selected the Sigmoid activation function, so that, each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
+Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021}.
+For the proposed model, we selected the Sigmoid activation function, so that, each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
 \begin{equation}
@@
 After some tests of different types of network architecture and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and 7 neurons for the second layer give the best compromise between prediction, learning time and model compactness.
-From the global architecture point of view, the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
+From a global architecture point of view, the input layer is composed of $3$ neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
 This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second layer and 8 for the output layer).
@@
 The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
-The training data are those from the tests presented in section \ref{sec:ComTestResults} and composed of $21~000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
-The learning is performed on the basis of $5~000$ epochs of the experimental data set.
-Fourty minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
-Figure \ref{fig:ANN-6-conv} show the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$  during the training phase.
+The training data were those from the tests presented in Section \ref{sec:ComTestResults} and were composed of $21~000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
+The learning was performed on the basis of $5~000$ epochs of the experimental data set.
+$40$ minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allowed to obtain the converged parameters of the ANN model.
+Figure \ref{fig:ANN-6-conv} shows the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$  during the training phase.
 \begin{figure}[!ht]
@@
 \end{figure}
-As we can see on this figure, after $5~000$ epoch, we can consider that we have reached a stationary state of the model learning and that it is useless to continue the learning phase.
+As can be seen in this figure, after $5~000$ epoch, we can consider that we have reached a stationary state of the model learning and that it is useless to continue with the learning phase.
 
-Once the learning phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data in the same way as is done with the analytical models.
+Once the learning phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data similarly to what is done with analytical models.
 One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}) which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code) as proposed in Pantalé \eal \cite{Pantale-2021}.
-For reasons of compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix.
+For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix.
 
@@
 {Figures/CompExp-3-15-7-1-sigmoid}
-\caption{Comparison between the experimental and predicted flow stresses by the 3-15-7-1-sigmoid ANN model}
+\caption{Comparison between the experimental flow stresses and those predicted by the the 3-15-7-1-sigmoid ANN model}
 \label{fig:CompExp-3-15-7-1-sigmoid}
 \end{figure}
-The correlation between the experimental data and the ANN prediction is very good over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
+The experimental data and the ANN prediction correlate very well over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
 For the ANN model, $\AARE=0.62~\%$ and $\RMSE=0.38~\MPa$ which is excellent.
@@
 \end{table}
-From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally 6 times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.
+From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.
+Globally, the values of $\AARE$ and $\RMSE$ are $6$ times lower than with the best of the analytical models, \ie, the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.
 
-The ANN, Arrhenius and PTM models are the only models that take into account the softening with the deformation of medium carbon at low strain rate, unlike the other three models that only present an increase of the flow stress with the strain, whatever the strain rate and temperature, hence their poor performance in predicting the behavior of this material and more particularly at low strain rates.
-The parameters reported in Table \ref{tab:Errors}, the correlations visible in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow us to conclude here that the ANN model is the most efficient of all the models presented to describe the behavior of the medium carbon alloy for high temperature deformation applications.
+The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material and more particularly at low strain rates.
+The parameters reported in Table \ref{tab:Errors}, the correlations that can be seen in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow to conclude  that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high temperature deformation applications.
 
 %----------------------------------------------------------------------------------
-\section{Interpolation and extrapolation capability of analytical and ANN models \label{sec:IntExt}}
+\section{Interpolation and Extrapolation Capability of Analytical and ANN Models \label{sec:IntExt}}
 %----------------------------------------------------------------------------------
@@
 In order to better compare the performances of the models presented previously (the 5 analytical models and the neural network based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
-The identification of the models performed without the section is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
-In order to test the learning capabilities and fidelity of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
+The identification of the performed models is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
+To test the learning capacity and fidelity of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
 
-Thus, one of the omitted strain rates ($\mdot\varepsilon=1~\ps$) is within the range of strain rates for model identification ($0.001~\ps\text{ to }5~\ps$), so we can test the ability of the models to interpolate the results from the other 5 strain rates and be able to quantify the deviation from the experimental values.
-On the other hand, the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates of identification of the models ($0.001~\ps\text{ to }2~\ps$), we will then test the ability of the models to extrapolate the results and also be able to quantify the deviation with the experimental values.
+Thus, one of the omitted strain rates ($\mdot\varepsilon=1~\ps$) is within the range of strain rates for model identification ($0.001~\ps\text{ to }5~\ps$), and therefore, we can test the ability of the models to interpolate the results from the other 5 strain rates and be able to quantify any deviation from experimental values.
+On the other hand, since the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates for the model identification ($0.001~\ps\text{ to }2~\ps$), we will test the ability of the models to extrapolate results and quantify deviation with the experimental values.
 
@@
 
-For the validation of the interpolation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for ANN) are the 5 other, \ie $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
+For the interpolation validation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for ANN) are the 5 others, \ie $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
 All models were re-identified from the same experimental data on a data set corresponding to 5 strain rates and 5 temperatures.
@@
 From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
-Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates (named id.
+Table \ref{tab:IntVal} shows a quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates (named id.
 $\mdot\varepsilon$), on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
-It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.
+It appears from this Table that while the two models, AR and ANN, give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives a globally better result across the entire strain rates spectrum, with values of $\AARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively, that is to say, values approximately 2 to 3 times lower for the ANN model than for the AR model.
 
@@
 For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0.01, 0.1, 1, 2]~\ps$.
-The strain rate omitted in this analysis is therefore the highest value, which restricts the learning domain.
+The strain rate omitted in this analysis therefore has the highest value, which restricts the learning domain.
 
@@
 Nevertheless, these values are too large for proper use.
-It is again the inability of these models to take into account the softening of the behavior at low strain rates and low temperatures that is at the origin of these values.
+Once again, it is the inability of these models to take into account the softening of the behavior at low strain rates and low temperatures that is at the origin of these values.
 
-The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models compared to the other two models.
-Table \ref{tab:ExtVal} shows the comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
-The HS model performs worse on extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\AARE$ and $\RMSE$ superior to $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
-The two models AR and ANN give the best results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
-The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.09\%$ and $\RMSE=2.40~\MPa$ respectively.
+The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models than for the other two models.
+Table \ref{tab:ExtVal} shows a comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
+The HS model performs worse on extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\AARE$ and $\RMSE$ greater than $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
+The two models, AR and ANN, give the best results for the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
+Tis time, the AR model performs a little better on the $\mdot\varepsilon=5~\ps$ strain rate as compared to the ANN model, but the latter gives  a globally better result across the entire strain rates spectrum, with values of  $\AARE=1.09\%$ and $\RMSE=2.40~\MPa$ respectively.
 
-We can therefore conclude from this part of the study that the AR model is the best performing of the 5 analytical models presented, which is in agreement with the fact that it is widely used for thermomechanical processing, but the ANN model approach has advantages over the AR model approach in that, overall, the ANN model is more faithful to the experimental data than the AR model for all strain rates.
+We can therefore conclude from this part of the study that the AR model is the best performing of the 5 analytical models presented, which is in agreement with the fact that it is widely used for thermomechanical processing, but the ANN model approach has advantages over the AR model approach in that, overall, the ANN model is more faithful to experimental data than is the AR model, for all strain rates.
 
@@
 {Figures/Performance}
-\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
+\caption{Comparison between experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
 \label{fig:Performance}
 \end{figure}
-In this part a technique is proposed to have a better interpolation of data.
-Indeed, as mentioned in the introduction, it is important to know how to reassure oneself of the effectiveness of the model that well describes the behavior of a material for a good use on new data.
+In this section a technique is proposed to obtain a better interpolation of data.
+Indeed, as mentioned in the introduction, it is important to know how to ensure the effectiveness of the model that well describes the behavior of a material for a good use on new data different from those used for its identification.
 It is therefore a question of choosing models that have a good correlation with experience and proposing a formula for a good use of their parameters on unknown data.
@@
 \end{equation}
-Where $\dot{\varepsilon}_{p}$ is the unkown strain rate and $m\in[50-300]$
-Applaying this formule the new figures are plotted in Figure \ref{fig:Performance}. From these results we can see clearly that the results are better that the initial ones. 
+Where $\dot{\varepsilon}_{p}$ is the unknown strain rate and $m\in[50-300]$
+Applying this formula, the new figures are plotted in Figure \ref{fig:Performance}. These results are clearly better than the initial ones.
+
 \section{Conclusions and future work\label{sec:Conclusion}}
@@
 
-Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-The analytical models selected for this study are the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model  \cite{TizeMha-2022}.
-Analysis of the data from the Gleeble trials, and comparison of the 6 models proposed in this study against the experiments, led to the following conclusions.
+Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
+The analytical models selected for this study were the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model  \cite{TizeMha-2022}.
+An analysis of the data from the Gleeble trials, and comparison of the 6 models proposed in this study against the experiments, led to the following conclusions.
 
-From an experimental point of view, it appears from the tests carried out that the flow stress $\sigma^y$ increases with the decrease of the temperature $T$ and the increase of the strain rate $\mdot\varepsilon$ due to the competitive appearance of the dynamic softening and work hardening mechanisms.
+From an experimental point of view, it appears from the tests carried out that the flow stress $\sigma^y$ increases with a decrease of the temperature $T$ and an increase of the strain rate $\mdot\varepsilon$ due to the competitive appearance of the dynamic softening and work hardening mechanisms.
 The dynamic recrystallization (DRX) phenomenon, introduced through the difference between the maximum and permanent strain, shows a partially complete microstructure evolution.
@@
 
-Five analytical models have been identified for this alloy, as well as an Artificial Neural Network based model.
-Among the analytical models, the JC and MZA models proved to be inappropriate to reproduce the behavior of this material, while the HS, PTM and AR models showed their capabilities since they present an acceptable $\AARE$ error (from $3.5\%$ to $7.7\%$), with a superiority of the AR model ($3.56\%$) over the other two which confirms its use in thermomechanical processes.
-The ANN model, is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of the medium carbon with a value of $\AARE=0.62\%$.
+Five analytical models and an Artificial Neural Network-based model were identified for this alloy,
+Among the analytical models, the JC and MZA models proved inadequate to reproduce the behavior of this material, while the HS, PTM and AR models showed their capabilities, presenting an acceptable $\AARE$ error (from $3.5\%$ to $7.7\%$).
+The AR model (with a $3.56\%$ error) proved superior to the other two, thus justifying its use in thermomechanical processes.
+The ANN model, is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of the medium carbon with a $\AARE=0.62\%$.
 
 To test the performance of each proposed model, a study was conducted to evaluate the interpolation and extrapolation capability of the developed models.
-In the case of interpolation, the HS, PTM and AR models have a good correlation with the experiment, but the ANN model shows superiority with an error factor 5 times lower than the AR model.
-For the extrapolation of the data, the HS, PTM and AR models have again a good correlation with the experiment, but the ANN model is again globally better performing.
+In the case of interpolation, the HS, PTM and AR models correlated well with the experiment, but the ANN model was superior, with an error factor 5 times lower than the AR model.
+For data extrapolation, the HS, PTM and AR models again correlated well with the experiment, but the ANN model once again performed better globally.
 These two parts of the study confirm what was demonstrated in the model identifications.
@@
 Identifying the parameters of an ANN model from experimental data requires more time than identifying the parameters of analytical models (about 40 minutes on a working laptop), but as shown by Pantalé \eal \cite{Pantale-2021}, implementing an ANN model in a computational code is straightforward.
-Therefore, we recommend using the ANN model when conducting a study involving this alloy under these experimental conditions.
+Therefore, we recommend using the ANN model when conducting a study involving this alloy under the experimental conditions examined here in.
 
-As part of the perspectives of this work, we will develop another ANN model to characterize this time the microstructure in terms of DRX and formation of phases such as ferrite, bainite and martensite for example.
+For future work perspectives, we will develop another ANN model to characterize the microstructure in terms of DRX and the formation of phases such as ferrite, bainite and martensite for example.
 This ANN model can then be compared to the most commonly used classical models such as the JMAK model.
@@
 In order to complete this paper, we report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
-In order to use this model we describe here after the procedure to compute the flow stress $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$.
-This process can be decomposed in 3 phases:
+In order to use this model we describe $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$ after the procedure to compute the flow stress.
+This process can be decomposed into 3 phases:
 \begin{itemize}
-\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, Lu-2011-ANN}.
+\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid an ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, Lu-2011-ANN}.
 Therefore, the three components of the input vector $\overrightarrow{x}$ are obtained from the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$ and the temperature $T$ using the following expressions:
@@
 The reference strain rate is $\mdot{\varepsilon_0} = 0.001~\ps$.
-\item Then we compute the output $s$ of the ANN from the input vector $\overrightarrow{x}$ using the three following equations.
+\item Then we compute the output $s$ of the ANN from the input vector $\overrightarrow{x}$ using the  following three equations.
 \begin{equation}
@@
 \end{equation*}
-The biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$ components vector:
+The bias of the first hidden layer $\overrightarrow{b_1}$ is a $15$ components vector:
 \begin{equation*}
@@
 \end{equation*}
-The biases of the second hidden layer $\overrightarrow{b_2}$ is a 7 components vector:
+The bias of the second hidden layer $\overrightarrow{b_2}$ is a 7 component vector:
 \begin{equation*}
@@
 \end{equation*}
-The weight vector for the output layer $\overrightarrow{w}$ is a 7 components vector:
+The weight vector for the output layer $\overrightarrow{w}$ is a 7 component vector:
 \begin{equation*}

### 2023-01-17 Article.tex
Update Whole article for corrections

@@
 \DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
-\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
-\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
+\DeclareRobustCommand{\ie}{i.e.\@\xspace}
+\DeclareRobustCommand{\eal}{et al.\@\xspace}
 \DeclareRobustCommand{\eg}{e.g.,\@\xspace}
 \DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
-\DeclareRobustCommand{\AARE}{\text{E}_\text{AAR}}
+\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
 \DeclareRobustCommand{\R}{\text{R}}
@@
 \definecolor{VWyellow}{RGB}{255,251,150}
-\DeclareRobustCommand{\OP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
-\DeclareRobustCommand{\OPP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
+\sethlcolor{VWyellow}
+
+\DeclareRobustCommand{\OP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
+\DeclareRobustCommand{\OPP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
+\DeclareRobustCommand{\CR}[1]{\textcolor{red}{#1}}
+\DeclareRobustCommand{\SP}[1]{\textcolor{red}{\sout{#1}}}
 
@@
 
-\title{Interpolation and extrapolation based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}
+\title{Interpolation and extrapolation-based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}
 
@@
 \address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, 65016, France}
-\address[ETS]{École de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3, Canada}
+\address[ETS]{École de technologie supérieure, 1100 Notre Dame St. W., Montreal, QC H3C 1K3, Canada}
 
 \begin{abstract}
-\textcolor{red}{In the present work, a critical analysis of the most commonly used analytical models as well as recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them}.
-To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Geleeble $3800$ thermomechanical simulator.
-The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
-The Mean Absolute Relative Error (MARE) and the Root Mean Square Error (RMSE) values were used to quantify the predictive accuracy of the analyzed models.
-The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented significant error, MARRE of  $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with about $3.56\%$ error.
-The Artificial Neural Network model, on the other hand, showed excellent agreement, less than $0.62\%$ error, between the predicted and experimental flow curves.
+In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
+To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
+The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius \CR{models}, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
+The Mean Absolute Relative Error \CR{($\MARE$)} and the Root Mean Square Error \CR{($\RMSE$)} values were used to quantify the predictive accuracy of the analyzed models.
+The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented \CR{a} significant error, \CR{$\MARE$} of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
+The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
 To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
-The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability with a notable superiority for the Arrhenius model compared to the other two.
-The Artificial Neural Networks model was however, still the most performant compared to all the models.
-A correlation factor is proposed to extend the applicability of some of the investigated models to deformation conditions not included in the original experimental plan.
+The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability\CR{,} with the notable superiority of the Arrhenius model over the other two.
+The Artificial Neural Networks model was\CR{,} however, still the most performant among all the models.
+\SP{A correlation factor was proposed to extend the applicability of some of the investigated models to deformation conditions not included in the original experimental plan.}\OP{Has to be removed}
 \end{abstract}
@@
 %----------------------------------------------------------------------------------
-Large size forged blocks made of medium carbon high-strength steels are extensively used in automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
-The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and quench $\&$ temper heat treatment process to achieve the desired mechanical properties  \cite{chadha2017deformation,chadha2018influence,murugesan2019two}.
-In recent years, in order to respond to the market demand, larger size forgings need to be produced.
-In parallel, more stringent condition on chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block are required.
-Among the three manufacturing steps (casting, forging, heat treatment), forging is the one where the most important microstructural changes take place and influences the final properties that could be achieved \cite{murugesan2019hybrid,chadha2020microstructure,sripada2022effect}.
-Open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, concomitantly take place with softening phenomena such as   recovery and recrystallization under static and/or dynamic \cite{tian2022deformation,tavakoli2019ferrite}.
-It has also been reported that phase transformation could take place during deformation.
-The extent and intensity of the above strengthening or softening phenomena strongly depend on three macroscopic quantities \ie the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$  \cite{ ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}.
+Large size forged blocks made of medium carbon high-strength steels are extensively used in the automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
+The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and a quench and temper heat treatment process to achieve the desired mechanical properties \cite{chadha2017deformation, chadha2018influence, murugesan2019two}.
+In recent years, in order to respond to the market demand, larger size forgings have had to be produced.
+In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block have been required.
+Of the three manufacturing steps (casting, forging and heat treatment), forging is where the most important microstructural changes take place, and which greatly influences the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
+The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic \CR{thermomechanical loads} \cite{tian2022deformation, tavakoli2019ferrite}.
+It has also been reported that phase transformation can occur during deformation.
+The extent and intensity of the above phenomena strongly depend on three macroscopic quantities\CR{,} namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, Ashtiani-2012, He-2013, Changizian-2012}.
 
-Considering the large size of the blocks, a purely experimental approach, based on trial and error, could not be used by industry and reliable predictive tools, such a Finite Element analysis (FEA) codes have been developed and are commercially available.
-However, the prediction reliability of such analyses is dependent on the accuracy of the material constitutive model, which describes the mutual interactions between strain, strain rate, and temperature during deformation.
-Precipitation and phase changes as mentioned above are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
-Hence most of the constitutive models depend on macroscopic parameters that influence the hardening and softening of the material.
-A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed among them, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
-Despite their simplicity, each of them suffer from shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from lack of non-coupling between strain, strain rate and temperature  while the HS model is better adapted for higher strain rate deformation conditions \cite{chadha2018approach}.
-To circumvent these shortcomings, several modified forms of models have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
-However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, could not be accurately predicted and none of the models is able to accurately predict flow behavior outside the experimental testing interval that was used to determine the model constants.
-Due to its more physics-based formulation, the ZA model and its modified form, MZA, \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021} and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS  models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
-The Arrhenius formulation has been revised several times for a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
-To overcome the strong dependency of the models to a specific alloy, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
-This formulation is based on the MZA model and polynomial functions of undefined order that are used during the identification.
-However, in the PTM model, the high order of the polynomial function (up to $10$ in some cases) can affect its accuracy.
+Considering the large size of blocks, a purely experimental approach, based on trial and error, can not be used by industry, and therefore, reliable predictive tools, such a Finite Element analysis (FEA) codes, have been developed, and are commercially available.
+However, the prediction reliability of such analyses is a function of the accuracy of the material constitutive model, which describes the mutual interactions between the strain, the strain rate, and the temperature during deformation.
+As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
+Hence, most constitutive models depend on macroscopic parameters which influence the hardening and softening of the material.
+A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed.
+Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
+Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate \SP{deformation} conditions \cite{chadha2018approach}.
+To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
+However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, \CR{cannot} be accurately predicted\CR{,} and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
+Due to its more physics-based formulation, the ZA model and its modified form, MZA\SP{,} \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
+The Arrhenius formulation has been revised \CR{repeatedly} to achieve a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
+To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
+This formulation is based on the MZA model and the polynomial functions of undefined order that are used during the identification.
+However, in the PTM model, the high order of the polynomial function (up-to $10$ in some cases) can affect its accuracy.
 
-Artificial Neural Network (ANN) is an approach to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
+The Artificial Neural Network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
 It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
-Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
+Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
 Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
 Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
-Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software as reported by Pantalé \eal \cite{Pantale-2021}.
-In fact, the implementation of constitutive model in a FEA code requires the derivatives of this model with respect to strain, strain rate and temperature.
+Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
+In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to strain, strain rate and temperature.
 
-Although progress has been made in improvement of constitutive models to better predict the flow stress behavior of materials, there is still a problem with the efficiency of all the above models.
-Indeed, a model is considered appropriate to the prediction of the material's behavior when its predictions and experimental results correlate well.
-It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those it was identified for.
-In other words, can interpolation and extrapolation techniques be used to extent the applicability of a constitutive equation for different materials and processing windows?
+Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problem still persist with the \CR{models'} efficiency.
+Indeed, a model is considered appropriate for predicting the material's behavior if its predictions and experimental results correlate well.
+It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those for which it was identified.
+In other words, the question is whether interpolation and extrapolation techniques can be used to extend the applicability of a constitutive equation for different \SP{materials and}\OP{Out of this scope concerning different materials} processing windows.
 
-The present work aims to address the above question using a combination of the recently introduced PTM model and ANN.
-To this end, initially, hot compression tests, simulating the open die forging process, were carried out and the generated flow curves were modeled using the above mentioned constitutive equations and an ANN model developed in this work.
-Then the interpolation and extrapolation capabilities of each model is evaluated and a solution is proposed that responds to the main question of the paper.
-The results are validated based on experimental work carried out in the present work and data obtained from the literature.
+The present work aims to address the preceding question using \SP{a combination of} the recently introduced \SP{PTM model and} ANN \CR{model}.\OP{Objective updated}
+To this end, initially, hot compression tests, simulating the open die forging process, are carried out and the flow curves generated are modeled using the above--mentioned constitutive equations and an ANN model developed in this work.
+Then, the interpolation and extrapolation capabilities of each model are evaluated \SP{and a solution proposed, responding to the main question of the paper}.
+The results are validated based on experimental work carried out \CR{herein} and on data obtained from the literature.
 
@@
 
-The material used in this study is a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
+The material used in this study consists of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
 \begin{table}[h!]
 \centering
-\caption{Chemical composition of medium carbon steel, Fe = balance.}
+\caption{Chemical composition of medium carbon steel, Fe = balance}
 \begin{tabular}{lccccccc}
@@
 Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
-Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
+Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$\CR{,} with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
 \begin{figure}[!ht]
@@
 \includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
-\caption{Schematic diagram of the experimental process.}
+\caption{Schematic diagram of the experimental process}
 \label{fig:GleebleProcess}
@@
 
-The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as true stress and true strain according to L-gauge where the formula to get those curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2r_0$ and $F$ is the force as measured by Gleeble load cell.
-As there are noises from raw data, savgolfilter method from scipy library is used to remove noise and have more smooth data.
-For further usage of data in numerical simulation elastic parts have been removed.
+The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
+As raw data contains noises, \CR{the} savgol\_filter method from the scipy library is used to remove noise and provide smoother data.
+To allow further use of the data in numerical simulations, elastic parts are removed.
 
@@
 \includegraphics[width=\columnwidth]{Figures/rawData}
-\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
+\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$}
 \label{fig:RawData}
 \end{figure}
-All data curve contains $700$ equidistant strain values up-to $\varepsilon=0.7$.
-So, there are $6$ strain rates and $5$ temperatures, the database consists of $21~000$ data points.
-The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
+All data curves contain $700$ equidistant strain values up-to $\varepsilon=0.7$.
+Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of \CR{$21,000$} data points.
+The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$\CR{,} but decreases with increasing temperature $T$.
 It should be noted that the strain also influences the flow stress.
-Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
+Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, and then decreases to maintain a more or less constant value until the end of the test.
 For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
 The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{buckley2001deformation}.
-The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time and thus friction increases.
-The increase of stresses observed at the beginning of the deformation up to $0.1$ is due to the work hardening (WH).
-After $0.1$ up to $0.2$ the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of work-hardening rate.
-This behavior describes that thermal softening becomes more and more predominant until it exceeds WH.
+The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time, and friction thus increases.
+The increase of stress observed at the beginning of the deformation and up-to $0.1$ is due to work hardening (WH).
+After $0.1$ and up-to $0.2$, the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of the work-hardening rate.
+This behavior indicates that thermal softening becomes more and more predominant until it exceeds WH.
 At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening.
-This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$ except those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and strain rate of $0.1$ $\text{s}^{-1}$ ; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
+This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$, except for those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and a $0.1$ $\text{s}^{-1}$ strain rate; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
 Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates.
@@
 stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$.
-As an example, Figure \ref{fig:Micrography} shows the microstructures of medium carbon held during $5$~min at $1260\celsius$ before and after the compression phase.
+
+As an example, Figure \ref{fig:Micrography} shows the medium carbon \CR{microstructures} held for $5$~min at $1260\celsius$ before and after the compression phase.
 \begin{figure}[!ht]
@@
 \end{subfigure}
-\caption{Optical micrographs of a medium carbon steel before (a) and after (b) hot compression.}
+\caption{Optical micrographs of a medium carbon steel (a) before and (b) after hot compression}
 \label{fig:Micrography}
 \end{figure}
-As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
-From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the 6 proposed flow laws will be presented in the next section in order to predict the behavior of the material in any test condition.
+As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get austenitized grain on the one hand, and on the other hand, held for $1$ minute at $1150^\circ$C before compression with a $0.001~\text{s}^{-1}$ strain rate.
+\SP{The results reported in Figure \ref{fig:RawData},will be used in the next section to identify the parameters of the $6$ proposed flow laws in order to see which mode will matches with experimental.}
+The data presented in Figure \ref{fig:RawData} will be utilized in the following section to determine the parameters of the $6$ flow laws proposed and to determine which model most closely aligns with experimental results.
 
 %----------------------------------------------------------------------------------
-\section{Identification of constitutive flow laws parameters\label{sec:ConstLaws}}
+\section{Identification of Constitutive Flow Laws Parameters\label{sec:ConstLaws}}
 %----------------------------------------------------------------------------------
@@
 where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
-The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
-For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$ respectively.
+The other values are reference values: $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and thus $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$\CR{,} respectively.
 
-The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
-This method allows obtaining one after the other the 5 parameters in the order $A$, $B$, $n$, $C$ and $m$.
-Thus, according to our experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
-For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
+The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
+This method allows sequentially obtaining the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
+Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
+For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then \CR{be} determined by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
 Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
-Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
-Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
+Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering \CR{only} all the curves at $T=T_0$ then gives $C=0.3404$.
+Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the \CR{previously identified} parameters and gives $m=0.7057$.
 All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.
@@
 \centering
-\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
+\caption{Parameter values of the Johnson-Cook flow law for a medium carbon steel}
 \begin{tabular}{ccccc}
@@
 \includegraphics[width=\columnwidth]{Figures/CompExp-JC-6}
-\caption{Comparison between the experimental and predicted flow stresses by JC model.}
+\caption{Comparison between the experimental flow stresses and those \CR{predicted} by \CR{the} JC model}
 \label{fig:CompExp-JC-6}
 \end{figure}
-The JC model is not able to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
+The JC model is unable to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several strain \CR{rate} values.
 The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
-As expected, the mathematical formulation of the Johnson-Cook flow law is unable to represent the stress drop at low strain rates, the JC model being only monotonically increasing with strain.
+As expected, the mathematical formulation of the Johnson-Cook flow law is unable to represent the stress drop at low strain rates, with the JC model increasing only monotonically with the strain.
 Since most of the parameters are identified at low strain rates ($A$, $B$ and $n$), this results in a very poor fit of the model to the experimental data.
 
-The accuracy and predictive ability of the models are usually assessed by certain coefficients such as the Mean Absolute Relative Error ($\AARE$) defined by Equation (\ref{eq:AARE}):
+The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the Mean Absolute Relative Error ($\MARE$) defined by Equation (\ref{eq:AARE}):
 \begin{equation}
-\AARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
+\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
 \end{equation}
@@
 \end{equation}
-where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the predicted value using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
-For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
-As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
-Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction we avoided its use in our analysis.
+where $\sigma_i^e$ is the experimental value\CR{,} $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
+For the JC model, $\MARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
+As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure \SP{in our case of study} because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
+Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model\CR{,} but simply establishes a good linearity correlation between the experiment and the prediction\CR{,} we avoided its use in our analysis.
 
@@
 
-The MZA which is the modified form of ZA model, as the JC model is one of widely used models and implemented in many FEM codes like Abaqus.
-The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experimental.
-Indeed, in the JC model, those parameters are considered separately where they are simultaneously considered in MZA and for that formulation MZA is preferred to JC model \cite{Hull-2011}.
-But the original form of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
+\CR{The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most widely used models implemented in many FEM codes such as the Abaqus software.}\OP{The previous sentence has been completely rewritten!}
+The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experiments.
+In the JC model, the parameters are considered separately, while in MZA, they are considered simultaneously\CR{,} and for that formulation, MZA is preferred to the JC model \cite{Hull-2011}.
+However, the original form of the ZA model has some limitations due to the fact that it is considered as \CR{a two terms function} (thermal and athermal functions), and to \CR{improve the} formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
 \begin{equation}
@@
 \end{equation}
-where the 7 coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
-To get the parameters of the MZA model we apply the medod proposed by \cite{Samantaray-2009} and those parameters are summurizedin in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
+where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
+To get the parameters of the MZA model, we apply the method proposed by \cite{Samantaray-2009}\CR{,} and the parameters are summarized in \SP{in} Table \ref{tab:MZA}\CR{,} while their predictions are plotted in Figure \ref{fig:CompExp-MZA-6}.
 \begin{table}[h!]
 \centering{}
-\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
+\caption{Parameter\SP{s'} constants of Modified Zerilli-Armstrong model}
 \begin{tabular}{ccccccc}
@@
 {Figures/CompExp-MZA-6}
-\caption{Comparison between the experimental and predicted flow stresses by MZA model}
+\caption{Comparison between the experimental flow stresses and those predicted by the MZA model}
 \label{fig:CompExp-MZA-6}
 \end{figure}
-It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
-The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
-For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\MPa$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.
+It can be seen from \CR{this figure} that the MZA model as \CR{well as the} JC model is not \SP{suitable to describe experimental}\CR{able to faithfully reproduce the experimental data} at low strain rates\CR{,} but \CR{is} much better for high strain rates.
+The deviation between the predicted values and the experimental values is large because this model has \CR{a} problem correctly describing the softening in its formulation.
+For the MZA model, $\MARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model\CR{,} as reported in \cite{TizeMha-2022}.
 
@@
 \end{equation}
-where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature as proposed earlier.
+where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature\CR{,} as proposed earlier.
 The coefficients $A$ and $m_i$ are the 9 parameters of the model to be identified.
 However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification.
-For its identification, several authors restrict its expression to a reduced number of 5 or 6 $m_i$ parameters only, by forcing a zero value for the other parameters \cite{Chadha-2018, Mehtedi-2015, Rudnytskyj-2020}.
+For its identification, several authors restrict its expression to a reduced number of only $5$ or $6$ $m_i$ parameters, by forcing a zero value for the other parameters \cite{Chadha-2018, Mehtedi-2015, Rudnytskyj-2020}.
 
 In the present study, the best results were obtained by taking the model defined by only the first 7 $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.
-From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HS}.
+From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} allowed to compute the parameters reported in Table
+ \ref{tab:HS}.
 
@@
 \centering
-\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
+\caption{Parameter\SP{s'} values of the Hansel-Spittel flow law for the medium carbon steel}
 \begin{tabular}{ccccc}
@@
 
-The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
-For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\MPa$.
-It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1~\ps$.
-This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate.
-The DRX phenomena cannot be reproduced by this type of model.
+A comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6}, where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
+For the HS model, $\MARE=7.75~\%$ and $\RMSE=3.80~\MPa$.
+It appears that both this model and the previous ones do not adequately predict the experimental one, and the difference is relatively significant for all strain rates below $1~\ps$.
+This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong non-linear \SP{the} behavior observed for low strain rate values.
+The DRX phenomenon cannot be reproduced by this type of model.
 
@@
 \end{equation}
-Where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent of the material.
-The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperature by regression method.
-Combination of Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allow expressing the flow stress $\sigma^y$ as a function of the $Z$ parameter:
+where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent on the material.
+The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperatures by the regression method.
+Combining Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allows to express the flow stress $\sigma^y$ as a function of the $Z$ parameter:
 \begin{equation}
@@
 
-To obtain the constitutive equation, it is necessary to determine all the parameters $A$, $Q$ $\alpha$ and $n$ for a given material.
-The strain has a significant non-linear influence on the behavior of the material by the mechanism of strain hardening and softening at high values of deformation.
-A compensation in strain must therefore be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$ $\alpha$ and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
+To obtain the constitutive equation, all the parameters $A$, $Q$ $\alpha$ and $n$ \CR{must} be determined for a given material.
+The strain has a significant non-linear influence on the behavior of the material by the strain hardening and softening mechanisms at high values of deformation.
+A strain dependent factor must therefore be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$ $\alpha$ and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
 \begin{equation}
@@
 
-The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
-The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
-Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:AR}.
+The determination of the order $m$ of the polynomials \SP{defined by}\CR{defining} Equations (\ref{eq:ArA}-\ref{eq:Arn}) \SP{is defined according to}\CR{depends on} the ability of the model to represent the non-linear dependence of the stress \SP{versus the}\CR{on} strain and its generalization.
+The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials used to determine using a regression method.
+Setting $m=9$ gives the best results\CR{,} and the corresponding parameters are reported in Table \ref{tab:AR}.
 \begin{table}[h!]
 \centering
-\caption{Parameters' values of the Arrhenius flow law for the P20 steel.}
+\caption{Parameter\SP{s'} values of the Arrhenius flow law for the medium carbon steel}
 \begin{tabular}{llll}
@@
 
-Figure \ref{fig:CompExp-AR-6} shows the comparison of the values predicted by the Arrhenius model and the experimental values.
+Figure \ref{fig:CompExp-AR-6} shows a comparison of the values predicted by the Arrhenius model and the experimental values.
 The difference between the experimental and predicted values is small.
-But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
-For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\MPa$.
-
+However for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is unable to predict the softening.
+For the AR model, $\MARE=3.56~\%$ and $\RMSE=2.18~\MPa$.
 \begin{figure}[!ht]
@@
 {Figures/CompExp-AR-6}
-\caption{Comparison between the experimental and predicted flow stresses by AR model}
+\caption{Comparison between the experimental flow stresses and those predicted \SP{flow stresses} \SP{flow stresses} by the AR model}
 \label{fig:CompExp-AR-6}
@@
 The PTM model \cite{TizeMha-2022} is a generalized formulation of the MZA model presented in Section \ref{sec:MZA}.
-When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to make the PTM model flexible for any type of material studied because there is no need for a limited number of parameters as in the MZA model.
-Its construction is based on the use of polynomial functions as in the AR model.
-Thus, the intrinsic functions of the model, of polynomial type, allow adjusting the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
+When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to render the PTM model flexible for any type of material studied because it removes \CR{the} need for a limited number of parameters as in the MZA model.
+Its construction is based on the use of polynomial functions, as is the case in the AR model.
+Thus, the physical parameters' dependent intrinsic functions of the PTM model, allow adjusting the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
 The equation describing the PTM model is therefore given by :
@@
 Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
-The larger these quantities are, the more parameters need to be identified for the PTM model.
-The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016} and for more details about this model  we invite the reader to read our previous work \cite{TizeMha-2022}.
+The larger these quantities, the greater the number of parameters needing to be identified for the PTM model.
+The determination of the parameters of this model is \SP{calculated}\CR{done} thanks to the LMFIT Python library \cite{Newville-2016} (for more details about this model we refer the reader to our previous work \cite{TizeMha-2022}).
 Thus, all the parameters of this model are calculated with $q=5$, $r=5$, $s=1$ and $t=5$.
 
-Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
-The PTM model is suitable to describe the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
-The deviation between the predicted values and the experimental values for other strain rates is relatively good.
-For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\MPa$ and this shows an overall worse performance than the AR model.
+\CR{Figure }\ref{fig:CompExp-PTM-6} presents a \CR{comparison} of values predicted by the PTM model and experimental values.
+The PTM model is suitable for describing the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$, the prediction is not very good.
+The deviation between the predicted values and the experimental values for other strain rates is relatively low.
+For the PTM model, $\MARE=4.79~\%$ and $\RMSE=4.59~\MPa$, which is an overall worse performance than the AR model.
 
@@
 \centering
-\caption{Parameters' values of the PTM flow law for the P20 steel.}
+\caption{Parameter\SP{s'} values of the PTM flow law for the P20 steel}
 \begin{tabular}{llll}
@@
 
-Because of their predictive capacity and their adaptability, Artificial Neural Networks (ANNs) are more and more widely used today in many scientific fields.
+Because of their predictive capacity and adaptability, Artificial Neural Networks (ANNs) are increasingly widely used today in many scientific fields.
 Their operation is based on a learning process during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine learning process.
 
-There are generally two uses of neural networks: classification and regression.
-The first is the ability to classify data into different groups and for example to distinguish between images of cats and dogs.
-The second one corresponds to the capacity of universal approximator of these neural networks, which interests us in this application, and thus to the ability after learning to predict the values of the flow stress $\sigma^y$ according to the input data, as do the analytical models previously identified.
-The main difference is that this approximation is not linked to a fixed mathematical formulation (JC, MZA, AR, HS, PTM model), but is only dependent on the data used for training, the number of layers, the number of neurons per layer and the activation functions associated with the neurons of the network.
+Neural networks generally have two uses: classification and regression.
+The first is the ability to classify data into different groups\CR{,} and for example\CR{,} to distinguish between images of cats and dogs.
+The second corresponds to the universal approximation capacity of these neural networks, which \CR{is} of interest to us \CR{herein}, and thus, to the ability, after learning\CR{,} to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by the previously identified analytical models.
+The main difference is that this approximation is not linked to a fixed mathematical formulation (as in JC, MZA, AR, HS and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer\CR{,} and the activation functions associated with the neurons of the network.
 A feed-forward ANN, as used in our application, contains an input layer, an output layer and a number of hidden layers ($2$ in our case).
@@
 where $y_i\lay{k}$ is the entry of the $i^{th}$ neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j^{th}$ neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i^{th}$ neuron of layer $k$ and the $j^{th}$ neuron of layer $(k-1)$ and $b_i\lay{k}$ is the associated bias of the $i^{th}$ neuron of layer $k$.
-Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN that we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021}.
-For the proposed model, we have selected the Sigmoid activation function, so that, each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
+Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
+For the proposed model, we selected the Sigmoid activation function, so that, each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
 \begin{equation}
@@
 \end{equation}
-No activation function is used for the output neuron of the ANN.
 
-After some tests of different types of network architecture and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and 7 neurons for the second layer give the best compromise between prediction, learning time and model compactness.
-From the global architecture point of view, the input layer is composed of three neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
-This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second layer and 8 for the output layer).
+No activation function is used for the output neuron of the ANN as usually done in regression ANN.
 
-The Python program used for training the neural network was developed using the specialized Python library Tensorflow \cite{Abadi-2016}.
+After some tests of different types of network \CR{architectures,} and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer give the best compromise between prediction, learning time and model compactness.
+From a global architecture point of view, the input layer is composed of $3$ neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
+This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second layer and $8$ for the output layer).
+
+The Python program used for training the neural network was developed using the specialized Python library\CR{,} Tensorflow \cite{Abadi-2016}.
 The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
-The training data are those from the tests presented in section \ref{sec:ComTestResults} and composed of $21~000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
-The learning is performed on the basis of $5~000$ epochs of the experimental data set.
-Fourty minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
-Figure \ref{fig:ANN-6-conv} show the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$  during the training phase.
+The training data were those from the tests presented in Section \ref{sec:ComTestResults}\CR{,} and were composed of \CR{$21,000$} quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
+The learning was performed on the basis of \CR{$5,000$} epochs of the experimental data set.
+$40$ minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allowed to obtain the converged parameters of the ANN model.
+Figure \ref{fig:ANN-6-conv} shows the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$ during the training phase.
 \begin{figure}[!ht]
@@
 {Figures/Conv-ANN-6}
-\caption{Convergence of the ANN model during the training phase.}
+\caption{Convergence of the ANN model during the training phase}
 \label{fig:ANN-6-conv}
 \end{figure}
-As we can see on this figure, after $5~000$ epoch, we can consider that we have reached a stationary state of the model learning and that it is useless to continue the learning phase.
+As can be seen in this figure, after $5,000$ \CR{epochs}, we can consider that we have reached a stationary state of the model learning\CR{,} and that it is useless to continue with the learning phase.
 
-Once the learning phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data in the same way as is done with the analytical models.
-One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}) which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code) as proposed in Pantalé \eal \cite{Pantale-2021}.
-For reasons of compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix.
+Once the learning phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data similarly to what is done with analytical models.
+One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2})\CR{,} which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code)\CR{,} as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
+For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix.
 
@@
 {Figures/CompExp-3-15-7-1-sigmoid}
-\caption{Comparison between the experimental and predicted flow stresses by the 3-15-7-1-sigmoid ANN model}
+\caption{Comparison between the experimental flow stresses and those predicted by \SP{the} the 3-15-7-1-sigmoid ANN model}
 \label{fig:CompExp-3-15-7-1-sigmoid}
 \end{figure}
-The correlation between the experimental data and the ANN prediction is very good over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
-For the ANN model, $\AARE=0.62~\%$ and $\RMSE=0.38~\MPa$ which is excellent.
+The experimental data and the ANN prediction correlate very well over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
+For the ANN model, $\MARE=0.62~\%$ and $\RMSE=0.38~\MPa$ which is excellent.
 This model can be used to simulate the hot deformation of this type of alloy with much greater fidelity to the actual material behavior than the analytical models presented previously.
@@
 \centering
-\caption{Accuracy coefficients for all the analyzed models.}
+\caption{Accuracy coefficients for all the analyzed models}
 \begin{tabular}{lcccccc}
@@
 	Coefficients  &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
-	$\AARE(\%)$         & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
+	$\MARE(\%)$   & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
 	$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \hline
@@
 \end{table}
-From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally 6 times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.
+From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.
+Globally, the values of $\MARE$ and $\RMSE$ are $6$ times lower than with the best of the analytical models, \ie, the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.
 
-The ANN, Arrhenius and PTM models are the only models that take into account the softening with the deformation of medium carbon at low strain rate, unlike the other three models that only present an increase of the flow stress with the strain, whatever the strain rate and temperature, hence their poor performance in predicting the behavior of this material and more particularly at low strain rates.
-The parameters reported in Table \ref{tab:Errors}, the correlations visible in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow us to conclude here that the ANN model is the most efficient of all the models presented to describe the behavior of the medium carbon alloy for high temperature deformation applications.
+The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material\CR{,} and more particularly\CR{,} at low strain rates.
+The parameters reported in Table \ref{tab:Errors} \CR{and} the correlations that can be seen in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow \SP{to conclude}\CR{concluding} that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for \CR{high-temperature} deformation applications.
 
 %----------------------------------------------------------------------------------
-\section{Interpolation and extrapolation capability of analytical and ANN models \label{sec:IntExt}}
+\section{Interpolation and Extrapolation Capability of Analytical and ANN Models \label{sec:IntExt}}
 %----------------------------------------------------------------------------------
 
-In order to better compare the performances of the models presented previously (the 5 analytical models and the neural network based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
-The identification of the models performed without the section is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
-In order to test the learning capabilities and fidelity of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
+In order to better compare the performances of the models presented previously (the 5 analytical models and the ANN based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
+The identification of the \SP{performed}\CR{previously presented} models is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
+To test the learning capacity and fidelity of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
 
-Thus, one of the omitted strain rates ($\mdot\varepsilon=1~\ps$) is within the range of strain rates for model identification ($0.001~\ps\text{ to }5~\ps$), so we can test the ability of the models to interpolate the results from the other 5 strain rates and be able to quantify the deviation from the experimental values.
-On the other hand, the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates of identification of the models ($0.001~\ps\text{ to }2~\ps$), we will then test the ability of the models to extrapolate the results and also be able to quantify the deviation with the experimental values.
+Thus, one of the omitted strain rates ($\mdot\varepsilon=1~\ps$) is within the range of strain rates for model identification ($0.001~\ps\text{ to }5~\ps$), and therefore, we can test the ability of the models to interpolate the results from the other 5 strain rates and be able to quantify any deviation from experimental values.
+On the other hand, since the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates for the model identification ($0.001~\ps\text{ to }2~\ps$), we will test the ability of the models to extrapolate results and quantify \CR{deviations} with the experimental values.
 
@@
 
-For the validation of the interpolation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for ANN) are the 5 other, \ie $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
+For \SP{the} interpolation validation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for \CR{the} ANN) are the 5 others, \ie\CR{,} $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
 All models were re-identified from the same experimental data on a data set corresponding to 5 strain rates and 5 temperatures.
 
-Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
+Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as dots) for the 5 analytical models and the neural network.
 \begin{figure}[!ht]
@@
 \end{figure}
-Table \ref{tab:IntVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=1~\ps$.
+Table \ref{tab:IntVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for \CR{the $5$ identified strain rates (lines referred as id.
+$\mdot\varepsilon$)}, the $6$ strain rates (lines referred as\SP{:} all $\mdot\varepsilon$) or only on the strain rate $\mdot\varepsilon=1~\ps$.
 \begin{table}[h!]
@@
 	Strain rate & Coefficients & JC & MZA & HS & AR & PTM & ANN \\ \hline
-	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
+	\mr{2}{id. $\mdot\varepsilon$} & $\MARE(\%)$ & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
 	 & $\RMSE(\MPa)$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
-	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
+	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\MARE(\%)$ & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
 	 & $\RMSE(\MPa)$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
-	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
+	\mr{2}{all $\mdot\varepsilon$} & $\MARE(\%)$ & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
 	 & $\RMSE(\MPa)$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
@@
 
-In Figure \ref{fig:CompInt} it can be seen that the first two models (JC and MZA), presented in this study do not have the ability to reproduce the behavior of the material for the strain rate $\mdot\varepsilon=1~\ps$.
-Overall, the JC model gives better results than the MZA model for $\mdot\varepsilon=1~\ps$, which is reflected in Table \ref{tab:IntVal} by a lower value of $\AARE$ and $\RMSE$ for JC than for MZA.
+In Figure \ref{fig:CompInt}\CR{,} it can be seen that the first two models (JC and MZA), presented in this study do not have the ability to reproduce the behavior of the material for the strain rate $\mdot\varepsilon=1~\ps$.
+Overall, the JC model gives better results than the MZA model for $\mdot\varepsilon=1~\ps$, which is reflected in Table \ref{tab:IntVal} by a lower value of $\MARE$ and $\RMSE$ for JC than for MZA.
 Nevertheless, these values are higher than $10\%$ for the JC model and $20\%$ for the MZA model, which reflects the poor ability of these models to correctly model the behavior of this material.
-This finding is in agreement with the previous findings of Sections \ref{sec:JC} and \ref{sec:MZA} which showed the inability of these models to take into account the softening of the behavior visible at low strain rates and low temperatures.
+This finding is in agreement with the previous findings of Sections \ref{sec:JC} and \ref{sec:MZA}\CR{,} which showed the inability of these models to take into account the softening of the behavior visible at low strain rates and low temperatures.
 
-From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
-Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates (named id.
-$\mdot\varepsilon$), on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
-It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.
+From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results\CR{,} with a higher fidelity for the AR and ANN models compared to the other two models.
+Table \ref{tab:IntVal} shows a quantitative comparison on $\MARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates, on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
+It appears from this \CR{table} that while the two models, AR and ANN, give equivalent (and excellent) results concerning the values of $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives a globally better result across the entire strain \CR{rate} spectrum, with values of $\MARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively\CR{;} that is to say, values \CR{that are} approximately 2 to 3 times lower for the ANN model than for the AR model.
 
-This shows the superior fidelity of the ANN model compared to the 5 analytical models presented in this study both in the interpolation capability of the model and in the overall behavior.
+This shows the superior fidelity of the ANN model \CR{over} to the 5 analytical models presented in this study both in \CR{terms of} the interpolation capability of the model and \CR{of} the overall behavior.
 
@@
 For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0.01, 0.1, 1, 2]~\ps$.
-The strain rate omitted in this analysis is therefore the highest value, which restricts the learning domain.
+The strain rate omitted in this analysis therefore has the highest value, which restricts the learning domain.
 
-In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
+In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as dots) for the 5 analytical models and the neural network.
 \begin{figure}[!ht]
@@
 \end{figure}
-Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
+Table \ref{tab:ExtVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for \CR{the $5$ identified strain rates (lines referred as id.
+$\mdot\varepsilon$)}, the $6$ strain rates (lines referred as\SP{:} all $\mdot\varepsilon$) or only on the strain rate $\mdot\varepsilon=5~\ps$.
 \begin{table}[h!]
@@
 	Strain rate & Coefficients & JC & MZA & HS & AR & PTM & ANN \\ \hline
-	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$ \\
+	\mr{2}{id. $\mdot\varepsilon$} & $\MARE(\%)$ & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$ & $0.61$ \\
 	 & $\RMSE(\MPa)$ & $9.86$ & $16.26$ & $3.36$ & $2.32$ & $3.63$ & $0.32$ \\ \hline
-	\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$ \\
+	\mr{2}{$\mdot\varepsilon=5~\ps$} & $\MARE(\%)$ & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$ \\
 	 & $\RMSE(\MPa)$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ \hline
-	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$ \\
+	\mr{2}{all $\mdot\varepsilon$} & $\MARE(\%)$ & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$ & $1.09$ \\
 	 & $\RMSE(\MPa)$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$ & $2.40$ \\ \hline
@@
 As presented in the previous section regarding the interpolation capability of the models, in Figure \ref{fig:CompExt} it can be seen that the first two models, JC and MZA, in this study again do not have the ability to correctly reproduce the material behavior for the strain rate $\mdot\varepsilon=5~\ps$.
-The JC model performs better than the MZA model for $\mdot\varepsilon=5~\ps$, which is reflected in Table \ref{tab:ExtVal} by a lower value of $\AARE$ and $\RMSE$ for JC than for MZA.
+The JC model performs better than the MZA model for $\mdot\varepsilon=5~\ps$, which is reflected in Table \ref{tab:ExtVal} by a lower value of $\MARE$ and $\RMSE$ for JC than for MZA.
 Nevertheless, these values are too large for proper use.
-It is again the inability of these models to take into account the softening of the behavior at low strain rates and low temperatures that is at the origin of these values.
+Once again, it is the inability of these models to take into account the softening of the behavior at low strain rates and low temperatures that is at the origin of these values.
 
-The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models compared to the other two models.
-Table \ref{tab:ExtVal} shows the comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
-The HS model performs worse on extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\AARE$ and $\RMSE$ superior to $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
-The two models AR and ANN give the best results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
-The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.09\%$ and $\RMSE=2.40~\MPa$ respectively.
+The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models than for the other two models.
+Table \ref{tab:ExtVal} shows a comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
+The HS model performs worse \CR{in} extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\MARE$ and $\RMSE$ greater than $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
+The two models, AR and ANN, give the best results for the values of $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
+\CR{This} time, the AR model performs a little better on the $\mdot\varepsilon=5~\ps$ strain rate as compared to the ANN model, but the latter gives a globally better result across the entire strain \CR{rate} spectrum, with values of $\MARE=1.09\%$ and $\RMSE=2.40~\MPa$ respectively.
 
-We can therefore conclude from this part of the study that the AR model is the best performing of the 5 analytical models presented, which is in agreement with the fact that it is widely used for thermomechanical processing, but the ANN model approach has advantages over the AR model approach in that, overall, the ANN model is more faithful to the experimental data than the AR model for all strain rates.
+We can therefore conclude from this part of the study that the AR model is the best performing of the 5 analytical models presented, which is in agreement with the fact that it is widely used for thermomechanical processing, but the ANN model approach has advantages over the AR model approach in that, overall, the ANN model is more faithful to experimental data than is the AR model, for all strain rates.
+
+\OP{Section Proposed technique for better interpolation has been removed in this version.}
+%%----------------------------------------------------------------------------------
+%\subsection{Proposed technique for better interpolation}
+%%----------------------------------------------------------------------------------
+%\begin{figure}[!ht]
+%\centering
+%\includegraphics[width=\columnwidth]
+%{Figures/Performance}
+%\caption{Comparison between experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
+%\label{fig:Performance}
+%\end{figure}
+%In this section a technique is proposed to obtain a better interpolation of data.
+Indeed, as mentioned in the introduction, it is important to know how to ensure the effectiveness of the model that well describes the behavior of a material for a good use on new data different from those used for its identification.
+It is therefore a question of choosing models that have a good correlation with experience and proposing a formula for a good use of their parameters on unknown data.
+The AR, HS, PTM and ANN models are therefore chosen and it emerges that each model must be multiplied by a lambda factor whose formula is given as follows.
+%\begin{equation}
+% \lambda = \left(\frac{\dot{\varepsilon}_{max} - \dot{\varepsilon}_{p} }{\dot{\varepsilon}_{p} - \dot{\varepsilon}_{min}}\right)^{\frac{\dot{\varepsilon}_p}{m}}
+%\end{equation}
+%Where $\dot{\varepsilon}_{p}$ is the unknown strain rate and $m\in[50-300]$
+%Applying this formula, the new figures are plotted in Figure \ref{fig:Performance}. These results are clearly better than the initial ones.
 
 %----------------------------------------------------------------------------------
-\subsection{Proposed technique for better interpolation}
-%----------------------------------------------------------------------------------
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]
-{Figures/Performance}
-\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
-\label{fig:Performance}
-\end{figure}
-In this part a technique is proposed to have a better interpolation of data.
-Indeed, as mentioned in the introduction, it is important to know how to reassure oneself of the effectiveness of the model that well describes the behavior of a material for a good use on new data.
-It is therefore a question of choosing models that have a good correlation with experience and proposing a formula for a good use of their parameters on unknown data.
-The AR, HS, PTM and ANN models are therefore chosen and it emerges that each model must be multiplied by a lambda factor whose formula is given as follows.
-\begin{equation}
- \lambda = \left(\frac{\dot{\varepsilon}_{max} - \dot{\varepsilon}_{p} }{\dot{\varepsilon}_{p} - \dot{\varepsilon}_{min}}\right)^{\frac{\dot{\varepsilon}_p}{m}}
-\end{equation}
-Where $\dot{\varepsilon}_{p}$ is the unkown strain rate and $m\in[50-300]$
-Applaying this formule the new figures are plotted in Figure \ref{fig:Performance}. From these results we can see clearly that the results are better that the initial ones. 
 \section{Conclusions and future work\label{sec:Conclusion}}
@@
 
-Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-The analytical models selected for this study are the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model  \cite{TizeMha-2022}.
-Analysis of the data from the Gleeble trials, and comparison of the 6 models proposed in this study against the experiments, led to the following conclusions.
+Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
+The analytical models selected for this study were the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model \cite{TizeMha-2022}.
+The ANN model selected is the one introduced by Pantalé \eal \cite{Pantale-2021}.
+An analysis of the data from the Gleeble trials\SP{,} and \CR{a} comparison of the 6 models proposed in this study against the experiments\SP{,} led to the following conclusions.
 
-From an experimental point of view, it appears from the tests carried out that the flow stress $\sigma^y$ increases with the decrease of the temperature $T$ and the increase of the strain rate $\mdot\varepsilon$ due to the competitive appearance of the dynamic softening and work hardening mechanisms.
-The dynamic recrystallization (DRX) phenomenon, introduced through the difference between the maximum and permanent strain, shows a partially complete microstructure evolution.
+From an experimental point of view, it appears from the tests carried out that the flow stress $\sigma^y$ increases with a decrease of the temperature $T$ and an increase of the strain rate $\mdot\varepsilon$ due to the competitive appearance of the dynamic softening and work hardening mechanisms.
+The dynamic recrystallization (DRX) phenomenon, introduced through the difference between the maximum and permanent \CR{strains}, shows a partially complete microstructure evolution.
 Thus, at high strain rates, it is difficult to visualize the DRX phenomenon on the flow curves due to the sensitivity of this phenomenon to the strain rate.
@@
 
-Five analytical models have been identified for this alloy, as well as an Artificial Neural Network based model.
-Among the analytical models, the JC and MZA models proved to be inappropriate to reproduce the behavior of this material, while the HS, PTM and AR models showed their capabilities since they present an acceptable $\AARE$ error (from $3.5\%$ to $7.7\%$), with a superiority of the AR model ($3.56\%$) over the other two which confirms its use in thermomechanical processes.
-The ANN model, is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of the medium carbon with a value of $\AARE=0.62\%$.
+Five analytical models and an Artificial Neural Network-based model were identified for this alloy.
+Among the analytical models, the JC and MZA models proved inadequate to reproduce the behavior of this material, while the HS, PTM and AR models showed their capabilities, presenting an acceptable $\MARE$ error (from $3.5\%$ to $7.7\%$).
+The AR model (with a $3.56\%$ error) proved superior to the other two, thus justifying its use in thermomechanical processes.
+The ANN model\SP{,} is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of \SP{the} medium carbon\CR{,} with a $\MARE=0.62\%$.
 
 To test the performance of each proposed model, a study was conducted to evaluate the interpolation and extrapolation capability of the developed models.
-In the case of interpolation, the HS, PTM and AR models have a good correlation with the experiment, but the ANN model shows superiority with an error factor 5 times lower than the AR model.
-For the extrapolation of the data, the HS, PTM and AR models have again a good correlation with the experiment, but the ANN model is again globally better performing.
-These two parts of the study confirm what was demonstrated in the model identifications.
+In the case of interpolation, the HS, PTM and AR models correlated well with the experiment, but the ANN model was superior, with an error factor 5 times lower than the AR model.
+For data extrapolation, the HS, PTM and AR models again correlated well with the experiment, but the ANN model once again performed better globally.
+\SP{These two parts of the study confirm what was demonstrated in the model identifications.}
 
-Identifying the parameters of an ANN model from experimental data requires more time than identifying the parameters of analytical models (about 40 minutes on a working laptop), but as shown by Pantalé \eal \cite{Pantale-2021}, implementing an ANN model in a computational code is straightforward.
-Therefore, we recommend using the ANN model when conducting a study involving this alloy under these experimental conditions.
+Identifying the parameters of an ANN model from experimental data requires more time than identifying the parameters of analytical models (about 40 minutes on a working laptop), but as shown by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, implementing an ANN model in a computational code is straightforward.
+Therefore, we recommend using the ANN model when conducting a study involving this alloy under the experimental conditions examined \CR{herein}.
 
-As part of the perspectives of this work, we will develop another ANN model to characterize this time the microstructure in terms of DRX and formation of phases such as ferrite, bainite and martensite for example.
+For future work perspectives, we will develop another ANN model to characterize the microstructure in terms of DRX and the formation of phases such as ferrite, bainite and martensite\CR{,} for example.
 This ANN model can then be compared to the most commonly used classical models such as the JMAK model.
@@
 
-In order to complete this paper, we report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
-In order to use this model we describe here after the procedure to compute the flow stress $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$.
-This process can be decomposed in 3 phases:
+\SP{In order to complete this paper, we}\CR{We} report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
+In order to use this model\CR{,} we describe \CR{here after the details of the procedure to compute the flow stress} $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$\SP{after the procedure to compute the flow stress}.
+This process can be decomposed into 3 phases:
 \begin{itemize}
-\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, Lu-2011-ANN}.
+\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid an ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, Lu-2011-ANN}.
 Therefore, the three components of the input vector $\overrightarrow{x}$ are obtained from the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$ and the temperature $T$ using the following expressions:
@@
 The reference strain rate is $\mdot{\varepsilon_0} = 0.001~\ps$.
-\item Then we compute the output $s$ of the ANN from the input vector $\overrightarrow{x}$ using the three following equations.
+\item Then\CR{,} we compute the output $s$ of the ANN from the input vector $\overrightarrow{x}$ using the following three equations\CR{:}
 \begin{equation}
@@
 \begin{array}{rrr}
-2.2206 & -3.7555 & -6.7246\\
--4.8598 & 5.7431 & -5.8538\\
-2.3099 & 3.3325 & -5.1795\\
-2.0475 & 0.8006 & -1.4259\\
-8.8358 & -6.0362 & 0.8226\\
--1.2613 & -0.9274 & -2.3725\\
--0.3561 & 6.5032 & -10.7573\\
--11.7226 & -2.0455 & 1.2248\\
-3.1066 & 26.5580 & 18.6540\\
--0.5150 & -5.6922 & 1.0104\\
--6.4755 & 8.4888 & -2.4459\\
--1.8791 & -0.5380 & 2.2295\\
--6.0206 & 1.2776 & 0.2169\\
-0.2619 & -4.7974 & -1.1282\\
--27.1456 & -0.5327 & -0.5303\\
+	2.2206   & -3.7555 & -6.7246  \\
+	-4.8598  & 5.7431  & -5.8538  \\
+	2.3099   & 3.3325  & -5.1795  \\
+	2.0475   & 0.8006  & -1.4259  \\
+	8.8358   & -6.0362 & 0.8226   \\
+	-1.2613  & -0.9274 & -2.3725  \\
+	-0.3561  & 6.5032  & -10.7573 \\
+	-11.7226 & -2.0455 & 1.2248   \\
+	3.1066   & 26.5580 & 18.6540  \\
+	-0.5150  & -5.6922 & 1.0104   \\
+	-6.4755  & 8.4888  & -2.4459  \\
+	-1.8791  & -0.5380 & 2.2295   \\
+	-6.0206  & 1.2776  & 0.2169   \\
+	0.2619   & -4.7974 & -1.1282  \\
+	-27.1456 & -0.5327 & -0.5303
 \end{array}\right]
 \end{equation*}
-The biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$ components vector:
+The \CR{biases} of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
 \begin{equation*}
@@
 \begin{array}{r}
-5.9164\\
--1.9074\\
--2.6837\\
--1.0954\\
--0.9509\\
-3.1682\\
--4.3964\\
-0.6343\\
--5.0676\\
-2.0228\\
-1.1267\\
--0.9671\\
--0.6263\\
-2.3110\\
--0.3037\\
+	5.9164  \\
+	-1.9074 \\
+	-2.6837 \\
+	-1.0954 \\
+	-0.9509 \\
+	3.1682  \\
+	-4.3964 \\
+	0.6343  \\
+	-5.0676 \\
+	2.0228  \\
+	1.1267  \\
+	-0.9671 \\
+	-0.6263 \\
+	2.3110  \\
+	-0.3037
 \end{array}\right]
@@
 \begin{array}{rrrrrrr}
--0.5783 & 1.2724 & 0.5747 & 0.6449 & -4.2203 & -0.2380 & 0.2591\\
--0.4852 & 5.2807 & 0.8888 & -8.2324 & -2.0075 & -0.6474 & -1.0787\\
-4.4499 & -0.0137 & 0.1657 & 0.3198 & 4.9765 & -1.2503 & 0.8219\\
-1.7571 & 0.7730 & 0.0208 & -1.3316 & -0.8945 & -0.7284 & -0.1831\\
--1.0866 & 0.1330 & -0.8615 & -0.1283 & 0.2218 & -0.1772 & -2.7458\\
--0.3925 & 1.3994 & 0.0630 & -1.8397 & -1.1047 & -1.9839 & 0.5767\\
--0.2121 & 0.9977 & 1.2028 & -9.6525 & 0.5520 & 0.1062 & -0.0409\\
--1.1518 & -1.6402 & -4.1501 & -1.0759 & 0.4749 & -2.8350 & 0.9225\\
--1.1453 & -0.2173 & -0.1382 & 0.8264 & -0.5125 & 0.1882 & -0.8654\\
--4.3301 & -0.3711 & -7.4305 & 3.5926 & -9.6217 & -1.2375 & 1.6171\\
-2.3907 & -1.0085 & -0.8828 & -1.1891 & 0.9947 & 1.1178 & -1.0953\\
--1.5955 & 1.6313 & 0.4916 & 0.1906 & -1.9216 & -1.4140 & 1.3827\\
--1.6985 & 1.4277 & -3.4462 & -8.3777 & -1.2132 & -1.2158 & 2.8512\\
--1.9954 & -2.0159 & -8.3455 & -0.5205 & 0.2942 & -1.3337 & 0.2026\\
-4.3040 & -0.7164 & -1.0859 & 3.4294 & -23.8003 & 12.5859 & 7.3721\\
+	-0.5783 & 1.2724  & 0.5747  & 0.6449  & -4.2203  & -0.2380 & 0.2591  \\
+	-0.4852 & 5.2807  & 0.8888  & -8.2324 & -2.0075  & -0.6474 & -1.0787 \\
+	4.4499  & -0.0137 & 0.1657  & 0.3198  & 4.9765   & -1.2503 & 0.8219  \\
+	1.7571  & 0.7730  & 0.0208  & -1.3316 & -0.8945  & -0.7284 & -0.1831 \\
+	-1.0866 & 0.1330  & -0.8615 & -0.1283 & 0.2218   & -0.1772 & -2.7458 \\
+	-0.3925 & 1.3994  & 0.0630  & -1.8397 & -1.1047  & -1.9839 & 0.5767  \\
+	-0.2121 & 0.9977  & 1.2028  & -9.6525 & 0.5520   & 0.1062  & -0.0409 \\
+	-1.1518 & -1.6402 & -4.1501 & -1.0759 & 0.4749   & -2.8350 & 0.9225  \\
+	-1.1453 & -0.2173 & -0.1382 & 0.8264  & -0.5125  & 0.1882  & -0.8654 \\
+	-4.3301 & -0.3711 & -7.4305 & 3.5926  & -9.6217  & -1.2375 & 1.6171  \\
+	2.3907  & -1.0085 & -0.8828 & -1.1891 & 0.9947   & 1.1178  & -1.0953 \\
+	-1.5955 & 1.6313  & 0.4916  & 0.1906  & -1.9216  & -1.4140 & 1.3827  \\
+	-1.6985 & 1.4277  & -3.4462 & -8.3777 & -1.2132  & -1.2158 & 2.8512  \\
+	-1.9954 & -2.0159 & -8.3455 & -0.5205 & 0.2942   & -1.3337 & 0.2026  \\
+	4.3040  & -0.7164 & -1.0859 & 3.4294  & -23.8003 & 12.5859 & 7.3721
 \end{array}\right]
 \end{equation*}
-The biases of the second hidden layer $\overrightarrow{b_2}$ is a 7 components vector:
+The \CR{biases} of the second hidden layer $\overrightarrow{b_2}$ is a 7-component vector:
 \begin{equation*}
@@
 \begin{array}{r}
-0.7534\\
-0.9473\\
-0.6055\\
--0.7793\\
--1.0305\\
--1.5779\\
--0.1471\\
+	0.7534  \\
+	0.9473  \\
+	0.6055  \\
+	-0.7793 \\
+	-1.0305 \\
+	-1.5779 \\
+	-0.1471
 \end{array}\right]
 \end{equation*}
-The weight vector for the output layer $\overrightarrow{w}$ is a 7 components vector:
+The weight vector for the output layer $\overrightarrow{w}$ is a 7-component vector:
 \begin{equation*}
@@
 \begin{array}{r}
-0.1920\\
-0.3406\\
-0.3839\\
--0.2880\\
-1.2047\\
--1.4126\\
--0.2215\\
+	0.1920  \\
+	0.3406  \\
+	0.3839  \\
+	-0.2880 \\
+	1.2047  \\
+	-1.4126 \\
+	-0.2215
 \end{array}\right]

### 2023-01-17 Article.tex
Cleanning of the comments and addons in Latex file

@@
 \DeclareRobustCommand{\OPP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
-\DeclareRobustCommand{\CR}[1]{\textcolor{red}{#1}}
-\DeclareRobustCommand{\SP}[1]{\textcolor{red}{\sout{#1}}}
 
@@
 To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
-The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius \CR{models}, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
-The Mean Absolute Relative Error \CR{($\MARE$)} and the Root Mean Square Error \CR{($\RMSE$)} values were used to quantify the predictive accuracy of the analyzed models.
-The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented \CR{a} significant error, \CR{$\MARE$} of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
+The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius models, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
+The Mean Absolute Relative Error ($\MARE$) and the Root Mean Square Error ($\RMSE$) values were used to quantify the predictive accuracy of the analyzed models.
+The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented a significant error, $\MARE$ of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
 The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
 To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
-The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability\CR{,} with the notable superiority of the Arrhenius model over the other two.
-The Artificial Neural Networks model was\CR{,} however, still the most performant among all the models.
-\SP{A correlation factor was proposed to extend the applicability of some of the investigated models to deformation conditions not included in the original experimental plan.}\OP{Has to be removed}
+The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability, with the notable superiority of the Arrhenius model over the other two.
+The Artificial Neural Networks model was, however, still the most performant among all the models.
 \end{abstract}
@@
 Of the three manufacturing steps (casting, forging and heat treatment), forging is where the most important microstructural changes take place, and which greatly influences the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
-The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic \CR{thermomechanical loads} \cite{tian2022deformation, tavakoli2019ferrite}.
+The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic thermomechanical loads \cite{tian2022deformation, tavakoli2019ferrite}.
 It has also been reported that phase transformation can occur during deformation.
-The extent and intensity of the above phenomena strongly depend on three macroscopic quantities\CR{,} namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, Ashtiani-2012, He-2013, Changizian-2012}.
+The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, Ashtiani-2012, He-2013, Changizian-2012}.
 
@@
 Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
-Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate \SP{deformation} conditions \cite{chadha2018approach}.
+Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
 To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
-However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, \CR{cannot} be accurately predicted\CR{,} and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
-Due to its more physics-based formulation, the ZA model and its modified form, MZA\SP{,} \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
-The Arrhenius formulation has been revised \CR{repeatedly} to achieve a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
+However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
+Due to its more physics-based formulation, the ZA model and its modified form, MZA \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
+The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
 To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
@@
 
-Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problem still persist with the \CR{models'} efficiency.
+Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problem still persist with the models' efficiency.
 Indeed, a model is considered appropriate for predicting the material's behavior if its predictions and experimental results correlate well.
 It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those for which it was identified.
-In other words, the question is whether interpolation and extrapolation techniques can be used to extend the applicability of a constitutive equation for different \SP{materials and}\OP{Out of this scope concerning different materials} processing windows.
+In other words, the question is whether interpolation and extrapolation techniques can be used to extend the applicability of a constitutive equation for different processing windows.
 
-The present work aims to address the preceding question using \SP{a combination of} the recently introduced \SP{PTM model and} ANN \CR{model}.\OP{Objective updated}
+The present work aims to address the preceding question using the recently introduced ANN model.
 To this end, initially, hot compression tests, simulating the open die forging process, are carried out and the flow curves generated are modeled using the above--mentioned constitutive equations and an ANN model developed in this work.
-Then, the interpolation and extrapolation capabilities of each model are evaluated \SP{and a solution proposed, responding to the main question of the paper}.
-The results are validated based on experimental work carried out \CR{herein} and on data obtained from the literature.
+Then, the interpolation and extrapolation capabilities of each model are evaluated.
+The results are validated based on experimental work carried out herein and on data obtained from the literature.
 
@@
 Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
-Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$\CR{,} with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
+Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
 \begin{figure}[!ht]
@@
 The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
-As raw data contains noises, \CR{the} savgol\_filter method from the scipy library is used to remove noise and provide smoother data.
+As raw data contains noises, the savgol\_filter method from the scipy library is used to remove noise and provide smoother data.
 To allow further use of the data in numerical simulations, elastic parts are removed.
@@
 All data curves contain $700$ equidistant strain values up-to $\varepsilon=0.7$.
-Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of \CR{$21,000$} data points.
-The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$\CR{,} but decreases with increasing temperature $T$.
+Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of $21,000$ data points.
+The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$, but decreases with increasing temperature $T$.
 It should be noted that the strain also influences the flow stress.
@@
 
-As an example, Figure \ref{fig:Micrography} shows the medium carbon \CR{microstructures} held for $5$~min at $1260\celsius$ before and after the compression phase.
+As an example, Figure \ref{fig:Micrography} shows the medium carbon microstructures held for $5$~min at $1260\celsius$ before and after the compression phase.
 \begin{figure}[!ht]
@@
 As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get austenitized grain on the one hand, and on the other hand, held for $1$ minute at $1150^\circ$C before compression with a $0.001~\text{s}^{-1}$ strain rate.
-\SP{The results reported in Figure \ref{fig:RawData},will be used in the next section to identify the parameters of the $6$ proposed flow laws in order to see which mode will matches with experimental.}
 The data presented in Figure \ref{fig:RawData} will be utilized in the following section to determine the parameters of the $6$ flow laws proposed and to determine which model most closely aligns with experimental results.
@@
 The other values are reference values: $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and thus $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
-For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$\CR{,} respectively.
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$, respectively.
 
@@
 Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
-For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then \CR{be} determined by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
+For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then be determined by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
 Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
-Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering \CR{only} all the curves at $T=T_0$ then gives $C=0.3404$.
-Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the \CR{previously identified} parameters and gives $m=0.7057$.
+Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering only all the curves at $T=T_0$ then gives $C=0.3404$.
+Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the previously identified parameters and gives $m=0.7057$.
 All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.
@@
 \includegraphics[width=\columnwidth]{Figures/CompExp-JC-6}
-\caption{Comparison between the experimental flow stresses and those \CR{predicted} by \CR{the} JC model}
+\caption{Comparison between the experimental flow stresses and those predicted by the JC model}
 \label{fig:CompExp-JC-6}
 \end{figure}
-The JC model is unable to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several strain \CR{rate} values.
+The JC model is unable to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several strain rate values.
 The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
@@
 \end{equation}
-where $\sigma_i^e$ is the experimental value\CR{,} $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
+where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
 For the JC model, $\MARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
-As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure \SP{in our case of study} because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
-Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model\CR{,} but simply establishes a good linearity correlation between the experiment and the prediction\CR{,} we avoided its use in our analysis.
+As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
+Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction, we avoided its use in our analysis.
 
@@
 
-\CR{The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most widely used models implemented in many FEM codes such as the Abaqus software.}\OP{The previous sentence has been completely rewritten!}
+The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most widely used models implemented in many FEM codes such as the Abaqus software.
 The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experiments.
-In the JC model, the parameters are considered separately, while in MZA, they are considered simultaneously\CR{,} and for that formulation, MZA is preferred to the JC model \cite{Hull-2011}.
-However, the original form of the ZA model has some limitations due to the fact that it is considered as \CR{a two terms function} (thermal and athermal functions), and to \CR{improve the} formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
+In the JC model, the parameters are considered separately, while in MZA, they are considered simultaneously, and for that formulation, MZA is preferred to the JC model \cite{Hull-2011}.
+However, the original form of the ZA model has some limitations due to the fact that it is considered as a two terms function (thermal and athermal functions), and to improve the formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
 \begin{equation}
@@
 where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
-To get the parameters of the MZA model, we apply the method proposed by \cite{Samantaray-2009}\CR{,} and the parameters are summarized in \SP{in} Table \ref{tab:MZA}\CR{,} while their predictions are plotted in Figure \ref{fig:CompExp-MZA-6}.
+To get the parameters of the MZA model, we apply the method proposed by \cite{Samantaray-2009}, and the parameters are summarized in Table \ref{tab:MZA}, while their predictions are plotted in Figure \ref{fig:CompExp-MZA-6}.
 \begin{table}[h!]
 \centering{}
-\caption{Parameter\SP{s'} constants of Modified Zerilli-Armstrong model}
+\caption{Parameter constants of Modified Zerilli-Armstrong model}
 \begin{tabular}{ccccccc}
@@
 \end{figure}
-It can be seen from \CR{this figure} that the MZA model as \CR{well as the} JC model is not \SP{suitable to describe experimental}\CR{able to faithfully reproduce the experimental data} at low strain rates\CR{,} but \CR{is} much better for high strain rates.
-The deviation between the predicted values and the experimental values is large because this model has \CR{a} problem correctly describing the softening in its formulation.
-For the MZA model, $\MARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model\CR{,} as reported in \cite{TizeMha-2022}.
+It can be seen from this figure that the MZA model as well as the JC model is not able to faithfully reproduce the experimental data at low strain rates, but is much better for high strain rates.
+The deviation between the predicted values and the experimental values is large because this model has a problem correctly describing the softening in its formulation.
+For the MZA model, $\MARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model, as reported in \cite{TizeMha-2022}.
 
@@
 \end{equation}
-where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature\CR{,} as proposed earlier.
+where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature, as proposed earlier.
 The coefficients $A$ and $m_i$ are the 9 parameters of the model to be identified.
@@
 \centering
-\caption{Parameter\SP{s'} values of the Hansel-Spittel flow law for the medium carbon steel}
+\caption{Parameter values of the Hansel-Spittel flow law for the medium carbon steel}
 \begin{tabular}{ccccc}
@@
 It appears that both this model and the previous ones do not adequately predict the experimental one, and the difference is relatively significant for all strain rates below $1~\ps$.
-This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong non-linear \SP{the} behavior observed for low strain rate values.
+This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong non-linear behavior observed for low strain rate values.
 The DRX phenomenon cannot be reproduced by this type of model.
@@
 
-To obtain the constitutive equation, all the parameters $A$, $Q$ $\alpha$ and $n$ \CR{must} be determined for a given material.
+To obtain the constitutive equation, all the parameters $A$, $Q$ $\alpha$ and $n$ must be determined for a given material.
 The strain has a significant non-linear influence on the behavior of the material by the strain hardening and softening mechanisms at high values of deformation.
@@
 
-The determination of the order $m$ of the polynomials \SP{defined by}\CR{defining} Equations (\ref{eq:ArA}-\ref{eq:Arn}) \SP{is defined according to}\CR{depends on} the ability of the model to represent the non-linear dependence of the stress \SP{versus the}\CR{on} strain and its generalization.
+The determination of the order $m$ of the polynomials defining Equations (\ref{eq:ArA}-\ref{eq:Arn}) depends on the ability of the model to represent the non-linear dependence of the stress on strain and its generalization.
 The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials used to determine using a regression method.
-Setting $m=9$ gives the best results\CR{,} and the corresponding parameters are reported in Table \ref{tab:AR}.
+Setting $m=9$ gives the best results, and the corresponding parameters are reported in Table \ref{tab:AR}.
 \begin{table}[h!]
 \centering
-\caption{Parameter\SP{s'} values of the Arrhenius flow law for the medium carbon steel}
+\caption{Parameter values of the Arrhenius flow law for the medium carbon steel}
 \begin{tabular}{llll}
@@
 {Figures/CompExp-AR-6}
-\caption{Comparison between the experimental flow stresses and those predicted \SP{flow stresses} \SP{flow stresses} by the AR model}
+\caption{Comparison between the experimental flow stresses and those predicted by the AR model}
 \label{fig:CompExp-AR-6}
@@
 The PTM model \cite{TizeMha-2022} is a generalized formulation of the MZA model presented in Section \ref{sec:MZA}.
-When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to render the PTM model flexible for any type of material studied because it removes \CR{the} need for a limited number of parameters as in the MZA model.
+When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to render the PTM model flexible for any type of material studied because it removes the need for a limited number of parameters as in the MZA model.
 Its construction is based on the use of polynomial functions, as is the case in the AR model.
@@
 The larger these quantities, the greater the number of parameters needing to be identified for the PTM model.
-The determination of the parameters of this model is \SP{calculated}\CR{done} thanks to the LMFIT Python library \cite{Newville-2016} (for more details about this model we refer the reader to our previous work \cite{TizeMha-2022}).
+The determination of the parameters of this model is done thanks to the LMFIT Python library \cite{Newville-2016} (for more details about this model we refer the reader to our previous work \cite{TizeMha-2022}).
 Thus, all the parameters of this model are calculated with $q=5$, $r=5$, $s=1$ and $t=5$.
 
-\CR{Figure }\ref{fig:CompExp-PTM-6} presents a \CR{comparison} of values predicted by the PTM model and experimental values.
+Figure \ref{fig:CompExp-PTM-6} presents a comparison of values predicted by the PTM model and experimental values.
 The PTM model is suitable for describing the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$, the prediction is not very good.
@@
 \centering
-\caption{Parameter\SP{s'} values of the PTM flow law for the P20 steel}
+\caption{Parameter values of the PTM flow law for the P20 steel}
 \begin{tabular}{llll}
@@
 Neural networks generally have two uses: classification and regression.
-The first is the ability to classify data into different groups\CR{,} and for example\CR{,} to distinguish between images of cats and dogs.
-The second corresponds to the universal approximation capacity of these neural networks, which \CR{is} of interest to us \CR{herein}, and thus, to the ability, after learning\CR{,} to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by the previously identified analytical models.
-The main difference is that this approximation is not linked to a fixed mathematical formulation (as in JC, MZA, AR, HS and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer\CR{,} and the activation functions associated with the neurons of the network.
+The first is the ability to classify data into different groups, and for example, to distinguish between images of cats and dogs.
+The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after learning, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by the previously identified analytical models.
+The main difference is that this approximation is not linked to a fixed mathematical formulation (as in JC, MZA, AR, HS and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer, and the activation functions associated with the neurons of the network.
 A feed-forward ANN, as used in our application, contains an input layer, an output layer and a number of hidden layers ($2$ in our case).
@@
 
-After some tests of different types of network \CR{architectures,} and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer give the best compromise between prediction, learning time and model compactness.
+After some tests of different types of network architectures, and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer give the best compromise between prediction, learning time and model compactness.
 From a global architecture point of view, the input layer is composed of $3$ neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
@@
 
-The Python program used for training the neural network was developed using the specialized Python library\CR{,} Tensorflow \cite{Abadi-2016}.
+The Python program used for training the neural network was developed using the specialized Python library, Tensorflow \cite{Abadi-2016}.
 The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
-The training data were those from the tests presented in Section \ref{sec:ComTestResults}\CR{,} and were composed of \CR{$21,000$} quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
-The learning was performed on the basis of \CR{$5,000$} epochs of the experimental data set.
+The training data were those from the tests presented in Section \ref{sec:ComTestResults}, and were composed of $21,000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
+The learning was performed on the basis of $5,000$ epochs of the experimental data set.
 $40$ minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allowed to obtain the converged parameters of the ANN model.
@@
 \end{figure}
-As can be seen in this figure, after $5,000$ \CR{epochs}, we can consider that we have reached a stationary state of the model learning\CR{,} and that it is useless to continue with the learning phase.
+As can be seen in this figure, after $5,000$ epochs, we can consider that we have reached a stationary state of the model learning, and that it is useless to continue with the learning phase.
 
 Once the learning phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data similarly to what is done with analytical models.
-One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2})\CR{,} which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code)\CR{,} as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
+One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
 For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix.
@@
 {Figures/CompExp-3-15-7-1-sigmoid}
-\caption{Comparison between the experimental flow stresses and those predicted by \SP{the} the 3-15-7-1-sigmoid ANN model}
+\caption{Comparison between the experimental flow stresses and those predicted by the 3-15-7-1-sigmoid ANN model}
 \label{fig:CompExp-3-15-7-1-sigmoid}
@@
 
-The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material\CR{,} and more particularly\CR{,} at low strain rates.
-The parameters reported in Table \ref{tab:Errors} \CR{and} the correlations that can be seen in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow \SP{to conclude}\CR{concluding} that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for \CR{high-temperature} deformation applications.
+The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material, and more particularly, at low strain rates.
+The parameters reported in Table \ref{tab:Errors} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.
 
@@
 In order to better compare the performances of the models presented previously (the 5 analytical models and the ANN based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
-The identification of the \SP{performed}\CR{previously presented} models is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
+The identification of the previously presented models is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
 To test the learning capacity and fidelity of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
@@
 Thus, one of the omitted strain rates ($\mdot\varepsilon=1~\ps$) is within the range of strain rates for model identification ($0.001~\ps\text{ to }5~\ps$), and therefore, we can test the ability of the models to interpolate the results from the other 5 strain rates and be able to quantify any deviation from experimental values.
-On the other hand, since the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates for the model identification ($0.001~\ps\text{ to }2~\ps$), we will test the ability of the models to extrapolate results and quantify \CR{deviations} with the experimental values.
+On the other hand, since the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates for the model identification ($0.001~\ps\text{ to }2~\ps$), we will test the ability of the models to extrapolate results and quantify deviations with the experimental values.
 
@@
 
-For \SP{the} interpolation validation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for \CR{the} ANN) are the 5 others, \ie\CR{,} $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
+For interpolation validation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for the ANN) are the 5 others, \ie, $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
 All models were re-identified from the same experimental data on a data set corresponding to 5 strain rates and 5 temperatures.
@@
 \end{figure}
-Table \ref{tab:IntVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for \CR{the $5$ identified strain rates (lines referred as id.
-$\mdot\varepsilon$)}, the $6$ strain rates (lines referred as\SP{:} all $\mdot\varepsilon$) or only on the strain rate $\mdot\varepsilon=1~\ps$.
+Table \ref{tab:IntVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the $5$ identified strain rates (lines referred as id.
+$\mdot\varepsilon$), the $6$ strain rates (lines referred as all $\mdot\varepsilon$) or only on the strain rate $\mdot\varepsilon=1~\ps$.
 \begin{table}[h!]
@@
 
-In Figure \ref{fig:CompInt}\CR{,} it can be seen that the first two models (JC and MZA), presented in this study do not have the ability to reproduce the behavior of the material for the strain rate $\mdot\varepsilon=1~\ps$.
+In Figure \ref{fig:CompInt}, it can be seen that the first two models (JC and MZA), presented in this study do not have the ability to reproduce the behavior of the material for the strain rate $\mdot\varepsilon=1~\ps$.
 Overall, the JC model gives better results than the MZA model for $\mdot\varepsilon=1~\ps$, which is reflected in Table \ref{tab:IntVal} by a lower value of $\MARE$ and $\RMSE$ for JC than for MZA.
 Nevertheless, these values are higher than $10\%$ for the JC model and $20\%$ for the MZA model, which reflects the poor ability of these models to correctly model the behavior of this material.
-This finding is in agreement with the previous findings of Sections \ref{sec:JC} and \ref{sec:MZA}\CR{,} which showed the inability of these models to take into account the softening of the behavior visible at low strain rates and low temperatures.
+This finding is in agreement with the previous findings of Sections \ref{sec:JC} and \ref{sec:MZA}, which showed the inability of these models to take into account the softening of the behavior visible at low strain rates and low temperatures.
 
-From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results\CR{,} with a higher fidelity for the AR and ANN models compared to the other two models.
+From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results, with a higher fidelity for the AR and ANN models compared to the other two models.
 Table \ref{tab:IntVal} shows a quantitative comparison on $\MARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates, on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
-It appears from this \CR{table} that while the two models, AR and ANN, give equivalent (and excellent) results concerning the values of $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives a globally better result across the entire strain \CR{rate} spectrum, with values of $\MARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively\CR{;} that is to say, values \CR{that are} approximately 2 to 3 times lower for the ANN model than for the AR model.
+It appears from this table that while the two models, AR and ANN, give equivalent (and excellent) results concerning the values of $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives a globally better result across the entire strain rate spectrum, with values of $\MARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively; that is to say, values that are approximately 2 to 3 times lower for the ANN model than for the AR model.
 
-This shows the superior fidelity of the ANN model \CR{over} to the 5 analytical models presented in this study both in \CR{terms of} the interpolation capability of the model and \CR{of} the overall behavior.
+This shows the superior fidelity of the ANN model over to the 5 analytical models presented in this study both in terms of the interpolation capability of the model and of the overall behavior.
 
@@
 \end{figure}
-Table \ref{tab:ExtVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for \CR{the $5$ identified strain rates (lines referred as id.
-$\mdot\varepsilon$)}, the $6$ strain rates (lines referred as\SP{:} all $\mdot\varepsilon$) or only on the strain rate $\mdot\varepsilon=5~\ps$.
+Table \ref{tab:ExtVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the $5$ identified strain rates (lines referred as id.
+$\mdot\varepsilon$), the $6$ strain rates (lines referred as all $\mdot\varepsilon$) or only on the strain rate $\mdot\varepsilon=5~\ps$.
 \begin{table}[h!]
@@
 Table \ref{tab:ExtVal} shows a comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
-The HS model performs worse \CR{in} extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\MARE$ and $\RMSE$ greater than $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
+The HS model performs worse in extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\MARE$ and $\RMSE$ greater than $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
 The two models, AR and ANN, give the best results for the values of $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
-\CR{This} time, the AR model performs a little better on the $\mdot\varepsilon=5~\ps$ strain rate as compared to the ANN model, but the latter gives a globally better result across the entire strain \CR{rate} spectrum, with values of $\MARE=1.09\%$ and $\RMSE=2.40~\MPa$ respectively.
+This time, the AR model performs a little better on the $\mdot\varepsilon=5~\ps$ strain rate as compared to the ANN model, but the latter gives a globally better result across the entire strain rate spectrum, with values of $\MARE=1.09\%$ and $\RMSE=2.40~\MPa$ respectively.
 
 We can therefore conclude from this part of the study that the AR model is the best performing of the 5 analytical models presented, which is in agreement with the fact that it is widely used for thermomechanical processing, but the ANN model approach has advantages over the AR model approach in that, overall, the ANN model is more faithful to experimental data than is the AR model, for all strain rates.
-
-\OP{Section Proposed technique for better interpolation has been removed in this version.}
-%%----------------------------------------------------------------------------------
-%\subsection{Proposed technique for better interpolation}
-%%----------------------------------------------------------------------------------
-%\begin{figure}[!ht]
-%\centering
-%\includegraphics[width=\columnwidth]
-%{Figures/Performance}
-%\caption{Comparison between experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
-%\label{fig:Performance}
-%\end{figure}
-%In this section a technique is proposed to obtain a better interpolation of data.
-Indeed, as mentioned in the introduction, it is important to know how to ensure the effectiveness of the model that well describes the behavior of a material for a good use on new data different from those used for its identification.
-It is therefore a question of choosing models that have a good correlation with experience and proposing a formula for a good use of their parameters on unknown data.
-The AR, HS, PTM and ANN models are therefore chosen and it emerges that each model must be multiplied by a lambda factor whose formula is given as follows.
-%\begin{equation}
-% \lambda = \left(\frac{\dot{\varepsilon}_{max} - \dot{\varepsilon}_{p} }{\dot{\varepsilon}_{p} - \dot{\varepsilon}_{min}}\right)^{\frac{\dot{\varepsilon}_p}{m}}
-%\end{equation}
-%Where $\dot{\varepsilon}_{p}$ is the unknown strain rate and $m\in[50-300]$
-%Applying this formula, the new figures are plotted in Figure \ref{fig:Performance}. These results are clearly better than the initial ones.
 
@@
 The ANN model selected is the one introduced by Pantalé \eal \cite{Pantale-2021}.
-An analysis of the data from the Gleeble trials\SP{,} and \CR{a} comparison of the 6 models proposed in this study against the experiments\SP{,} led to the following conclusions.
+An analysis of the data from the Gleeble trials and a comparison of the 6 models proposed in this study against the experiments led to the following conclusions.
 
 From an experimental point of view, it appears from the tests carried out that the flow stress $\sigma^y$ increases with a decrease of the temperature $T$ and an increase of the strain rate $\mdot\varepsilon$ due to the competitive appearance of the dynamic softening and work hardening mechanisms.
-The dynamic recrystallization (DRX) phenomenon, introduced through the difference between the maximum and permanent \CR{strains}, shows a partially complete microstructure evolution.
+The dynamic recrystallization (DRX) phenomenon, introduced through the difference between the maximum and permanent strains, shows a partially complete microstructure evolution.
 Thus, at high strain rates, it is difficult to visualize the DRX phenomenon on the flow curves due to the sensitivity of this phenomenon to the strain rate.
@@
 The AR model (with a $3.56\%$ error) proved superior to the other two, thus justifying its use in thermomechanical processes.
-The ANN model\SP{,} is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of \SP{the} medium carbon\CR{,} with a $\MARE=0.62\%$.
+The ANN model is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of medium carbon, with a $\MARE=0.62\%$.
 
@@
 For data extrapolation, the HS, PTM and AR models again correlated well with the experiment, but the ANN model once again performed better globally.
-\SP{These two parts of the study confirm what was demonstrated in the model identifications.}
 
 Identifying the parameters of an ANN model from experimental data requires more time than identifying the parameters of analytical models (about 40 minutes on a working laptop), but as shown by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, implementing an ANN model in a computational code is straightforward.
-Therefore, we recommend using the ANN model when conducting a study involving this alloy under the experimental conditions examined \CR{herein}.
+Therefore, we recommend using the ANN model when conducting a study involving this alloy under the experimental conditions examined herein.
 
-For future work perspectives, we will develop another ANN model to characterize the microstructure in terms of DRX and the formation of phases such as ferrite, bainite and martensite\CR{,} for example.
+For future work perspectives, we will develop another ANN model to characterize the microstructure in terms of DRX and the formation of phases such as ferrite, bainite and martensite, for example.
 This ANN model can then be compared to the most commonly used classical models such as the JMAK model.
@@
 
-\SP{In order to complete this paper, we}\CR{We} report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
-In order to use this model\CR{,} we describe \CR{here after the details of the procedure to compute the flow stress} $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$\SP{after the procedure to compute the flow stress}.
+We report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
+In order to use this model, we describe here after the details of the procedure to compute the flow stress $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$.
 This process can be decomposed into 3 phases:
@@
 The reference strain rate is $\mdot{\varepsilon_0} = 0.001~\ps$.
-\item Then\CR{,} we compute the output $s$ of the ANN from the input vector $\overrightarrow{x}$ using the following three equations\CR{:}
+\item Then, we compute the output $s$ of the ANN from the input vector $\overrightarrow{x}$ using the following three equations:
 \begin{equation}
@@
 \end{equation*}
-The \CR{biases} of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
+The biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
 \begin{equation*}
@@
 \end{equation*}
-The \CR{biases} of the second hidden layer $\overrightarrow{b_2}$ is a 7-component vector:
+The biases of the second hidden layer $\overrightarrow{b_2}$ is a 7-component vector:
 \begin{equation*}

### 2023-01-23 Article.tex
order of authors
new modifications

@@
 % specify here the journal
-\journal{International Journal of Mechanical Sciences}
+\journal{Materials \& Design}
 
@@
 \author[ETS]{Prashant Dhondapure}
+\author[LGP]{Olivier Pantalé\corref{cor1}}
+\author[ETS]{Mohammad Jahazi}
 \author[LGP]{Amèvi Tongne}
-\author[ETS]{Mohammad Jahazi}
-\author[LGP]{Olivier Pantalé\corref{cor1}}
 \ead{Olivier.Pantale@enit.fr}
@@
 It has also been reported that phase transformation can occur during deformation.
-The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, Ashtiani-2012, He-2013, Changizian-2012}.
+The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, shi2022constitutive, zeng2022constitutive, rudra2019constitutive}.
 
@@
 Hence, most constitutive models depend on macroscopic parameters which influence the hardening and softening of the material.
-A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed.
-Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
+A large number of phenomenological, semi-empirical, or physical models \cite{jia2022thermo, costa2016study, rudnytskyj2020constitutive, Pantale-2021} have been developed.
+Among these, the Johnson-Cook (JC) \cite{jia2021modified}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{sim2022modified} models are the best known and most widely available in FEA codes.
 Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
-To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
+To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, liu2021modified, jia2022thermo1, bai2022comparison, zhu2022constitutive}.
 However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
-Due to its more physics-based formulation, the ZA model and its modified form, MZA \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
-The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
+Due to its more physics-based formulation, the ZA model and its modified form, MZA \cite{ovesy2020explicit, niu2020constitutive, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{derazkola2021review, wang2022deformation, miao2022deformation}.
+The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high temperature deformation \cite{rudnytskyj2022investigating, ji2020optimization}.
 To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
@@
 Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
-Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
+Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{wu2022experimental, stoffel2020deep, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
 Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
@@
 For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
-The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{buckley2001deformation}.
+The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{galos2022review}.
 The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time, and friction thus increases.
@@
 Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model, hence its inability to describe the phenomenon of softening induced by temperature.
-The equation that describes this model is given as follows \cite{Johnson-1983}:
+The equation that describes this model is given as follows \cite{jia2021modified}:
 \begin{equation}
@@
 
-The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
+The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{zeng2022constitutive}.
 This method allows sequentially obtaining the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
@@
 Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering only all the curves at $T=T_0$ then gives $C=0.3404$.
-Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the previously identified parameters and gives $m=0.7057$.
+Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the parameters $A, B, C, n$ and gives $m=0.7057$.
 All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.
@@
 For the JC model, $\MARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
-As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
-Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction, we avoided its use in our analysis.
+As reported by Phaniraj \cite{Phaniraj-2003},  the correlation coefficient ($\R$) is not always an accurate measure to evaluate the reliability of the constitutive law espacially in the case of a highly non-linear functions because it only shows the correlation of the model with respect to the data and not its accuracy.
+Therefore, a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction, we avoided its use in our analysis.
 
@@
 The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experiments.
-In the JC model, the parameters are considered separately, while in MZA, they are considered simultaneously, and for that formulation, MZA is preferred to the JC model \cite{Hull-2011}.
+In the JC model, the parameters are considered separately, while in MZA, they are considered simultaneously, and for that formulation, MZA is preferred to the JC model \cite{zhu2022thermal}.
 However, the original form of the ZA model has some limitations due to the fact that it is considered as a two terms function (thermal and athermal functions), and to improve the formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
@@
 
-The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEM codes, although its parameters can more easily be determined than those of the JC or MZA models.
+The Hansel-Spittel model \cite{savaedi2022review} is one of the least known models in terms of integration in FEM codes, although its parameters can more easily be determined than those of the JC or MZA models.
 Programming a simple identification script is sufficient to identify its parameters for a given material.
@@
 
-The Arrhenius type model \cite{Sellars-1966} is one of the most used models in the framework of material forming, especially when it comes to studying the material microstructure.
+The Arrhenius type model \cite{zhou2022hot} is one of the most used models in the framework of material forming, especially when it comes to studying the material microstructure.
 The model takes into account the physical phenomena describing the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ expressed as power law, exponential law and hyperbolic sine.
@@
 \end{equation}
-where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent on the material.
+where $Z$ is the Zenner-Hollomon parameter \cite{liu2019effect}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent on the material.
 The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperatures by the regression method.
@@
 Because of their predictive capacity and adaptability, Artificial Neural Networks (ANNs) are increasingly widely used today in many scientific fields.
-Their operation is based on a learning process during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine learning process.
+Their operation is based on a training process during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine training process.
 
@@
 The first is the ability to classify data into different groups, and for example, to distinguish between images of cats and dogs.
-The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after learning, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by the previously identified analytical models.
+The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after training, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by the above identified analytical models.
 The main difference is that this approximation is not linked to a fixed mathematical formulation (as in JC, MZA, AR, HS and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer, and the activation functions associated with the neurons of the network.
@@
 
-After some tests of different types of network architectures, and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer give the best compromise between prediction, learning time and model compactness.
+After some tests of different types of network architectures, and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer give the best compromise between prediction, training time and model compactness.
 From a global architecture point of view, the input layer is composed of $3$ neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
@@
 The training data were those from the tests presented in Section \ref{sec:ComTestResults}, and were composed of $21,000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
-The learning was performed on the basis of $5,000$ epochs of the experimental data set.
+The training was performed on the basis of $5,000$ epochs of the experimental data set.
 $40$ minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allowed to obtain the converged parameters of the ANN model.
@@
 \end{figure}
-As can be seen in this figure, after $5,000$ epochs, we can consider that we have reached a stationary state of the model learning, and that it is useless to continue with the learning phase.
+As can be seen in this figure, after $5,000$ epochs, we can consider that we have reached a stationary state of the model training, and that it is useless to continue with the training phase.
 
-Once the learning phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data similarly to what is done with analytical models.
+Once the training phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data similarly to what is done with analytical models.
 One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
@@
 
-As for the analytical models presented previously, Figure \ref{fig:CompExp-3-15-7-1-sigmoid} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
+As for the above considered analytical models, Figure \ref{fig:CompExp-3-15-7-1-sigmoid} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
 \begin{figure}[!ht]
@@
 For the ANN model, $\MARE=0.62~\%$ and $\RMSE=0.38~\MPa$ which is excellent.
-This model can be used to simulate the hot deformation of this type of alloy with much greater fidelity to the actual material behavior than the analytical models presented previously.
+This model can be used to simulate the hot deformation of this type of alloy with much greater reliability to the actual material behavior than the analytical models presented in the above sections.
 
@@
 \end{table}
-From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.
+From the Table \ref{tab:Errors}, we can see that the ANN model has a much better predictive capacity than all the analytical models presented in the above sections.
 Globally, the values of $\MARE$ and $\RMSE$ are $6$ times lower than with the best of the analytical models, \ie, the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.
@@
 
-In order to better compare the performances of the models presented previously (the 5 analytical models and the ANN based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
-The identification of the previously presented models is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
-To test the learning capacity and fidelity of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
+In order to better compare the performances of the above analysed models (the 5 analytical models and the ANN based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
+The identification of the above analysed models is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
+To test the training capacity and reliability of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
 
@@
 
-From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results, with a higher fidelity for the AR and ANN models compared to the other two models.
+From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results, with a higher reliability for the AR and ANN models compared to the other two models.
 Table \ref{tab:IntVal} shows a quantitative comparison on $\MARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates, on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
@@
 
-This shows the superior fidelity of the ANN model over to the 5 analytical models presented in this study both in terms of the interpolation capability of the model and of the overall behavior.
+This shows the superior reliability of the ANN model over to the 5 analytical models presented in this study both in terms of the interpolation capability of the model and of the overall behavior.
 
@@
 For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0.01, 0.1, 1, 2]~\ps$.
-The strain rate omitted in this analysis therefore has the highest value, which restricts the learning domain.
+The strain rate omitted in this analysis therefore has the highest value, which restricts the training domain.
 
@@
 
-The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models than for the other two models.
+The other 4 models, HS, AR, PTM and ANN, give better results with higher reliability for the AR and ANN models than for the other two models.
 Table \ref{tab:ExtVal} shows a comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
@@
 Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-The analytical models selected for this study were the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model \cite{TizeMha-2022}.
+The analytical models selected for this study were the Johnson-Cook (JC) model \cite{jia2021modified}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{savaedi2022review}, the Arrhenius (AR) model \cite{zhou2022hot} and the PTM model \cite{TizeMha-2022}.
 The ANN model selected is the one introduced by Pantalé \eal \cite{Pantale-2021}.
@@
 Identifying the parameters of an ANN model from experimental data requires more time than identifying the parameters of analytical models (about 40 minutes on a working laptop), but as shown by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, implementing an ANN model in a computational code is straightforward.
-Therefore, we recommend using the ANN model when conducting a study involving this alloy under the experimental conditions examined herein.
-
-For future work perspectives, we will develop another ANN model to characterize the microstructure in terms of DRX and the formation of phases such as ferrite, bainite and martensite, for example.
-This ANN model can then be compared to the most commonly used classical models such as the JMAK model.
-Then, these ANN models will be implemented in FEM software such as Abaqus or Forge in order to validate them.
 
@@
 \begin{itemize}
-\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid an ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, Lu-2011-ANN}.
+\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid an ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, stoffel2020deep}.
 Therefore, the three components of the input vector $\overrightarrow{x}$ are obtained from the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$ and the temperature $T$ using the following expressions:

### 2023-01-23 Article.tex
Update latex and Bibliography files

@@
 \author[ETS]{Prashant Dhondapure}
-\author[LGP]{Olivier Pantalé\corref{cor1}}
 \author[ETS]{Mohammad Jahazi}
 \author[LGP]{Amèvi Tongne}
+\author[LGP]{Olivier Pantalé\corref{cor1}}
 \ead{Olivier.Pantale@enit.fr}
@@
 A large number of phenomenological, semi-empirical, or physical models \cite{jia2022thermo, costa2016study, rudnytskyj2020constitutive, Pantale-2021} have been developed.
-Among these, the Johnson-Cook (JC) \cite{jia2021modified}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{sim2022modified} models are the best known and most widely available in FEA codes.
+Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
 Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
-To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, liu2021modified, jia2022thermo1, bai2022comparison, zhu2022constitutive}.
+To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, liu2021modified, jia2022thermo1, bai2022comparison, zhu2022constitutive, jia2021modified, sim2022modified}.
 However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
@@
 Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model, hence its inability to describe the phenomenon of softening induced by temperature.
-The equation that describes this model is given as follows \cite{jia2021modified}:
+The equation that describes this model is given as follows \cite{Johnson-1983}:
 \begin{equation}
@@
 As reported by Phaniraj \cite{Phaniraj-2003},  the correlation coefficient ($\R$) is not always an accurate measure to evaluate the reliability of the constitutive law espacially in the case of a highly non-linear functions because it only shows the correlation of the model with respect to the data and not its accuracy.
-Therefore, a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction, we avoided its use in our analysis.
+A good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction, we therefore avoided its use in our analysis.
 
@@
 
-The Hansel-Spittel model \cite{savaedi2022review} is one of the least known models in terms of integration in FEM codes, although its parameters can more easily be determined than those of the JC or MZA models.
+The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEM codes, although its parameters can more easily be determined than those of the JC or MZA models.
 Programming a simple identification script is sufficient to identify its parameters for a given material.
@@
 
-The Arrhenius type model \cite{zhou2022hot} is one of the most used models in the framework of material forming, especially when it comes to studying the material microstructure.
+The Arrhenius type model \cite{Sellars-1966} is one of the most used models in the framework of material forming, especially when it comes to studying the material microstructure.
 The model takes into account the physical phenomena describing the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ expressed as power law, exponential law and hyperbolic sine.
@@
 \end{equation}
-where $Z$ is the Zenner-Hollomon parameter \cite{liu2019effect}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent on the material.
+where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent on the material.
 The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperatures by the regression method.
@@
 Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-The analytical models selected for this study were the Johnson-Cook (JC) model \cite{jia2021modified}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{savaedi2022review}, the Arrhenius (AR) model \cite{zhou2022hot} and the PTM model \cite{TizeMha-2022}.
+The analytical models selected for this study were the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model \cite{TizeMha-2022}.
 The ANN model selected is the one introduced by Pantalé \eal \cite{Pantale-2021}.

### 2023-01-26 Article.tex
Final adds to the Latex file before submission

@@
 % !TeX encoding = UTF-8
-\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
+%% 
+%% Copyright 2007-2020 Elsevier Ltd
+%% 
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%% 
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%%
+
+%% Template article for Elsevier's document class `elsarticle'
+%% with numbered style bibliographic references
+%% SP 2008/03/01
+%%
+%% 
+%%
+%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
+%%
+%%
+\documentclass[preprint,12pt,sort&compress]{elsarticle}
+%\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
+
 \usepackage[T1]{fontenc}
@@
 
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  \addtocounter{footnote}{-1}%
+  \endgroup
+}
+
 \makeatother
@@
 %
-\usepackage{soul}
-\usepackage{color}
-\definecolor{VWyellow}{RGB}{255,251,150}
-\sethlcolor{VWyellow}
-
-\DeclareRobustCommand{\OP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
-\DeclareRobustCommand{\OPP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
+%\usepackage{soul}
+%\usepackage{color}
+%\definecolor{VWyellow}{RGB}{255,251,150}
+%\sethlcolor{VWyellow}
+%
+%\DeclareRobustCommand{\OP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
+%\DeclareRobustCommand{\OPP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
 
 \begin{document}
+
 \begin{frontmatter}
@@
 
-\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, 65016, France}
-\address[ETS]{École de technologie supérieure, 1100 Notre Dame St. W., Montreal, QC H3C 1K3, Canada}
+\affiliation[LGP]{organization={Laboratoire Génie de Production, INP/ENIT, Université de Toulouse},
+             addressline={47 Av d'Azereix},
+             city={Tarbes},
+             postcode={65016},
+             state={},
+             country={France}}
+
+\affiliation[ETS]{organization={École de technologie supérieure},
+             addressline={1100 Notre Dame St. W.},
+             city={Montreal},
+             postcode={QC H3C 1K3},
+             state={},
+             country={Canada}}
 
 \begin{abstract}
-In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
+\blfootnote{This article is an open access article distributed under the terms and
+conditions of the Creative Commons Attribution (CC BY) license (\href{http://creativecommons.org/licenses/by/4.0}{http://creativecommons.org/licenses/by/4.0}).} In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
 To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
@@
 \end{abstract}
+
+%%Graphical abstract
+\begin{graphicalabstract}
+%\includegraphics{grabs}
+\end{graphicalabstract}
+
+%%Research highlights
+\begin{highlights}
+\item Analytical and ANN based flow laws are identified from hot compression of medium carbon steel alloy.
+\item Comparison of models is done using error measure with regard to the experiments.
+\item The efficiency of each model is evaluated using interpolation and extrapolation techniques.
+\item The Arrhenius model is the more accurate of all analytical models.
+\item The ANN based model is the most accurate of all proposed models.
+\end{highlights}
 
@@
 %----------------------------------------------------------------------------------
-\section{Interpolation and Extrapolation Capability of Analytical and ANN Models \label{sec:IntExt}}
+\section{Interpolation and Extrapolation Capability of Models\label{sec:IntExt}}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\section{Conclusions and future work\label{sec:Conclusion}}
+\section{Conclusions\label{sec:Conclusion}}
 %----------------------------------------------------------------------------------
@@
 Identifying the parameters of an ANN model from experimental data requires more time than identifying the parameters of analytical models (about 40 minutes on a working laptop), but as shown by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, implementing an ANN model in a computational code is straightforward.
+
+\section*{Data availability}
+The raw/processed data required to reproduce these findings cannot be shared at this time due to privacy and ethical concerns.
+
+\section*{Declaration of Competing Interest}
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+
+\section*{Authors Contribution}
+\textbf{Pierre Tize Mha}: Conceptualization, Data Curation, Software, Writing - Original Draft;
+\textbf{Prashant Dhondapure}: Investigation, Data Curation;
+\textbf{Mohammad Jahazi}: Supervision, Project administration, Funding acquisition;
+\textbf{Amèvi Tongne}: Supervision;
+\textbf{Olivier Pantalé}: Conceptualization, Methodology, Validation, Formal analysis, Software, Supervision, Visualization, Writing - Review \& Editing.
+%Conceptualization
+%Methodology
+%Software
+%Validation
+%Formal analysis
+%Investigation
+%Resources
+%Data Curation
+%Writing - Original Draft
+%Writing - Review \& Editing
+%Visualization
+%Supervision
+%Project administration
+%Funding acquisition
+
+All authors have read and agreed to the published version of the manuscript.
+
+\section*{Acknowledgements}
+The authors acknowledge Finkl Steel-Sorel Co., École de Technologie Supérieure, and École Nationale d’ingénieurs de Tarbes, France, for providing technical data, materials, and  testing facilities.
+
+\section*{Fundings}
+This work was supported by the Natural Sciences and Engineering Research Council of Canada (NSERC) in the framework of a Collaborative Research and Development project (CRD) [Grant number 5364418].
 

### 2023-01-30 Article.tex
Final Submitted Article

@@
 
-\title{Interpolation and extrapolation-based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}
+\title{Interpolation and Extrapolation Performance Measurement of Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium Carbon Steel}
 
@@
 \blfootnote{This article is an open access article distributed under the terms and
-conditions of the Creative Commons Attribution (CC BY) license (\href{http://creativecommons.org/licenses/by/4.0}{http://creativecommons.org/licenses/by/4.0}).} In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
-To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
-The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius models, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
-The Mean Absolute Relative Error ($\MARE$) and the Root Mean Square Error ($\RMSE$) values were used to quantify the predictive accuracy of the analyzed models.
-The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented a significant error, $\MARE$ of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
-The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
-To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
-The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability, with the notable superiority of the Arrhenius model over the other two.
-The Artificial Neural Networks model was, however, still the most performant among all the models.
+conditions of the Creative Commons Attribution (CC BY) license (\href{http://creativecommons.org/licenses/by/4.0}{http://creativecommons.org/licenses/by/4.0}).} 
+%In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
+%To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
+%The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius models, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
+%The Mean Absolute Relative Error ($\MARE$) and the Root Mean Square Error ($\RMSE$) values were used to quantify the predictive accuracy of the analyzed models.
+%The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented a significant error, $\MARE$ of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
+%The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
+%To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
+%The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability, with the notable superiority of the Arrhenius model over the other two.
+%The Artificial Neural Networks model was, however, still the most performant among all the models.
+In the present work, a critical analysis of the most commonly used analytical models and recently introduced ANN-based models is performed to evaluate their predictive accuracy within and outside the experimental interval used to generate them.
+The high temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800.
+The experimental flow curves were modeled using Johnson-Cook, Modified-Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and PTM models, as well as an ANN model.
+The mean absolute relative error and root mean square error values were used to quantify the predictive accuracy of the models analyzed.
+The results indicated that the Johnson-Cook and Modified-Zerilli-Armstrong models had a significant error, while the Hansel-Spittel, PTM, and Arrhenius models were able to predict the behavior of this alloy.
+The ANN model showed excellent agreement, with less than a 0.62\% error, between the predicted and experimental flow curves.
+To validate the performance, the ability to interpolate and extrapolate the experimental data was also tested.
+The Hansel-Spittel, PTM, and Arrhenius models showed good interpolation and extrapolation capabilities.
+However, the ANN model was the most powerful of all the models.
 \end{abstract}
 
-%%Graphical abstract
-\begin{graphicalabstract}
-%\includegraphics{grabs}
-\end{graphicalabstract}
-
-%%Research highlights
-\begin{highlights}
-\item Analytical and ANN based flow laws are identified from hot compression of medium carbon steel alloy.
-\item Comparison of models is done using error measure with regard to the experiments.
-\item The efficiency of each model is evaluated using interpolation and extrapolation techniques.
-\item The Arrhenius model is the more accurate of all analytical models.
-\item The ANN based model is the most accurate of all proposed models.
-\end{highlights}
+%%%Graphical abstract
+%\begin{graphicalabstract}
+%\includegraphics[width=\columnwidth]{Figures/GraphicalAbstract}
+%\end{graphicalabstract}
+%
+%%%Research highlights
+%\begin{highlights}
+%\item Analytical and ANN based flow laws are identified from hot compression of medium carbon steel alloy.
+%\item Comparison of models is done using error measure with regard to the experiments.
+%\item The efficiency of each model is evaluated using interpolation and extrapolation techniques.
+%\item The Arrhenius model is the more accurate of all analytical models.
+%\item The ANN based model is the most accurate of all proposed models.
+%\end{highlights}
 
 \begin{keyword}
-Johnson-Cook \sep Zerilli-Armstrong \sep Arrhenius \sep Hansel-Spittel \sep Artificial Neural Network \sep interpolation \sep extrapolation
+Artificial Neural Network\sep Constitutive flow Law\sep Analytical flow law\sep Interpolation\sep Extrapolation\sep Gleeble
 \end{keyword}
@@
 {Figures/ANN-scheme-2HL}
-\caption{Multi-layer Artificial Neural Network architecture}
+\caption{Two hidden layers Artificial Neural Network architecture}
 \label{fig:ANN-2HL}

### 2023-02-06 Article.tex
Transfer to MDPI/Metals

--- 2023-01-23 Article.tex
@@
-% !TeX encoding = UTF-8
-\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\pagestyle{headings}
-\usepackage{amsthm}
+%  LaTeX support: latex@mdpi.com 
+%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
+
+%=================================================================
+\documentclass[metals,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
+The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
+This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
+For preprints.org, the editorial staff will make this change immediately prior to posting.
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.
+
+%=================================================================
+% MDPI internal commands - do not modify
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
+\pubvolume{1}
+\issuenum{1}
+\articlenumber{0}
+\pubyear{2023}
+\copyrightyear{2023}
+%\externaleditor{Academic Editor: Firstname Lastname}
+\datereceived{ } 
+\daterevised{ } % Comment out if no revised date
+\dateaccepted{ } 
+\datepublished{ } 
+%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
+%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
+\hreflink{https://doi.org/} % If needed use \linebreak
+%\doinum{}
+%\pdfoutput=1 % Uncommented for upload to arXiv.org
+
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
+% cleveref: load \crefname definitions after \begin{document}
+
 \usepackage{gensymb}
+\usepackage{accents}
 \usepackage{xspace}
-\usepackage{amsmath}
-\usepackage{accents}
-\usepackage{multirow}
-\usepackage{arydshln}
-\usepackage{xcolor}
-\usepackage{amssymb}
 \usepackage{subcaption}
-\usepackage{adjustbox}
-\usepackage{placeins}
-\usepackage{ulem}
-\usepackage[colorlinks = true]{hyperref}
-
-% To have Times only in text not maths
-\renewcommand{\rmdefault}{ptm}
-
-\makeatletter
-
-\theoremstyle{plain}
-\newtheorem{thm}{\protect\theoremname}
-
-% specify here the journal
-\journal{Materials \& Design}
-
-% use this if you need line numbers
-\usepackage{lineno}
-
-\makeatother
-
-\usepackage{babel}
-\providecommand{\theoremname}{Theorem}
-
 \DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
@@
 
-% This is used to add comments into the text
-%
-% Will have to be removed from final version
-%
-\usepackage{soul}
-\usepackage{color}
-\definecolor{VWyellow}{RGB}{255,251,150}
-\sethlcolor{VWyellow}
+%=================================================================
+% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
 
-\DeclareRobustCommand{\OP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
-\DeclareRobustCommand{\OPP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{Interpolation and Extrapolation Performance Measurement of Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium Carbon Steel}
 
+% MDPI internal command: Title for citation in the left column
+\TitleCitation{Interpolation and Extrapolation Performance Measurement of Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium Carbon Steel}
+
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
+\Author{Pierre Tize Mha$^{1}$, Prashant Dhondapure$^{2}$, Mohammad Jahazi$^{2}$\orcidB{}, Amèvi Tongne$^{1}$, Olivier Pantalé *$^{1}$\orcidA{}}
+
+%\longauthorlist{yes}
+
+% MDPI internal command: Authors, for metadata in PDF
+\AuthorNames{Pierre Tize Mha, Prashant Dhondapure, Mohammad Jahazi, Amèvi Tongne, Olivier Pantalé}
+
+% MDPI internal command: Authors, for citation in the left column
+\AuthorCitation{P. Tize Mha, P. Dhondapure, M. Jahazi, A. Tongne, O. Pantalé}
+% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{
+$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France\\
+$^{2}$ \quad École de Technologie Supérieure, 1100 Notre Dame St. W., QC H3C 1K3, Montréal, Canada}
+
+% Contact information of the corresponding author
+\corres{Correspondence: Olivier.Pantale@enit.fr; Tel.: +33-562442933}
+
+% Current address and/or shared authorship
+%\firstnote{Current address: Affiliation 3.} 
+%\secondnote{These authors contributed equally to this work.}
+% The commands \thirdnote{} till \eighthnote{} are available for further notes
+
+%\simplesumm{} % Simple summary
+
+%\conference{} % An extended version of a conference paper
+
+% Abstract (Do not insert blank lines, i.e. \\) 
+\abstract{In the present work, a critical analysis of the most commonly used analytical models and recently introduced ANN-based models is performed to evaluate their predictive accuracy within and outside the experimental interval used to generate them.
+The high temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800.
+The experimental flow curves were modeled using Johnson-Cook, Modified-Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and PTM models, as well as an ANN model.
+The mean absolute relative error and root mean square error values were used to quantify the predictive accuracy of the models analyzed.
+The results indicated that the Johnson-Cook and Modified-Zerilli-Armstrong models had a significant error, while the Hansel-Spittel, PTM, and Arrhenius models were able to predict the behavior of this alloy.
+The ANN model showed excellent agreement, with less than a 0.62\% error, between the predicted and experimental flow curves.
+To validate the performance, the ability to interpolate and extrapolate the experimental data was also tested.
+The Hansel-Spittel, PTM, and Arrhenius models showed good interpolation and extrapolation capabilities.
+However, the ANN model was the most powerful of all the models.}
+
+% Keywords
+\keyword{Artificial Neural Network; Constitutive flow Law; Analytical flow law; Interpolation; Extrapolation; Gleeble}
+
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{J0101}
+%\MSC{}
+%\JEL{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Diversity
+%\LSID{\url{http://}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Applied Sciences
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Data
+%\dataset{DOI number or link to the deposited data set if the data set is published separately.
+If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors.
+In this case, please submit the data set as a supplement.}
+%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Toxins
+%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Encyclopedia
+%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Advances in Respiratory Medicine
+%\addhighlights{yes}
+%\renewcommand{\addhighlights}{%
+
+%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
+Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it.
+Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
+%\textbf{What are the main findings?}
+% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
+% \item First bullet.
+% \item Second bullet.
+% \end{itemize}\vspace{3pt}
+%\textbf{What is the implication of the main finding?}
+% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
+% \item First bullet.
+% \item Second bullet.
+% \end{itemize}
+%}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
-\begin{frontmatter}
-
-\title{Interpolation and extrapolation-based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}
-
-\author[LGP]{Pierre Tize Mha}
-\author[ETS]{Prashant Dhondapure}
-\author[ETS]{Mohammad Jahazi}
-\author[LGP]{Amèvi Tongne}
-\author[LGP]{Olivier Pantalé\corref{cor1}}
-\ead{Olivier.Pantale@enit.fr}
-\ead[url]{http://www.enit.fr}
-
-\cortext[cor1]{Corresponding author}
-
-\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, 65016, France}
-\address[ETS]{École de technologie supérieure, 1100 Notre Dame St. W., Montreal, QC H3C 1K3, Canada}
-
-\begin{abstract}
-In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
-To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
-The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius models, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
-The Mean Absolute Relative Error ($\MARE$) and the Root Mean Square Error ($\RMSE$) values were used to quantify the predictive accuracy of the analyzed models.
-The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented a significant error, $\MARE$ of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
-The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
-To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
-The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability, with the notable superiority of the Arrhenius model over the other two.
-The Artificial Neural Networks model was, however, still the most performant among all the models.
-\end{abstract}
-
-\begin{keyword}
-Johnson-Cook \sep Zerilli-Armstrong \sep Arrhenius \sep Hansel-Spittel \sep Artificial Neural Network \sep interpolation \sep extrapolation
-\end{keyword}
-
-\end{frontmatter}
-\linenumbers
 
@@
 \begin{tabular}{lccccccc}
-	\hline
-	Element &  C   &  Mn  &  Mo  &  Si  &  Ni  &  Cr  &  Cu  \\ \hline
-	Wt~\%   & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17 \\ \hline
+	\toprule
+	\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\ \midrule
+	\textbf{Wt~\%}   &   $0.30$   &   $0.89$    &   $0.52$    &   $0.34$    &   $0.68$    &   $1.86$    &   $0.17$    \\ \bottomrule
 \end{tabular}
@@
 \begin{tabular}{ccccc}
-	\hline
-	$A~(\MPa)$ & $B~(\MPa)$ &   $n$    &   $C$    &   $m$    \\
-	$13.5143$  &  $21.816$  & $0.0746$ & $0.3404$ & $0.7057$ \\ \hline
+	\toprule
+	\boldmath{$A~(\MPa)$} & \boldmath{$B~(\MPa)$} & \boldmath{$n$} & \boldmath{$C$} & \boldmath{$m$} \\ \midrule
+	      $13.5143$       &       $21.816$        &    $0.0746$    &    $0.3404$    &    $0.7057$    \\ \bottomrule
 \end{tabular}
@@
 
-The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most widely used models implemented in many FEM codes such as the Abaqus software.
+The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most widely used models implemented in many FEA codes such as the Abaqus software.
 The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experiments.
@@
 \begin{tabular}{ccccccc}
-	\hline
-	  $C_1$   &   $C_2$   &         $C_3$          &         $C_4$          &  $C_5$   &         $C_6$         &   $n$    \\
-	$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$ \\ \hline
+	\toprule
+	\boldmath{$C_1$} & \boldmath{$C_2$} &    \boldmath{$C_3$}    &    \boldmath{$C_4$}    & \boldmath{$C_5$} &   \boldmath{$C_6$}    & \boldmath{$n$} \\ \midrule
+	   $13.5143$     &    $21.2591$     & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ &     $0.1389$     & $1.495\times 10^{-4}$ &    $0.0621$    \\ \bottomrule
 \end{tabular}
@@
 
-The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEM codes, although its parameters can more easily be determined than those of the JC or MZA models.
+The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEA codes, although its parameters can more easily be determined than those of the JC or MZA models.
 Programming a simple identification script is sufficient to identify its parameters for a given material.
@@
 \begin{tabular}{ccccc}
-	\hline
-	        $A$          &         $m_1$          &   $m_2$   &        $m_3$         &         $m_4$         \\
-	$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$  &      $-0.0868$       & $2.2688\times10^{-4}$ \\ \hline
-	                     &         $m_5$          &   $m_6$   &        $m_7$         &         $m_8$         \\
-	                     & $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ &          $0$          \\ \hline
+	\toprule
+	   \boldmath{$A$}    &    \boldmath{$m_1$}    & \boldmath{$m_2$} &   \boldmath{$m_3$}   &   \boldmath{$m_4$}    \\
+	$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ &     $0.2641$     &      $-0.0868$       & $2.2688\times10^{-4}$ \\ \midrule
+	                     &    \boldmath{$m_5$}    & \boldmath{$m_6$} &   \boldmath{$m_7$}   &   \boldmath{$m_8$}    \\
+	                     & $-4.2163\times10^{-4}$ &    $-0.0561$     & $2.264\times10^{-4}$ &          $0$          \\ \bottomrule
 \end{tabular}
@@
 \begin{tabular}{llll}
-	\hline
-	\multicolumn{1}{c}{$\alpha_i$}  & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}  \\ \hline
+	\toprule
+	\multicolumn{1}{c}{\boldmath{$\alpha_i$}}  & \multicolumn{1}{c}{\boldmath{$Q_i~(\times 10^{-6})$}} & \multicolumn{1}{c}{\boldmath{$\ln\!A_i$}} & \multicolumn{1}{c}{\boldmath{$n_i$}}  \\ \midrule
 	$\alpha_0=0.0407$               & $Q_0=0.467$                                & $A_0=35.8092$                  & $n_0=4.8217$               \\
@@
 	$\alpha_8=952.0619$             & $Q_8=-3.9394\times 10^{3}$                 & $A_8=-2.9725\times 10^{5}$     & $n_8=1.0239\times 10^{5}$  \\
-	$\alpha_9=-267.4994$            & $Q_9=1.397\times 10^{3}$                   & $A_9=1.0759\times 10^{5}$      & $n_9=-2.9621\times 10^{4}$ \\ \hline
+	$\alpha_9=-267.4994$            & $Q_9=1.397\times 10^{3}$                   & $A_9=1.0759\times 10^{5}$      & $n_9=-2.9621\times 10^{4}$ \\ \bottomrule
 \end{tabular}
@@
 \begin{tabular}{llll}
-	\hline
-	\multicolumn{1}{c}{$A_i$} & \multicolumn{1}{c}{$B_i$} & \multicolumn{1}{c}{$C_0^i$} & \multicolumn{1}{c}{$C_1^i$} \\ \hline
+	\toprule
+	\multicolumn{1}{c}{\boldmath{$A_i$}} & \multicolumn{1}{c}{\boldmath{$B_i$}} & \multicolumn{1}{c}{\boldmath{$C_0^i$}} & \multicolumn{1}{c}{\boldmath{$C_1^i$}}  \\ \midrule
 	$A_0=16.8529$ & $B_0=-3.5418\times 10^{-3}$ & $C_0^0=0.1608$ & $C_1^0=-1.9037\times 10^{-5}$ \\
@@
 	$A_4=-5.5176\times 10^{3}$ & $B_4=-0.4988$ & $C_0^4=15.25$ & $C_1^4=0.0609$ \\
-	$A_5=2.4058\times 10^{3}$ & $B_5=0.3211$ & $C_0^5=-6.587$ & $C_1^5=-0.0413$ \\ \hline
+	$A_5=2.4058\times 10^{3}$ & $B_5=0.3211$ & $C_0^5=-6.587$ & $C_1^5=-0.0413$ \\ \bottomrule
 \end{tabular}
@@
 Once the training phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data similarly to what is done with analytical models.
-One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEM code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
+One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
 For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix.
@@
 \begin{tabular}{lcccccc}
-	\hline
-	Coefficients  &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
+	\toprule
+	\textbf{Coefficients}  &   \textbf{JC}    &   \textbf{MZA}   &   \textbf{HS}   &   \textbf{AR}   &  \textbf{PTM}   &  \textbf{ANN}   \\ \midrule
 	$\MARE(\%)$   & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
-	$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \hline
+	$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \bottomrule
 \end{tabular}
@@
 \begin{tabular}{llcccccc}
-	\hline
-	Strain rate & Coefficients & JC & MZA & HS & AR & PTM & ANN \\ \hline
+	\toprule
+	\textbf{Strain rate} & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\ \midrule
 	\mr{2}{id. $\mdot\varepsilon$} & $\MARE(\%)$ & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
-	 & $\RMSE(\MPa)$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
+	 & $\RMSE(\MPa)$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \midrule
 	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\MARE(\%)$ & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
-	 & $\RMSE(\MPa)$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
+	 & $\RMSE(\MPa)$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \midrule
 	\mr{2}{all $\mdot\varepsilon$} & $\MARE(\%)$ & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
-	 & $\RMSE(\MPa)$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
+	 & $\RMSE(\MPa)$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \bottomrule
 \end{tabular}
@@
 \begin{tabular}{llcccccc}
-	\hline
-	Strain rate & Coefficients & JC & MZA & HS & AR & PTM & ANN \\ \hline
+	\toprule
+	\textbf{Strain rate}             & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\ \midrule
 	\mr{2}{id. $\mdot\varepsilon$}   & $\MARE(\%)$           &   $13.09$   &   $19.09$    &   $7.30$    &   $4.03$    &    $4.34$    &    $0.61$    \\
-	 & $\RMSE(\MPa)$ & $9.86$ & $16.26$ & $3.36$ & $2.32$ & $3.63$ & $0.32$ \\ \hline
+	                                 & $\RMSE(\MPa)$         &   $9.86$    &   $16.26$    &   $3.36$    &   $2.32$    &    $3.63$    &    $0.32$    \\ \midrule
 	\mr{2}{$\mdot\varepsilon=5~\ps$} & $\MARE(\%)$           &   $20.16$   &   $24.27$    &   $7.73$    &   $3.53$    &   $11.46$    &    $3.87$    \\
-	 & $\RMSE(\MPa)$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ \hline
+	                                 & $\RMSE(\MPa)$         &   $20.73$   &   $25.95$    &   $7.83$    &   $4.02$    &   $12.91$    &    $5.84$    \\ \midrule
 	\mr{2}{all $\mdot\varepsilon$}   & $\MARE(\%)$           &   $15.12$   &   $25.87$    &   $7.12$    &   $3.86$    &    $5.34$    &    $1.09$    \\
-	 & $\RMSE(\MPa)$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$ & $2.40$ \\ \hline
+	                                 & $\RMSE(\MPa)$         &   $12.36$   &   $18.24$    &   $4.43$    &   $2.68$    &    $6.23$    &    $2.40$    \\ 
+	                                 \bottomrule
 \end{tabular}
@@
 
-\bibliographystyle{elsarticle-num}
-\bibliography{Bibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{6pt}
 
-%----------------------------------------------------------------------------------
-\section*{Appendix\label{sec:Appendix}}
-%----------------------------------------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
+
+% Only for the journal Methods and Protocols:
+% If you wish to submit a video article, please do so with any other supplementary material.
+% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
+A supporting video article is available at doi: link.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{
+Conceptualization, P.T.M. and O.P.;
+methodology, O.P.;
+software, P.T.M. and O.P.;
+validation, O.P.;
+formal analysis, O.P.;
+investigation, P.D.;
+resources, P.D. and M.J.;
+data curation, P.T.M. and P.D.;
+writing---original draft preparation, P.T.M.;
+writing---review and editing, O.P.;
+visualization, O.P.;
+supervision, M.J., A.T. and O.P.;
+project administration, M.J.;
+funding acquisition, M.J. 
+All authors have read and agreed to the published version of the manuscript.}
+
+\funding{This work was supported by the Natural Sciences and Engineering Research Council of Canada (NSERC) in the framework of a Collaborative Research and Development project (CRD) [Grant number 5364418].}
+
+%\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
+You might choose to exclude this statement if the study did not require ethical approval.
+Please note that the Editorial Office might ask you for further information.
+Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans.
+OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals.
+OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}
+
+%\informedconsent{Any research article describing a study involving humans should contain this statement.
+Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
+You might also choose to exclude this statement if the study did not involve humans.
+%
+%Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
+Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
+
+\dataavailability{The raw/processed data required to reproduce these findings cannot be shared at this time due to privacy and ethical concerns.}
+
+\acknowledgments{The authors acknowledge Finkl Steel-Sorel Co., École de Technologie Supérieure, and École Nationale d’Ingénieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}
+
+\conflictsofinterest{The authors declare no conflict of interest.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional
+%\sampleavailability{Samples of the compounds ... are available from the authors.}
+
+%% Only for journal Encyclopedia
+%\entrylink{The Link to this entry published on the encyclopedia platform.}
+
+\abbreviations{Abbreviations}{
+The following abbreviations are used in this manuscript:\\
+
+\noindent
+\begin{tabular}{@{}ll}
+	ANN & Artificial Neural Network  \\
+	AR  & Arrhenius                  \\
+	CPU & Central Processing Unit    \\
+	DRV & Dynamic Recovery\\
+	DRX & Dynamic Recrystallization  \\
+	FEA & Finite Element Analysis    \\
+	HS  & Hansel-Spittel             \\
+	JC  & Johnson-Cook               \\
+	MZA & Modified Zerilli-Armstrong \\
+	WH  & Work Hardening             \\
+	ZA  & Zerilli-Armstrong         
+\end{tabular}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional
+\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\appendixstart
+\appendix
+\section[\appendixname~\thesection]{}\label{sec:Appendix}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{adjustwidth}{-\extralength}{0cm}
+%\printendnotes[custom] % Un-comment to print a list of endnotes
+
+\reftitle{References}
+
+% Please provide either the correct journal abbreviation (e.g.
+according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
+
+%=====================================
+% References, variant A: external bibliography
+%=====================================
+\bibliography{Bibliography}
+
+% If authors have biography, please use the format below
+%\section*{Short Biography of Authors}
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
+%{\textbf{Firstname Lastname} Biography of first author}
+%
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
+%{\textbf{Firstname Lastname} Biography of second author}
+
+% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
+% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
+% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
+328; \citeyear{ref-journal-3b}, p.475).
+This produces: Wong (1999, p.
+328; 2000, p.
+475)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% for journal Sci
+%\reviewreports{\\
+%Reviewer 1 comments and authors’ response\\
+%Reviewer 2 comments and authors’ response\\
+%Reviewer 3 comments and authors’ response
+%}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\PublishersNote{}
+\end{adjustwidth}
 \end{document}

### 2023-02-06 Article.tex
Small update of figure captions

@@
 The experimental flow curves were modeled using Johnson-Cook, Modified-Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and PTM models, as well as an ANN model.
-The mean absolute relative error and root mean square error values were used to quantify the predictive accuracy of the models analyzed.
+The mean absolute relative error and root-mean-square error values were used to quantify the predictive accuracy of the models analyzed.
 The results indicated that the Johnson-Cook and Modified-Zerilli-Armstrong models had a significant error, while the Hansel-Spittel, PTM, and Arrhenius models were able to predict the behavior of this alloy.
-The ANN model showed excellent agreement, with less than a 0.62\% error, between the predicted and experimental flow curves.
+The ANN model showed excellent agreement between the predicted and experimental flow curves, with an error of less than 0.62\%.
 To validate the performance, the ability to interpolate and extrapolate the experimental data was also tested.
@@
 \includegraphics[width=\columnwidth]{Figures/CompExp-JC-6}
-\caption{Comparison between the experimental flow stresses and those predicted by the JC model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson-Cook model}
 \label{fig:CompExp-JC-6}
@@
 {Figures/CompExp-MZA-6}
-\caption{Comparison between the experimental flow stresses and those predicted by the MZA model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Modified Zerilli-Armstrong model}
 \label{fig:CompExp-MZA-6}
@@
 {Figures/CompExp-HS-6}
-\caption{Comparison between the experimental flow stresses and those predicted by the HS model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Hansel-Spittel model}
 \label{fig:CompExp-HS-6}
@@
 {Figures/CompExp-AR-6}
-\caption{Comparison between the experimental flow stresses and those predicted by the AR model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Arrhenius model}
 \label{fig:CompExp-AR-6}
@@
 {Figures/CompExp-PTM-6}
-\caption{Comparison between the experimental flow stresses and those predicted the PTM model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the PTM model}
 \label{fig:CompExp-PTM-6}
@@
 {Figures/CompExp-3-15-7-1-sigmoid}
-\caption{Comparison between the experimental flow stresses and those predicted by the 3-15-7-1-sigmoid ANN model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the 3-15-7-1-sigmoid ANN model}
 \label{fig:CompExp-3-15-7-1-sigmoid}
@@
 {Figures/CompInt}
-\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=1~\ps$}
 \label{fig:CompInt}
@@
 {Figures/CompExt}
-\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=5~\ps$}
 \label{fig:CompExt}

### 2023-02-10 Article.tex
Update Acknowledgments section

@@
 \newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorC}{0000-0002-5360-5121}
 
 % Authors, for the paper (add full first names)
-\Author{Pierre Tize Mha$^{1}$, Prashant Dhondapure$^{2}$, Mohammad Jahazi$^{2}$\orcidB{}, Amèvi Tongne$^{1}$, Olivier Pantalé *$^{1}$\orcidA{}}
+\Author{Pierre Tize Mha$^{1}$, Prashant Dhondapure$^{2}$, Mohammad Jahazi$^{2}$\orcidB{}, Amèvi Tongne$^{1}$\orcidC{}, Olivier Pantalé $^{1*}$\orcidA{}}
 
@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{
-$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France\\
+\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France\\
 $^{2}$ \quad École de Technologie Supérieure, 1100 Notre Dame St. W., QC H3C 1K3, Montréal, Canada}
@@
 \toprule
-	\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\ \midrule
-	\textbf{Wt~\%}   &   $0.30$   &   $0.89$    &   $0.52$    &   $0.34$    &   $0.68$    &   $1.86$    &   $0.17$    \\ \bottomrule
+\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\ 
+\midrule
+\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\ 
+\bottomrule
 \end{tabular}
@@
 \includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
-\caption{Schematic diagram of the experimental process}
+\caption{Schematic diagram of the experimental process on the Gleeble-3800 thermomechanical simulator}
 \label{fig:GleebleProcess}
@@
 \toprule
-	\boldmath{$A~(\MPa)$} & \boldmath{$B~(\MPa)$} & \boldmath{$n$} & \boldmath{$C$} & \boldmath{$m$} \\ \midrule
-	      $13.5143$       &       $21.816$        &    $0.0746$    &    $0.3404$    &    $0.7057$    \\ \bottomrule
+\boldmath{$A~(\MPa)$} & \boldmath{$B~(\MPa)$} & \boldmath{$n$} & \boldmath{$C$} & \boldmath{$m$} \\ 
+\midrule
+$13.5143$ & $21.816$ & $0.0746$ & $0.3404$ & $0.7057$ \\ 
+\bottomrule
 \end{tabular}
@@
 \toprule
-	\boldmath{$C_1$} & \boldmath{$C_2$} &    \boldmath{$C_3$}    &    \boldmath{$C_4$}    & \boldmath{$C_5$} &   \boldmath{$C_6$}    & \boldmath{$n$} \\ \midrule
-	   $13.5143$     &    $21.2591$     & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ &     $0.1389$     & $1.495\times 10^{-4}$ &    $0.0621$    \\ \bottomrule
+\boldmath{$C_1$} & \boldmath{$C_2$} & \boldmath{$C_3$} & \boldmath{$C_4$} & \boldmath{$C_5$} & \boldmath{$C_6$} & \boldmath{$n$} \\
+\midrule
+$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$ \\ 
+\bottomrule
 \end{tabular}
@@
 \boldmath{$A$} & \boldmath{$m_1$} & \boldmath{$m_2$} & \boldmath{$m_3$} & \boldmath{$m_4$} \\ 
-	$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ &     $0.2641$     &      $-0.0868$       & $2.2688\times10^{-4}$ \\ \midrule
+\midrule
+$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$ & $-0.0868$ & $2.2688\times10^{-4}$ \\ 
+\toprule
 & \boldmath{$m_5$} & \boldmath{$m_6$} & \boldmath{$m_7$} & \boldmath{$m_8$} \\ 
-	                     & $-4.2163\times10^{-4}$ &    $-0.0561$     & $2.264\times10^{-4}$ &          $0$          \\ \bottomrule
+\midrule
+& $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$ \\ 
+\bottomrule
 \end{tabular}
@@
 \toprule
-	\multicolumn{1}{c}{\boldmath{$\alpha_i$}}  & \multicolumn{1}{c}{\boldmath{$Q_i~(\times 10^{-6})$}} & \multicolumn{1}{c}{\boldmath{$\ln\!A_i$}} & \multicolumn{1}{c}{\boldmath{$n_i$}}  \\ \midrule
+\multicolumn{1}{c}{\boldmath{$\alpha_i$}} & \multicolumn{1}{c}{\boldmath{$Q_i~(\times 10^{-6})$}} & \multicolumn{1}{c}{\boldmath{$\ln\!A_i$}} & \multicolumn{1}{c}{\boldmath{$n_i$}} \\ 
+\midrule
 $\alpha_0=0.0407$ & $Q_0=0.467$ & $A_0=35.8092$ & $n_0=4.8217$ \\
@@
 $\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$ \\
-	$\alpha_9=-267.4994$            & $Q_9=1.397\times 10^{3}$                   & $A_9=1.0759\times 10^{5}$      & $n_9=-2.9621\times 10^{4}$ \\ \bottomrule
+$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$ \\ 
+\bottomrule
 \end{tabular}
@@
 \toprule
-	\multicolumn{1}{c}{\boldmath{$A_i$}} & \multicolumn{1}{c}{\boldmath{$B_i$}} & \multicolumn{1}{c}{\boldmath{$C_0^i$}} & \multicolumn{1}{c}{\boldmath{$C_1^i$}}  \\ \midrule
+\multicolumn{1}{c}{\boldmath{$A_i$}} & \multicolumn{1}{c}{\boldmath{$B_i$}} & \multicolumn{1}{c}{\boldmath{$C_0^i$}} & \multicolumn{1}{c}{\boldmath{$C_1^i$}} \\ 
+\midrule
 $A_0=16.8529$ & $B_0=-3.5418\times 10^{-3}$ & $C_0^0=0.1608$ & $C_1^0=-1.9037\times 10^{-5}$ \\
@@
 $A_4=-5.5176\times 10^{3}$ & $B_4=-0.4988$ & $C_0^4=15.25$ & $C_1^4=0.0609$ \\
-	$A_5=2.4058\times 10^{3}$ & $B_5=0.3211$ & $C_0^5=-6.587$ & $C_1^5=-0.0413$ \\ \bottomrule
+$A_5=2.4058\times 10^{3}$ & $B_5=0.3211$ & $C_0^5=-6.587$ & $C_1^5=-0.0413$ \\ 
+\bottomrule
 \end{tabular}
@@
 \toprule
-	\textbf{Coefficients}  &   \textbf{JC}    &   \textbf{MZA}   &   \textbf{HS}   &   \textbf{AR}   &  \textbf{PTM}   &  \textbf{ANN}   \\ \midrule
+\textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\ 
+\midrule
 $\MARE(\%)$ & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
-	$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \bottomrule
+$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ 
+\bottomrule
 \end{tabular}
@@
 \toprule
-	\textbf{Strain rate} & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\ \midrule
+\textbf{Strain rate} & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\ 
+\midrule
 \mr{2}{id. $\mdot\varepsilon$} & $\MARE(\%)$ & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
-	 & $\RMSE(\MPa)$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \midrule
+& $\RMSE(\MPa)$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ 
+\midrule
 \mr{2}{$\mdot\varepsilon=1~\ps$} & $\MARE(\%)$ & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
-	 & $\RMSE(\MPa)$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \midrule
+& $\RMSE(\MPa)$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ 
+\midrule
 \mr{2}{all $\mdot\varepsilon$} & $\MARE(\%)$ & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
-	 & $\RMSE(\MPa)$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \bottomrule
+& $\RMSE(\MPa)$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ 
+\bottomrule
 \end{tabular}
@@
 \toprule
-	\textbf{Strain rate}             & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\ \midrule
+\textbf{Strain rate} & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\ 
+\midrule
 \mr{2}{id. $\mdot\varepsilon$} & $\MARE(\%)$ & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$ & $0.61$ \\
-	                                 & $\RMSE(\MPa)$         &   $9.86$    &   $16.26$    &   $3.36$    &   $2.32$    &    $3.63$    &    $0.32$    \\ \midrule
+& $\RMSE(\MPa)$ & $9.86$ & $16.26$ & $3.36$ & $2.32$ & $3.63$ & $0.32$ \\ 
+\midrule
 \mr{2}{$\mdot\varepsilon=5~\ps$} & $\MARE(\%)$ & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$ \\
-	                                 & $\RMSE(\MPa)$         &   $20.73$   &   $25.95$    &   $7.83$    &   $4.02$    &   $12.91$    &    $5.84$    \\ \midrule
+& $\RMSE(\MPa)$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ 
+\midrule
 \mr{2}{all $\mdot\varepsilon$} & $\MARE(\%)$ & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$ & $1.09$ \\
@@
 
-\acknowledgments{The authors acknowledge Finkl Steel-Sorel Co., École de Technologie Supérieure, and École Nationale d’Ingénieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}
+\acknowledgments{The authors acknowledge Mr.
+Jean-Benoit Morin, Director of Metallurgy and Quality from Finkl Steel-Sorel, Dr.
+Abdelhalim Loucif from R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d’Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}
 

### 2023-03-15 Article.tex
Update after reviews from Metals journal

@@
 Thin tantalum sheets were used as lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
+\textcolor{red}{Figure \ref{fig:Inside-Gleeble3800} shows the inside of the Gleeble thermomechanical simulator with the specimen in place.
+We used 3 thermocouples soldered to the specimen to record the temperature history during the test and to ensure that the specimen was at the correct temperature prior to testing.}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-1}
+\caption{The inside of the Gleeble-3800 thermomechanical simulator with the specimen in place}
+\label{fig:Inside-Gleeble3800}
+\end{figure}
+
 As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
@@
 
-The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
+The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and \textcolor{red}{$\varepsilon=\ln\left(1+\Delta h / h_0\right)$} or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
 As raw data contains noises, the savgol\_filter method from the scipy library is used to remove noise and provide smoother data.
@@
 Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of $21,000$ data points.
+\textcolor{red}{For the identification of the parameters of all the analytical models presented in this article, we restricted the database to 35 strain values between $0.02$ and $0.7$, with a step of $0.02$ (this is illustrated in Figure \ref{fig:RawData}, where the data used correspond to the dots on the graphs).}
 The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$, but decreases with increasing temperature $T$.
@@
 
-As an example, Figure \ref{fig:Micrography} shows the medium carbon microstructures held for $5$~min at $1260\celsius$ before and after the compression phase.
+\textcolor{red}{Figure \ref{fig:Micrography}(a) shows the microstructure obtained when the sample is held at $1260\celsius$ for $5$ minutes and rapidly cooled to room temperature.
+From this image, large grains can be observed.
+On the other hand, Figure \ref{fig:Micrography}(b) shows the microstructure after compression at $1150\celsius$ with a $0.001~\text{s}^{-1}$ strain rate.
+To obtain this, the sample is heated up to $1260\celsius$, then held for $5$ minutes and cooled down to $1150\celsius$ to be held at this temperature for $1$ minute before compression.
+After compression, the sample is rapidly cooled to room temperature to preserve the microstructure.
+From this image, full recrystallization can be observed and is in correlation with Figure \ref{fig:RawData}, where after the peak, a steady stress is observed that describes the end of the recrystallization.}
+
+%As an example, Figure \ref{fig:Micrography} shows the medium carbon microstructures held for $5$~min at $1260\celsius$ before and after the compression phase.
 \begin{figure}[!ht]
@@
 \end{subfigure}
-\caption{Optical micrographs of a medium carbon steel (a) before and (b) after hot compression}
+\caption{Optical micrographs of a medium carbon steel (a) before and (b) after hot compression at $1150\celsius$ with a $0.001~\text{s}^{-1}$ strain rate.}
 \label{fig:Micrography}
 \end{figure}
-As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get austenitized grain on the one hand, and on the other hand, held for $1$ minute at $1150^\circ$C before compression with a $0.001~\text{s}^{-1}$ strain rate.
+\textcolor{red}{The material is in the single phase austenite state at all of the test temperatures examined.}
+%As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get austenitized grain on the one hand, and on the other hand, held for $1$ minute at $1150^\circ$C before compression with a $0.001~\text{s}^{-1}$ strain rate.
 The data presented in Figure \ref{fig:RawData} will be utilized in the following section to determine the parameters of the $6$ flow laws proposed and to determine which model most closely aligns with experimental results.
@@
 \begin{equation}
-\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
+\sigma^y=\left(A+B{\varepsilon^p}^{n}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
 \end{equation}
@@
 The other values are reference values: $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and thus $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
-For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$, respectively.
-
-The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{zeng2022constitutive}.
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$.
+\textcolor{red}{In our approach, the reference strain rate and reference temperature for identifying the JC model are the lowest values used during the test, however, sometimes these values do not always give the best results for the model.}
+
+The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by Zeng \eal \cite{zeng2022constitutive}.
 This method allows sequentially obtaining the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
 Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
-For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then be determined by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
+For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then be determined by considering only the first term $\left(A+B{\varepsilon^p}^{n}\right)$ in Equation (\ref{eq:Johnson-Cook}).
 Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
@@
 \end{figure}
-The JC model is unable to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several strain rate values.
+\textcolor{red}{The JC model is unable to describe the evolution of the average carbon flow stress for all strain and strain rate levels.
+The experimental flow stresses show a growth and then a decrease with strain, especially for low strain rates, while the JC model, by its formulation, only allows an increasing evolution of the flow stress $\sigma^y$ as a function of the strain whatever the strain rate.}
+%The JC model is unable to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several strain rate values.
 The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
@@
 \label{eq:MZA-model}
-\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right],
+\sigma^y = \left(C_{1}+C_{2}{\varepsilon^p}^{n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right],
 \end{equation}
@@
 \toprule
-\boldmath{$C_1$} & \boldmath{$C_2$} & \boldmath{$C_3$} & \boldmath{$C_4$} & \boldmath{$C_5$} & \boldmath{$C_6$} & \boldmath{$n$} \\
+\boldmath{$C_1~(\MPa)$} & \boldmath{$C_2~(\MPa)$} & \boldmath{$C_3$} & \boldmath{$C_4$} & \boldmath{$C_5$} & \boldmath{$C_6$} & \boldmath{$n$} \\
 \midrule
@@
 \end{figure}
-It can be seen from this figure that the MZA model as well as the JC model is not able to faithfully reproduce the experimental data at low strain rates, but is much better for high strain rates.
+\textcolor{red}{It can be seen from this figure that both the MZA and JC models are not able to faithfully reproduce the experimental data, especially at low strain rates, but they are slightly better at higher strain rates.}
+%It can be seen from this figure that the MZA model as well as the JC model is not able to faithfully reproduce the experimental data at low strain rates, but is much better for high strain rates.
 The deviation between the predicted values and the experimental values is large because this model has a problem correctly describing the softening in its formulation.
 For the MZA model, $\MARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model, as reported in \cite{TizeMha-2022}.
-
+\textcolor{red}{In addition, it can be observed that at high strain rates the MZA is not good either, even if there is no softening effect, and this can be explained by the fact that this model is formulated for quasi-static phenomena.}
 %----------------------------------------------------------------------------------
@@
 \midrule
-$\alpha_0=0.0407$ & $Q_0=0.467$ & $A_0=35.8092$ & $n_0=4.8217$ \\
-$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & $A_1=-58.822$ & $n_1=3.2814$ \\
-$\alpha_2=6.3912$ & $Q_2=7.6084$ & $A_2=740.3303$ & $n_2=71.5963$ \\
-$\alpha_3=-47.3364$ & $Q_3=-48.016$ & $A_3=-5.0493\times 10^{3}$ & $n_3=-1.9562\times 10^{3}$ \\
-$\alpha_4=220.0014$ & $Q_4=66.795$ & $A_4=1.1305\times 10^{4}$ & $n_4=1.4461\times 10^{4}$ \\
-$\alpha_5=-654.4553$ & $Q_5=468.8898$ & $A_5=2.022\times 10^{4}$ & $n_5=-5.431\times 10^{4}$ \\
-$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & $A_6=-1.5387\times 10^{5}$ & $n_6=1.1761\times 10^{5}$ \\
-$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & $A_7=3.1798\times 10^{5}$ & $n_7=-1.4882\times 10^{5}$ \\
-$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$ \\
-$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$ \\ 
+$\alpha_0=0.0407$ & $Q_0=0.467$ & \textcolor{red}{$\ln\!A_0=35.8092$} & $n_0=4.8217$ \\
+$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & \textcolor{red}{$\ln\!A_1=-58.822$} & $n_1=3.2814$ \\
+$\alpha_2=6.3912$ & $Q_2=7.6084$ & \textcolor{red}{$\ln\!A_2=740.3303$} & $n_2=71.5963$ \\
+$\alpha_3=-47.3364$ & $Q_3=-48.016$ & \textcolor{red}{$\ln\!A_3=-5.0493\times 10^{3}$} & $n_3=-1.9562\times 10^{3}$ \\
+$\alpha_4=220.0014$ & $Q_4=66.795$ & \textcolor{red}{$\ln\!A_4=1.1305\times 10^{4}$} & $n_4=1.4461\times 10^{4}$ \\
+$\alpha_5=-654.4553$ & $Q_5=468.8898$ & \textcolor{red}{$\ln\!A_5=2.022\times 10^{4}$} & $n_5=-5.431\times 10^{4}$ \\
+$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & \textcolor{red}{$\ln\!A_6=-1.5387\times 10^{5}$} & $n_6=1.1761\times 10^{5}$ \\
+$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & \textcolor{red}{$\ln\!A_7=3.1798\times 10^{5}$} & $n_7=-1.4882\times 10^{5}$ \\
+$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & \textcolor{red}{$\ln\!A_8=-2.9725\times 10^{5}$} & $n_8=1.0239\times 10^{5}$ \\
+$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & \textcolor{red}{$\ln\!A_9=1.0759\times 10^{5}$} & $n_9=-2.9621\times 10^{4}$ \\ 
 \bottomrule
@@
 \label{eq:PTM-model}
-\sigma^y = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
+\sigma^y = \left(\sum_{i=0}^{q}{A_i{\varepsilon^p}^{i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j{\varepsilon^p}^{j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l{\varepsilon^p}^{l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
 \end{equation}

### 2023-03-16 Article.tex
Final version after revision #1

@@
 Thin tantalum sheets were used as lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
-\textcolor{red}{Figure \ref{fig:Inside-Gleeble3800} shows the inside of the Gleeble thermomechanical simulator with the specimen in place.
-We used 3 thermocouples soldered to the specimen to record the temperature history during the test and to ensure that the specimen was at the correct temperature prior to testing.}
+Figure \ref{fig:Inside-Gleeble3800} shows the inside of the Gleeble thermomechanical simulator with the specimen in place.
+We used 3 thermocouples soldered to the specimen to record the temperature history during the test and to ensure that the specimen was at the correct temperature prior to testing.
 \begin{figure}[!ht]
@@
 
-The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and \textcolor{red}{$\varepsilon=\ln\left(1+\Delta h / h_0\right)$} or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
+The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(1+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
 As raw data contains noises, the savgol\_filter method from the scipy library is used to remove noise and provide smoother data.
@@
 Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of $21,000$ data points.
-\textcolor{red}{For the identification of the parameters of all the analytical models presented in this article, we restricted the database to 35 strain values between $0.02$ and $0.7$, with a step of $0.02$ (this is illustrated in Figure \ref{fig:RawData}, where the data used correspond to the dots on the graphs).}
+For the identification of the parameters of all the analytical models presented in this article, we restricted the database to 35 strain values between $0.02$ and $0.7$, with a step of $0.02$ (this is illustrated in Figure \ref{fig:RawData}, where the data used correspond to the dots on the graphs).
 The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$, but decreases with increasing temperature $T$.
@@
 
-\textcolor{red}{Figure \ref{fig:Micrography}(a) shows the microstructure obtained when the sample is held at $1260\celsius$ for $5$ minutes and rapidly cooled to room temperature.
+Figure \ref{fig:Micrography}(a) shows the microstructure obtained when the sample is held at $1260\celsius$ for $5$ minutes and rapidly cooled to room temperature.
 From this image, large grains can be observed.
@@
 After compression, the sample is rapidly cooled to room temperature to preserve the microstructure.
-From this image, full recrystallization can be observed and is in correlation with Figure \ref{fig:RawData}, where after the peak, a steady stress is observed that describes the end of the recrystallization.}
+From this image, full recrystallization can be observed and is in correlation with Figure \ref{fig:RawData}, where after the peak, a steady stress is observed that describes the end of the recrystallization.
 
@@
 \end{figure}
-\textcolor{red}{The material is in the single phase austenite state at all of the test temperatures examined.}
-%As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get austenitized grain on the one hand, and on the other hand, held for $1$ minute at $1150^\circ$C before compression with a $0.001~\text{s}^{-1}$ strain rate.
+The material is in the single phase austenite state at all of the test temperatures examined.
 The data presented in Figure \ref{fig:RawData} will be utilized in the following section to determine the parameters of the $6$ flow laws proposed and to determine which model most closely aligns with experimental results.
@@
 For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$.
-\textcolor{red}{In our approach, the reference strain rate and reference temperature for identifying the JC model are the lowest values used during the test, however, sometimes these values do not always give the best results for the model.}
+In our approach, the reference strain rate and reference temperature for identifying the JC model are the lowest values used during the test, however, sometimes these values do not always give the best results for the model.
 
@@
 \end{figure}
-\textcolor{red}{The JC model is unable to describe the evolution of the average carbon flow stress for all strain and strain rate levels.
-The experimental flow stresses show a growth and then a decrease with strain, especially for low strain rates, while the JC model, by its formulation, only allows an increasing evolution of the flow stress $\sigma^y$ as a function of the strain whatever the strain rate.}
-%The JC model is unable to describe the evolution of the flow stress of medium carbon for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several strain rate values.
+The JC model is unable to describe the evolution of the average flow stress for all strain and strain rate levels.
+The experimental flow stresses show a growth and then a decrease with strain, especially for low strain rates, while the JC model, by its formulation, only allows an increasing evolution of the flow stress $\sigma^y$ as a function of the strain independently of the strain rate value.
 The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
@@
 \end{figure}
-\textcolor{red}{It can be seen from this figure that both the MZA and JC models are not able to faithfully reproduce the experimental data, especially at low strain rates, but they are slightly better at higher strain rates.}
-%It can be seen from this figure that the MZA model as well as the JC model is not able to faithfully reproduce the experimental data at low strain rates, but is much better for high strain rates.
+It can be seen from this figure that both the MZA and JC models are not able to faithfully reproduce the experimental data, especially at low strain rates, but they are slightly better at higher strain rates.
 The deviation between the predicted values and the experimental values is large because this model has a problem correctly describing the softening in its formulation.
 For the MZA model, $\MARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model, as reported in \cite{TizeMha-2022}.
-\textcolor{red}{In addition, it can be observed that at high strain rates the MZA is not good either, even if there is no softening effect, and this can be explained by the fact that this model is formulated for quasi-static phenomena.}
+In addition, it can be observed that at high strain rates the MZA is not good either, even if there is no softening effect, and this can be explained by the fact that this model is formulated for quasi-static phenomena.
+
 %----------------------------------------------------------------------------------
@@
 \midrule
-$\alpha_0=0.0407$ & $Q_0=0.467$ & \textcolor{red}{$\ln\!A_0=35.8092$} & $n_0=4.8217$ \\
-$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & \textcolor{red}{$\ln\!A_1=-58.822$} & $n_1=3.2814$ \\
-$\alpha_2=6.3912$ & $Q_2=7.6084$ & \textcolor{red}{$\ln\!A_2=740.3303$} & $n_2=71.5963$ \\
-$\alpha_3=-47.3364$ & $Q_3=-48.016$ & \textcolor{red}{$\ln\!A_3=-5.0493\times 10^{3}$} & $n_3=-1.9562\times 10^{3}$ \\
-$\alpha_4=220.0014$ & $Q_4=66.795$ & \textcolor{red}{$\ln\!A_4=1.1305\times 10^{4}$} & $n_4=1.4461\times 10^{4}$ \\
-$\alpha_5=-654.4553$ & $Q_5=468.8898$ & \textcolor{red}{$\ln\!A_5=2.022\times 10^{4}$} & $n_5=-5.431\times 10^{4}$ \\
-$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & \textcolor{red}{$\ln\!A_6=-1.5387\times 10^{5}$} & $n_6=1.1761\times 10^{5}$ \\
-$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & \textcolor{red}{$\ln\!A_7=3.1798\times 10^{5}$} & $n_7=-1.4882\times 10^{5}$ \\
-$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & \textcolor{red}{$\ln\!A_8=-2.9725\times 10^{5}$} & $n_8=1.0239\times 10^{5}$ \\
-$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & \textcolor{red}{$\ln\!A_9=1.0759\times 10^{5}$} & $n_9=-2.9621\times 10^{4}$ \\ 
+$\alpha_0=0.0407$ & $Q_0=0.467$ & $\ln\!A_0=35.8092$ & $n_0=4.8217$ \\
+$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & $\ln\!A_1=-58.822$ & $n_1=3.2814$ \\
+$\alpha_2=6.3912$ & $Q_2=7.6084$ & $\ln\!A_2=740.3303$ & $n_2=71.5963$ \\
+$\alpha_3=-47.3364$ & $Q_3=-48.016$ & $\ln\!A_3=-5.0493\times 10^{3}$ & $n_3=-1.9562\times 10^{3}$ \\
+$\alpha_4=220.0014$ & $Q_4=66.795$ & $\ln\!A_4=1.1305\times 10^{4}$ & $n_4=1.4461\times 10^{4}$ \\
+$\alpha_5=-654.4553$ & $Q_5=468.8898$ & $\ln\!A_5=2.022\times 10^{4}$ & $n_5=-5.431\times 10^{4}$ \\
+$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & $\ln\!A_6=-1.5387\times 10^{5}$ & $n_6=1.1761\times 10^{5}$ \\
+$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & $\ln\!A_7=3.1798\times 10^{5}$ & $n_7=-1.4882\times 10^{5}$ \\
+$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $\ln\!A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$ \\
+$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $\ln\!A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$ \\
 \bottomrule

### 2023-03-21 Article.tex
Corrected proofs after acceptance

@@
 %=================================================================
-\documentclass[metals,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+\documentclass[metals,article,accept,pdftex,moreauthors]{Definitions/mdpi}
 % For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
@@
 %=================================================================
+% MDPI internal commands - do not modify
 % MDPI internal commands - do not modify
@@
 \copyrightyear{2023}
-%\externaleditor{Academic Editor: Firstname Lastname}
-\datereceived{ }
-\daterevised{ } % Comment out if no revised date
-\dateaccepted{ }
+\externaleditor{Academic Editor: \hl{Ji Hoon Kim} %MDPI: Please add it.
+}
+\datereceived{ 10 February 2023}
+\daterevised{ 16 March 2023} % Comment out if no revised date
+\dateaccepted{20 March 2023}
 \datepublished{ }
@@
 \usepackage{xspace}
-\usepackage{subcaption}
+\usepackage[labelformat=simple]{subcaption}
+\renewcommand\thesubfigure{\alph{subfigure}}
+\DeclareCaptionLabelFormat{subcaptionlabel}{\normalfont(\textbf{#2}\normalfont)}
+\captionsetup[subfigure]{labelformat=subcaptionlabel}
+
 \DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
@@
 \DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
-\DeclareRobustCommand{\ie}{i.e.\@\xspace}
+\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
 \DeclareRobustCommand{\eal}{et al.\@\xspace}
@@
 \DeclareRobustCommand{\MPa}{\text{MPa}}
+\newcommand{\hlok}[1]{\colorbox{green}{#1}}
 
@@
 % Authors, for the paper (add full first names)
-\Author{Pierre Tize Mha$^{1}$, Prashant Dhondapure$^{2}$, Mohammad Jahazi$^{2}$\orcidB{}, Amèvi Tongne$^{1}$\orcidC{}, Olivier Pantalé $^{1*}$\orcidA{}}
+\Author{\hlok{Pierre Tize Mha} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading. All names are correct
+$^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
 
@@
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{P. Tize Mha, P. Dhondapure, M. Jahazi, A. Tongne, O. Pantalé}
+\AuthorCitation{Tize Mha, P.; Dhondapure, P.; Jahazi, M.; Tongne, A.; Pantalé, O.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France\\
-$^{2}$ \quad École de Technologie Supérieure, 1100 Notre Dame St. W., QC H3C 1K3, Montréal, Canada}
+\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; \hlok{ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)} %MDPI: We added emails from our system.
+Please confirm.
+OK
+\\
+$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St.
+W., \hlok{Montréal,} %MDPI: We suggest to use English format city name.
+we add the department information, please confirm.
+OK
+ QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}
 
 % Contact information of the corresponding author
-\corres{Correspondence: Olivier.Pantale@enit.fr; Tel.: +33-562442933}
+\corres{Correspondence: olivier.pantale@enit.fr; Tel.: +33-562442933}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{In the present work, a critical analysis of the most commonly used analytical models and recently introduced ANN-based models is performed to evaluate their predictive accuracy within and outside the experimental interval used to generate them.
-The high temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800.
-The experimental flow curves were modeled using Johnson-Cook, Modified-Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and PTM models, as well as an ANN model.
-The mean absolute relative error and root-mean-square error values were used to quantify the predictive accuracy of the models analyzed.
-The results indicated that the Johnson-Cook and Modified-Zerilli-Armstrong models had a significant error, while the Hansel-Spittel, PTM, and Arrhenius models were able to predict the behavior of this alloy.
+\abstract{In the present work, a critical analysis of the most-commonly used analytical models and recently introduced ANN-based models was performed to evaluate their predictive accuracy within and outside the experimental interval used to generate them.
+The high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800.
+The experimental flow curves were modeled using the Johnson--Cook, Modified-Zerilli--Armstrong, Hansel--Spittel, Arrhenius, and PTM models, as well as an ANN model.
+The mean absolute relative error and root-mean-squared error values were used to quantify the predictive accuracy of the models analyzed.
+The results indicated that the Johnson--Cook and Modified-Zerilli--Armstrong models had a significant error, while the Hansel--Spittel, PTM, and Arrhenius models were able to predict the behavior of this alloy.
 The ANN model showed excellent agreement between the predicted and experimental flow curves, with an error of less than 0.62\%.
 To validate the performance, the ability to interpolate and extrapolate the experimental data was also tested.
-The Hansel-Spittel, PTM, and Arrhenius models showed good interpolation and extrapolation capabilities.
-However, the ANN model was the most powerful of all the models.}
+The Hansel--Spittel, PTM, and Arrhenius models showed good interpolation and extrapolation capabilities.
+However, the ANN model was the most-powerful of all the models.}
 
 % Keywords
-\keyword{Artificial Neural Network; Constitutive flow Law; Analytical flow law; Interpolation; Extrapolation; Gleeble}
+\keyword{\hlok{artificial} %mdpi: please check the first letter format (uppercase/lowercase) for every word in keywords.
+please check all the keywords.
+we suggest to use lowercase if the uppercase is not necessary: OK
+neural network; constitutive flow law; analytical flow law; interpolation; extrapolation; Gleeble}
 
@@
 Large size forged blocks made of medium carbon high-strength steels are extensively used in the automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
-The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and a quench and temper heat treatment process to achieve the desired mechanical properties \cite{chadha2017deformation, chadha2018influence, murugesan2019two}.
+The manufacturing process of the large blocks starts with ingot casting, followed by open die forging and a quench and temper heat treatment process to achieve the desired mechanical properties \cite{chadha2017deformation, chadha2018influence, murugesan2019two}.
 In recent years, in order to respond to the market demand, larger size forgings have had to be produced.
-In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block have been required.
-Of the three manufacturing steps (casting, forging and heat treatment), forging is where the most important microstructural changes take place, and which greatly influences the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
-The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic thermomechanical loads \cite{tian2022deformation, tavakoli2019ferrite}.
+In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size, and mechanical properties from the surface to the core of the forged block have been required.
+Of the three manufacturing steps (casting, forging, and heat treatment), forging is where the most-important microstructural changes take place, which greatly influence the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
+The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic thermomechanical loads~\cite{tian2022deformation, tavakoli2019ferrite}.
 It has also been reported that phase transformation can occur during deformation.
-The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, shi2022constitutive, zeng2022constitutive, rudra2019constitutive}.
-
-Considering the large size of blocks, a purely experimental approach, based on trial and error, can not be used by industry, and therefore, reliable predictive tools, such a Finite Element analysis (FEA) codes, have been developed, and are commercially available.
+The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely the strain $\varepsilon$, the strain rate $\mdot\varepsilon$, and the temperature $T$ \cite{ebrahimi2017flow, shi2022constitutive, zeng2022constitutive, rudra2019constitutive}.
+
+Considering the large size of blocks, a purely experimental approach, based on trial and error, cannot be used by industry, and therefore, reliable predictive tools, such a finite element analysis (FEA) codes, have been developed and are commercially available.
 However, the prediction reliability of such analyses is a function of the accuracy of the material constitutive model, which describes the mutual interactions between the strain, the strain rate, and the temperature during deformation.
-As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
-Hence, most constitutive models depend on macroscopic parameters which influence the hardening and softening of the material.
-A large number of phenomenological, semi-empirical, or physical models \cite{jia2022thermo, costa2016study, rudnytskyj2020constitutive, Pantale-2021} have been developed.
-Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
-Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
-To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, liu2021modified, jia2022thermo1, bai2022comparison, zhu2022constitutive, jia2021modified, sim2022modified}.
-However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
+As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite phase at temperatures above the dissolution temperature of most carbides.
+Hence, most constitutive models depend on macroscopic parameters, which influence the hardening and softening of the material.
+A large number of phenomenological, semi-empirical, or physical \mbox{models~\cite{jia2022thermo, costa2016study, rudnytskyj2020constitutive, Pantale-2021}} have been developed.
+Among these, the Johnson--Cook (JC) \cite{Johnson-1983}, Hansel--Spittel (HS) \cite{chadha2018approach}, and Zerilli--Armstrong (ZA) \cite{Zerilli-1987} models are the best-known and most-widely available in FEA codes.
+Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate, and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
+To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, liu2021modified, jia2022thermo1, bai2022comparison, zhu2022constitutive, Jia-2021, sim2022modified}.
+However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high-temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
 Due to its more physics-based formulation, the ZA model and its modified form, MZA \cite{ovesy2020explicit, niu2020constitutive, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{derazkola2021review, wang2022deformation, miao2022deformation}.
-The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high temperature deformation \cite{rudnytskyj2022investigating, ji2020optimization}.
+The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high-temperature deformation \cite{rudnytskyj2022investigating, ji2020optimization}.
 To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
 This formulation is based on the MZA model and the polynomial functions of undefined order that are used during the identification.
-However, in the PTM model, the high order of the polynomial function (up-to $10$ in some cases) can affect its accuracy.
-
-The Artificial Neural Network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
+However, in the PTM model, the high order of the polynomial function (up to $10$ in some cases) can affect its accuracy.
+
+The artificial neural network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
 It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
-Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
-Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
+Since the behavior of materials is highly nonlinear at high temperatures and depends on many factors, which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
+Faced with these limitations, ANN models are of major interest because they are particularly suited to dealing with complex and nonlinear relationships.
 Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{wu2022experimental, stoffel2020deep, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
-Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
-In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to strain, strain rate and temperature.
-
-Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problem still persist with the models' efficiency.
+Although ANN models can predict well the material flow behavior, there is a problem with their implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
+In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to the strain, strain rate, and temperature.
+
+Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problems still persist with the models' efficiency.
 Indeed, a model is considered appropriate for predicting the material's behavior if its predictions and experimental results correlate well.
@@
 
-The present work aims to address the preceding question using the recently introduced ANN model.
-To this end, initially, hot compression tests, simulating the open die forging process, are carried out and the flow curves generated are modeled using the above--mentioned constitutive equations and an ANN model developed in this work.
-Then, the interpolation and extrapolation capabilities of each model are evaluated.
-The results are validated based on experimental work carried out herein and on data obtained from the literature.
+The present work aimed to address the preceding question using the recently introduced ANN model.
+To this end, initially, hot compression tests, simulating the open die forging process, were carried out, and the flow curves generated were modeled using the above-mentioned constitutive equations and an ANN model developed in this work.
+Then, the interpolation and extrapolation capabilities of each model were evaluated.
+The results were validated based on experimental work carried out herein and on data obtained from the~literature.
 
@@
 %----------------------------------------------------------------------------------
-\subsection{Experimental procedure}
-%----------------------------------------------------------------------------------
-
-The material used in this study consists of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
-\begin{table}[h!]
+\subsection{Experimental Procedure}
+%----------------------------------------------------------------------------------
+
+The material used in this study consisted of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
+\begin{table}[H]
 \centering
-\caption{Chemical composition of medium carbon steel, Fe = balance}
-\begin{tabular}{lccccccc}
+\caption{Chemical composition of medium carbon steel. Fe = balance.}
+
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{LCCCCCCC}
 \toprule
@@
 \midrule
-\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
+\textbf{\hlok{Wt}%MDPI: Is the bold necessary?. You can remove the bold, if it does not correspond to the editorial line of the journal.
+~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
 \bottomrule
-\end{tabular}
+\end{tabularx}
 \label{tab:Composition}
@@
 Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
-Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
-\begin{figure}[!ht]
-\centering
+Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely $1050~\celsius$, $1100~\celsius$, $1150~\celsius$, $1200~\celsius$, and $1250~\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$, and $5~\ps$.
+\begin{figure}[H]
+
 \includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
-\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
+\caption{The Gleeble-3800 thermomechanical simulator system used for this study.}
 \label{fig:Gleeble3800}
 \end{figure}
-Thin tantalum sheets were used as lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
+Thin tantalum sheets were used as the lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
 Figure \ref{fig:Inside-Gleeble3800} shows the inside of the Gleeble thermomechanical simulator with the specimen in place.
 We used 3 thermocouples soldered to the specimen to record the temperature history during the test and to ensure that the specimen was at the correct temperature prior to testing.
-\begin{figure}[!ht]
-\centering
+\begin{figure}[H]
+
 \includegraphics[width=0.7\columnwidth]{Figures/Gleeble-1}
-\caption{The inside of the Gleeble-3800 thermomechanical simulator with the specimen in place}
+\caption{The inside of the Gleeble-3800 thermomechanical simulator with the specimen in place.}
 \label{fig:Inside-Gleeble3800}
@@
 
-As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
-They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
+As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260~\celsius$ with a heating rate of $2$~\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
+They were then cooled down with a rate of $1$~\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
 During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
 After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
-Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
-\begin{figure}[!ht]
-\centering
+Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$, and $r_t$ are the height, large radius, and small radius of the specimen after compression, respectively.
+\begin{figure}[H]
+
 \includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
-\caption{Schematic diagram of the experimental process on the Gleeble-3800 thermomechanical simulator}
+\caption{\textls[-25]{Schematic diagram of the experimental process on the Gleeble-3800 thermomechanical simulator.}}
 \label{fig:GleebleProcess}
@@
 
-The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(1+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
-As raw data contains noises, the savgol\_filter method from the scipy library is used to remove noise and provide smoother data.
-To allow further use of the data in numerical simulations, elastic parts are removed.
-
-%----------------------------------------------------------------------------------
-\subsection{Compression tests results\label{sec:ComTestResults}}
-%----------------------------------------------------------------------------------
-
-The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]{Figures/rawData}
-\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$}
+The stress--strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to obtain the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(1+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$ and where $F$ is the force as measured by the Gleeble load cell.
+As the raw data contain noises, the savgol\_filter method from the scipy library was used to remove noise and provide smoother data.
+To allow further use of the data in numerical simulations, the elastic parts were removed.
+
+%----------------------------------------------------------------------------------
+\subsection{Compression Tests' Results\label{sec:ComTestResults}}
+%----------------------------------------------------------------------------------
+
+The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5~temperatures) is presented in Figure \ref{fig:RawData}.
+\begin{figure}[H]
+
+\includegraphics[width=0.99\columnwidth]{Figures/rawData}
+\caption{Stress--strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
 \label{fig:RawData}
 \end{figure}
-All data curves contain $700$ equidistant strain values up-to $\varepsilon=0.7$.
-Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of $21,000$ data points.
+All data curves contain $700$ equidistant strain values up to $\varepsilon=0.7$.
+Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of 21,000 data points.
 For the identification of the parameters of all the analytical models presented in this article, we restricted the database to 35 strain values between $0.02$ and $0.7$, with a step of $0.02$ (this is illustrated in Figure \ref{fig:RawData}, where the data used correspond to the dots on the graphs).
@@
 It should be noted that the strain also influences the flow stress.
-Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, and then decreases to maintain a more or less constant value until the end of the test.
+Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
 For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
 The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{galos2022review}.
-The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time, and friction thus increases.
-The increase of stress observed at the beginning of the deformation and up-to $0.1$ is due to work hardening (WH).
-After $0.1$ and up-to $0.2$, the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of the work-hardening rate.
+The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time and friction, thus, increases.
+The increase of stress observed at the beginning of the deformation and up to $0.1$ is due to work hardening (WH).
+After $0.1$ and up to $0.2$, the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of the work hardening rate.
 This behavior indicates that thermal softening becomes more and more predominant until it exceeds WH.
 At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening.
-This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$, except for those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and a $0.1$ $\text{s}^{-1}$ strain rate; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
+This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1~\ps$, except for those at $1050~\celsius$ and $1100~\celsius$; (ii) higher stress levels without significant softening and work hardening at $1050~\celsius$ and $1100~\celsius$ and a $0.1~\ps$ strain rate; (iii) a continuous increase with significant work hardening (all deformation temperatures and strain rate of $1~\ps$).
 Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates.
@@
 In fact, the drop observed in
-stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$.
-
-Figure \ref{fig:Micrography}(a) shows the microstructure obtained when the sample is held at $1260\celsius$ for $5$ minutes and rapidly cooled to room temperature.
+stress is because of DRX occurrence at all temperatures and strain rates of $0.001$--$5~\ps$.
+
+Figure \ref{fig:Micrography}a shows the microstructure obtained when the sample is held at $1260~\celsius$ for $5$ minutes and rapidly cooled to room temperature.
 From this image, large grains can be observed.
-On the other hand, Figure \ref{fig:Micrography}(b) shows the microstructure after compression at $1150\celsius$ with a $0.001~\text{s}^{-1}$ strain rate.
-To obtain this, the sample is heated up to $1260\celsius$, then held for $5$ minutes and cooled down to $1150\celsius$ to be held at this temperature for $1$ minute before compression.
+On the other hand, Figure \ref{fig:Micrography}b shows the microstructure after compression at $1150~\celsius$ with a $0.001~\ps$ strain rate.
+To obtain this, the sample is heated up to $1260~\celsius$, then held for $5$ minutes and cooled down to $1150~\celsius$ to be held at this temperature for $1$ minute before compression.
 After compression, the sample is rapidly cooled to room temperature to preserve the microstructure.
@@
 %As an example, Figure \ref{fig:Micrography} shows the medium carbon microstructures held for $5$~min at $1260\celsius$ before and after the compression phase.
-\begin{figure}[!ht]
-\centering
-\begin{subfigure}[b]{0.45\columnwidth}
-\centering
+\begin{figure}[H]
+
+\begin{subfigure}[b]{0.44\columnwidth}
+
 \includegraphics[width=\columnwidth]{Figures/BeforeCompM}
-\caption{Before hot compression}
+\caption{\centering Before hot compression}
 \end{subfigure}
-\hfill
-\begin{subfigure}[b]{0.45\columnwidth}
-\centering
+\hspace{10mm}
+\begin{subfigure}[b]{0.44\columnwidth}
+
 \includegraphics[width=\columnwidth]{Figures/AfterCompM}
-\caption{After hot compression}
+\caption{\centering After hot compression}
 \end{subfigure}
-\caption{Optical micrographs of a medium carbon steel (a) before and (b) after hot compression at $1150\celsius$ with a $0.001~\text{s}^{-1}$ strain rate.}
+\vspace{6pt}
+\caption{Optical micrographs of a medium carbon steel (\textbf{a}) before and (\textbf{b}) after hot compression at $1150~\celsius$ with a $0.001~\ps$ strain rate.}
 \label{fig:Micrography}
 \end{figure}
-The material is in the single phase austenite state at all of the test temperatures examined.
-The data presented in Figure \ref{fig:RawData} will be utilized in the following section to determine the parameters of the $6$ flow laws proposed and to determine which model most closely aligns with experimental results.
-
-%----------------------------------------------------------------------------------
-\section{Identification of Constitutive Flow Laws Parameters\label{sec:ConstLaws}}
-%----------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------
-\subsection{The Johnson-Cook model\label{sec:JC}}
-%----------------------------------------------------------------------------------
-
-The JC model, as mentioned above, is one of the most widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon$, strain rate $\mdot\varepsilon$, and temperature $T$.
-However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
-Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model, hence its inability to describe the phenomenon of softening induced by temperature.
+The material is in the single-phase austenite state at all of the test temperatures examined.
+The data presented in Figure \ref{fig:RawData} will be utilized in the following section to determine the parameters of the $6$ flow laws proposed and to determine which model most closely aligns with the experimental results.
+
+%----------------------------------------------------------------------------------
+\section{Identification of Constitutive Flow Laws' Parameters\label{sec:ConstLaws}}
+%----------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------
+\subsection{The Johnson--Cook Model\label{sec:JC}}
+%----------------------------------------------------------------------------------
+
+The JC model, as mentioned above, is one of the most-widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon$, strain rate $\mdot\varepsilon$, and temperature $T$.
+However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate, and temperature.
+Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$, and $T$) separately as a factor in the mathematical expression of the model, hence its inability to describe the phenomenon of softening induced by temperature.
 The equation that describes this model is given as follows \cite{Johnson-1983}:
 \begin{equation}
-\sigma^y=\left(A+B{\varepsilon^p}^{n}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
-\end{equation}
-where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
-The other values are reference values: $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and thus $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
-For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$.
-In our approach, the reference strain rate and reference temperature for identifying the JC model are the lowest values used during the test, however, sometimes these values do not always give the best results for the model.
-
-The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by Zeng \eal \cite{zeng2022constitutive}.
-This method allows sequentially obtaining the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
+\sigma^y=\left(A+B{\varepsilon^p}^{n}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson--Cook}
+\end{equation}
+where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, and $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
+The other values are reference values: $\mdot\varepsilon_0$ is the reference strain rate; $T_m$ and, thus, $T_0$ are the melting temperature ($1460~\celsius$ in our case) and the reference temperature, respectively.
+For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050~\celsius$.
+In our approach, the reference strain rate and reference temperature for identifying the JC model are the lowest values used during the test; however, sometimes, these values do not always give the best results for the model.
+
+The procedure used to determine the parameters of the Johnson--Cook law is in accordance with the one proposed by Zeng \eal \cite{zeng2022constitutive}.
+This method allows sequentially obtaining the $5$ parameters in the order $A$, $B$, $n$, $C$, and $m$.
 Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
-For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then be determined by considering only the first term $\left(A+B{\varepsilon^p}^{n}\right)$ in Equation (\ref{eq:Johnson-Cook}).
+For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then be determined by considering only the first term $\left(A+B{\varepsilon^p}^{n}\right)$ in Equation (\ref{eq:Johnson--Cook}).
 Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
-Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering only all the curves at $T=T_0$ then gives $C=0.3404$.
+Once the parameters $A$, $B$, and $n$ are known, the determination of $C$, considering only all the curves at $T=T_0$, then gives $C=0.3404$.
 Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the parameters $A, B, C, n$ and gives $m=0.7057$.
-All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.
-
-\begin{table}[h!]
-\centering
-\caption{Parameter values of the Johnson-Cook flow law for a medium carbon steel}
-\begin{tabular}{ccccc}
+All parameters of the Johnson--Cook model are reported in Table \ref{tab:JC}.
+
+\begin{table}[H]
+
+\caption{Parameter values of the Johnson--Cook flow law for a medium carbon steel.}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{CCCCC}
 \toprule
-\boldmath{$A~(\MPa)$} & \boldmath{$B~(\MPa)$} & \boldmath{$n$} & \boldmath{$C$} & \boldmath{$m$} \\
+\boldmath{$A$~\bf (MPa)} & \boldmath{$B$~\bf (MPa)} & \boldmath{$n$} & \boldmath{$C$} & \boldmath{$m$} \\
 \midrule
@@
 \bottomrule
-\end{tabular}
+\end{tabularx}
 \label{tab:JC}
@@
 
-The values predicted by the Johnson-Cook flow law (solid line) and the experimental values (dots) are compared in Figure \ref{fig:CompExp-JC-6}.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]{Figures/CompExp-JC-6}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson-Cook model}
+The values predicted by the Johnson--Cook flow law (solid line) and the experimental values (dots) are compared in Figure \ref{fig:CompExp-JC-6}.
+\begin{figure}[H]
+
+\includegraphics[width=0.99\columnwidth]{Figures/CompExp-JC-6}
+\caption{\hlok{Comparison} %MDPI: Many figures are very similar.
+Please confirm there is no duplicate figure.
+No, every figure is different, the name of the figure correspond to the section, and everything is OK.
+ between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson--Cook model.}
 \label{fig:CompExp-JC-6}
@@
 The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
-As expected, the mathematical formulation of the Johnson-Cook flow law is unable to represent the stress drop at low strain rates, with the JC model increasing only monotonically with the strain.
-Since most of the parameters are identified at low strain rates ($A$, $B$ and $n$), this results in a very poor fit of the model to the experimental data.
-
-The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the Mean Absolute Relative Error ($\MARE$) defined by Equation (\ref{eq:AARE}):
+As expected, the mathematical formulation of the Johnson--Cook flow law is unable to represent the stress drop at low strain rates, with the JC model increasing only monotonically with the strain.
+Since most of the parameters are identified at low strain rates ($A$, $B$, and $n$), this results in a very poor fit of the model to the experimental data.
+
+The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the mean absolute relative error ($\MARE$) defined by Equation (\ref{eq:AARE}):
 \begin{equation}
@@
 \end{equation}
-and the Root Mean Square Error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
+and the root-mean-squared error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
 \begin{equation}
@@
 \end{equation}
-where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
+where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$, and $N$ is the total number of data points used to compute those coefficients (in our case $N$ = 21,000).
 For the JC model, $\MARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
-As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is not always an accurate measure to evaluate the reliability of the constitutive law espacially in the case of a highly non-linear functions because it only shows the correlation of the model with respect to the data and not its accuracy.
-A good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction, we therefore avoided its use in our analysis.
-
-%----------------------------------------------------------------------------------
-\subsection{The Modified Zerilli-Armstrong model\label{sec:MZA}}
-%----------------------------------------------------------------------------------
-
-The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most widely used models implemented in many FEA codes such as the Abaqus software.
+As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is not always an accurate measure to evaluate the reliability of the constitutive law especially in the case of a highly nonlinear functions because it only shows the correlation of the model with respect to the data and not its accuracy.
+A good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction; we, therefore, avoided its use in our analysis.
+
+%----------------------------------------------------------------------------------
+\subsection{The Modified-Zerilli--Armstrong Model\label{sec:MZA}}
+%----------------------------------------------------------------------------------
+
+The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most-widely used models implemented in many FEA codes such as the Abaqus software.
 The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experiments.
-In the JC model, the parameters are considered separately, while in MZA, they are considered simultaneously, and for that formulation, MZA is preferred to the JC model \cite{zhu2022thermal}.
-However, the original form of the ZA model has some limitations due to the fact that it is considered as a two terms function (thermal and athermal functions), and to improve the formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
+In the JC model, the parameters are considered separately, while in the MZA model, they are considered simultaneously, and for that formulation, the MZA model is preferred over the JC model \cite{zhu2022thermal}.
+However, the original form of the ZA model has some limitations due to the fact that it is considered as a two-term function (thermal and athermal functions), and to improve the formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
 \begin{equation}
@@
 where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
-To get the parameters of the MZA model, we apply the method proposed by \cite{Samantaray-2009}, and the parameters are summarized in Table \ref{tab:MZA}, while their predictions are plotted in Figure \ref{fig:CompExp-MZA-6}.
-\begin{table}[h!]
-\centering{}
-\caption{Parameter constants of Modified Zerilli-Armstrong model}
-\begin{tabular}{ccccccc}
+To obtain the parameters of the MZA model, we applied the method proposed by~\cite{Samantaray-2009}, and the parameters are summarized in Table \ref{tab:MZA}, while their predictions are plotted in \mbox{Figure \ref{fig:CompExp-MZA-6}}.
+\begin{table}[H]
+
+\caption{Parameter constants of the Modified-Zerilli--Armstrong model.}
+
+\begin{adjustwidth}{-\extralength}{0cm}
+%\centering %% If there is a figure in wide page, please release command \centering
+\begin{minipage}{\fulllength}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{CCCCCCC}
 \toprule
-\boldmath{$C_1~(\MPa)$} & \boldmath{$C_2~(\MPa)$} & \boldmath{$C_3$} & \boldmath{$C_4$} & \boldmath{$C_5$} & \boldmath{$C_6$} & \boldmath{$n$} \\
+\boldmath{$C_1$}~\bf (MPa) & \boldmath{$C_2$}~\bf (MPa) & \boldmath{$C_3$} & \boldmath{$C_4$} & \boldmath{$C_5$} & \boldmath{$C_6$} & \boldmath{$n$} \\
 \midrule
@@
 \bottomrule
-\end{tabular}
+\end{tabularx}
+\end{minipage}
+\end{adjustwidth}
 \label{tab:MZA}
 \end{table}
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]
+
+It can be seen from this figure that both the MZA and JC models are not able to faithfully reproduce the experimental data, especially at low strain rates, but they are slightly better at higher strain rates.
+The deviation between the predicted values and the experimental values is large because this model has a problem correctly describing the softening in its formulation.
+For the MZA model, $\MARE=21.20\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model, as reported in \cite{TizeMha-2022}.
+In addition, it can be observed that, at high strain rates, the MZA model is not good either, even if there is no softening effect, and this can be explained by the fact that this model is formulated for quasi-static phenomena.
+
+\begin{figure}[H]
+\includegraphics[width=0.99\columnwidth]
 {Figures/CompExp-MZA-6}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Modified Zerilli-Armstrong model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Modified-Zerilli--Armstrong model.}
 \label{fig:CompExp-MZA-6}
 \end{figure}
-It can be seen from this figure that both the MZA and JC models are not able to faithfully reproduce the experimental data, especially at low strain rates, but they are slightly better at higher strain rates.
-The deviation between the predicted values and the experimental values is large because this model has a problem correctly describing the softening in its formulation.
-For the MZA model, $\MARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model, as reported in \cite{TizeMha-2022}.
-In addition, it can be observed that at high strain rates the MZA is not good either, even if there is no softening effect, and this can be explained by the fact that this model is formulated for quasi-static phenomena.
-
-%----------------------------------------------------------------------------------
-\subsection{The Hansel-Spittel model\label{sec:HSmodel}}
-%----------------------------------------------------------------------------------
-
-The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEA codes, although its parameters can more easily be determined than those of the JC or MZA models.
+
+%----------------------------------------------------------------------------------
+\subsection{The Hansel--Spittel Model\label{sec:HSmodel}}
+%----------------------------------------------------------------------------------
+
+The Hansel--Spittel model \cite{Hensel-1978} is one of the least-known models in terms of integration in FEA codes, although its parameters can more easily be determined than those of the JC or MZA models.
 Programming a simple identification script is sufficient to identify its parameters for a given material.
-The equation of the HS model is given by the following relation:
+The equation of the HS model is given by the following~relation:
 \begin{equation}
@@
 \end{equation}
-where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature, as proposed earlier.
+where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate, and $T$ is the temperature, as proposed earlier.
 The coefficients $A$ and $m_i$ are the 9 parameters of the model to be identified.
 However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification.
-For its identification, several authors restrict its expression to a reduced number of only $5$ or $6$ $m_i$ parameters, by forcing a zero value for the other parameters \cite{Chadha-2018, Mehtedi-2015, Rudnytskyj-2020}.
+For its identification, several authors restrict its expression to a reduced number of only $5$ or $6$ $m_i$ parameters, by forcing a zero value for the other \mbox{parameters \cite{chadha2018approach, Mehtedi-2015, rudnytskyj2020constitutive}.}
 
 In the present study, the best results were obtained by taking the model defined by only the first 7 $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.
-From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} allowed to compute the parameters reported in Table
+From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} allowed computing the parameters reported in Table
  \ref{tab:HS}.
 
-\begin{table}[h!]
-\centering
-\caption{Parameter values of the Hansel-Spittel flow law for the medium carbon steel}
-\begin{tabular}{ccccc}
+\begin{table}[H]
+
+\caption{Parameter values of the Hansel--Spittel flow law for the medium carbon steel.}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{CCCCC}
 \toprule
@@
 \toprule
-& \boldmath{$m_5$} & \boldmath{$m_6$} & \boldmath{$m_7$} & \boldmath{$m_8$} \\
+& \boldmath{$m_5$} & \boldmath{$m_6$} & \boldmath{$m_7$} & \boldmath{$m_8$} \\ %MDPI: Please confirm if all the bold should be kept: You can remove the bold, if it does not correspond to the editorial line of the journal.
 \midrule
@@
 \bottomrule
-\end{tabular}
+\end{tabularx}
 \label{tab:HS}
@@
 
-A comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6}, where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
+A comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6}, where the dots represent the experimental values and the solid lines are the values predicted by the Hansel--Spittel flow law.
 For the HS model, $\MARE=7.75~\%$ and $\RMSE=3.80~\MPa$.
 It appears that both this model and the previous ones do not adequately predict the experimental one, and the difference is relatively significant for all strain rates below $1~\ps$.
-This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong non-linear behavior observed for low strain rate values.
+This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong nonlinear behavior observed for low strain rate values.
 The DRX phenomenon cannot be reproduced by this type of model.
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]
+\begin{figure}[H]
+
+\includegraphics[width=0.9\columnwidth]
 {Figures/CompExp-HS-6}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Hansel-Spittel model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Hansel--Spittel model.}
 \label{fig:CompExp-HS-6}
@@
 %----------------------------------------------------------------------------------
-\subsection{The Arrhenius model\label{sec:ARmodel}}
-%----------------------------------------------------------------------------------
-
-The Arrhenius type model \cite{Sellars-1966} is one of the most used models in the framework of material forming, especially when it comes to studying the material microstructure.
-The model takes into account the physical phenomena describing the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ expressed as power law, exponential law and hyperbolic sine.
+\subsection{The Arrhenius Model\label{sec:ARmodel}}
+%----------------------------------------------------------------------------------
+
+The Arrhenius type model \cite{Sellars-1966} is one of the most-used models in the framework of material forming, especially when it comes to studying the material microstructure.
+The model takes into account the physical phenomena describing the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$, and the temperature $T$ expressed as the power law, exponential law, and hyperbolic sine.
 This makes it easier to describe the softening phenomenon observed in the material due to increasing temperature.
@@
 \end{equation}
-where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent on the material.
-The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperatures by the regression method.
-Combining Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allows to express the flow stress $\sigma^y$ as a function of the $Z$ parameter:
+where $Z$ is the Zenner--Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate, and temperature, and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$, and $\beta=\alpha~n_1$ are dependent on the material.
+The corresponding values are independent of the temperature and are obtained from the stress--strain curves at different strain rates and temperatures by the regression method.
+Combining Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allows expressing the flow stress $\sigma^y$ as a function of the $Z$~parameter:
 \begin{equation}
@@
 
-To obtain the constitutive equation, all the parameters $A$, $Q$ $\alpha$ and $n$ must be determined for a given material.
-The strain has a significant non-linear influence on the behavior of the material by the strain hardening and softening mechanisms at high values of deformation.
-A strain dependent factor must therefore be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$ $\alpha$ and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
+To obtain the constitutive equation, all the parameters $A$, $Q$, $\alpha$, and $n$ must be determined for a given material.
+The strain has a significant nonlinear influence on the behavior of the material by the strain hardening and softening mechanisms at high values of deformation.
+A strain-dependent factor must, therefore, be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$, $\alpha$, and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
 \begin{equation}
@@
 
-The determination of the order $m$ of the polynomials defining Equations (\ref{eq:ArA}-\ref{eq:Arn}) depends on the ability of the model to represent the non-linear dependence of the stress on strain and its generalization.
+The determination of the order $m$ of the polynomials defining Equations (\ref{eq:ArA})--(\ref{eq:Arn}) depends on the ability of the model to represent the nonlinear dependence of the stress on strain and its generalization.
 The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=0,1,2,3,\cdots,m$) are the coefficients of the polynomials used to determine using a regression method.
 Setting $m=9$ gives the best results, and the corresponding parameters are reported in Table \ref{tab:AR}.
-\begin{table}[h!]
+\begin{table}[H]
 \centering
-\caption{Parameter values of the Arrhenius flow law for the medium carbon steel}
-\begin{tabular}{llll}
+\caption{Parameter values of the Arrhenius flow law for the medium carbon steel.}
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\begin{tabularx}{\textwidth}{LLLL}
 \toprule
@@
 \bottomrule
-\end{tabular}
+\end{tabularx}
 \label{tab:AR}
@@
 This modified form of the Arrhenius behavior law allows an accurate and reliable prediction over a wide range of temperatures and strain rates.
-Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$:
+Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$, and the temperature $T$:
 \begin{equation}
@@
 The difference between the experimental and predicted values is small.
-However for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is unable to predict the softening.
+However, for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is unable to predict the softening.
 For the AR model, $\MARE=3.56~\%$ and $\RMSE=2.18~\MPa$.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]
-{Figures/CompExp-AR-6}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Arrhenius model}
-\label{fig:CompExp-AR-6}
-\end{figure}
-
-%----------------------------------------------------------------------------------
-\subsection{The PTM model\label{sec:PTM}}
+
+%----------------------------------------------------------------------------------
+\subsection{The PTM Model\label{sec:PTM}}
 %----------------------------------------------------------------------------------
@@
 Its construction is based on the use of polynomial functions, as is the case in the AR model.
-Thus, the physical parameters' dependent intrinsic functions of the PTM model, allow adjusting the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
-The equation describing the PTM model is therefore given by :
+Thus, the physical parameters' dependent intrinsic functions of the PTM model allow adjusting the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
+The equation describing the PTM model is, therefore, given by:
+
+\begin{adjustwidth}{-\extralength}{0cm}
+%\centering %% If there is a figure in wide page, please release command \centering
 \begin{equation}
@@
 \end{equation}
+\end{adjustwidth}
+\vspace{6pt}
 where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM}) of the model to be identified using the procedure proposed in \cite{TizeMha-2022}.
-Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
-The larger these quantities, the greater the number of parameters needing to be identified for the PTM model.
-The determination of the parameters of this model is done thanks to the LMFIT Python library \cite{Newville-2016} (for more details about this model we refer the reader to our previous work \cite{TizeMha-2022}).
-Thus, all the parameters of this model are calculated with $q=5$, $r=5$, $s=1$ and $t=5$.
-
-Figure \ref{fig:CompExp-PTM-6} presents a comparison of values predicted by the PTM model and experimental values.
+Quantities $q$, $r$, $s$, and $t$ define the degree of the polynomials used to describe the behavior of the material.
+The larger these quantities, the greater the number of parameters that need to be identified for the PTM model.
+The determination of the parameters of this model was performed thanks to the LMFIT Python library \cite{Newville-2016} (for more details about this model, we refer the reader to our previous work \cite{TizeMha-2022}).
+Thus, all the parameters of this model were calculated with $q=5$, $r=5$, $s=1$, and $t=5$.
+
+\begin{figure}[H]
+
+\includegraphics[width=0.98\columnwidth]
+{Figures/CompExp-AR-6}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Arrhenius model.}
+\label{fig:CompExp-AR-6}
+\end{figure}
+
+Figure \ref{fig:CompExp-PTM-6} presents a comparison of the values predicted by the PTM model and the experimental values.
 The PTM model is suitable for describing the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$, the prediction is not very good.
@@
 
-\begin{table}[h!]
+\begin{table}[H]
 \centering
-\caption{Parameter values of the PTM flow law for the P20 steel}
-\begin{tabular}{llll}
+\caption{Parameter values of the PTM flow law for the P20 steel.}
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\begin{tabularx}{\textwidth}{LLLL}
 \toprule
@@
 \bottomrule
-\end{tabular}
+\end{tabularx}
 \label{tab:PTM}
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]
+\begin{figure}[H]
+
+\includegraphics[width=0.98\columnwidth]
 {Figures/CompExp-PTM-6}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the PTM model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the PTM model.}
 \label{fig:CompExp-PTM-6}
@@
 %----------------------------------------------------------------------------------
-\subsection{The Artificial Neural Network model\label{sec:ANNmodel}}
-%----------------------------------------------------------------------------------
-
-Because of their predictive capacity and adaptability, Artificial Neural Networks (ANNs) are increasingly widely used today in many scientific fields.
-Their operation is based on a training process during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine training process.
+\subsection{The Artificial Neural Network Model\label{sec:ANNmodel}}
+%----------------------------------------------------------------------------------
+
+Because of their predictive capacity and adaptability, artificial neural networks (ANNs) are increasingly widely used today in many scientific fields.
+Their operation is based on a training process, during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine training process.
 
 Neural networks generally have two uses: classification and regression.
-The first is the ability to classify data into different groups, and for example, to distinguish between images of cats and dogs.
-The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after training, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by the above identified analytical models.
-The main difference is that this approximation is not linked to a fixed mathematical formulation (as in JC, MZA, AR, HS and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer, and the activation functions associated with the neurons of the network.
-A feed-forward ANN, as used in our application, contains an input layer, an output layer and a number of hidden layers ($2$ in our case).
+The first is the ability to classify data into different groups, for example to distinguish between images of cats and dogs.
+The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after training, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is achieved by the above-identified analytical models.
+The main difference is that this approximation is not linked to a fixed mathematical formulation (as in the JC, MZA, AR, HS, and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer, and the activation functions associated with the neurons of the network.
+A feed-forward ANN, as used in our application, contains an input layer, an output layer, and a number of hidden layers ($2$ in our case).
 Each layer of neurons is connected to the one before it and the one after it by weighted connections.
-Thus, all the neurons of the $k$ layer are connected to all the neurons of the ($k-1$) layer as shown in Figure \ref{fig:ANN-2HL}.
-\begin{figure}[!ht]
-\centering
+Thus, all the neurons of the $k^{th}$ layer are connected to all the neurons of the ($k-1^{th}$) layer, as shown in~Figure~\ref{fig:ANN-2HL}.
+\begin{figure}[H]
+
 \includegraphics[width=0.7\columnwidth]
 {Figures/ANN-scheme-2HL}
-\caption{Two hidden layers Artificial Neural Network architecture}
+\caption{\hlok{Two} %MDPI: Should green and red dot be explained?. Caption modified.
+ hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
 \label{fig:ANN-2HL}
@@
 
-Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following equation:
+Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
 \begin{equation}
@@
 \end{equation}
-where $y_i\lay{k}$ is the entry of the $i^{th}$ neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j^{th}$ neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i^{th}$ neuron of layer $k$ and the $j^{th}$ neuron of layer $(k-1)$ and $b_i\lay{k}$ is the associated bias of the $i^{th}$ neuron of layer $k$.
-Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
-For the proposed model, we selected the Sigmoid activation function, so that, each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
+where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output \hlok{of the} %MDPI: We suggest to remove the superscript and italic format of ``th''.
+Please check all the ``th''.
+Notation has been changed following your request.
+  $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
+Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
+For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
 \begin{equation}
@@
 
-No activation function is used for the output neuron of the ANN as usually done in regression ANN.
-
-After some tests of different types of network architectures, and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer give the best compromise between prediction, training time and model compactness.
+No activation function was used for the output neuron of the ANN as usually done in a regression ANN.
+
+After some tests of different types of network architectures and in accordance with previous works, a network structure with two hidden layers including $15$ neurons for the first hidden layer and $7$ neurons for the second layer gave the best compromise between prediction, training time, and model compactness.
 From a global architecture point of view, the input layer is composed of $3$ neurons ($\varepsilon^p$, $\mdot\varepsilon$, $T$) and the output layer is composed of a single neuron corresponding to the $\sigma^y$ flow stress.
-This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second layer and $8$ for the output layer).
+This architecture leads to a global model with $180$ parameters to be identified ($60$ for the first layer, $112$ for the second layer, and $8$ for the output layer).
 
@@
 The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
-The training data were those from the tests presented in Section \ref{sec:ComTestResults}, and were composed of $21,000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
-The training was performed on the basis of $5,000$ epochs of the experimental data set.
-$40$ minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allowed to obtain the converged parameters of the ANN model.
+The training data were those from the tests presented in Section \ref{sec:ComTestResults} and were composed of 21,000 quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
+The training was performed on the basis of $5000$ epochs of the experimental dataset.
+It took $40$~min of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of RAM and an Intel 4-core i7-10510U processor to obtain the converged parameters of the ANN model.
 Figure \ref{fig:ANN-6-conv} shows the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$ during the training phase.
-\begin{figure}[!ht]
-\centering
+\begin{figure}[H]
 \includegraphics[width=0.7\columnwidth]
 {Figures/Conv-ANN-6}
-\caption{Convergence of the ANN model during the training phase}
+\caption{Convergence of the ANN model during the training phase.}
 \label{fig:ANN-6-conv}
 \end{figure}
-As can be seen in this figure, after $5,000$ epochs, we can consider that we have reached a stationary state of the model training, and that it is useless to continue with the training phase.
-
-Once the training phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data similarly to what is done with analytical models.
-One can either use the model directly by providing it with new input data, or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
-For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in the Appendix.
-
-As for the above considered analytical models, Figure \ref{fig:CompExp-3-15-7-1-sigmoid} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]
+As can be seen in this figure, after $5000$ epochs, we can consider that we have reached a stationary state of the model training, such that it is useless to continue with the training~phase.
+
+\textls[-25]{Once the training phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data, similarly to what was done with the analytical models.
+One can either use the model directly by providing it with new input data or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
+For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in \hlok{Appendix} %MDPI: We changed Appendix to Appendix A.
+OK
+ \ref{sec:Appendix}.}
+
+As for the above-considered analytical models, Figure \ref{fig:CompExp-3-15-7-1-sigmoid} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
+
+The experimental data and the ANN prediction correlate very well over the entire range of data, and the predicted data can track the hardening and softening regions of the hot deformed material well.
+For the ANN model, $\MARE=0.62\%$ and $\RMSE=0.38~\MPa$, which is excellent.
+This model can be used to simulate the hot deformation of this type of alloy with much greater reliability with respect to the actual material behavior than the analytical models presented in the above sections.
+
+\begin{figure}[H]
+
+\includegraphics[width=0.98\columnwidth]
 {Figures/CompExp-3-15-7-1-sigmoid}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the 3-15-7-1-sigmoid ANN model}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the 3-15-7-1-sigmoid ANN model.}
 \label{fig:CompExp-3-15-7-1-sigmoid}
 \end{figure}
-The experimental data and the ANN prediction correlate very well over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
-For the ANN model, $\MARE=0.62~\%$ and $\RMSE=0.38~\MPa$ which is excellent.
-This model can be used to simulate the hot deformation of this type of alloy with much greater reliability to the actual material behavior than the analytical models presented in the above sections.
-
-%----------------------------------------------------------------------------------
-\subsection{Comparison of analytical and ANN models\label{sec:Comparison}}
+
+%----------------------------------------------------------------------------------
+\subsection{Comparison of Analytical and ANN Models\label{sec:Comparison}}
 %----------------------------------------------------------------------------------
@@
 A summary of the coefficients for evaluating the high-temperature flow stress prediction capability of the medium carbon alloy for all models presented in this work is reported in Table \ref{tab:Errors}.
-\begin{table}[h!]
-\centering
-\caption{Accuracy coefficients for all the analyzed models}
-\begin{tabular}{lcccccc}
+\begin{table}[H]
+
+\caption{Accuracy coefficients for all the analyzed models.}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\begin{tabularx}{\textwidth}{LCCCCCC}
 \toprule
@@
 \bottomrule
-\end{tabular}
+\end{tabularx}
 \label{tab:Errors}
 \end{table}
-From the Table \ref{tab:Errors}, we can see that the ANN model has a much better predictive capacity than all the analytical models presented in the above sections.
-Globally, the values of $\MARE$ and $\RMSE$ are $6$ times lower than with the best of the analytical models, \ie, the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.
-
-The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material, and more particularly, at low strain rates.
-The parameters reported in Table \ref{tab:Errors} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6} to \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.
+From Table \ref{tab:Errors}, we can see that the ANN model has a much better predictive capacity than all the analytical models presented in the above sections.
+Globally, the values of $\MARE$ and $\RMSE$ are six-times lower than with the best of the analytical models, \ie, the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.
+
+The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at a low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material and, more particularly, at low strain rates.
+The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}\hlok{--}%MDPI: We changed ``to'' to en dash.
+OOPS, there is a mistake, it's figures 6,7,8,9,10, and 13.
+Figures 11 and 12 cannot be included in this list.
+I updated the cross references.
+\ref{fig:CompExp-PTM-6} and \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.
 
@@
 
-In order to better compare the performances of the above analysed models (the 5 analytical models and the ANN based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
-The identification of the above analysed models is based on a set of experimental data corresponding to 6 strain rates, 5 temperatures and strains ranging from $0$ to $0.7$.
-To test the training capacity and reliability of these models, we propose here to perform the training of the models on only 5 strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
-
-Thus, one of the omitted strain rates ($\mdot\varepsilon=1~\ps$) is within the range of strain rates for model identification ($0.001~\ps\text{ to }5~\ps$), and therefore, we can test the ability of the models to interpolate the results from the other 5 strain rates and be able to quantify any deviation from experimental values.
-On the other hand, since the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates for the model identification ($0.001~\ps\text{ to }2~\ps$), we will test the ability of the models to extrapolate results and quantify deviations with the experimental values.
-
-%----------------------------------------------------------------------------------
-\subsection{Interpolation validation}
-%----------------------------------------------------------------------------------
-
-For interpolation validation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for the ANN) are the 5 others, \ie, $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
-All models were re-identified from the same experimental data on a data set corresponding to 5 strain rates and 5 temperatures.
-
-Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as dots) for the 5 analytical models and the neural network.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]
-{Figures/CompInt}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=1~\ps$}
-\label{fig:CompInt}
-\end{figure}
-Table \ref{tab:IntVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the $5$ identified strain rates (lines referred as id.
-$\mdot\varepsilon$), the $6$ strain rates (lines referred as all $\mdot\varepsilon$) or only on the strain rate $\mdot\varepsilon=1~\ps$.
-\begin{table}[h!]
+In order to better compare the performances of the above analyzed models (the five~analytical models and the ANN based model), in this section, we present the ability of each of these models to interpolate and extrapolate the results as a function of the strain rate $\mdot\varepsilon$.
+The identification of the above-analyzed models was based on a set of experimental data corresponding to six strain rates, five temperatures, and strains ranging from $0$ to $0.7$.
+To test the training capacity and reliability of these models, we propose here to perform the training of the models on only five strain rates by voluntarily omitting the strain rate $\mdot\varepsilon=1~\ps$ or $\mdot\varepsilon=5~\ps$.
+
+Thus, one of the omitted strain rates ($\mdot\varepsilon=1~\ps$) is within the range of strain rates for model identification ($0.001~\ps\text{ to }5~\ps$), and therefore, we can test the ability of the models to interpolate the results from the other five strain rates and be able to quantify any deviation from experimental values.
+On the other hand, since the omitted strain rate ($\mdot\varepsilon=5~\ps$) is outside the range of strain rates for the model identification ($0.001~\ps\text{ to }2~\ps$), we tested the ability of the models to extrapolate the results and quantify deviations with the experimental values.
+
+%----------------------------------------------------------------------------------
+\subsection{Interpolation Validation}
+%----------------------------------------------------------------------------------
+
+For interpolation validation, the chosen omitted strain rate was $\mdot\varepsilon=1~\ps$, and those used for identification (or training for the ANN) were the five others, \ie, $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
+All models were re-identified from the same experimental data on a dataset corresponding to five strain rates and five temperatures.
+
+Figure \ref{fig:CompInt} shows a comparison, for the strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as dots) for the five analytical models and the neural network.
+
+Table \ref{tab:IntVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the five identified strain rates (lines referred as id.
+$\mdot\varepsilon$), the six strain rates (lines referred as all $\mdot\varepsilon$), or only on the strain rate $\mdot\varepsilon=1~\ps$.
+\begin{table}[H]
 \centering{}
-\caption{Accuracy coefficients of interpolation for all models with $\mdot\varepsilon=1~\ps$}
-\begin{tabular}{llcccccc}
+\caption{Accuracy coefficients of interpolation for all models with $\mdot\varepsilon=1~\ps$.}
+
+\begin{adjustwidth}{-\extralength}{0cm}
+%\centering %% If there is a figure in wide page, please release command \centering
+\begin{minipage}{\fulllength}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\begin{tabularx}{\textwidth}{LLCCCCCC}
 \toprule
-\textbf{Strain rate} & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\
+\textbf{Strain Rate} & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\
 \midrule
@@
 \bottomrule
-\end{tabular}
+\end{tabularx}
+\end{minipage}
+\end{adjustwidth}
 \label{tab:IntVal}
@@
 
-In Figure \ref{fig:CompInt}, it can be seen that the first two models (JC and MZA), presented in this study do not have the ability to reproduce the behavior of the material for the strain rate $\mdot\varepsilon=1~\ps$.
-Overall, the JC model gives better results than the MZA model for $\mdot\varepsilon=1~\ps$, which is reflected in Table \ref{tab:IntVal} by a lower value of $\MARE$ and $\RMSE$ for JC than for MZA.
+\begin{figure}[H]
+
+\includegraphics[width=0.98\columnwidth]
+{Figures/CompInt}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=1~\ps$.}
+\label{fig:CompInt}
+\end{figure}
+
+In Figure \ref{fig:CompInt}, it can be seen that the first two models (JC and MZA) presented in this study do not have the ability to reproduce the behavior of the material for the strain rate $\mdot\varepsilon=1~\ps$.
+Overall, the JC model gives better results than the MZA model for $\mdot\varepsilon=1~\ps$, which is reflected in Table \ref{tab:IntVal} by a lower value of the $\MARE$ and $\RMSE$ for the JC than for the MZA model.
 Nevertheless, these values are higher than $10\%$ for the JC model and $20\%$ for the MZA model, which reflects the poor ability of these models to correctly model the behavior of this material.
-This finding is in agreement with the previous findings of Sections \ref{sec:JC} and \ref{sec:MZA}, which showed the inability of these models to take into account the softening of the behavior visible at low strain rates and low temperatures.
-
-From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results, with a higher reliability for the AR and ANN models compared to the other two models.
-Table \ref{tab:IntVal} shows a quantitative comparison on $\MARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates, on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
-It appears from this table that while the two models, AR and ANN, give equivalent (and excellent) results concerning the values of $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives a globally better result across the entire strain rate spectrum, with values of $\MARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively; that is to say, values that are approximately 2 to 3 times lower for the ANN model than for the AR model.
-
-This shows the superior reliability of the ANN model over to the 5 analytical models presented in this study both in terms of the interpolation capability of the model and of the overall behavior.
-
-%----------------------------------------------------------------------------------
-\subsection{Extrapolation validation}
-%----------------------------------------------------------------------------------
-
-For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0.01, 0.1, 1, 2]~\ps$.
-The strain rate omitted in this analysis therefore has the highest value, which restricts the training domain.
-
-In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as dots) for the 5 analytical models and the neural network.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\columnwidth]
+This finding is in agreement with the previous findings of \mbox{Sections \ref{sec:JC} and \ref{sec:MZA}}, which showed the inability of these models to take into account the softening of the behavior visible at low strain rates and low temperatures.
+
+From a general appearance point of view, the other four models, HS, AR, PTM, and ANN, give globally similar results, with a higher reliability for the AR and ANN models compared to the other two models.
+Table \ref{tab:IntVal} shows a quantitative comparison of the $\MARE$ and $\RMSE$ for three different cases: the 5 identified strain rates, only the strain rate $\mdot\varepsilon=1~\ps$, and all 6 strain rates for these six models.
+It appears from this table that, while the two models, AR and ANN, give equivalent (and excellent) results concerning the values of the $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives a globally better result across the entire strain rate spectrum, with values of $\MARE=0.96\%$ and $\RMSE=1.18~\MPa$, respectively, that is to say, values that are approximately 2- to 3-times lower for the ANN model than for the AR model.
+
+This shows the superior reliability of the ANN model over the five analytical models presented in this study both in terms of the interpolation capability of the model and of the overall behavior.
+
+%----------------------------------------------------------------------------------
+\subsection{Extrapolation Validation}
+%----------------------------------------------------------------------------------
+
+For the validation of the models' ability to extrapolate, the omitted strain rate chosen was $\mdot\varepsilon=5~\ps$ and those used for identification were $\mdot\varepsilon=[0.001, 0.01, 0.1, 1, 2]~\ps$.
+The strain rate omitted in this analysis, therefore, has the highest value, which restricts the training domain.
+
+In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as dots) for the five analytical models and the neural network.
+\begin{figure}[H]
+
+\includegraphics[width=0.98\columnwidth]
 {Figures/CompExt}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=5~\ps$}
+\caption{\hlok{Comparison} %MDPI: Should hyphen be changed to en dash in 3-15-7-1?.
+No, since, this will lead to longuer notations, I have used hyphen instead of en dash to reduce the width of the notation ANN-3-15-7-1-sigmoid for the model.
+ between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=5~\ps$.}
 \label{fig:CompExt}
@@
 Table \ref{tab:ExtVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the $5$ identified strain rates (lines referred as id.
-$\mdot\varepsilon$), the $6$ strain rates (lines referred as all $\mdot\varepsilon$) or only on the strain rate $\mdot\varepsilon=5~\ps$.
-\begin{table}[h!]
-\centering{}
-\caption{Accuracy coefficients of extrapolation for all models with $\mdot\varepsilon=5~\ps$}
-\begin{tabular}{llcccccc}
+$\mdot\varepsilon$), the $6$ strain rates (lines referred as all $\mdot\varepsilon$), or only on the strain rate $\mdot\varepsilon=5~\ps$.
+\begin{table}[H]
+
+\caption{Accuracy coefficients of extrapolation for all models with $\mdot\varepsilon=5~\ps$.}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\begin{tabularx}{\textwidth}{LLCCCCCC}
 \toprule
-\textbf{Strain rate} & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\
+\textbf{Strain Rate} & \textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\
 \midrule
@@
 \bottomrule
-\end{tabular}
+\end{tabularx}
 \label{tab:ExtVal}
@@
 
-As presented in the previous section regarding the interpolation capability of the models, in Figure \ref{fig:CompExt} it can be seen that the first two models, JC and MZA, in this study again do not have the ability to correctly reproduce the material behavior for the strain rate $\mdot\varepsilon=5~\ps$.
-The JC model performs better than the MZA model for $\mdot\varepsilon=5~\ps$, which is reflected in Table \ref{tab:ExtVal} by a lower value of $\MARE$ and $\RMSE$ for JC than for MZA.
+As presented in the previous section regarding the interpolation capability of the models, in Figure \ref{fig:CompExt}, it can be seen that the first two models, JC and MZA, in this study again do not have the ability to correctly reproduce the material behavior for the strain rate $\mdot\varepsilon=5~\ps$.
+The JC model performs better than the MZA model for $\mdot\varepsilon=5~\ps$, which is reflected in Table \ref{tab:ExtVal} by a lower value of the $\MARE$ and $\RMSE$ for JC than for MZA.
 Nevertheless, these values are too large for proper use.
@@
 
-The other 4 models, HS, AR, PTM and ANN, give better results with higher reliability for the AR and ANN models than for the other two models.
-Table \ref{tab:ExtVal} shows a comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
-The HS model performs worse in extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\MARE$ and $\RMSE$ greater than $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
-The two models, AR and ANN, give the best results for the values of $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
-This time, the AR model performs a little better on the $\mdot\varepsilon=5~\ps$ strain rate as compared to the ANN model, but the latter gives a globally better result across the entire strain rate spectrum, with values of $\MARE=1.09\%$ and $\RMSE=2.40~\MPa$ respectively.
-
-We can therefore conclude from this part of the study that the AR model is the best performing of the 5 analytical models presented, which is in agreement with the fact that it is widely used for thermomechanical processing, but the ANN model approach has advantages over the AR model approach in that, overall, the ANN model is more faithful to experimental data than is the AR model, for all strain rates.
+The other four models, HS, AR, PTM, and ANN, give better results with higher reliability for the AR and ANN models than for the other two models.
+Table \ref{tab:ExtVal} shows a comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these six models.
+The HS model performs worse in extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of the $\MARE$ and $\RMSE$ greater than $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
+The two models, AR and ANN, give the best results for the values of the $\MARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
+This time, the AR model performs a little better on the $\mdot\varepsilon=5~\ps$ strain rate as compared to the ANN model, but the latter gives a globally better result across the entire strain rate spectrum, with values of $\MARE=1.09\%$ and $\RMSE=2.40~\MPa$, respectively.
+
+We can, therefore, conclude from this part of the study that the AR model is the best-performing of the five analytical models presented, which is in agreement with the fact that it is widely used for thermomechanical processing, but the ANN model approach has advantages over the AR model approach in that, overall, the ANN model is more faithful to the experimental data than is the AR model, for all strain rates.
 
@@
 
-Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon alloy to investigate the applicability and predictive accuracy of 5 analytical models and an Artificial Neural Network model over a range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$).
-The analytical models selected for this study were the Johnson-Cook (JC) model \cite{Johnson-1983}, the Modified Zerilli-Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel-Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966} and the PTM model \cite{TizeMha-2022}.
-The ANN model selected is the one introduced by Pantalé \eal \cite{Pantale-2021}.
-An analysis of the data from the Gleeble trials and a comparison of the 6 models proposed in this study against the experiments led to the following conclusions.
-
-From an experimental point of view, it appears from the tests carried out that the flow stress $\sigma^y$ increases with a decrease of the temperature $T$ and an increase of the strain rate $\mdot\varepsilon$ due to the competitive appearance of the dynamic softening and work hardening mechanisms.
-The dynamic recrystallization (DRX) phenomenon, introduced through the difference between the maximum and permanent strains, shows a partially complete microstructure evolution.
+Experimental tests were performed on a Gleeble thermomechanical simulator for a modified medium carbon alloy to investigate the applicability and predictive accuracy of five analytical models and an artificial neural network model over a range of strains (0.0--0.7), strain rates (0.001~$\ps$--5~$\ps$), and temperatures (1050 $\celsius$--1250 $\celsius$).
+The analytical models selected for this study were the Johnson--Cook (JC) model \cite{Johnson-1983}, the Modified-Zerilli--Armstrong (MZA) model \cite{Samantaray-2009}, the Hansel--Spittle (HS) model \cite{Hensel-1978}, the Arrhenius (AR) model \cite{Sellars-1966}, and the PTM model \cite{TizeMha-2022}.
+The ANN model selected was the one introduced by Pantalé \eal \cite{Pantale-2021}.
+An analysis of the data from the Gleeble trials and a comparison of the six~models proposed in this study against the experiments led to the following conclusions.
+
+From an experimental point of view, it appeared from the tests carried out that the flow stress $\sigma^y$ increased with a decrease of the temperature $T$ and an increase of the strain rate $\mdot\varepsilon$ due to the competitive appearance of the dynamic softening and work hardening mechanisms.
+The dynamic recrystallization (DRX) phenomenon, introduced through the difference between the maximum and permanent strains, showed a partially complete microstructure evolution.
 Thus, at high strain rates, it is difficult to visualize the DRX phenomenon on the flow curves due to the sensitivity of this phenomenon to the strain rate.
-A study focused on an in-depth analysis of the microstructure of this steel alloy and its impact on mechanical properties is currently underway.
-
-Five analytical models and an Artificial Neural Network-based model were identified for this alloy.
-Among the analytical models, the JC and MZA models proved inadequate to reproduce the behavior of this material, while the HS, PTM and AR models showed their capabilities, presenting an acceptable $\MARE$ error (from $3.5\%$ to $7.7\%$).
+A study focused on an in-depth analysis of the microstructure of this steel alloy, and its impact on mechanical properties is currently underway.
+
+Five analytical models and an artificial-neural-network-based model were identified for this alloy.
+Among the analytical models, the JC and MZA models proved inadequate to reproduce the behavior of this material, while the HS, PTM, and AR models showed their capabilities, presenting an acceptable $\MARE$ error (from $3.5\%$ to $7.7\%$).
 The AR model (with a $3.56\%$ error) proved superior to the other two, thus justifying its use in thermomechanical processes.
-The ANN model is largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of medium carbon, with a $\MARE=0.62\%$.
+The ANN model was largely more accurate than the analytical models in predicting the flow stress $\sigma^y$ of medium carbon, with an $\MARE=0.62\%$.
 
 To test the performance of each proposed model, a study was conducted to evaluate the interpolation and extrapolation capability of the developed models.
-In the case of interpolation, the HS, PTM and AR models correlated well with the experiment, but the ANN model was superior, with an error factor 5 times lower than the AR model.
-For data extrapolation, the HS, PTM and AR models again correlated well with the experiment, but the ANN model once again performed better globally.
+In the case of interpolation, the HS, PTM, and AR models correlated well with the experiment, but the ANN model was superior, with an error factor five-times lower than the AR model.
+For data extrapolation, the HS, PTM, and AR models again correlated well with the experiment, but the ANN model once again performed better globally.
 
@@
 visualization, O.P.;
-supervision, M.J., A.T. and O.P.;
+supervision, M.J., A.T., and O.P.;
 project administration, M.J.;
@@
 
-\funding{This work was supported by the Natural Sciences and Engineering Research Council of Canada (NSERC) in the framework of a Collaborative Research and Development project (CRD) [Grant number 5364418].}
+\funding{This work was supported by the Natural Sciences and Engineering Research Council of Canada (NSERC) in the framework of a Collaborative Research and Development project (CRD) (Grant Number 5364418).}
 
@@
 
-\acknowledgments{The authors acknowledge Mr.
-Jean-Benoit Morin, Director of Metallurgy and Quality from Finkl Steel-Sorel, Dr.
-Abdelhalim Loucif from R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d’Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}
+\acknowledgments{The authors acknowledge \hlok{Jean}-Benoit Morin, \hlok{Director of} %MDPI: Titles should be removed in this part. Please revise
+ Metallurgy and Quality from Finkl Steel-Sorel, \hlok{Abdelhalim} Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK
 
@@
 \begin{tabular}{@{}ll}
-ANN & Artificial Neural Network \\
+ANN & Artificial neural network \\
 AR & Arrhenius \\
-CPU & Central Processing Unit \\
-DRV & Dynamic Recovery\\
-DRX & Dynamic Recrystallization \\
-FEA & Finite Element Analysis \\
-HS & Hansel-Spittel \\
-JC & Johnson-Cook \\
-MZA & Modified Zerilli-Armstrong \\
-WH & Work Hardening \\
-ZA & Zerilli-Armstrong
+CPU & Central processing unit \\
+DRV & Dynamic recovery\\
+DRX & Dynamic recrystallization \\
+FEA & Finite element analysis \\
+HS & Hansel--Spittel \\
+JC & Johnson--Cook \\
+MZA & Modified-Zerilli--Armstrong \\
+WH & Work hardening \\
+ZA & Zerilli--Armstrong
 \end{tabular}
@@
 
-We report here after the computing process and the $180$ coefficients of the Artificial Neural Network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
-In order to use this model, we describe here after the details of the procedure to compute the flow stress $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$.
-This process can be decomposed into 3 phases:
+We report hereafter the computing process and the $180$ coefficients of the artificial neural network ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
+In order to use this model, we describe hereafter the details of the procedure to compute the flow stress $\sigma^y$ from the input variables $\varepsilon^p$, $\mdot\varepsilon$, and $T$.
+This process can be decomposed into three phases:
 \begin{itemize}
-\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid an ill-conditioned system as presented by many other authors in the literature \cite{Lin-2008-ANN, stoffel2020deep}.
-Therefore, the three components of the input vector $\overrightarrow{x}$ are obtained from the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$ and the temperature $T$ using the following expressions:
+\item We first have to normalize the input values of the ANN $x_i$ within the range $[0,1]$ to avoid an ill-conditioned system, as presented by many other authors in the literature~\cite{Lin-2008-ANN, stoffel2020deep}.
+Therefore, the three components of the input vector $\overrightarrow{x}$ are obtained from the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$, and the temperature $T$ using the following expressions:
 \begin{equation}
@@
 \end{equation}
-where $[~]_{min}$ and $[~]_{max}$ are the boundaries of the range of the corresponding field: $\varepsilon^p\!\in\!\left[0.0,0.7\right]$, $\mdot{\varepsilon}\!\in\!\left[0.001~\ps,5.0~\ps\right]$, $T\!\in\!\left[1050~\celsius,1250~\celsius\right]$ and $\sigma\!\in\!\left[1.311~\MPa,153.739~\MPa\right]$.
+where $[~]_{min}$ and $[~]_{max}$ are the boundaries of the range of the corresponding field: $\varepsilon^p\!\in\!\left[0.0,0.7\right]$, $\mdot{\varepsilon}\!\in\!\left[0.001~\ps,5.0~\ps\right]$, $T\!\in\!\left[1050~\celsius,1250~\celsius\right]$, and $\sigma\!\in\!$ $[1.311~\MPa,$ $153.739~\MPa]$.
 The reference strain rate is $\mdot{\varepsilon_0} = 0.001~\ps$.
@@
 
-Conforming to the computing process proposed by Equations (\ref{eq:CR1}-\ref{eq:CR2}), we report hereafter the $180$ coefficients of the ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
+Conforming to the computing process proposed by Equations (\ref{eq:CR1})--(\ref{eq:CR2}), we report hereafter the $180$ coefficients of the ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
 The weight matrix for the first hidden layer $\w_1$ is a $15\times3$ matrix:
@@
 \end{equation*}
-The biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
+
+\hlok{The} %MDPI: We added indent. OK
+ biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
 \begin{equation*}
@@
 \end{equation*}
-The weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
+
+\hlok{The} weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
 \begin{equation*}
@@
 \end{equation*}
-The biases of the second hidden layer $\overrightarrow{b_2}$ is a 7-component vector:
+
+\hlok{The} biases of the second hidden layer $\overrightarrow{b_2}$ is a seven-component vector:
 \begin{equation*}
@@
 \end{equation*}
-The weight vector for the output layer $\overrightarrow{w}$ is a 7-component vector:
+
+\hlok{The} weight vector for the output layer $\overrightarrow{w}$ is a seven-component vector:
 \begin{equation*}
@@
 \end{equation*}
-The bias of the output layer $b$ is a scalar:
+
+\hlok{The} bias of the output layer $b$ is a scalar:
 \begin{equation*}
@@
 %=====================================
-\bibliography{Bibliography}
+\begin{thebibliography}{999}
+
+\bibitem[Chadha \em{et~al.}(2017)Chadha, Shahriari, Tremblay, Bhattacharjee,
+ and Jahazi]{chadha2017deformation}
+Chadha, K.; Shahriari, D.; Tremblay, R.; Bhattacharjee, P.P.; Jahazi, M.
+\newblock Deformation and recrystallization behavior of the cast structure in
+ large size, high strength steel ingots: Experimentation and modeling.
+\newblock {\em Metall. Mater. Trans. A} {\bf 2017}, {\em
+ 48},~4297--4313.
+\newblock {\url{https://doi.org/10.1007/s11661-017-4177-8}}.
+
+\bibitem[Chadha \em{et~al.}(2018)Chadha, Ahmed, Aranas~Jr, Shahriari, and
+ Jahazi]{chadha2018influence}
+Chadha, K.; Ahmed, Z.; Aranas, C.,~Jr.; Shahriari, D.; Jahazi, M.
+\newblock Influence of strain rate on dynamic transformation of austenite in an
+ as-cast medium-carbon low-alloy steel.
+\newblock {\em Materialia} {\bf 2018}, {\em 1},~155--167.
+\newblock {\url{https://doi.org/10.1016/j.mtla.2018.04.006}}.
+
+\bibitem[Murugesan and Jung(2019)]{murugesan2019two}
+Murugesan, M.; Jung, D.W.
+\newblock {Two flow stress models for describing hot deformation behavior of
+ AISI-1045 medium carbon steel at elevated temperatures}.
+\newblock {\em Heliyon} {\bf 2019}, {\em 5},~e01347.
+\newblock {\url{https://doi.org/10.1016/j.heliyon.2019.e01347}}.
+
+\bibitem[Murugesan \em{et~al.}(2019)Murugesan, Sajjad, and
+ Jung]{murugesan2019hybrid}
+Murugesan, M.; Sajjad, M.; Jung, D.W.
+\newblock {Hybrid machine learning optimization approach to predict hot
+ deformation behavior of medium carbon steel material}.
+\newblock {\em Metals} {\bf 2019}, {\em 9},~1315.
+\newblock {\url{https://doi.org/10.3390/met9121315}}.
+
+\bibitem[Chadha \em{et~al.}(2020)Chadha, Tian, Bocher, Spray, and
+ Aranas~Jr]{chadha2020microstructure}
+Chadha, K.; Tian, Y.; Bocher, P.; Spray, J.G.; Aranas, C.,~Jr.
+\newblock Microstructure evolution, mechanical properties and deformation
+ behavior of an additively manufactured maraging steel.
+\newblock {\em Materials} {\bf 2020}, {\em 13},~2380.
+\newblock {\url{https://doi.org/10.3390/ma13102380}}.
+
+\bibitem[Sripada \em{et~al.}(2022)Sripada, Tian, Chadha, Saha, Jahazi, Spray,
+ and Aranas~Jr]{sripada2022effect}
+Sripada, J.; Tian, Y.; Chadha, K.; Saha, G.; Jahazi, M.; Spray, J.; Aranas,
+ C.,~Jr.
+\newblock Effect of hot isostatic pressing on microstructural and
+ micromechanical properties of additively manufactured 17--4PH steel.
+\newblock {\em Mater. Charact.} {\bf 2022}, {\em 192},~112174.
+\newblock {\url{https://doi.org/10.1016/j.matchar.2022.112174}}.
+
+\bibitem[Tian \em{et~al.}(2022)Tian, Chadha, and Aranas]{tian2022deformation}
+Tian, Y.; Chadha, K.; Aranas, C.
+\newblock Deformation-Induced Strengthening Mechanism in a Newly Designed L-40
+ Tool Steel Manufactured by Laser Powder Bed Fusion.
+\newblock {\em Acta Metall. Sin. (Engl. Lett.)} {\bf 2022}, \hlok{\emph{36}, 21--34}.
+\newblock {\url{https://doi.org/10.1007/s40195-022-01461-z}}.%MDPI: Highlight without comment: newly added/revised information. Following are the same. Please confirm: OK
+
+\bibitem[Tavakoli \em{et~al.}(2019)Tavakoli, Mirzadeh, and
+ Zamani]{tavakoli2019ferrite}
+Tavakoli, M.; Mirzadeh, H.; Zamani, M.
+\newblock {Ferrite recrystallisation and intercritical annealing of cold-rolled
+ low alloy medium carbon steel}.
+\newblock {\em Mater. Sci. Technol.} {\bf 2019}, {\em
+ 35},~1932--1941.
+\newblock {\url{https://doi.org/10.1080/02670836.2019.1655862}}.
+
+\bibitem[Ebrahimi \em{et~al.}(2017)Ebrahimi, Momeni, Kazemi, and
+ Alinejad]{ebrahimi2017flow}
+Ebrahimi, G.; Momeni, A.; Kazemi, S.; Alinejad, H.
+\newblock {Flow curves, dynamic recrystallization and precipitation in a medium
+ carbon low alloy steel}.
+\newblock {\em Vacuum} {\bf 2017}, {\em 142},~135--145.
+\newblock {\url{https://doi.org/10.1016/j.vacuum.2017.05.010}}.
+
+\bibitem[Shi \em{et~al.}(2022)Shi, Zhang, He, Zhan, Gao, and
+ Li]{shi2022constitutive}
+Shi, D.; Zhang, F.; He, Z.; Zhan, Z.; Gao, W.; Li, Z.
+\newblock {Constitutive equation and dynamic recovery mechanism of high
+ strength cast Al-Cu-Mn alloy during hot deformation}.
+\newblock {\em Mater. Today Commun.} {\bf 2022}, {\em 33},~104199.
+\newblock {\url{https://doi.org/10.1016/j.mtcomm.2022.104199}}.
+
+\bibitem[Zeng \em{et~al.}(2022)Zeng, Hu, Peng, Hu, and
+ Xiao]{zeng2022constitutive}
+Zeng, S.; Hu, S.; Peng, B.; Hu, K.; Xiao, M.
+\newblock {The constitutive relations and thermal deformation mechanism of
+ nickel aluminum bronze}.
+\newblock {\em Mater. Des.} {\bf 2022}, {\em 220},~110853.
+\newblock {\url{https://doi.org/10.1016/j.matdes.2022.110853}}.
+
+\bibitem[Rudra \em{et~al.}(2019)Rudra, Das, and
+ Dasgupta]{rudra2019constitutive}
+Rudra, A.; Das, S.; Dasgupta, R.
+\newblock {Constitutive modeling for hot deformation behavior of Al-5083+ SiC
+ composite}.
+\newblock {\em J. Mater. Eng. Perform.} {\bf 2019},
+ {\em 28},~87--99.
+\newblock {\url{https://doi.org/10.1007/s11665-018-3813-9}}.
+
+\bibitem[Jia \em{et~al.}(2022)Jia, Chen, Rusinek, and Zhou]{jia2022thermo}
+Jia, B.; Chen, P.; Rusinek, A.; Zhou, Q.
+\newblock Thermo-viscoplastic behavior of DP800 steel at quasi-static,
+ intermediate, high and ultra-high strain rates.
+\newblock {\em Int. J. Mech. Sci.} {\bf 2022}, \hl{\emph{226}},
+ 107408.
+\newblock {\url{https://doi.org/10.1016/j.ijmecsci.2022.107408}}.
+
+\bibitem[Costa \em{et~al.}(2016)Costa, Mendon{\c{c}}a, and
+ Peixinho]{costa2016study}
+Costa, S.L.; Mendon{\c{c}}a, J.P.; Peixinho, N.
+\newblock Study on the impact behaviour of a new safety toe cap model made of
+ ultra-high-strength steels.
+\newblock {\em Mater. Des.} {\bf 2016}, {\em 91},~143--154.
+\newblock {\url{https://doi.org/10.1016/j.matdes.2015.11.082}}.
+
+\bibitem[Rudnytskyj \em{et~al.}(2020)Rudnytskyj, Simon, Jech, and
+ Gachot]{rudnytskyj2020constitutive}
+\hlok{Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C.} %MDPI: Refs 15 and 53 are the same. Please check and revise it. Ref 53, has been removed and cross references in the text changed.
+\newblock Constitutive modelling of the 6061 aluminium alloy under hot rolling
+ conditions and large strain ranges.
+\newblock {\em Mater. Des.} {\bf 2020}, {\em 190},~108568.
+\newblock {\url{https://doi.org/10.1016/j.matdes.2020.108568}}.
+
+\bibitem[Pantalé \em{et~al.}(2022)Pantalé, Tize~Mha, and
+ Tongne]{Pantale-2021}
+Pantalé, O.; Tize~Mha, P.; Tongne, A.
+\newblock {Efficient implementation of nonlinear flow law using neural network
+ into the Abaqus Explicit FEM code}.
+\newblock {\em Finite Elem. Anal. Des.} {\bf 2022}, {\em
+ 198},~103647.
+\newblock {\url{https://doi.org/10.1016/j.finel.2021.103647}}.
+
+\bibitem[Johnson and Cook(1983)]{Johnson-1983}
+Johnson, G.R.; Cook, W.H.
+\newblock {A constitutive model and data for materials subjected to large strains, high strain rates, and high temperatures}.
+\newblock {In Proceedings of the 7th International Symposium on Ballistics, The
+ Hague, The Netherlands, 19--21 April} {1983}; \hlok{pp. 541--547}.
+%\newblock {\url{https://doi.org/10.1299/kikaia.65.1412}}. Wrong doi, doesn't exists
+
+\bibitem[Chadha \em{et~al.}(2018)Chadha, Shahriari, and
+ Jahazi]{chadha2018approach}
+\hlok{Chadha, K.; Shahriari, D.; Jahazi, M.} %MDPI: Refs 18 and 51 are the same. Please check and revise it. Ok, Ref 51 has been removed and crossref has been updated in the text
+\newblock An approach to develop Hansel--Spittel constitutive equation during
+ ingot breakdown operation of low alloy steels. In {\em Frontiers in Materials
+ Processing, Applications, Research and Technology}; Springer: \hlok{Berlin/Heidelberg, Germany,} %newly added information, please confirm: OK
+ 2018; pp.
+ 239--246.
+\newblock {\url{https://doi.org/10.1007/978-981-10-4819-7_20}}.
+
+\bibitem[Zerilli and Armstrong(1987)]{Zerilli-1987}
+Zerilli, F.J.; Armstrong, R.W.
+\newblock {Dislocation‐mechanics‐based constitutive relations for material
+ dynamics calculations}.
+\newblock {\em J. Appl. Phys.} {\bf 1987}, {\em 61},~1816--1825.
+\newblock {\url{https://doi.org/10.1063/1.338024}}.
+
+\bibitem[Jia \em{et~al.}(2021)Jia, Guan, Zang, Wang, and Lei]{Jia-2021}
+\hlok{Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Lei, M.} %MDPI: Refs 20 and 25 are the same. Please check and revise it: Ref 25 removed and crossref updated in text.
+\newblock {Modified Johnson--Cook model of aluminum alloy 6016-T6 sheets at low
+ dynamic strain rates}.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2021}, {\em
+ 820},~141565.
+\newblock {\url{https://doi.org/10.1016/j.msea.2021.141565}}.
+
+\bibitem[Liu \em{et~al.}(2021)Liu, Ma, and Fan]{liu2021modified}
+Liu, X.; Ma, H.; Fan, F.
+\newblock {Modified Johnson--Cook model of SWRH82B steel under different
+ manufacturing and cold-drawing conditions}.
+\newblock {\em J. Constr. Steel Res.} {\bf 2021}, {\em
+ 186},~106894.
+\newblock \hlok{{\url{https://doi.org/10.1016/j.jcsr.2021.106894}}}. % Corrected doi
+
+\bibitem[Jia \em{et~al.}(2022)Jia, Zhang, Rusinek, Xiao, Chai, and
+ Gu]{jia2022thermo1}
+Jia, B.; Zhang, Y.; Rusinek, A.; Xiao, X.; Chai, R.; Gu, G.
+\newblock {Thermo-viscoplastic behavior and constitutive relations for 304
+ austenitic stainless steel over a wide range of strain rates covering
+ quasi-static, medium, high and very high regimes}.
+\newblock {\em Int. J. Impact Eng.} {\bf 2022}, {\em
+ 164},~104208.
+\newblock {\url{https://doi.org/10.1016/j.ijimpeng.2022.104208}}.
+
+\bibitem[Bai \em{et~al.}(2022)Bai, Huo, He, Bian, Ren, and
+ Du]{bai2022comparison}
+Bai, J.; Huo, Y.; He, T.; Bian, Z.; Ren, X.; Du, X.
+\newblock {Comparison of Five Different Models Predicting the Hot Deformation
+ Behavior of EA4T Steel}.
+\newblock {\em J. Mater. Eng. Perform.} {\bf 2022},
+ \hl{\emph{31}, 8169--8182.}
+\newblock {\url{https://doi.org/10.1007/s11665-022-06828-y}}.
+
+\bibitem[Zhu and Ou(2022)]{zhu2022constitutive}
+Zhu, H.; Ou, H.
+\newblock {Constitutive modelling of hot deformation behaviour of metallic
+ materials}.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2022}, {\em
+ 832},~142473.
+\newblock {\url{https://doi.org/10.1016/j.msea.2021.142473}}.
+
+% REMOVED duplicated reference
+%\bibitem[Jia \em{et~al.}(2021)Jia, Guan, Zang, Wang, and Mu]{Jia-2021}
+%\hl{Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Mu, L.}
+%\newblock {Modified Johnson--Cook model of aluminum alloy 6016-T6 sheets at low
+% dynamic strain rates}.
+%\newblock {\em Mater. Sci. Eng. A} {\bf 2021}, {\em
+% 820},~141565.
+%\newblock {\url{https://doi.org/10.1016/j.msea.2021.141565}}.
+
+\bibitem[Sim \em{et~al.}(2022)Sim, Ri, Jo, Kim, Kim, and Pak]{sim2022modified}
+Sim, K.H.; Ri, Y.C.; Jo, C.H.; Kim, O.J.; Kim, R.S.; Pak, H.
+\newblock {Modified Zerilli--Armstrong and Khan-Huang-Liang constitutive models
+ to predict hot deformation behavior in a powder metallurgy Ti-22Al-25Nb
+ alloy}.
+\newblock {\em Vacuum} {\bf 2022}, \emph{210}, \hlok{111749.} %MDPI: Please add volume. Vol 210 added and doi corrected.
+\newblock \hlok{{\url{https://doi.org/10.1016/j.vacuum.2022.111749}}}.
+
+\bibitem[Li \em{et~al.}(2013)Li, Wang, Duan, and Liu]{Li-2013}
+Li, H.Y.; Wang, X.F.; Duan, J.Y.; Liu, J.J.
+\newblock {A modified Johnson Cook model for elevated temperature flow behavior
+ of T24 steel}.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2013}, {\em
+ 577},~138--146.
+\newblock {\url{https://doi.org/10.1016/j.msea.2013.04.041}}.
+
+\bibitem[Zhang \em{et~al.}(2015)Zhang, Shangguan, Xie, and Liu]{Zhang-2015}
+Zhang, D.N.; Shangguan, Q.Q.; Xie, C.J.; Liu, F.
+\newblock {A modified Johnson–Cook model of dynamic tensile behaviors for
+ 7075-T6 aluminum alloy}.
+\newblock {\em J. Alloys Compd.} {\bf 2015}, {\em
+ 619},~186--194.
+\newblock {\url{https://doi.org/10.1016/j.jallcom.2014.09.002}}.
+
+\bibitem[Zhou \em{et~al.}(2019)Zhou, Ji, and Zhu]{Zhou-2019}
+Zhou, Q.; Ji, C.; Zhu, M.Y.
+\newblock {Research on several constitutive models to predict the flow
+ behaviour of GCr15 continuous casting bloom with heavy reduction}.
+\newblock {\em Mater. Res. Express} {\bf 2019}, {\em 6},~1265f2.
+\newblock {\url{https://doi.org/10.1088/2053-1591/ab52c2}}.
+
+\bibitem[Ovesy \em{et~al.}(2020)Ovesy, Aeschlimann, and
+ Zysset]{ovesy2020explicit}
+Ovesy, M.; Aeschlimann, M.; Zysset, P.K.
+\newblock {Explicit finite element analysis can predict the mechanical response
+ of conical implant press-fit in homogenized trabecular bone}.
+\newblock {\em J. Biomech.} {\bf 2020}, {\em 107},~109844.
+\newblock {\url{https://doi.org/10.1016/j.jbiomech.2020.109844}}.
+
+\bibitem[Niu \em{et~al.}(2020)Niu, Zhao, Li, Wang, Luo, and
+ Zhang]{niu2020constitutive}
+Niu, D.; Zhao, C.; Li, D.; Wang, Z.; Luo, Z.; Zhang, W.
+\newblock {Constitutive modeling of the flow stress behavior for the hot
+ deformation of Cu-15Ni-8Sn alloys}.
+\newblock {\em Front. Mater.} {\bf 2020}, {\em 7},~577867.
+\newblock {\url{https://doi.org/10.3389/fmats.2020.577867}}.
+
+\bibitem[Lennon and Ramesh(2017)]{Muralli-2017}
+Lennon, A.M.; Ramesh, K.T.
+\newblock {On the performance of modified Zerilli--Armstrong constitutive model
+ in simulating the metal-cutting process}.
+\newblock {\em J. Manuf. Process.} {\bf 2017}, {\em
+ 28},~253--265.
+\newblock {\url{https://doi.org/10.1016/j.jmapro.2017.06.011}}.
+
+\bibitem[Cheng and Mahnken(2021)]{Cheng-2021}
+Cheng, C.; Mahnken, R.
+\newblock {A modified Zerilli–Armstrong model as the asymmetric visco-plastic
+ part of a multi-mechanism model for cutting simulations}.
+\newblock {\em Arch. Appl. Mech.} {\bf 2021}, \hl{\emph{91}, 3869--3888}.
+\newblock {\url{https://doi.org/10.1007/s00419-021-01982-6}}.
+
+\bibitem[Gurusamy \em{et~al.}(2021)Gurusamy, Palaniappan, Murthy, and
+ Rao]{Muralli-2021}
+Gurusamy, M.; Palaniappan, K.; Murthy, H.; Rao, B.C.
+\newblock {A Finite Element Study of Large Strain Extrusion Machining Using
+ Modified Zerilli–Armstrong Constitutive Relation}.
+\newblock {\em J. Manuf. Sci. Eng.} {\bf 2021},
+ {\em 143}, \hl{101004}.
+\newblock {\url{https://doi.org/10.1115/1.4050652}}.
+
+\bibitem[Derazkola \em{et~al.}(2021)Derazkola, Garc{\'\i}a~Gil,
+ Murillo-Marrod{\'a}n, and M{\'e}resse]{derazkola2021review}
+Derazkola, H.A.; Garc{\'\i}a~Gil, E.; Murillo-Marrod{\'a}n, A.; M{\'e}resse, D.
+\newblock {Review on Dynamic Recrystallization of Martensitic Stainless Steels
+ during Hot Deformation: Part I—Experimental Study}.
+\newblock {\em Metals} {\bf 2021}, {\em 11},~572.
+\newblock {\url{https://doi.org/10.3390/met11040572}}.
+
+\bibitem[Wang \em{et~al.}(2022)Wang, Yang, Gao, and Guan]{wang2022deformation}
+Wang, Y.; Yang, B.; Gao, M.; Guan, R.
+\newblock {Deformation behavior and dynamic recrystallization during hot
+ compression in homogenized Al--6Mg--0.8 Mn alloys}.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2022}, {\em
+ 840},~142953.
+\newblock {\url{https://doi.org/10.1016/j.msea.2022.142953}}.
+
+\bibitem[Miao \em{et~al.}(2022)Miao, Sutton, and Luo]{miao2022deformation}
+Miao, J.; Sutton, S.; Luo, A.A.
+\newblock {Deformation microstructure and thermomechanical processing maps of
+ homogenized AA2070 aluminum alloy}.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2022}, {\em
+ 834},~142619.
+\newblock {\url{https://doi.org/10.1016/j.msea.2022.142619}}.
+
+\bibitem[Rudnytskyj \em{et~al.}(2022)Rudnytskyj, Varga, Krenn, Vorlaufer,
+ Leimhofer, Jech, and Gachot]{rudnytskyj2022investigating}
+Rudnytskyj, A.; Varga, M.; Krenn, S.; Vorlaufer, G.; Leimhofer, J.; Jech, M.;
+ Gachot, C.
+\newblock {Investigating the relationship of hardness and flow stress in metal
+ forming}.
+\newblock {\em Int. J. Mech. Sci.} {\bf 2022}, {\em
+ 232},~107571.
+\newblock {\url{https://doi.org/10.1016/j.ijmecsci.2022.107571}}.
+
+\bibitem[Ji \em{et~al.}(2020)Ji, Duan, Li, Li, Huang, Pei, and
+ Lu]{ji2020optimization}
+Ji, H.; Duan, H.; Li, Y.; Li, W.; Huang, X.; Pei, W.; Lu, Y.
+\newblock {Optimization the working parameters of as-forged 42CrMo steel by
+ constitutive equation-dynamic recrystallization equation and processing
+ maps}.
+\newblock {\em J. Mater. Res. Technol.} {\bf 2020}, {\em
+ 9},~7210--7224.
+\newblock {\url{https://doi.org/10.1016/j.jmrt.2020.04.078}}.
+
+\bibitem[Tize~Mha \em{et~al.}(2022)Tize~Mha, Tongne, and
+ Pantal{\'e}]{TizeMha-2022}
+\textls[-25]{Tize~Mha, P.; Tongne, A.; Pantal{\'e}, O.
+\newblock {A generalized nonlinear flow law based on modified
+ Zerilli--Armstrong model and its implementation into Abaqus/Explicit FEM
+ Code}.
+\newblock {\em World J. Eng. Technol.} {\bf 2022}, {\em
+ 10},~334--362.
+\newblock {\url{https://doi.org/10.4236/wjet.2022.102021}}.}
+
+\bibitem[Wu \em{et~al.}(2022)Wu, Liu, Li, and Lu]{wu2022experimental}
+Wu, Z.; Liu, Z.; Li, L.; Lu, Z.
+\newblock {Experimental and neural networks analysis on elevated-temperature
+ mechanical properties of structural steels}.
+\newblock {\em Mater. Today Commun.} {\bf 2022}, {\em 32},~104092.
+\newblock {\url{https://doi.org/10.1016/j.mtcomm.2022.104092}}.
+
+\bibitem[Stoffel \em{et~al.}(2020)Stoffel, Bamer, and Markert]{stoffel2020deep}
+Stoffel, M.; Bamer, F.; Markert, B.
+\newblock {Deep convolutional neural networks in structural dynamics under
+ consideration of viscoplastic material behaviour}.
+\newblock {\em Mech. Res. Commun.} {\bf 2020}, {\em
+ 108},~103565.
+\newblock {\url{https://doi.org/10.1016/j.mechrescom.2020.103565}}.
+
+\bibitem[Ashtiani and Shahsavari(2016)]{Ashtiani-2016-CSP}
+Ashtiani, H.R.; Shahsavari, P.
+\newblock {A comparative study on the phenomenological and artificial neural
+ network models to predict hot deformation behavior of AlCuMgPb alloy}.
+\newblock {\em J. Alloys Compd.} {\bf 2016}, {\em
+ 687},~263--273.
+\newblock {\url{https://doi.org/10.1016/j.jallcom.2016.04.300}}.
+
+\bibitem[Stoffel \em{et~al.}(2019)Stoffel, Bamer, and
+ Markert]{Stoffel-2019-NNB}
+Stoffel, M.; Bamer, F.; Markert, B.
+\newblock {Neural network based constitutive modeling of nonlinear viscoplastic
+ structural response}.
+\newblock {\em Mech. Res. Commun.} {\bf 2019}, {\em 95},~85--88.
+\newblock {\url{https://doi.org/10.1016/j.mechrescom.2019.01.004}}.
+
+\bibitem[Pantalé(2023)]{Pantale-2023}
+Pantalé, O.
+\newblock Development and Implementation of an ANN Based Flow Law for Numerical
+ Simulations of Thermo-Mechanical Processes at High Temperatures in FEM
+ Software.
+\newblock {\em Algorithms} {\bf 2023}, {\em 16}, \hl{56}.
+\newblock {\url{https://doi.org/10.3390/a16010056}}.
+
+\bibitem[Galos \em{et~al.}(2022)Galos, Das, Sutcliffe, and
+ Mouritz]{galos2022review}
+Galos, J.; Das, R.; Sutcliffe, M.P.; Mouritz, A.P.
+\newblock {Review of balsa core sandwich composite structures}.
+\newblock {\em Mater. Des.} {\bf 2022}, \hl{\em 221}, 111013.
+\newblock {\url{https://doi.org/10.1016/j.matdes.2022.111013}}.
+
+\bibitem[Phaniraj and Lahiri(2003)]{Phaniraj-2003}
+Phaniraj, M.P.; Lahiri, A.K.
+\newblock {The applicability of neural network model to predict flow stress for
+ carbon steels}.
+\newblock {\em J. Mater. Process. Technol.} {\bf 2003}, {\em
+ 141},~219--227.
+\newblock {\url{https://doi.org/10.1016/S0924-0136(02)01123-8}}.
+
+\bibitem[Zhu \em{et~al.}(2022)Zhu, Chen, Hou, and Wang]{zhu2022thermal}
+Zhu, Y.; Chen, Y.; Hou, D.; Wang, Z.
+\newblock {Thermal effect on dislocation interactions in magnesium alloy}.
+\newblock {\em Materialia} {\bf 2022}, {\em 26},~101579.
+\newblock {\url{https://doi.org/10.1016/j.mtla.2022.101579}}.
+
+\bibitem[Samantaray \em{et~al.}(2009)Samantaray, Mandal, Borah, Bhaduri, and
+ Sivaprasad]{Samantaray-2009}
+Samantaray, D.; Mandal, S.; Borah, U.; Bhaduri, A.K.; Sivaprasad, P.V.
+\newblock {A thermo-viscoplastic constitutive model to predict
+ elevated-temperature flow behaviour in a titanium-modified austenitic
+ stainless steel}.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2009}, {\em
+ 526},~1--6.
+\newblock {\url{https://doi.org/10.1016/j.msea.2009.08.009}}.
+
+\bibitem[Hensel and Spittel(1978)]{Hensel-1978}
+Hensel, A.; Spittel, T.
+\newblock {\em {Kraft- und Arbeitsbedarf Bildsamer Formgebungsverfahren}};
+ Deutscher Verlag f{\"u}r Grundstoffindustrie: \hl{Leipzig, Germany}, 1978.
+
+% REMOVED duplicated reference
+%\bibitem[Chadha \em{et~al.}(2018)Chadha, Shahriari, and Jahazi]{chadha2018approach}
+%\hl{Chadha, K.; Shahriari, D.; Jahazi, M.}
+%\newblock {An Approach to Develop Hansel–Spittel Constitutive Equation during
+% Ingot Breakdown Operation of Low Alloy Steels}. In {\em Frontiers in
+% Materials Processing, Applications, Research and Technology}; Springer: \hl{Berlin/Heidelberg, Germany,} %newly added information, please confirm
+% 2018; pp. 239--246.
+%\newblock {\url{https://doi.org/10.1007/978-981-10-4819-7_20}}.
+
+\bibitem[El~Mehtedi \em{et~al.}(2015)El~Mehtedi, Spigarelli, Gabrielli, and
+ Donati]{Mehtedi-2015}
+El~Mehtedi, M.; Spigarelli, S.; Gabrielli, F.; Donati, L.
+\newblock {Comparison Study of Constitutive Models in Predicting the Hot
+ Deformation Behavior of AA6060 and AA6063 Aluminium Alloys}.
+\newblock {\em Mater. Today Proc.} {\bf 2015}, {\em 2},~4732--4739.
+\newblock {\url{https://doi.org/10.1016/j.matpr.2015.10.006}}.
+
+% REMOVED duplicated reference
+%\bibitem[Rudnytskyj \em{et~al.}(2020)Rudnytskyj, Simon, Jech, and
+% Gachot]{Rudnytskyj-2020}\hl{
+%Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C.}
+%\newblock {Constitutive modelling of the 6061 aluminium alloy under hot rolling
+% conditions and large strain ranges}.
+%\newblock {\em Mater. Des.} {\bf 2020}, {\em 190},~108568.
+%\newblock {\url{https://doi.org/10.1016/j.matdes.2020.108568}}.
+
+\bibitem[Newville \em{et~al.}(2016)Newville, Stensitzki, Allen, Rawlik,
+ Ingargiola, and Nelson]{Newville-2016}
+Newville, M.; Stensitzki, T.; Allen, D.B.; Rawlik, M.; Ingargiola, A.; Nelson,
+ A.
+\newblock {\em LMFIT: Non-Linear Least-Square Minimization and Curve-Fitting for
+ Python};
+\newblock \hlok{Astrophysics Source Code Library}: {2016}; p. ascl:1606.014.%MDPI: Please add publisher location. There is no published location for ASCL, it's online: see https://ascl.net
+
+\bibitem[Sellars and McTegart(1966)]{Sellars-1966}
+Sellars, C.; McTegart, W.
+\newblock {On the mechanism of hot deformation}.
+\newblock {\em Acta Metall.} {\bf 1966}, {\em 14},~1136--1138.
+\newblock {\url{https://doi.org/10.1016/0001-6160(66)90207-0}}.
+
+\bibitem[Zener and Hollomon(1944)]{Zener-1944}
+Zener, C.; Hollomon, J.H.
+\newblock {Effect of Strain Rate Upon Plastic Flow of Steel}.
+\newblock {\em J. Appl. Phys.} {\bf 1944}, {\em 15},~22--32.
+\newblock {\url{https://doi.org/10.1063/1.1707363}}.
+
+\bibitem[Abadi \em{et~al.}(2016)Abadi, Barham, Chen, Chen, Davis, Dean, Devin,
+ Ghemawat, Irving, Isard, Kudlur, Levenberg, Monga, Moore, Murray, Steiner,
+ Tucker, Vasudevan, Warden, Wicke, Yu, and Zheng]{Abadi-2016}
+Abadi, M.; Barham, P.; Chen, J.; Chen, Z.; Davis, A.; Dean, J.; Devin, M.;
+ Ghemawat, S.; Irving, G.; Isard, M.; et~al.
+\newblock {TensorFlow: A System for Large-Scale Machine Learning}.
+\newblock In Proceedings of the 12th {{USENIX}} Conference
+ on {{Operating Systems Design}} and {{Implementation}}, {{OSDI}}'16, \hl{Savannah, GA, USA, 2--4 November 2016}; {USENIX Association}:
+\hl{Berkeley, CA,} {USA}, 2016; pp. 265--283.
+
+\bibitem[Kingma and Lei(2015)]{Kingma-2015}
+Kingma, D.P.; Lei, J.
+\newblock {Adam: A method for stochastic optimization} \hl{\emph{arXiv}} {\bf 2015}, \hl{arXiv.1412.6980.}
+%\newblock \hlok{p.~15.} %MDPI: Should it be kept?. Removed
+\newblock {\url{https://doi.org/10.48550/arXiv.1412.6980}}.
+
+\bibitem[Liang \em{et~al.}(2022)Liang, Kong, Zhang, and Li]{Liang-2022}
+Liang, P.; Kong, N.; Zhang, J.; Li, H.
+\newblock {A Modified Arrhenius-Type Constitutive Model and its Implementation
+ by Means of the Safe Version of Newton–Raphson Method}.
+\newblock {\em Steel Res. Int.} {\bf 2022}.
+\newblock {\url{https://doi.org/10.1002/srin.202200443}}.
+
+\bibitem[Lin \em{et~al.}(2008)Lin, Zhang, and Zhong]{Lin-2008-ANN}
+Lin, Y.; Zhang, J.; Zhong, J.
+\newblock {Application of neural networks to predict the elevated temperature
+ flow behavior of a low alloy steel}.
+\newblock {\em Comput. Mater. Sci.} {\bf 2008}, {\em 43},~752--758.
+\newblock {\url{https://doi.org/10.1016/j.commatsci.2008.01.039}}.
+
+\end{thebibliography}
 

### 2023-03-22 Article.tex
Remove highlights

@@
 \copyrightyear{2023}
-\externaleditor{Academic Editor: \hl{Ji Hoon Kim} %MDPI: Please add it.
+\externaleditor{Academic Editor: Ji Hoon Kim %MDPI: Please add it.
 }
@@
 \DeclareRobustCommand{\MPa}{\text{MPa}}
-\newcommand{\hlok}[1]{\colorbox{green}{#1}}
 
@@
 % Authors, for the paper (add full first names)
-\Author{\hlok{Pierre Tize Mha} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading. All names are correct
-$^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
+\Author{Pierre Tize Mha $^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
 
@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; \hlok{ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)} %MDPI: We added emails from our system.
-Please confirm.
-OK
-\\
+\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)\\
 $^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St.
-W., \hlok{Montréal,} %MDPI: We suggest to use English format city name.
-we add the department information, please confirm.
-OK
- QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}
+W., Montréal, QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}
 
@@
 % Keywords
-\keyword{\hlok{artificial} %mdpi: please check the first letter format (uppercase/lowercase) for every word in keywords.
-please check all the keywords.
-we suggest to use lowercase if the uppercase is not necessary: OK
-neural network; constitutive flow law; analytical flow law; interpolation; extrapolation; Gleeble}
+\keyword{artificial neural network; constitutive flow law; analytical flow law; interpolation; extrapolation; Gleeble}
 
@@
 \midrule
-\textbf{\hlok{Wt}%MDPI: Is the bold necessary?. You can remove the bold, if it does not correspond to the editorial line of the journal.
-~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
+\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
 \bottomrule
@@
 \includegraphics[width=0.99\columnwidth]{Figures/CompExp-JC-6}
-\caption{\hlok{Comparison} %MDPI: Many figures are very similar.
-Please confirm there is no duplicate figure.
-No, every figure is different, the name of the figure correspond to the section, and everything is OK.
- between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson--Cook model.}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson--Cook model.}
 \label{fig:CompExp-JC-6}
@@
 {Figures/ANN-scheme-2HL}
-\caption{\hlok{Two} %MDPI: Should green and red dot be explained?. Caption modified.
- hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
+\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
 \label{fig:ANN-2HL}
@@
 \end{equation}
-where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output \hlok{of the} %MDPI: We suggest to remove the superscript and italic format of ``th''.
-Please check all the ``th''.
-Notation has been changed following your request.
-  $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
+where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
 Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
@@
 One can either use the model directly by providing it with new input data or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
-For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in \hlok{Appendix} %MDPI: We changed Appendix to Appendix A.
-OK
- \ref{sec:Appendix}.}
+For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in Appendix \ref{sec:Appendix}.}
 
@@
 The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at a low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material and, more particularly, at low strain rates.
-The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}\hlok{--}%MDPI: We changed ``to'' to en dash.
-OOPS, there is a mistake, it's figures 6,7,8,9,10, and 13.
-Figures 11 and 12 cannot be included in this list.
-I updated the cross references.
-\ref{fig:CompExp-PTM-6} and \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.
+The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}--\ref{fig:CompExp-PTM-6} and \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.
 
@@
 {Figures/CompExt}
-\caption{\hlok{Comparison} %MDPI: Should hyphen be changed to en dash in 3-15-7-1?.
-No, since, this will lead to longuer notations, I have used hyphen instead of en dash to reduce the width of the notation ANN-3-15-7-1-sigmoid for the model.
- between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=5~\ps$.}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=5~\ps$.}
 \label{fig:CompExt}
@@
 
-\acknowledgments{The authors acknowledge \hlok{Jean}-Benoit Morin, \hlok{Director of} %MDPI: Titles should be removed in this part. Please revise
- Metallurgy and Quality from Finkl Steel-Sorel, \hlok{Abdelhalim} Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK
+\acknowledgments{The authors acknowledge Jean-Benoit Morin, Director of Metallurgy and Quality from Finkl Steel-Sorel, Abdelhalim Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK
 
@@
 
-\hlok{The} %MDPI: We added indent. OK
- biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
+The biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
 \begin{equation*}
@@
 
-\hlok{The} weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
+The weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
 \begin{equation*}
@@
 
-\hlok{The} biases of the second hidden layer $\overrightarrow{b_2}$ is a seven-component vector:
+The biases of the second hidden layer $\overrightarrow{b_2}$ is a seven-component vector:
 \begin{equation*}
@@
 
-\hlok{The} weight vector for the output layer $\overrightarrow{w}$ is a seven-component vector:
+The weight vector for the output layer $\overrightarrow{w}$ is a seven-component vector:
 \begin{equation*}
@@
 
-\hlok{The} bias of the output layer $b$ is a scalar:
+The bias of the output layer $b$ is a scalar:
 \begin{equation*}
@@
  Tool Steel Manufactured by Laser Powder Bed Fusion.
-\newblock {\em Acta Metall. Sin. (Engl. Lett.)} {\bf 2022}, \hlok{\emph{36}, 21--34}.
+\newblock {\em Acta Metall. Sin. (Engl. Lett.)} {\bf 2022}, \emph{36}, 21--34.
 \newblock {\url{https://doi.org/10.1007/s40195-022-01461-z}}.%MDPI: Highlight without comment: newly added/revised information. Following are the same. Please confirm: OK
@@
  intermediate, high and ultra-high strain rates.
-\newblock {\em Int. J. Mech. Sci.} {\bf 2022}, \hl{\emph{226}},
+\newblock {\em Int. J. Mech. Sci.} {\bf 2022}, \emph{226},
  107408.
@@
  Gachot]{rudnytskyj2020constitutive}
-\hlok{Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C.} %MDPI: Refs 15 and 53 are the same. Please check and revise it. Ref 53, has been removed and cross references in the text changed.
+Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C. %MDPI: Refs 15 and 53 are the same. Please check and revise it. Ref 53, has been removed and cross references in the text changed.
 \newblock Constitutive modelling of the 6061 aluminium alloy under hot rolling
@@
 \newblock {In Proceedings of the 7th International Symposium on Ballistics, The
- Hague, The Netherlands, 19--21 April} {1983}; \hlok{pp. 541--547}.
+ Hague, The Netherlands, 19--21 April} {1983}; pp. 541--547.
 %\newblock {\url{https://doi.org/10.1299/kikaia.65.1412}}. Wrong doi, doesn't exists
@@
  Jahazi]{chadha2018approach}
-\hlok{Chadha, K.; Shahriari, D.; Jahazi, M.} %MDPI: Refs 18 and 51 are the same. Please check and revise it. Ok, Ref 51 has been removed and crossref has been updated in the text
+Chadha, K.; Shahriari, D.; Jahazi, M. %MDPI: Refs 18 and 51 are the same. Please check and revise it. Ok, Ref 51 has been removed and crossref has been updated in the text
 \newblock An approach to develop Hansel--Spittel constitutive equation during
  ingot breakdown operation of low alloy steels. In {\em Frontiers in Materials
- Processing, Applications, Research and Technology}; Springer: \hlok{Berlin/Heidelberg, Germany,} %newly added information, please confirm: OK
+ Processing, Applications, Research and Technology}; Springer: Berlin/Heidelberg, Germany, %newly added information, please confirm: OK
  2018; pp.
@@
 \bibitem[Jia \em{et~al.}(2021)Jia, Guan, Zang, Wang, and Lei]{Jia-2021}
-\hlok{Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Lei, M.} %MDPI: Refs 20 and 25 are the same. Please check and revise it: Ref 25 removed and crossref updated in text.
+Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Lei, M. %MDPI: Refs 20 and 25 are the same. Please check and revise it: Ref 25 removed and crossref updated in text.
 \newblock {Modified Johnson--Cook model of aluminum alloy 6016-T6 sheets at low
@@
  186},~106894.
-\newblock \hlok{{\url{https://doi.org/10.1016/j.jcsr.2021.106894}}}. % Corrected doi
+\newblock {\url{https://doi.org/10.1016/j.jcsr.2021.106894}}. % Corrected doi
 
@@
 \newblock {\em J. Mater. Eng. Perform.} {\bf 2022},
- \hl{\emph{31}, 8169--8182.}
+ \emph{31}, 8169--8182.
 \newblock {\url{https://doi.org/10.1007/s11665-022-06828-y}}.
@@
  alloy}.
-\newblock {\em Vacuum} {\bf 2022}, \emph{210}, \hlok{111749.} %MDPI: Please add volume. Vol 210 added and doi corrected.
-\newblock \hlok{{\url{https://doi.org/10.1016/j.vacuum.2022.111749}}}.
+\newblock {\em Vacuum} {\bf 2022}, \emph{210}, 111749. %MDPI: Please add volume. Vol 210 added and doi corrected.
+\newblock {\url{https://doi.org/10.1016/j.vacuum.2022.111749}}.
 
@@
  part of a multi-mechanism model for cutting simulations}.
-\newblock {\em Arch. Appl. Mech.} {\bf 2021}, \hl{\emph{91}, 3869--3888}.
+\newblock {\em Arch. Appl. Mech.} {\bf 2021}, \emph{91}, 3869--3888.
 \newblock {\url{https://doi.org/10.1007/s00419-021-01982-6}}.
@@
 \newblock {\em J. Manuf. Sci. Eng.} {\bf 2021},
- {\em 143}, \hl{101004}.
+ {\em 143}, 101004.
 \newblock {\url{https://doi.org/10.1115/1.4050652}}.
@@
  Software.
-\newblock {\em Algorithms} {\bf 2023}, {\em 16}, \hl{56}.
+\newblock {\em Algorithms} {\bf 2023}, {\em 16}, 56.
 \newblock {\url{https://doi.org/10.3390/a16010056}}.
@@
 \newblock {Review of balsa core sandwich composite structures}.
-\newblock {\em Mater. Des.} {\bf 2022}, \hl{\em 221}, 111013.
+\newblock {\em Mater. Des.} {\bf 2022}, \em 221, 111013.
 \newblock {\url{https://doi.org/10.1016/j.matdes.2022.111013}}.
@@
 \newblock {\em {Kraft- und Arbeitsbedarf Bildsamer Formgebungsverfahren}};
- Deutscher Verlag f{\"u}r Grundstoffindustrie: \hl{Leipzig, Germany}, 1978.
+ Deutscher Verlag f{\"u}r Grundstoffindustrie: Leipzig, Germany, 1978.
 
@@
  Python};
-\newblock \hlok{Astrophysics Source Code Library}: {2016}; p. ascl:1606.014.%MDPI: Please add publisher location. There is no published location for ASCL, it's online: see https://ascl.net
+\newblock Astrophysics Source Code Library: {2016}; p. ascl:1606.014.%MDPI: Please add publisher location. There is no published location for ASCL, it's online: see https://ascl.net
 
@@
 \newblock In Proceedings of the 12th {{USENIX}} Conference
- on {{Operating Systems Design}} and {{Implementation}}, {{OSDI}}'16, \hl{Savannah, GA, USA, 2--4 November 2016}; {USENIX Association}:
-\hl{Berkeley, CA,} {USA}, 2016; pp. 265--283.
+ on {{Operating Systems Design}} and {{Implementation}}, {{OSDI}}'16, Savannah, GA, USA, 2--4 November 2016; {USENIX Association}:
+Berkeley, CA, {USA}, 2016; pp. 265--283.
 
@@
 Kingma, D.P.; Lei, J.
-\newblock {Adam: A method for stochastic optimization} \hl{\emph{arXiv}} {\bf 2015}, \hl{arXiv.1412.6980.}
+\newblock {Adam: A method for stochastic optimization} \emph{arXiv} {\bf 2015}, arXiv.1412.6980.
 %\newblock \hlok{p.~15.} %MDPI: Should it be kept?. Removed

### 2023-10-16 Metals-2023.tex
Rename final production article

--- 2023-03-21 Article.tex
@@
 \makeatother
-\pubvolume{1}
-\issuenum{1}
-\articlenumber{0}
+\pubvolume{13}
+\issuenum{3}
+\articlenumber{633}
 \pubyear{2023}
 \copyrightyear{2023}
-\externaleditor{Academic Editor: \hl{Ji Hoon Kim} %MDPI: Please add it.
+\externaleditor{Academic Editor: {Ji Hoon Kim} %MDPI: Please add it.
 }
@@
 \dateaccepted{20 March 2023}
-\datepublished{ }
+\datepublished{22 March 2023}
 %\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
 %\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
-\hreflink{https://doi.org/} % If needed use \linebreak
+\hreflink{https://doi.org/10.3390/\linebreak met13030633} % If needed use \linebreak
 %\doinum{}
@@
 \newcommand{\orcidauthorC}{0000-0002-5360-5121}
+\newcommand{\orcidauthorD}{0000-0002-0815-1984}
 
 % Authors, for the paper (add full first names)
-\Author{\hlok{Pierre Tize Mha} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading. All names are correct
-$^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
+\Author{{Pierre Tize Mha} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading. All names are correct
+$^{1}$\orcidD{}, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
 
@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; \hlok{ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)} %MDPI: We added emails from our system.
+\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; {ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)} %MDPI: We added emails from our system.
 Please confirm.
@@
 $^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St.
-W., \hlok{Montréal,} %MDPI: We suggest to use English format city name.
-we add the department information, please confirm.
-OK
- QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}
+W., \mbox{Montréal, QC H3C 1K3, Canada}; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); \mbox{mohammad.jahazi@etsmtl.ca (M.J.)}}
 
@@
 % Keywords
-\keyword{\hlok{artificial} %mdpi: please check the first letter format (uppercase/lowercase) for every word in keywords.
+\keyword{{artificial} %mdpi: please check the first letter format (uppercase/lowercase) for every word in keywords.
 please check all the keywords.
 we suggest to use lowercase if the uppercase is not necessary: OK
-neural network; constitutive flow law; analytical flow law; interpolation; extrapolation; Gleeble}
+neural network; constitutive flow law; analytical flow law; interpolation; \linebreak extrapolation; Gleeble}
 
@@
 \midrule
-\textbf{\hlok{Wt}%MDPI: Is the bold necessary?. You can remove the bold, if it does not correspond to the editorial line of the journal.
+{{Wt}%MDPI: Is the bold necessary?. You can remove the bold, if it does not correspond to the editorial line of the journal.
 ~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
@@
 Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely $1050~\celsius$, $1100~\celsius$, $1150~\celsius$, $1200~\celsius$, and $1250~\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$, and $5~\ps$.
+
+\vspace{2pt}
 \begin{figure}[H]
@@
 
-Figure \ref{fig:Micrography}a shows the microstructure obtained when the sample is held at $1260~\celsius$ for $5$ minutes and rapidly cooled to room temperature.
+Figure \ref{fig:Micrography}a shows the microstructure obtained when the sample is held at $1260~\celsius$ for $5$~min and rapidly cooled to room temperature.
 From this image, large grains can be observed.
 On the other hand, Figure \ref{fig:Micrography}b shows the microstructure after compression at $1150~\celsius$ with a $0.001~\ps$ strain rate.
-To obtain this, the sample is heated up to $1260~\celsius$, then held for $5$ minutes and cooled down to $1150~\celsius$ to be held at this temperature for $1$ minute before compression.
+To obtain this, the sample is heated up to $1260~\celsius$, then held for $5$ min and cooled down to $1150~\celsius$ to be held at this temperature for $1$ min before compression.
 After compression, the sample is rapidly cooled to room temperature to preserve the microstructure.
@@
 \includegraphics[width=0.99\columnwidth]{Figures/CompExp-JC-6}
-\caption{\hlok{Comparison} %MDPI: Many figures are very similar.
+\caption{{Comparison} %MDPI: Many figures are very similar.
 Please confirm there is no duplicate figure.
@@
 where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$, and $N$ is the total number of data points used to compute those coefficients (in our case $N$ = 21,000).
-For the JC model, $\MARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
+For the JC model, $\MARE=14.05\%$ and $\RMSE=12.00~\MPa$.
 As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is not always an accurate measure to evaluate the reliability of the constitutive law especially in the case of a highly nonlinear functions because it only shows the correlation of the model with respect to the data and not its accuracy.
@@
 \begin{figure}[H]
-\includegraphics[width=0.99\columnwidth]
+\includegraphics[width=0.93\columnwidth]
 {Figures/CompExp-MZA-6}
@@
 
+\vspace{-10pt}
 %----------------------------------------------------------------------------------
@@
 
-In the present study, the best results were obtained by taking the model defined by only the first 7 $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.
+In the present study, the best results were obtained by taking the model defined by only the first 7 $m_i$ terms of the Equation (\ref{eq:HS}), so that $m_8=0$.
 From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} allowed computing the parameters reported in Table
@@
 A comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6}, where the dots represent the experimental values and the solid lines are the values predicted by the Hansel--Spittel flow law.
-For the HS model, $\MARE=7.75~\%$ and $\RMSE=3.80~\MPa$.
+For the HS model, \mbox{$\MARE=7.75\%$} and $\RMSE=3.80~\MPa$.
 It appears that both this model and the previous ones do not adequately predict the experimental one, and the difference is relatively significant for all strain rates below $1~\ps$.
 This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong nonlinear behavior observed for low strain rate values.
-The DRX phenomenon cannot be reproduced by this type of model.
+The DRX phenomenon cannot be reproduced by this type of~model.
 
@@
 However, for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is unable to predict the softening.
-For the AR model, $\MARE=3.56~\%$ and $\RMSE=2.18~\MPa$.
+For the AR model, $\MARE=3.56\%$ and $\RMSE=2.18~\MPa$.
 
@@
 The deviation between the predicted values and the experimental values for other strain rates is relatively low.
-For the PTM model, $\MARE=4.79~\%$ and $\RMSE=4.59~\MPa$, which is an overall worse performance than the AR model.
+For the PTM model, $\MARE=4.79\%$ and $\RMSE=4.59~\MPa$, which is an overall worse performance than the AR model.
 
@@
 Thus, all the neurons of the $k^{th}$ layer are connected to all the neurons of the ($k-1^{th}$) layer, as shown in~Figure~\ref{fig:ANN-2HL}.
+
+\vspace{-2pt}
 \begin{figure}[H]
@@
 {Figures/ANN-scheme-2HL}
-\caption{\hlok{Two} %MDPI: Should green and red dot be explained?. Caption modified.
+\caption{{Two} %MDPI: Should green and red dot be explained?. Caption modified.
  hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
@@
 \end{equation}
-where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output \hlok{of the} %MDPI: We suggest to remove the superscript and italic format of ``th''.
+where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output {of the} %MDPI: We suggest to remove the superscript and italic format of ``th''.
 Please check all the ``th''.
@@
 The training was performed on the basis of $5000$ epochs of the experimental dataset.
-It took $40$~min of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of RAM and an Intel 4-core i7-10510U processor to obtain the converged parameters of the ANN model.
+It took $40$~min of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16~GB of RAM and an Intel 4-core i7-10510U processor to obtain the converged parameters of the ANN model.
 Figure \ref{fig:ANN-6-conv} shows the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$ during the training phase.
@@
 One can either use the model directly by providing it with new input data or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
-For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in \hlok{Appendix} %MDPI: We changed Appendix to Appendix A.
+For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in {Appendix} %MDPI: We changed Appendix to Appendix A.
 OK
@@
 From Table \ref{tab:Errors}, we can see that the ANN model has a much better predictive capacity than all the analytical models presented in the above sections.
-Globally, the values of $\MARE$ and $\RMSE$ are six-times lower than with the best of the analytical models, \ie, the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.
+Globally, the values of $\MARE$ and $\RMSE$ are six-times lower than with the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.
 
 The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at a low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material and, more particularly, at low strain rates.
-The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}\hlok{--}%MDPI: We changed ``to'' to en dash.
+The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}{--}%MDPI: We changed ``to'' to en dash.
 OOPS, there is a mistake, it's figures 6,7,8,9,10, and 13.
@@
 
-For interpolation validation, the chosen omitted strain rate was $\mdot\varepsilon=1~\ps$, and those used for identification (or training for the ANN) were the five others, \ie, $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
+For interpolation validation, the chosen omitted strain rate was $\mdot\varepsilon=1~\ps$, and \linebreak those used for identification (or training for the ANN) were the five others, \ie \linebreak \mbox{$\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$}.
 All models were re-identified from the same experimental data on a dataset corresponding to five strain rates and five temperatures.
@@
 $\mdot\varepsilon$), the six strain rates (lines referred as all $\mdot\varepsilon$), or only on the strain rate $\mdot\varepsilon=1~\ps$.
+
+\vspace{-2pt}
 \begin{table}[H]
@@
 For the validation of the models' ability to extrapolate, the omitted strain rate chosen was $\mdot\varepsilon=5~\ps$ and those used for identification were $\mdot\varepsilon=[0.001, 0.01, 0.1, 1, 2]~\ps$.
-The strain rate omitted in this analysis, therefore, has the highest value, which restricts the training domain.
+The strain rate omitted in this analysis, therefore, has the highest value, which restricts the training~domain.
 
@@
 {Figures/CompExt}
-\caption{\hlok{Comparison} %MDPI: Should hyphen be changed to en dash in 3-15-7-1?.
+\caption{{Comparison} %MDPI: Should hyphen be changed to en dash in 3-15-7-1?.
 No, since, this will lead to longuer notations, I have used hyphen instead of en dash to reduce the width of the notation ANN-3-15-7-1-sigmoid for the model.
@@
 
-As presented in the previous section regarding the interpolation capability of the models, in Figure \ref{fig:CompExt}, it can be seen that the first two models, JC and MZA, in this study again do not have the ability to correctly reproduce the material behavior for the strain rate $\mdot\varepsilon=5~\ps$.
+As presented in the previous section regarding the interpolation capability of the models, in Figure \ref{fig:CompExt}, it can be seen that the first two models, JC and MZA, in this study again do not have the ability to correctly reproduce the material behavior for the strain rate \mbox{$\mdot\varepsilon=5~\ps$}.
 The JC model performs better than the MZA model for $\mdot\varepsilon=5~\ps$, which is reflected in Table \ref{tab:ExtVal} by a lower value of the $\MARE$ and $\RMSE$ for JC than for MZA.
@@
 
-\acknowledgments{The authors acknowledge \hlok{Jean}-Benoit Morin, \hlok{Director of} %MDPI: Titles should be removed in this part. Please revise
- Metallurgy and Quality from Finkl Steel-Sorel, \hlok{Abdelhalim} Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK
+\acknowledgments{The authors acknowledge {Jean}-Benoit Morin, {Director of} %MDPI: Titles should be removed in this part. Please revise
+ Metallurgy and Quality from Finkl Steel-Sorel, {Abdelhalim} Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK
 
@@
 
-\hlok{The} %MDPI: We added indent. OK
+{The} %MDPI: We added indent. OK
  biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
@@
 
-\hlok{The} weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
+{The} weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
 \begin{equation*}
@@
 
-\hlok{The} biases of the second hidden layer $\overrightarrow{b_2}$ is a seven-component vector:
+{The} biases of the second hidden layer $\overrightarrow{b_2}$ is a seven-component vector:
 \begin{equation*}
@@
 
-\hlok{The} weight vector for the output layer $\overrightarrow{w}$ is a seven-component vector:
+{The} weight vector for the output layer $\overrightarrow{w}$ is a seven-component vector:
 \begin{equation*}
@@
 
-\hlok{The} bias of the output layer $b$ is a scalar:
+{The} bias of the output layer $b$ is a scalar:
 \begin{equation*}
@@
 \newblock {\em Metall. Mater. Trans. A} {\bf 2017}, {\em
- 48},~4297--4313.
-\newblock {\url{https://doi.org/10.1007/s11661-017-4177-8}}.
+48},~4297--4313. [\href{http://doi.org/10.1007/s11661-017-4177-8}{CrossRef}]
 
@@
 as-cast medium-carbon low-alloy steel.
-\newblock {\em Materialia} {\bf 2018}, {\em 1},~155--167.
-\newblock {\url{https://doi.org/10.1016/j.mtla.2018.04.006}}.
+\newblock {\em Materialia} {\bf 2018}, {\em 1},~155--167. [\href{http://dx.doi.org/10.1016/j.mtla.2018.04.006}{CrossRef}]
 
@@
 AISI-1045 medium carbon steel at elevated temperatures}.
-\newblock {\em Heliyon} {\bf 2019}, {\em 5},~e01347.
-\newblock {\url{https://doi.org/10.1016/j.heliyon.2019.e01347}}.
+\newblock {\em Heliyon} {\bf 2019}, {\em 5},~e01347. [\href{http://dx.doi.org/10.1016/j.heliyon.2019.e01347}{CrossRef}]
 
@@
 deformation behavior of medium carbon steel material}.
-\newblock {\em Metals} {\bf 2019}, {\em 9},~1315.
-\newblock {\url{https://doi.org/10.3390/met9121315}}.
+\newblock {\em Metals} {\bf 2019}, {\em 9},~1315. [\href{http://dx.doi.org/10.3390/met9121315}{CrossRef}]
 
@@
 behavior of an additively manufactured maraging steel.
-\newblock {\em Materials} {\bf 2020}, {\em 13},~2380.
-\newblock {\url{https://doi.org/10.3390/ma13102380}}.
+\newblock {\em Materials} {\bf 2020}, {\em 13},~2380. [\href{http://dx.doi.org/10.3390/ma13102380}{CrossRef}]
 
@@
 micromechanical properties of additively manufactured 17--4PH steel.
-\newblock {\em Mater. Charact.} {\bf 2022}, {\em 192},~112174.
-\newblock {\url{https://doi.org/10.1016/j.matchar.2022.112174}}.
+\newblock {\em Mater. Charact.} {\bf 2022}, {\em 192},~112174. [\href{http://dx.doi.org/10.1016/j.matchar.2022.112174}{CrossRef}]
 
@@
 Tool Steel Manufactured by Laser Powder Bed Fusion.
-\newblock {\em Acta Metall. Sin. (Engl. Lett.)} {\bf 2022}, \hlok{\emph{36}, 21--34}.
-\newblock {\url{https://doi.org/10.1007/s40195-022-01461-z}}.%MDPI: Highlight without comment: newly added/revised information. Following are the same. Please confirm: OK
+\newblock {\em Acta Metall. Sin. (Engl. Lett.)} {\bf 2022}, {\emph{36}, 21--34}. [\href{http://dx.doi.org/10.1007/s40195-022-01461-z}{CrossRef}]
 
@@
 \newblock {\em Mater. Sci. Technol.} {\bf 2019}, {\em
- 35},~1932--1941.
-\newblock {\url{https://doi.org/10.1080/02670836.2019.1655862}}.
+35},~1932--1941. [\href{http://dx.doi.org/10.1080/02670836.2019.1655862}{CrossRef}]
 
@@
 carbon low alloy steel}.
-\newblock {\em Vacuum} {\bf 2017}, {\em 142},~135--145.
-\newblock {\url{https://doi.org/10.1016/j.vacuum.2017.05.010}}.
+\newblock {\em Vacuum} {\bf 2017}, {\em 142},~135--145. [\href{http://dx.doi.org/10.1016/j.vacuum.2017.05.010}{CrossRef}]
 
@@
 strength cast Al-Cu-Mn alloy during hot deformation}.
-\newblock {\em Mater. Today Commun.} {\bf 2022}, {\em 33},~104199.
-\newblock {\url{https://doi.org/10.1016/j.mtcomm.2022.104199}}.
+\newblock {\em Mater. Today Commun.} {\bf 2022}, {\em 33},~104199. [\href{http://dx.doi.org/10.1016/j.mtcomm.2022.104199}{CrossRef}]
 
@@
 nickel aluminum bronze}.
-\newblock {\em Mater. Des.} {\bf 2022}, {\em 220},~110853.
-\newblock {\url{https://doi.org/10.1016/j.matdes.2022.110853}}.
+\newblock {\em Mater. Des.} {\bf 2022}, {\em 220},~110853. [\href{http://dx.doi.org/10.1016/j.matdes.2022.110853}{CrossRef}]
 
@@
 \newblock {\em J. Mater. Eng. Perform.} {\bf 2019},
- {\em 28},~87--99.
-\newblock {\url{https://doi.org/10.1007/s11665-018-3813-9}}.
+{\em 28},~87--99. [\href{http://dx.doi.org/10.1007/s11665-018-3813-9}{CrossRef}]
 
@@
 intermediate, high and ultra-high strain rates.
-\newblock {\em Int. J. Mech. Sci.} {\bf 2022}, \hl{\emph{226}},
- 107408.
-\newblock {\url{https://doi.org/10.1016/j.ijmecsci.2022.107408}}.
+\newblock {\em Int. J. Mech. Sci.} {\bf 2022}, {\emph{226}},
+107408. [\href{http://dx.doi.org/10.1016/j.ijmecsci.2022.107408}{CrossRef}]
 
@@
 ultra-high-strength steels.
-\newblock {\em Mater. Des.} {\bf 2016}, {\em 91},~143--154.
-\newblock {\url{https://doi.org/10.1016/j.matdes.2015.11.082}}.
+\newblock {\em Mater. Des.} {\bf 2016}, {\em 91},~143--154. [\href{http://dx.doi.org/10.1016/j.matdes.2015.11.082}{CrossRef}]
 
@@
 Gachot]{rudnytskyj2020constitutive}
-\hlok{Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C.} %MDPI: Refs 15 and 53 are the same. Please check and revise it. Ref 53, has been removed and cross references in the text changed.
+{Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C.} 
 \newblock Constitutive modelling of the 6061 aluminium alloy under hot rolling
 conditions and large strain ranges.
-\newblock {\em Mater. Des.} {\bf 2020}, {\em 190},~108568.
-\newblock {\url{https://doi.org/10.1016/j.matdes.2020.108568}}.
+\newblock {\em Mater. Des.} {\bf 2020}, {\em 190},~108568. [\href{http://dx.doi.org/10.1016/j.matdes.2020.108568}{CrossRef}]
 
@@
 \newblock {\em Finite Elem. Anal. Des.} {\bf 2022}, {\em
- 198},~103647.
-\newblock {\url{https://doi.org/10.1016/j.finel.2021.103647}}.
+198},~103647. [\href{http://dx.doi.org/10.1016/j.finel.2021.103647}{CrossRef}]
 
@@
 \newblock {In Proceedings of the 7th International Symposium on Ballistics, The
- Hague, The Netherlands, 19--21 April} {1983}; \hlok{pp. 541--547}.
+Hague, The Netherlands, 19--21 April} {1983}; {pp. 541--547}.
 %\newblock {\url{https://doi.org/10.1299/kikaia.65.1412}}. Wrong doi, doesn't exists
@@
 Jahazi]{chadha2018approach}
-\hlok{Chadha, K.; Shahriari, D.; Jahazi, M.} %MDPI: Refs 18 and 51 are the same. Please check and revise it. Ok, Ref 51 has been removed and crossref has been updated in the text
+{Chadha, K.; Shahriari, D.; Jahazi, M.} 
 \newblock An approach to develop Hansel--Spittel constitutive equation during
 ingot breakdown operation of low alloy steels. In {\em Frontiers in Materials
- Processing, Applications, Research and Technology}; Springer: \hlok{Berlin/Heidelberg, Germany,} %newly added information, please confirm: OK
+Processing, Applications, Research and Technology}; Springer: {Berlin/Heidelberg, Germany,} 
 2018; pp.
- 239--246.
-\newblock {\url{https://doi.org/10.1007/978-981-10-4819-7_20}}.
+239--246. [\href{http://dx.doi.org/10.1007/978-981-10-4819-7_20}{CrossRef}]
 
@@
 dynamics calculations}.
-\newblock {\em J. Appl. Phys.} {\bf 1987}, {\em 61},~1816--1825.
-\newblock {\url{https://doi.org/10.1063/1.338024}}.
+\newblock {\em J. Appl. Phys.} {\bf 1987}, {\em 61},~1816--1825. [\href{http://dx.doi.org/10.1063/1.338024}{CrossRef}]
 
 \bibitem[Jia \em{et~al.}(2021)Jia, Guan, Zang, Wang, and Lei]{Jia-2021}
-\hlok{Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Lei, M.} %MDPI: Refs 20 and 25 are the same. Please check and revise it: Ref 25 removed and crossref updated in text.
+{Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Lei, M.} 
 \newblock {Modified Johnson--Cook model of aluminum alloy 6016-T6 sheets at low
@@
 \newblock {\em Mater. Sci. Eng. A} {\bf 2021}, {\em
- 820},~141565.
-\newblock {\url{https://doi.org/10.1016/j.msea.2021.141565}}.
+820},~141565. [\href{http://dx.doi.org/10.1016/j.msea.2021.141565}{CrossRef}]
 
@@
 \newblock {\em J. Constr. Steel Res.} {\bf 2021}, {\em
- 186},~106894.
-\newblock \hlok{{\url{https://doi.org/10.1016/j.jcsr.2021.106894}}}. % Corrected doi
+186},~106894. [\href{http://dx.doi.org/10.1016/j.jcsr.2021.106894}{CrossRef}]
 
@@
 \newblock {\em Int. J. Impact Eng.} {\bf 2022}, {\em
- 164},~104208.
-\newblock {\url{https://doi.org/10.1016/j.ijimpeng.2022.104208}}.
+164},~104208. [\href{http://dx.doi.org/10.1016/j.ijimpeng.2022.104208}{CrossRef}]
 
@@
 \newblock {\em J. Mater. Eng. Perform.} {\bf 2022},
- \hl{\emph{31}, 8169--8182.}
-\newblock {\url{https://doi.org/10.1007/s11665-022-06828-y}}.
+{\emph{31}, 8169--8182.}
+\newblock. [\href{http://dx.doi.org/10.1007/s11665-022-06828-y}{CrossRef}]
 
@@
 \newblock {\em Mater. Sci. Eng. A} {\bf 2022}, {\em
- 832},~142473.
-\newblock {\url{https://doi.org/10.1016/j.msea.2021.142473}}.
+832},~142473. [\href{http://dx.doi.org/10.1016/j.msea.2021.142473}{CrossRef}]
 
@@
 %\bibitem[Jia \em{et~al.}(2021)Jia, Guan, Zang, Wang, and Mu]{Jia-2021}
-%\hl{Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Mu, L.}
+%{Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Mu, L.}
 %\newblock {Modified Johnson--Cook model of aluminum alloy 6016-T6 sheets at low
@@
 % 820},~141565.
-%\newblock {\url{https://doi.org/10.1016/j.msea.2021.141565}}.
+%\newblock.
 
@@
 alloy}.
-\newblock {\em Vacuum} {\bf 2022}, \emph{210}, \hlok{111749.} %MDPI: Please add volume. Vol 210 added and doi corrected.
-\newblock \hlok{{\url{https://doi.org/10.1016/j.vacuum.2022.111749}}}.
+\newblock {\em Vacuum} {\bf 2022}, \emph{210}, {111749.} 
+\newblock. [\href{http://dx.doi.org/10.1016/j.vacuum.2022.111749}{CrossRef}]
 
@@
 \newblock {\em Mater. Sci. Eng. A} {\bf 2013}, {\em
- 577},~138--146.
-\newblock {\url{https://doi.org/10.1016/j.msea.2013.04.041}}.
+577},~138--146. [\href{http://dx.doi.org/10.1016/j.msea.2013.04.041}{CrossRef}]
 
@@
 \newblock {\em J. Alloys Compd.} {\bf 2015}, {\em
- 619},~186--194.
-\newblock {\url{https://doi.org/10.1016/j.jallcom.2014.09.002}}.
+619},~186--194. [\href{http://dx.doi.org/10.1016/j.jallcom.2014.09.002}{CrossRef}]
 
@@
 behaviour of GCr15 continuous casting bloom with heavy reduction}.
-\newblock {\em Mater. Res. Express} {\bf 2019}, {\em 6},~1265f2.
-\newblock {\url{https://doi.org/10.1088/2053-1591/ab52c2}}.
+\newblock {\em Mater. Res. Express} {\bf 2019}, {\em 6},~1265f2. [\href{http://dx.doi.org/10.1088/2053-1591/ab52c2}{CrossRef}]
 
@@
 of conical implant press-fit in homogenized trabecular bone}.
-\newblock {\em J. Biomech.} {\bf 2020}, {\em 107},~109844.
-\newblock {\url{https://doi.org/10.1016/j.jbiomech.2020.109844}}.
+\newblock {\em J. Biomech.} {\bf 2020}, {\em 107},~109844. [\href{http://dx.doi.org/10.1016/j.jbiomech.2020.109844}{CrossRef}]
 
@@
 deformation of Cu-15Ni-8Sn alloys}.
-\newblock {\em Front. Mater.} {\bf 2020}, {\em 7},~577867.
-\newblock {\url{https://doi.org/10.3389/fmats.2020.577867}}.
+\newblock {\em Front. Mater.} {\bf 2020}, {\em 7},~577867. [\href{http://dx.doi.org/10.3389/fmats.2020.577867}{CrossRef}]
 
@@
 \newblock {\em J. Manuf. Process.} {\bf 2017}, {\em
- 28},~253--265.
-\newblock {\url{https://doi.org/10.1016/j.jmapro.2017.06.011}}.
+28},~253--265. [\href{http://dx.doi.org/10.1016/j.jmapro.2017.06.011}{CrossRef}]
 
@@
 part of a multi-mechanism model for cutting simulations}.
-\newblock {\em Arch. Appl. Mech.} {\bf 2021}, \hl{\emph{91}, 3869--3888}.
-\newblock {\url{https://doi.org/10.1007/s00419-021-01982-6}}.
+\newblock {\em Arch. Appl. Mech.} {\bf 2021}, {\emph{91}, 3869--3888}. [\href{http://dx.doi.org/10.1007/s00419-021-01982-6}{CrossRef}]
 
@@
 \newblock {\em J. Manuf. Sci. Eng.} {\bf 2021},
- {\em 143}, \hl{101004}.
-\newblock {\url{https://doi.org/10.1115/1.4050652}}.
+{\em 143}, {101004}. [\href{http://dx.doi.org/10.1115/1.4050652}{CrossRef}]
 
@@
 during Hot Deformation: Part I—Experimental Study}.
-\newblock {\em Metals} {\bf 2021}, {\em 11},~572.
-\newblock {\url{https://doi.org/10.3390/met11040572}}.
+\newblock {\em Metals} {\bf 2021}, {\em 11},~572. [\href{http://dx.doi.org/10.3390/met11040572}{CrossRef}]
 
@@
 \newblock {\em Mater. Sci. Eng. A} {\bf 2022}, {\em
- 840},~142953.
-\newblock {\url{https://doi.org/10.1016/j.msea.2022.142953}}.
+840},~142953. [\href{http://dx.doi.org/10.1016/j.msea.2022.142953}{CrossRef}]
 
@@
 \newblock {\em Mater. Sci. Eng. A} {\bf 2022}, {\em
- 834},~142619.
-\newblock {\url{https://doi.org/10.1016/j.msea.2022.142619}}.
+834},~142619. [\href{http://dx.doi.org/10.1016/j.msea.2022.142619}{CrossRef}]
 
@@
 \newblock {\em Int. J. Mech. Sci.} {\bf 2022}, {\em
- 232},~107571.
-\newblock {\url{https://doi.org/10.1016/j.ijmecsci.2022.107571}}.
+232},~107571. [\href{http://dx.doi.org/10.1016/j.ijmecsci.2022.107571}{CrossRef}]
 
@@
 \newblock {\em J. Mater. Res. Technol.} {\bf 2020}, {\em
- 9},~7210--7224.
-\newblock {\url{https://doi.org/10.1016/j.jmrt.2020.04.078}}.
+9},~7210--7224. [\href{http://dx.doi.org/10.1016/j.jmrt.2020.04.078}{CrossRef}]
 
@@
 10},~334--362.
-\newblock {\url{https://doi.org/10.4236/wjet.2022.102021}}.}
+\newblock.} [\href{http://dx.doi.org/10.4236/wjet.2022.102021}{CrossRef}]
 
@@
 mechanical properties of structural steels}.
-\newblock {\em Mater. Today Commun.} {\bf 2022}, {\em 32},~104092.
-\newblock {\url{https://doi.org/10.1016/j.mtcomm.2022.104092}}.
+\newblock {\em Mater. Today Commun.} {\bf 2022}, {\em 32},~104092. [\href{http://dx.doi.org/10.1016/j.mtcomm.2022.104092}{CrossRef}]
 
@@
 \newblock {\em Mech. Res. Commun.} {\bf 2020}, {\em
- 108},~103565.
-\newblock {\url{https://doi.org/10.1016/j.mechrescom.2020.103565}}.
+108},~103565. [\href{http://dx.doi.org/10.1016/j.mechrescom.2020.103565}{CrossRef}]
 
@@
 \newblock {\em J. Alloys Compd.} {\bf 2016}, {\em
- 687},~263--273.
-\newblock {\url{https://doi.org/10.1016/j.jallcom.2016.04.300}}.
+687},~263--273. [\href{http://dx.doi.org/10.1016/j.jallcom.2016.04.300}{CrossRef}]
 
@@
 structural response}.
-\newblock {\em Mech. Res. Commun.} {\bf 2019}, {\em 95},~85--88.
-\newblock {\url{https://doi.org/10.1016/j.mechrescom.2019.01.004}}.
+\newblock {\em Mech. Res. Commun.} {\bf 2019}, {\em 95},~85--88. [\href{http://dx.doi.org/10.1016/j.mechrescom.2019.01.004}{CrossRef}]
 
@@
 Software.
-\newblock {\em Algorithms} {\bf 2023}, {\em 16}, \hl{56}.
-\newblock {\url{https://doi.org/10.3390/a16010056}}.
+\newblock {\em Algorithms} {\bf 2023}, {\em 16}, {56}. [\href{http://dx.doi.org/10.3390/a16010056}{CrossRef}]
 
@@
 \newblock {Review of balsa core sandwich composite structures}.
-\newblock {\em Mater. Des.} {\bf 2022}, \hl{\em 221}, 111013.
-\newblock {\url{https://doi.org/10.1016/j.matdes.2022.111013}}.
+\newblock {\em Mater. Des.} {\bf 2022}, {\em 221}, 111013. [\href{http://dx.doi.org/10.1016/j.matdes.2022.111013}{CrossRef}]
 
@@
 \newblock {\em J. Mater. Process. Technol.} {\bf 2003}, {\em
- 141},~219--227.
-\newblock {\url{https://doi.org/10.1016/S0924-0136(02)01123-8}}.
+141},~219--227. [\href{http://dx.doi.org/10.1016/S0924-0136(02)01123-8}{CrossRef}]
 
@@
 \newblock {Thermal effect on dislocation interactions in magnesium alloy}.
-\newblock {\em Materialia} {\bf 2022}, {\em 26},~101579.
-\newblock {\url{https://doi.org/10.1016/j.mtla.2022.101579}}.
+\newblock {\em Materialia} {\bf 2022}, {\em 26},~101579. [\href{http://dx.doi.org/10.1016/j.mtla.2022.101579}{CrossRef}]
 
@@
 \newblock {\em Mater. Sci. Eng. A} {\bf 2009}, {\em
- 526},~1--6.
-\newblock {\url{https://doi.org/10.1016/j.msea.2009.08.009}}.
+526},~1--6. [\href{http://dx.doi.org/10.1016/j.msea.2009.08.009}{CrossRef}]
 
@@
 \newblock {\em {Kraft- und Arbeitsbedarf Bildsamer Formgebungsverfahren}};
- Deutscher Verlag f{\"u}r Grundstoffindustrie: \hl{Leipzig, Germany}, 1978.
+Deutscher Verlag f{\"u}r Grundstoffindustrie: {Leipzig, Germany}, 1978.
 
@@
 %\bibitem[Chadha \em{et~al.}(2018)Chadha, Shahriari, and Jahazi]{chadha2018approach}
-%\hl{Chadha, K.; Shahriari, D.; Jahazi, M.}
+%{Chadha, K.; Shahriari, D.; Jahazi, M.}
 %\newblock {An Approach to Develop Hansel–Spittel Constitutive Equation during
 % Ingot Breakdown Operation of Low Alloy Steels}. In {\em Frontiers in
-% Materials Processing, Applications, Research and Technology}; Springer: \hl{Berlin/Heidelberg, Germany,} %newly added information, please confirm
+% Materials Processing, Applications, Research and Technology}; Springer: {Berlin/Heidelberg, Germany,} 
 % 2018; pp. 239--246.
@@
 Deformation Behavior of AA6060 and AA6063 Aluminium Alloys}.
-\newblock {\em Mater. Today Proc.} {\bf 2015}, {\em 2},~4732--4739.
-\newblock {\url{https://doi.org/10.1016/j.matpr.2015.10.006}}.
+\newblock {\em Mater. Today Proc.} {\bf 2015}, {\em 2},~4732--4739. [\href{http://dx.doi.org/10.1016/j.matpr.2015.10.006}{CrossRef}]
 
@@
 %\bibitem[Rudnytskyj \em{et~al.}(2020)Rudnytskyj, Simon, Jech, and
-% Gachot]{Rudnytskyj-2020}\hl{
+% Gachot]{Rudnytskyj-2020}{
 %Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C.}
@@
 %\newblock {\em Mater. Des.} {\bf 2020}, {\em 190},~108568.
-%\newblock {\url{https://doi.org/10.1016/j.matdes.2020.108568}}.
+%\newblock.
 
@@
 Python};
-\newblock \hlok{Astrophysics Source Code Library}: {2016}; p. ascl:1606.014.%MDPI: Please add publisher location. There is no published location for ASCL, it's online: see https://ascl.net
+\newblock {Astrophysics Source Code Library}: {2016}; ascl:1606.014.  Available online: \url{https://ascl.net}  (accessed on \mbox{9 February 2023)}.
 
@@
 \newblock {On the mechanism of hot deformation}.
-\newblock {\em Acta Metall.} {\bf 1966}, {\em 14},~1136--1138.
-\newblock {\url{https://doi.org/10.1016/0001-6160(66)90207-0}}.
+\newblock {\em Acta Metall.} {\bf 1966}, {\em 14},~1136--1138. [\href{http://dx.doi.org/10.1016/0001-6160(66)90207-0}{CrossRef}]
 
@@
 \newblock {Effect of Strain Rate Upon Plastic Flow of Steel}.
-\newblock {\em J. Appl. Phys.} {\bf 1944}, {\em 15},~22--32.
-\newblock {\url{https://doi.org/10.1063/1.1707363}}.
+\newblock {\em J. Appl. Phys.} {\bf 1944}, {\em 15},~22--32. [\href{http://dx.doi.org/10.1063/1.1707363}{CrossRef}]
 
@@
 \newblock In Proceedings of the 12th {{USENIX}} Conference
- on {{Operating Systems Design}} and {{Implementation}}, {{OSDI}}'16, \hl{Savannah, GA, USA, 2--4 November 2016}; {USENIX Association}:
-\hl{Berkeley, CA,} {USA}, 2016; pp. 265--283.
+on {{Operating Systems Design}} and {{Implementation}}, {{OSDI}}'16, {Savannah, GA, USA, 2--4 November 2016}; {USENIX Association}:
+{Berkeley, CA,} {USA}, 2016; pp. 265--283.
 
@@
 Kingma, D.P.; Lei, J.
-\newblock {Adam: A method for stochastic optimization} \hl{\emph{arXiv}} {\bf 2015}, \hl{arXiv.1412.6980.}
-%\newblock \hlok{p.~15.} %MDPI: Should it be kept?. Removed
+\newblock {Adam: A method for stochastic optimization}. {\emph{arXiv}} {\bf 2015}, {arXiv:1412.6980.}
+%\newblock {p.~15.} 
 \newblock {\url{https://doi.org/10.48550/arXiv.1412.6980}}.
@@
 by Means of the Safe Version of Newton–Raphson Method}.
-\newblock {\em Steel Res. Int.} {\bf 2022}.
-\newblock {\url{https://doi.org/10.1002/srin.202200443}}.
+\newblock {\em Steel Res. Int.} {\bf 2022}, \emph{94}, 2200443. [\href{http://dx.doi.org/10.1002/srin.202200443}{CrossRef}]
 
@@
 flow behavior of a low alloy steel}.
-\newblock {\em Comput. Mater. Sci.} {\bf 2008}, {\em 43},~752--758.
-\newblock {\url{https://doi.org/10.1016/j.commatsci.2008.01.039}}.
+\newblock {\em Comput. Mater. Sci.} {\bf 2008}, {\em 43},~752--758. [\href{http://dx.doi.org/10.1016/j.commatsci.2008.01.039}{CrossRef}]
 
